### 2010-11-26 tutorials/grass_landsat_ETa/article_GIPE.tex
First draft of evapotranspiration mapping with Landsat 5TM in GRASS7
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44427 15284696-431f-4ddb-bdfa-cd5b030d7da7

% Template GRASS newsletter - Article
% Language: Latex
%

% Head

\title{Evapotranspiration mapping with Landsat 5TM in GRASS GIS}
\subtitle{Manual}
\author{Pakparvar M. and GRASS Development Team}

\maketitle

\section{Introduction}

This manual aims at explaining step-by-step how to prepare and process Landsat 5 TM imagery data after downloading it from GLOVIS (http://glovis.usgs.gov/) for a location in Iran, where a water harvesting project is being set up. The WRS-2 path=162 and row=040. The site is located south-central East border of the image, within an irrigation system. Fig.~\ref{fig:gipe000}\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe000.png}
   %caption of the figure
   \caption{Study Area in p162r040 of Landsat 5TM}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe000}
\end{figure}

\section{Downloading the image}
Scenes from the Landsat archive are available at no charge, processed to Standard Terrain Correction (Level 1T). While some scenes do not have the ground-control or elevation data necessary to perform L1T correction, the best level of correction is applied. More details at Landsat Product Information.\newline

The USGS Global Visualization Viewer is a quick and easy online search and order tool for selected satellite and aerial data. When the USGS Global Visualization Viewer is open, the Global View is seen.\newline

There is option to add the known latitude and longitude or select the desired region by curser tool.\newline

A new windows is appeared to search and request the imagery. This stage needs to install the last version of Java program and needs to permit the pop up to run by the windows firewall.
In new window go to Collection > Landsat Archive > to have access to updated landsat images or Collection > Landsat Legacy Collections for old images.\newline

After clicking on desired  category of  images it is possible to see the scenes on the screen. There are options in bottom left to determine the year and month of interest or pushing on "next scene" , "previous scene". In case of availability of desired scene for downloading, a red alarm is appeared top of screen mentioning "Downloadable".  Click on Add button to add the image in request list.\newline

In case of the image to be downloadable push the Download button otherwise the Submit button.\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe001.png}
   %caption of the figure
   \caption{Glovis Main Page}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe001}
\end{figure}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{gipe002.png}
   %caption of the figure
   \caption{Search within Glovis}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe002}
\end{figure}

For submitting the request it is needed to register to the USGS site. After a while a massage will be sent to the email of subscriber giving a link to give access for downloading the image.\newline

There is an easier way to request the images of successive time series. The USGS website has prepared a new envaironment of searching tool for the image requaest is called earth explorer. The link (http://edcsns17.cr.usgs.gov/NewEarthExplorer) give the access to the search window that looks like the google earth. There are 4 label at the top to determine the the images. In Search criteria, start and end date of the time series, exact lat. Long. and/or name of the location can be determined. In Data set it is possible to select the type of image. In Additional criteria there are options to  start and end path and row of the interest and some other criteria. In Result label, all of the scenes of interest will be shown, downloaded or requested. Subscription to the Earth Explorer is also needed for the request. There is  a limitation of 100 scenes per subscriber.\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.3]{gipe003.png}
   %caption of the figure
   \caption{Search Criteria within Glovis}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe003}
\end{figure}

In case of downloadable, a green downward arrow is appeared on the resulted sample image otherwise the sign of add to shop (like the shopping cart) is seen and has to be pushed changing it to green color.\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.5]{gipe004.png}
   %caption of the figure
   \caption{Shopping Cart Items}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe004}
\end{figure}

In case of submit and request a new menu is shown and needs a name for this request and some other criteria such as start and end time for the request. This timing is duration of the request and not the acquisition  time of the images. \newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe005.png}
   %caption of the figure
   \caption{Save as Standing Request}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe005}
\end{figure}

Afterward a message will be sent to the subscriber email to give access to downloading the images.\newline

All of the images are in the Zip format and should be collected in a unique folder.\newline

While most Landsat scenes are processed as Level 1T (precision and terrain corrected), certain scenes do not have ground-control or elevation data necessary for precision or terrain correction. In these cases the best level of correction is applied (Level 1G-systematic or Level 1Gt-systematic terrain). Additionally, the majority of all archived Landsat 1-5 MSS scenes, as well as a select number of Landsat 4-5 TM scenes are processed only as Level 1G (systematic) due to processing constraints. However, improvements to production capabilities are being investigated, which will allow more scenes to be processed at a higher level with a shorter processing time. The processing level of a downloaded scene is found in the metadata (MTL.txt) or processing history (WO.txt) files which are delivered with the data band files and other ancillary data.\newline

More details can be found at \href{http://landsat.usgs.gov/products\_productinformation.php}{landsat.usgs.gov} \newline

\section{Implementation environment}
GRASS GIS (Geographic resources Analysis Support System) is an open source, Free GIS software that operates on various platforms. Therefore binaries can be downloaded and installed on Unix, Linux, MS-Windows or MAC OS X workstation.\newline

The currently last version GRASS 7.0 is downloadable at www.grass.osgeo.org. It has a windows version in which the windows users can easily work in its environment.\newline

The new modules are all incorporated in the GRASS Image Processing Environment (GIPE) folder. The modules are accessible from the following link: http://trac.osge.org/grass/browser/grass-addons/gipe .\newline

After downloading and installing the software, an specific work area should be determined for first time of opening. All of the files imported and newly generated in GRASS are located in the determined path such as "C:/GRASSDATA/Landsat5/PERMANENT". \newline

Naming of the folders is optional except for the "PERMANENT" that is GRASS default name for administrator specific working environment that is called MAPSET. Every user has a username and password and have access to their own folders which is determined by admin. \newline

Image container folder is not the same as working folder. GRASS generated files are in the binary format and can not easily read by normal windows programs. Therefore, Copy and pasting as well as the exporting of these files must perform inside the GRASS. \newline

Linux users have easier and simpler access to script writing for automation of a repeatable task for faster and (man-made) error free results. But it doesn't mean the Windows users can not use it properly.\newline

Starting the GRASS in Windows is performed by klicking on the exe file. In Linux it should be written "grass70" (70 means version 7.0) in Terminal area and push the enter key.\newline

After the first time opening of the GRASS, the following menu is appeared to select the working area. There are possibilities to make a new location for the project and new name for mapset. Renaming the older mapsets can only be done in this menu and must not perform in the other programs (such as windows explorer). Followings are some examples of naming:\newline

Main working folder for GRASS data: GRASSDATA;\newline
Name of the specific project: L5;\newline
Name of the mapset: PERMANENT.\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe006.png}
   %caption of the figure
   \caption{GRASS GIS Welcome Interface}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe006}
\end{figure}

Starting the GRASS shows three new windows:\newline
GRASS Layer management: for main data analysis;\newline
GRASS Map Display for viewing the resulted layers;\newline
CLI (Command Line Interface): for scripting.\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.3]{gipe007.png}
   %caption of the figure
   \caption{GRASS GIS Manager and Map Display}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe007}
\end{figure}

After opening the GRASS It is also possible to change the working directory. In GRASS Layer Management go to Settings/GRASS working Environment/Change Location and mapset. Then it is possible change the working area.\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe008.png}
   %caption of the figure
   \caption{Change Location and Mapset}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe008}
\end{figure}

Scripting in GRASS helps the user to do the tasks fast. Scripts are in the format of C programing language. For writing and executing a script, first the location should be checked (where we are in hard disk?). To do this:\newline
Type pwd and press Enter\newline
\begin{smallverbatim}
>pwd
>/home/GRASSDATA/L5
\end{smallverbatim}

"pwd" means Path to Working Directory and will show the path that you are in now.\newline
For changing to desired path\newline
Type cd and space Folder/Sub folder and Enter\newline 
\begin{smallverbatim}
>cd home/RSDATA/Landsat5
>/home/RSDATA/Landsaat5
\end{smallverbatim}

Scripts now work in the correct directory.\newline

\section{Preparation and import in GRASS GIS}
GLOVIS is giving access to download a Landsat 5TM dataset in the form of a tarball (.tar.gz), which is a compressed format. This format compresses the files much more than the normal zip format. Decompressing the tarball for each available image in the directory can be done by the common Windows unzipping softwares one by one.\newline\linebreak
In Linux it is possible to decompress the files by using the script mentioned in \ref{appendixA}-1.\newline
Once this is done, start GRASS GIS and create a new location from the New Location wizard, name it as the Path and Row of the images (i.e. p162r040), and use any of the landsat5.TIF images available as a reference image to get the projection system and other information from.\newline
There is a need to import and rename the images inside the GRASS with the extensions in number format because the preprocessing module "i.landsat.toar" which imports DN and convert them into either radiance or reflectance is using a base name with numbered extensions.  For instance:\newline\linebreak
Landsat 5 TM:\newline
L5162040\_04020090705\_B10.TIF => L5162040\_04020090705.1\newline
The same for the other bands till band 7.0\newline
L5162040\_04020090705\_B70.TIF => L5162040\_04020090705.7\newline\linebreak
Landsat 7 ETM+:\newline
L71161040\_04020100607\_B10.TIF => L7\_161040\_04020100607.1\newline
The same for the other bands till band 7.0 except for the bands 6.1 and 6.2\newline
L71161040\_04020100607\_B61.TIF => L7\_161040\_04020100607.61\newline
L72161040\_04020100607\_B62.TIF => L7\_161040\_04020100607.62\newline\linebreak
It is possible to do one by one in GRASS Import menu. For every band that is selected from the image container folder, an output file should be written as the new file naming system mentioned above.\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe009.png}
   %caption of the figure
   \caption{Accessing Raster Import}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe009}
\end{figure}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe010.png}
   %caption of the figure
   \caption{Raster Import Module}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe010}
\end{figure}

It is possible also to import and rename the images by using the command line. Once inside the p162r040 location, access the Command Line Interface (CLI) and "cd" to the directory where all of your newly decompressed images are located. In that directory, launch the script mentioned in \ref{appendixA}-2.\newline

Imported images are now in the working environment of the GRASS (i.e. /home/GRASSDATA/L5/PERMANENT). So, it is impossible for common programs to access to and open the imported images except after the exporting.\newline

\section{Preprocessing}
\subsection{Determination of the region}
In GRASS it is possible to set the region of interest as a pre determined part of the image(s) whereby all of the processes will be done based on the data of  this region. Unlike the other softwares, it doesn't mean a separate sub image file to be produced. This activity reduces the time and increases the speed of processing  intensely.\newline

In GRASS Layer Manager push on the "Add various raster" button and select Add RGB Mapp Layer. In new window select desired band for every Red, Green or Blue band and press OK.\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe011.png}
   %caption of the figure
   \caption{Raster RGB Display}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe011}
\end{figure}

The selected composition (is called false color composite) is shown In GRASS Map Display. Once in this window zoom to interested area by zoom tool. To determine this region as the interested part of images to be processed, push the icone "zoom options" and select set the computational region from the map. It is possible also to save specifications of the region from the map.
Selected region in Map display will be the only part of image that attends to the further processes.\newline

\subsection{Georeferencing} 
According to the GLOVIS, as mentioned before, most Landsat scenes are processed as Level 1T (precision and terrain corrected), certain scenes do not have ground-control or elevation data necessary for precision or terrain correction. In these cases the best level of correction is applied (Level 1G-systematic or Level 1Gt-systematic terrain). So there is no need to perform geometric correction for newly downloaded landsat 5 TM or landsat 7 ETM images.\newline

In case of need, it is possible to do georeferencing in the GRASS that is called rectification.  This module rectifies an image by computing a coordinate transformation for each pixel in the image based on the control points. The procedure and steps is mentioned in detail in: "r.rectify" manual that is accessible in Grass Layer Management/Imagery/Rectify Image or Raster.\newline

\subsection{Change DN to radiance and reflectance at top of atmosphere}
Radiance and reflectance are the major basic input layer in ET calculation. DN can be converted to radiance by using the Lmax and Lmin of the spectral bands that is mentioned in the met or mtl files.\newline

Lmax and Lmin are the extreme values of actual radiance is sensed by the satellite sensor for each band. QCALmax and QCALmin are the extreme values of the DNs in each band and commonly is between 0-255 or 1 -255. The radiance value for each pixel is calculated by Gain and Bios data.\newline

\begin{smallverbatim}
Gain = (Lmax - Lmin) / (QCALmax - QCALmin) 
Bias = Lmin - gain * QCALmin 
Radiance = gain * DN + bias 
\end{smallverbatim}

The top of atmosphere reflectance (toar) is calculated by dividing the actual radiance at sensor with the potential radiance (sun incoming irradiance) at the top of atmosphere, which is calculated by using the sun elevation and astronomical equations.\newline
Then, to calculate at-sensor reflectance the equations are: \newline
\begin{smallverbatim}
sun_radiance = [Esun * sin(e)] / (PI * d^2) 
reflectance = radiance / sun_radiance 
\end{smallverbatim}

where, d is the earth-sun distance in astronomical units, e is the solar elevation angle, and Esun is the mean solar exo-atmospheric irradiance in W/(m2 * µm). \newline
Once the images are all imported in GRASS, go to Imagery/satellite image tools/Landsat DN to radiance-reflectance and run the i.landsat.toar module. \newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe012.png}
   %caption of the figure
   \caption{i.landsat.toar Module}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe012}
\end{figure}

Fill in the input file name and choose a new name for output file reminding the TOAR conversion has been applied to new file.\newline

The name of input file must not be included of the extension values. Assigning the main part of the image itself let the software.\newline

By default, all of the necessary input data is read from the "*.met" file that is present in the working directory. If the "*.mtl" is present rather than "*.met", it must be mentioned in Metadata section. Check the square for "Landsat TM5 has a .mtl instead of .met file.\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe013.png}
   %caption of the figure
   \caption{i.landsat.toar Module, L5TM with MTL}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe013}
\end{figure}

The output file is the reflectance by default. In the case of need to make the output radiance, it should mention in the Settings section.  Check the square for "output at-sensor radiance for all bands".\newline
Default reflectance output is more favorite because it will speed up the atmospheric correction in next step. But in some other steps there is a need for output radiance. So it is better to produce both radiance and reflectance by twice application of i.landsat.toar with checking and unchecking the  option of the radiance output file. \newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe014.png}
   %caption of the figure
   \caption{i.landsat.toar Module, output in Radiance}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe014}
\end{figure}

\subsection{Atmospheric correction} 
Natural light emitted from the Sun is not polarized. Before it enters the Earth's atmosphere, its intensity remains mostly unchanged and unaffected by the retardation of electric and magnetic components. However after interacting with atmospheric molecules and particles, the unpolarized light may become partially polarized. The degree of polarization depends on the type of scattering event. In the actual case, the signal is perturbed by the atmosphere. Only a fraction of the photons coming from the target reaches the satellite sensor, typically 80\%  at 0.45 μm and 50\% at 0.45  μm, so that the target seems less reflecting. The missing photons have been lost through two processes: absorption and scattering. Atmospheric correction minimizes the errors arise from both two sources.\newline
Through the atmospheric correction, radiance at top of the atmosphere is converted to radiance at the earth surface.\newline
There are two main tools for Atmospheric correction inside the GRASS.\newline

\subsubsection{Dark Object Subtraction (DOS)}
Dark Object Subtraction is one of the simplified methods that is implemented in i.landsat.toar module. It assumes a value called Path-radiance to subtract from all of the pixell's radiance value. \newline

Path-radiance is computed  by subtraction of the Sun\_ radiance from the dark object radiance. So, the equations are:\newline

\begin{smallverbatim}
Surface_radiance = \
 (at-sensor_radiance - radiance_path)

Radiance_path = \
 (dark_radiance - percent* Sun_radiance)

Sun_radiance = \
 TAUv * [Esun * sin(e) * TAUz + Esky] / (PI * d^2) 
\end{smallverbatim}

Where, percent is a value between 0.0 and 1.0 (usually 0.01), Esky is the diffuse sky irradiance, TAUz is the atmospheric transmittance along the path from the sun to the ground surface, and TAUv is the atmospheric transmittance along the path from the ground surface to the sensor. radiance\_dark is the at-sensor radiance calculated from the darkest object, i.e. DN with a least 'dark\_parameter' (usually 1000) pixels for the entire image. There are four methods of DOS inside the GRASS assuming different values:\newline

\begin{smallverbatim}
DOS1: TAUv = 1.0, TAUz = 1.0 and Esky = 0.0

DOS2: TAUv = 1.0, Esky = 0.0, \
 and TAUz = sin(e) for all bands with \
 maximum wave length less than 1. \
 (i.e. bands 4-6 MSS, 1-4 TM, and 1-4 ETM+) \
 other bands TAUz = 1.0

DOS2b:

DOS3: TAUv = exp[-t/cos(sat_zenith)], \
 TAUz = exp[-t/sin(e)], Esky = rayleigh

DOS4: TAUv = exp[-t/cos(sat_zenith)], \
 TAUz = exp[-t/sin(e)], Esky = PI * radiance_dark  
\end{smallverbatim}

In case of using DOS methods while in i.landsat.toar go to Metadata section and select one of the desired DOS methods of atmospheric correction and the kind of sensor (i.e TM5) and continue  to  convert DN to radiance and reflectance. \newline

In this case, the output file is reflectance or radiance that is atmospherically corrected (by DOS method) and must not be inserted to landsat atmospheric correction module "i.atcorr". \newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe015.png}
   %caption of the figure
   \caption{i.landsat.toar Module, DOS1 model enabled}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe015}
\end{figure}

The best method of atmospheric correction by the DOS concept can be verified by doing the comparison between the check points of final ET maps (based on each DOS method) with the ground truth data.\newline

\subsubsection{The 6S atmospheric correction model}

The module i.atcorr applies the 6S method to correct the atmospheric errors which is supposed to be the most accurate but input demanding procedure.  \newline
6S (Second Simulation of a Satellite Signal in the Solar Spectrum) is an advanced radiative transfer system designed to simulate the reflection of solar radiation by a coupled atmosphere-surface system for a wide range of atmospheric, spectral and geometrical conditions. \newline

At this point, if a "Dark Object Subtraction" atmospheric correction has not been computed in "i.landsat.toar", then an atmospheric correction must be applied to the TOAR radiance/reflectance values coming from "i.landsat.toar". This is done using "i.atcorr" module. This module is a port of 6S atmospheric correction model.\newline

Atmospheric correction in GRASS can be done in Imagery/Satellite image tools/Atmospheric correction that applies the i.atcorr module.\newline

The script mentioned in \ref{appendixA}-4 can be used for automated approach of atmospheric correction for a set of  landsat images.\newline

\begin{smallverbatim}
i.atcorr -r -o -f \
 input=L5162040_04020090705.toar.1 \
 elevation=dem90 \
 parameters=/home/icwater/param_L5.txt \
 output=L5162040_04020090705atcorr.1 \
 range=0,1 rescale=0,1 --overwrite
\end{smallverbatim}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe016.png}
   %caption of the figure
   \caption{i.atcorr Module}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe016}
\end{figure}

\section{Basic products creation}

Necessary images for energy balance calculation are NDVI, Albedo, Emissivity. These initial products have dedicated GRASS GIS modules.\newline

NDVI is calculated using "i.vi", following the example below:\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe017.png}
   %caption of the figure
   \caption{i.vi Module}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe017}
\end{figure}

Albedo is caculated from the "i.albedo" module:\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe018.png}
   %caption of the figure
   \caption{i.albedo Module}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe018}
\end{figure}

Emissivity is computed using the generic module "i.emissivity":\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe019.png}
   %caption of the figure
   \caption{i.emissivity Module}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe019}
\end{figure}

\section{Energy balance terms}

Net radiation at satellite overpass (instantaneous) and integrated over the day (think sunshine hours) are computed from a generic GRASS GIS raster module "r.sun".\newline

In mode 1, instantaneous net radiation is computed, in mode 2 the day integrated net radiation is computed. Both are necessary for the energy balance computation. Mode 1 for sensible heat flux computation and mode 2 for the Day ET potential.\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe020.png}
   %caption of the figure
   \caption{r.sun Module}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe020}
\end{figure}

Note that the following raster inputs are recommended: aspect, slope, albedo, latitude and longitude.\newline

Slope and Aspect can be computed with "r.slope.aspect", albedo with "i.albedo", latitude and longitude with "i.latlong".\newline

Soil heat flux can be computed with "i.eb.g0".\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe021.png}
   %caption of the figure
   \caption{i.eb.soilheatflux Module}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe021}
\end{figure}

Note that some additional input should be created, including a ".time" raster.\newline

Sensible heat flux can be calculated with "i.eb.h\_SEBAL01".\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe022.png}
   %caption of the figure
   \caption{i.eb.h\_SEBAL01 Module}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe022}
\end{figure}

Note that additional images should be created about surface roughness length (z0m), altitude corrected temperature (t0dem), the height independent wind speed (U*), along with coordinates of the "wet" and "dry" pixels (SEBAL method is geographically dependent on extrema energy balance points). \newline

Evaporative fraction can be calculated by "i.eb.evapfr":\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe023.png}
   %caption of the figure
   \caption{i.eb.evapfr Module}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe023}
\end{figure}

Evapotranspiration can be computed from "i.eb.eta":\newline

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{gipe024.png}
   %caption of the figure
   \caption{i.eb.eta Module}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:gipe024}
\end{figure}

\newpage

\section{Appendix A: GRASS SCRIPTS}
\label{appendixA}

\subsection{Unzipping the tarball compressed files}

For Linux users in Terminal and for Windows users in Dos prompt window should be written:\newline

\begin{smallverbatim}
for file in *.tar.gz
do
tar -xvzf \$file
done
\end{smallverbatim}

Control should be given to run the script in the same directory as the images are in.\newline

\subsection{Renaming and importing}
In GRASS Command Line Interface (CLI) write the script:

\begin{smallverbatim}
echo "RUN from the MTL.txt directory and within the GRASS environment"

for file in L5*0.TIF
do
	out=\$(echo \$file | sed 's/\\(.*\)\_\\(.*\)\_B\\(.*\)0.TIF/\1\\_\2\.\3/g')
	echo \$out
	r.in.gdal input=\$file output=\$out
done
\end{smallverbatim}

For more information about this script, refer to "sed" program manual in Unix/Linux and to the "r.in.gdal" help in GRASS GIS.

\subsection{Conversion of DN to radiance}
Conversion of DN to reflectance at top of atmosphere (TOAR) is done with the script:

\begin{smallverbatim}
echo "RUN from the MTL.txt directory and within \
 the GRASS environment"

path=162
row=040

for L5_MTL_file in L5\$path\$row*_MTL.txt
do
	L5_prefix=\$(echo \$L5_MTL_file \| \
	  sed 's/\\(.*\)_MTL.txt/\\1/')

	i.landsat.toar -t \
	  input_prefix=\$L5_prefix\. \
	  output_prefix=\$L5_prefix.toar.  \
	  metfile=/home/user1/\$L5\_MTL\_file \
	  sensor=tm5
done
\end{smallverbatim}

This script requires to change the path and row of the target images you are processing.\newline

\subsection{Atmospheric correction with i.atcorr}
Script for atmospheric correction by 6S method for landsat 5 TM.\newline

\begin{smallverbatim}
#!/bin/bash
# Basic script for i.atcorr for L 5 TM

#Geometrical conditions (L5TM)
geom=7
#Sensor height (satellite is -1000)
sens_height=-1000

#Here we suppose you have altitude (DEM) and \
 Visibility (VIS) maps ready
#--------------------------------------------- 
#Visibility dummy value (overwritten by VIS \
 raster input)
vis=9
r.mapcalc expression="visibility=\$vis" \
 --overwrite

#Altitude dummy value (in Km should be negative\
 in this param file)
#(overwritten by DEM raster input)
alt=-1.200

#---------------------------
# Please change as you need
#---------------------------
# L5 basename as stored in GRASS GIS and used \
 by i.landsat.toar
L5basename=L5162040\_04020090705

# Location of parameter file
root=/home/icwater/

#datetime of satellite overpass (month, day, \
 GMT decimal hour)
mdh="7 5 6.30"

# Central Lat/Long
Long=51.410
Lat=24.234

#Atmospheric mode
atm\_mode=6 #us standard 62 (for lack of more\
 precise model)

#Aerosol model
aerosol\_mode=1 #continental

#satellite band number (L5TM [25,26,27,28,29,30])
satbandno=25 #Band 1 of L5TM is first to undergo\
 atmospheric correction

for bandno in 1 2 3 4 5 7
do # Generate the parameterization file
	echo "\$geom                            \
         - geometrical conditions=Landsat 5 TM" \
         > \$root/param\_L5.txt
	echo "\$mdh \$Long \$Lat   \
         - month day hh.ddd longitude latitude \
         ("hh.ddd" is in decimal hours GMT)" >>\
         \$root/param\_L5.txt
	echo "\$atm\_mode                       \
         - atmospheric mode=tropical" >> \
         \$root/param\_L5.txt
	echo "\$aerosol\_mode                   \
         - aerosols model=continental" >>\
         \$root/param\_L5.txt
	echo "\$vis                           \
         - visibility [km] (aerosol model \
         concentration), not used as there is \
         raster input" >> \$root/param\_L5.txt
	echo "\$alt                       \
         - mean target elevation above sea level\
         [km] (here 600m asl), not used as there \
         is raster input" >> \$root/param\_L5.txt
	echo "\$sens\_height                     \
         - sensor height (here, sensor on board a\
         satellite)" >> \$root/param\_L5.txt
	echo "\$satbandno                        \
         - 'i'th band of TM Landsat 5" >>\
         \$root/param\_L5.txt
	# Process band-wise atmospheric correction with 6s
	i.atcorr -r -o -f \
         input=\$L5basename.toar.\$bandno\
         elevation=dem90 visibility=vis \
         parameters=\$root/param\_L5.txt \
         output=\$L5basename.surf.\$bandno \
         range=0,1 rescale=0,1 --overwrite
	# Increment satellite band number 
	satbandno=\$((satbandno+1))
done  
\end{smallverbatim}

\address{GRASS Development Team\\
  \url{http://grass.osgeo.org}\\
  \email{tmitchell@osgeo.org}}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: main\_document.tex
%%% End:

### 2010-11-30 tutorials/grass_landsat_ETa/article_GIPE.tex
Update Grass7 Landsat manual
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44499 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-This manual aims at explaining step-by-step how to prepare and process Landsat 5 TM imagery data after downloading it from GLOVIS (http://glovis.usgs.gov/) for a location in Iran, where a water harvesting project is being set up.
-The WRS-2 path=162 and row=040.
-The site is located south-central East border of the image, within an irrigation system.
+This manual aims at explaining step-by-step how to prepare and process Landsat 5 TM imagery data after downloading it from GLOVIS (http://glovis.usgs.gov) The location of study area is a water harvesting (floodwater spreading) project is being set up in South central Iran (Kowsar research station, Gareh Bygone, fars Province).
+Time series of Et maps is needed for integration and calculation the hydrologic balance.
+The WRS-2 path=164 and row=040.
+The site is located south-central East border of the image.
 Fig.~\ref{fig:gipe000}\newline
@@
 While some scenes do not have the ground-control or elevation data necessary to perform L1T correction, the best level of correction is applied.
-More details at Landsat Product Information.\newline
+More details at \href{http://landsat.usgs.gov/products_productinformation.php}{Landsat Product Information}.\newline
 
-The USGS Global Visualization Viewer is a quick and easy online search and order tool for selected satellite and aerial data.
+The \href{http://glovis.usgs.gov/BrowseBrowser.shtml}{USGS Global Visualization Viewer} is a quick and easy online search and order tool for selected satellite and aerial data.
 When the USGS Global Visualization Viewer is open, the Global View is seen.\newline
 
-There is option to add the known latitude and longitude or select the desired region by curser tool.\newline
+There is option to add the known latitude and longitude or select the desired region by cursor tool.\newline
 
@@
 
-After clicking on desired  category of  images it is possible to see the scenes on the screen.
-There are options in bottom left to determine the year and month of interest or pushing on "next scene" , "previous scene".
+After klicking on desired  category of  images it is possible to see the scenes on the screen.
+There are options in bottom left to determine the year and month of interest or pushing on "nest scene" , "previous scene".
 In case of availability of desired scene for downloading, a red alarm is appeared top of screen mentioning "Downloadable".
-Click on Add button to add the image in request list.\newline
+Klick on Add button to add the image in request list.\newline
 
@@
 The USGS website has prepared a new envaironment of searching tool for the image requaest is called earth explorer.
-The link (http://edcsns17.cr.usgs.gov/NewEarthExplorer) give the access to the search window that looks like the google earth.
+The link \href{http://edcsns17.cr.usgs.gov/NewEarthExplorer}{NewEarthExplorer} gives the access to the search window that looks like the google earth.
 There are 4 label at the top to determine the the images.
@@
 The new modules are all incorporated in the GRASS Image Processing Environment (GIPE) folder.
-The modules are accessible from the following link: http://trac.osge.org/grass/browser/grass-addons/gipe .\newline
+The modules are accessible from the \href{http://trac.osgeo.org/grass/browser/grass-addons/gipe}{trac.osgeo.org} website.\newline
 
@@
 
-The module i.atcorr applies the 6S method to correct the atmospheric errors which is supposed to be the most accurate but input demanding procedure.  \newline
-6S (Second Simulation of a Satellite Signal in the Solar Spectrum) is an advanced radiative transfer system designed to simulate the reflection of solar radiation by a coupled atmosphere-surface system for a wide range of atmospheric, spectral and geometrical conditions.
-\newline
-
+The module i.atcorr applies the 6S method to correct the atmospheric errors which is supposed to be the most accurate but input demanding procedure.\newline
+6S (Second Simulation of a Satellite Signal in the Solar Spectrum) is an advanced radiative transfer system designed to simulate the reflection of solar radiation by a coupled atmosphere-surface system for a wide range of atmospheric, spectral and geometrical conditions.\newline
 At this point, if a "Dark Object Subtraction" atmospheric correction has not been computed in "i.landsat.toar", then an atmospheric correction must be applied to the TOAR radiance/reflectance values coming from "i.landsat.toar".
 This is done using "i.atcorr" module.
-This module is a port of 6S atmospheric correction model.\newline
+This module is a port of 6S atmospheric correction model.
+Atmospheric correction in GRASS can be done in Imageray/Satellite image tools/Atmospheric correction that applies the i.atcorr module.\newline
+Parameterization of the i.atcorr is being done inside a text file including the below information (called parameter file).\newline
 
-Atmospheric correction in GRASS can be done in Imagery/Satellite image tools/Atmospheric correction that applies the i.atcorr module.\newline
+7                        - geometrical conditions=Landsat 5 TM\newline
+7 5 6.30 51.410 24.234   - month day hh.ddd longitude latitude ("hh.ddd" is in decimal hours GMT)\newline
+6                        - atmospheric mode=us standard 62\newline
+1                        - aerosols model=continental\newline
+9                        - visibility [km] (aerosol model concentration), not used as there is raster input\newline
+-1.200                   - mean target elevation above sea level [km] (here 1200m asl), not used as there is raster input\newline
+-1000                    - sensor height (here, sensor on board a satellite)\newline
+30                       - 'i'th band of TM Landsat 5\newline
 
-The script mentioned in \ref{appendixA}-4 can be used for automated approach of atmospheric correction for a set of  landsat images.\newline
+The figures at the left side are the parameters and the texts in the right side are the defenitions.
+The text file must be prepared before and browse inside the i.atcorr.
+The needed information are mentioned in the manual of i.atcorr.
+Some explanations are as follow.\newline
 
-\begin{smallverbatim}
-i.atcorr -r -o -f \
- input=L5162040_04020090705.toar.1 \
- elevation=dem90 \
- parameters=/home/icwater/param_L5.txt \
- output=L5162040_04020090705atcorr.1 \
- range=0,1 rescale=0,1 --overwrite
-\end{smallverbatim}
+Line 1 is included of geometric conditions and the correct number can be found in the section A of i.atcorr manual. For landsat 5 tm the number is 7.\newline
+Line 2 is mentioning the specifications of the image that is mentioned in mtl file.
+Latitude and longitudes are the geographic location of the center of region.
+If the position is not available in longitude-latitude (WGS84), the m.proj conversion module can be used to reproject from a different projection.
+It also can be accessed in  GRASS/Raster/Develop raster map/Reproject  raster map.\newline
+After reprojection the location of the center of the region can be determined by g.region module.\newline
+In line 3 the atmospheric model must be entered.
+The possible models are being mentioned in i.atcorr manual section B.
+In case of access to the radio sound weather data of the region, it is possible to include the user owned data.
+In this case it should be mentioned 7 (for user defined model) instead of 6 (us standard 62).
+Then write the requested weather parameters.\newline
+In line 4 the aerosole model is requested. The desired model should be found in section C of the i.atcorr. It is again possible to enter the user's model.\newline
+Line 5 is the value of visibility.
+The estimation is found in weather data.
+If you an estimate of aerosol optical depth is accessible, enter v=0 for the visibility and enter the aerosol optical depth at 550nm (iaer means 'i' for input and 'aer' for aerosol).\newline
+In line 6  the the elevation of the target pixel is described.
+It expresses the altitude of the target (e.g., mean elevation) in [km], given as negative value.
+If there is a DEM file input the line 7 is not used.
+In Line 7 the sensor height is described. The figure -1000 means that the sensor is on board a satellite.
+Line 8 is mentioning the sensor band. It is determined in he section F of the i.atcorr manual.\newline
+
+Once inside the i.atcorr, type a name for the input file.
+This file must be the reflectance at top of atmosphere file (generated in i.landsat.toar).
+Every band needs its own parameter text file to be browsed or directly enter the parameters values in the text box.\newline
 
@@
 
-\section{Basic products creation}
-
-Necessary images for energy balance calculation are NDVI, Albedo, Emissivity. These initial products have dedicated GRASS GIS modules.\newline
-
-NDVI is calculated using "i.vi", following the example below:\newline
+For selection the DEM and visibility bands as input, while inside the i.atcorr go to input label and select the desired files.
+Visibility map has no more extra benefit when the value of visibility is written in parameter file.
+But DEM file can help to get better results of i.atcorr.\newline
+Unlike the i.landsat.toar, the i.atcorr must be applied for every band individually for every given image.\newline
 
@@
    %caption of the figure
-   \caption{i.vi Module}
+   \caption{i.atcorr Module Input Tab}
    %label of the figure, which has to correspond to \ref{}:
@@
 
-Albedo is caculated from the "i.albedo" module:\newline
+The script mentioned in \ref{appendixA}-4 can be used for automated approach of atmospheric correction for a set of  landsat images.\newline
+
+The produced maps are reflectance at the surface for each band. The values range is between 0 and 1 showing the ratio of outgoing radiance to the incoming radiance at Earth Skin Surface.  
+In order to test the reality of the generated values look to the NDVI values that can be produced by the red and near infrared band through map r.mapcalc module.
+The values related to green vegetation  area must be the highest.
+
+\section{Basic products creation}
+
+Necessary images for energy balance calculation are NDVI, Albedo, Emissivity. These initial products have dedicated GRASS GIS modules.\newline
+
+\subsection{NDVI production}
+Vegetion index NDVI is a necessary basic product for some other higher level outputs such as Soil heat flux, Surface roughness (Z0m).
+It can be  calculated using "i.vi".
+Go to Imagery/Evapotranspiration calculation/vegetation indices, following the example below:\newline
 
@@
    %caption of the figure
-   \caption{i.albedo Module}
+   \caption{i.vi Module}
    %label of the figure, which has to correspond to \ref{}:
@@
 
-Emissivity is computed using the generic module "i.emissivity":\newline
+There are 13 vegetation indices (VI) possibility in i.vi module.
+After selecting the desired name of red band, enter the name of VI (such as NDVI, EVI, DVI,...).
+Then go to Optional label and select the near infrared band for NDVI and the other bands is needed in case of the other VIs.
+\newline
 
@@
    %caption of the figure
-   \caption{i.emissivity Module}
+   \caption{i.vi Module}
    %label of the figure, which has to correspond to \ref{}:
@@
 
-\section{Energy balance terms}
-
-Net radiation at satellite overpass (instantaneous) and integrated over the day (think sunshine hours) are computed from a generic GRASS GIS raster module "r.sun".\newline
-
-In mode 1, instantaneous net radiation is computed, in mode 2 the day integrated net radiation is computed.
-Both are necessary for the energy balance computation.
-Mode 1 for sensible heat flux computation and mode 2 for the Day ET potential.\newline
+\subsection{Albedo production}
+Albedo is shortwave surface reflectance in range of 0.3 to 3.0 micro meters (figures are dimensionless).\newline 
+Albedo is in fact an integration of the surface reflectance of all of the shortwave bands assuming a fraction for every band.
+The fractions for the bands are published by the landsat website and are as follow.
+\begin{smallverbatim}
+ Albedo = (0.293 * channel1 + 0.274 * channel2 \
+        + 0.233 * channel3 + 0.156 * channel4 + \
+        0.033 * channel5 + 0.011 * channel7)
+\end{smallverbatim}
+Albedo is calculated from the "i.albedo" module. It  computes broad band albedo from surface reflectance. This is an precursor to Soil heat flux, r.sun and Energy-Balance processing.\newline
+Inside the GRASS windows, go to Imagery/Evapotranspiration calculation/Albedo, and select the the bands 1 to 5 and 7 of atmospherically corrected surface reflectance.\newline
 
@@
    %caption of the figure
-   \caption{r.sun Module}
+   \caption{i.albedo Module}
    %label of the figure, which has to correspond to \ref{}:
@@
 
-Note that the following raster inputs are recommended: aspect, slope, albedo, latitude and longitude.\newline
-
-Slope and Aspect can be computed with "r.slope.aspect", albedo with "i.albedo", latitude and longitude with "i.latlong".\newline
-
-Soil heat flux can be computed with "i.eb.g0".\newline
+\subsection{Emissivity Production}
+Surface emisivity is the ratio of the thermal energy radiated by the surface to the thermal energy  radiated by black body at the same temprature (is dimensionless).\newline 
+The module r.emissivity calculates the emissivity in the longwave radiation spectrum, according to the semi-empirical equation related to NDVI by Caselles et al.
+(1997), valid in the NDVI range of 0.16 to 0.74.
+Estimation in the 8-14 micrometers range for sparse canopy.\newline
 
@@
    %caption of the figure
+   \caption{i.emissivity Module}
+   %label of the figure, which has to correspond to \ref{}:
+   \label{fig:gipe021}
+\end{figure}
+
+\section{Energy balance terms}
+
+Net radiation at satellite overpass (instantaneous) and integrated over the day are computed from a generic GRASS GIS raster module "r.sun".
+In mode 1, instantaneous net radiation is computed, in mode 2 the day integrated net radiation is computed.
+Both are necessary for the energy balance computation.
+Mode 1 for sensible heat flux computation and mode 2 for the Day ET potential.\newline
+
+Note that the following raster inputs are recommended: aspect, slope, albedo, latitude and longitude.
+Slope and Aspect can be computed with "r.slope.aspect" using the DEM raster file, albedo with "i.albedo", latitude and longitude with "i.latlong".\newline
+
+To run the r.sun while inside the GRASS go to Raster/Solar radiance and shadows/solar irradiance and irradiation.
+Input the name of DEM raster file and the Julian day of the year (image acquisition day).\newline
+
+%\setkeys{Gin}{width=1\textwidth}
+\begin{figure}[htbp]
+   \centering
+   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
+   \includegraphics[scale=0.4]{gipe022.png}
+   %caption of the figure
+   \caption{r.sun Module}
+   %label of the figure, which has to correspond to \ref{}:
+   \label{fig:gipe022}
+\end{figure}
+
+To determine the other input file go to the input\_options label and input the slop, aspect, albedo, langitude and latitude files.
+The Linke atmospheric turbidity should be found for the region of study.
+The default is 3.0.\newline
+
+%\setkeys{Gin}{width=1\textwidth}
+\begin{figure}[htbp]
+   \centering
+   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
+   \includegraphics[scale=0.4]{gipe023.png}
+   %caption of the figure
+   \caption{r.sun Module}
+   %label of the figure, which has to correspond to \ref{}:
+   \label{fig:gipe023}
+\end{figure}
+
+%\setkeys{Gin}{width=1\textwidth}
+\begin{figure}[htbp]
+   \centering
+   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
+   \includegraphics[scale=0.4]{gipe024.png}
+   %caption of the figure
+   \caption{r.sun Module}
+   %label of the figure, which has to correspond to \ref{}:
+   \label{fig:gipe024}
+\end{figure}
+
+In Optional label, push to the "Incorporate the shadowing effect of the terrain" and local (not GMT) time  of image acquisition.\newline
+In Out\_option label write the name of desired output names.
+It is possible only to generate the output files for one of the Modes 1 and 2 in the same time.
+So, add the desired names for 1,2,4,5 and 6 rows.
+Global or total irradiance output file is a product of the three base outputs Beam irradiance, Diffuse irradiance and reflected irradiance.\newline
+
+%\setkeys{Gin}{width=1\textwidth}
+\begin{figure}[htbp]
+   \centering
+   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
+   \includegraphics[scale=0.4]{gipe025.png}
+   %caption of the figure
+   \caption{r.sun Module}
+   %label of the figure, which has to correspond to \ref{}:
+   \label{fig:gipe025}
+\end{figure}
+
+To generate the output insolation time for Mode 2, the r.sun must be run again. And put all of the input files. In Output\_options the only output file in row 3 should be written.\newline
+
+r.sun -s --overwrite elevin=dem90 aspin=\_aspect slopein=\_slop albedo=L5162040\_04020090518.1Albedo latin=latitude longin=Longitude incidout=L5162040\_4020090518.2InAnMod1 beam\_rad=L5162040\_4020090518.2BeIr insol\_time=L5162040\_04020090518.2InTiMod2 diff\_rad=L5162040\_04020090518.2DiIrMod1 refl\_rad=L5162040\_04020090518.2GReIrMod1 glob\_rad=L5162040\_04020090518.2TIrMod1 day=138 time=10\newline
+
+\subsection{soil heat flux production}
+Soil heat flux can be computed with "i.eb.g0".\newline
+
+%\setkeys{Gin}{width=1\textwidth}
+\begin{figure}[htbp]
+   \centering
+   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
+   \includegraphics[scale=0.4]{gipe026.png}
+   %caption of the figure
    \caption{i.eb.soilheatflux Module}
    %label of the figure, which has to correspond to \ref{}:
-   \label{fig:gipe021}
+   \label{fig:gipe026}
 \end{figure}
@@
    %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
-   \includegraphics[scale=0.4]{gipe022.png}
+   \includegraphics[scale=0.4]{gipe027.png}
    %caption of the figure
@@
    %label of the figure, which has to correspond to \ref{}:
-   \label{fig:gipe022}
+   \label{fig:gipe027}
 \end{figure}
@@
    %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
-   \includegraphics[scale=0.4]{gipe023.png}
+   \includegraphics[scale=0.4]{gipe028.png}
    %caption of the figure
@@
    %label of the figure, which has to correspond to \ref{}:
-   \label{fig:gipe023}
+   \label{fig:gipe028}
 \end{figure}
@@
    %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
-   \includegraphics[scale=0.4]{gipe024.png}
+   \includegraphics[scale=0.4]{gipe029.png}
    %caption of the figure
@@
    %label of the figure, which has to correspond to \ref{}:
-   \label{fig:gipe024}
+   \label{fig:gipe029}
 \end{figure}
@@
 \begin{smallverbatim}
-echo "RUN from the MTL.txt directory and within the GRASS environment"
+echo "RUN from the MTL.txt directory and \
+ within the GRASS environment"
 
@@
 do
-	out=\$(echo \$file | sed 's/\\(.*\)\_\\(.*\)\_B\\(.*\)0.TIF/\1\\_\2\.\3/g')
+	out=\$(echo \$file | sed 's/\\(.*\) 
+        \_\\(.*\)\_B\\(.*\)0.TIF/\1\\_\2\.\3/g')
 	echo \$out

### 2010-12-03 tutorials/grass_landsat_ETa/article_GIPE.tex
Fit more text in the columns
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44533 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 Landsat 5 TM:\newline
-L5162040\_04020090705\_B10.TIF => L5162040\_04020090705.1\newline
+L5162040\_04020090705\_B10.TIF \newline
+=> L5162040\_04020090705.1\newline
 The same for the other bands till band 7.0\newline
-L5162040\_04020090705\_B70.TIF => L5162040\_04020090705.7\newline\linebreak
+L5162040\_04020090705\_B70.TIF \newline
+=> L5162040\_04020090705.7\newline\linebreak
 Landsat 7 ETM+:\newline
-L71161040\_04020100607\_B10.TIF => L7\_161040\_04020100607.1\newline
+L71161040\_04020100607\_B10.TIF \newline
+=> L7\_161040\_04020100607.1\newline
 The same for the other bands till band 7.0 except for the bands 6.1 and 6.2\newline
-L71161040\_04020100607\_B61.TIF => L7\_161040\_04020100607.61\newline
-L72161040\_04020100607\_B62.TIF => L7\_161040\_04020100607.62\newline\linebreak
+L71161040\_04020100607\_B61.TIF \newline
+=> L7\_161040\_04020100607.61\newline
+L72161040\_04020100607\_B62.TIF \newline
+=> L7\_161040\_04020100607.62\newline\linebreak
 It is possible to do one by one in GRASS Import menu.
@@
 Atmospheric correction in GRASS can be done in Imageray/Satellite image tools/Atmospheric correction that applies the i.atcorr module.\newline
-Parameterization of the i.atcorr is being done inside a text file including the below information (called parameter file).\newline
-
+Parameterization of the i.atcorr is being done inside a text file including the below information (called parameter file).\newline\linebreak 
 7                        - geometrical conditions=Landsat 5 TM\newline
@@
 
-To generate the output insolation time for Mode 2, the r.sun must be run again. And put all of the input files. In Output\_options the only output file in row 3 should be written.\newline
-
-r.sun -s --overwrite elevin=dem90 aspin=\_aspect slopein=\_slop albedo=L5162040\_04020090518.1Albedo latin=latitude longin=Longitude incidout=L5162040\_4020090518.2InAnMod1 beam\_rad=L5162040\_4020090518.2BeIr insol\_time=L5162040\_04020090518.2InTiMod2 diff\_rad=L5162040\_04020090518.2DiIrMod1 refl\_rad=L5162040\_04020090518.2GReIrMod1 glob\_rad=L5162040\_04020090518.2TIrMod1 day=138 time=10\newline
-
+To generate the output insolation time for Mode 2, the r.sun must be run again. And put all of the input files. In Output\_options the only output file in row 3 should be written.\newline\linebreak
+r.sun -s --overwrite elevin=dem90\newline
+aspin=\_aspect slopein=\_slop\newline
+albedo=L5162040\_04020090518.1Albedo\newline
+latin=latitude longin=Longitude\newline
+incidout=L5162040\_4020090518.2InAnMod1\newline
+beam\_rad=L5162040\_4020090518.2BeIr\newline
+insol\_time=L5162040\_04020090518.2InTiMod2\newline
+diff\_rad=L5162040\_04020090518.2DiIrMod1\newline
+refl\_rad=L5162040\_04020090518.2GReIrMod1\newline
+glob\_rad=L5162040\_04020090518.2TIrMod1\newline
+day=138 time=10
 \subsection{soil heat flux production}

### 2010-12-10 tutorials/grass_landsat_ETa/article_GIPE.tex
Upgraded r.sun section
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44577 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \maketitle
-
 \section{Introduction}
@@
 Surface emisivity is the ratio of the thermal energy radiated by the surface to the thermal energy  radiated by black body at the same temprature (is dimensionless).\newline 
-The module r.emissivity calculates the emissivity in the longwave radiation spectrum, according to the semi-empirical equation related to NDVI by Caselles et al.
+The module i.emissivity calculates the emissivity in the longwave radiation spectrum, according to the semi-empirical equation related to NDVI by Caselles et al.
 (1997), valid in the NDVI range of 0.16 to 0.74.
@@
 \section{Energy balance terms}
+\subsection{Net Radiation}
+Net radiation at satellite overpass (instantaneous) and integrated over the day are computed from a generic GRASS GIS raster module "r.sun". 
+The r.sun program works in two modes.
+In the first mode it calculates for the image acquisition local time a solar incidence angle [degrees] and solar irradiance values [W.m-2].
+In the second mode daily sums of solar radiation [Wh.m-2.day-1] are computed within a day.\newline
 
-Net radiation at satellite overpass (instantaneous) and integrated over the day are computed from a generic GRASS GIS raster module "r.sun".
-In mode 1, instantaneous net radiation is computed, in mode 2 the day integrated net radiation is computed.
+In the other hand, in mode 1, instantaneous net radiation, and in mode 2 the day integrated net radiation is computed.
 Both are necessary for the energy balance computation.
 Mode 1 for sensible heat flux computation and mode 2 for the Day ET potential.\newline
+
+The model computes all three components of total radiation (beam, diffused and reflected) for the clear sky conditions, i.e.
+not taking into consideration the spatial and temporal variation of clouds.
+\newline
 
@@
 
-To run the r.sun while inside the GRASS go to Raster/Solar radiance and shadows/solar irradiance and irradiation.
-Input the name of DEM raster file and the Julian day of the year (image acquisition day).\newline
+Run r.sun while inside the GRASS: go to Raster/Solar radiance and shadows/solar irradiance and irradiation.
+Input the name of DEM raster file and the Julian day of the year (image acquisition day).
+\newline
 
@@
 
-To determine the other input file go to the input\_options label and input the slop, aspect, albedo, langitude and latitude files.
-The Linke atmospheric turbidity should be found for the region of study.
-The default is 3.0.\newline
+To determine the other input file go to the input\_options label and input the slop, aspect, albedo, longitude and latitude files.
+The Linke atmospheric turbidity should be found in reference literature for the study area.
+The default is 3.0.
+Average monthly values of the Linke turbidity coefficient for a mild climate in the northern hemisphere is presented in \href{tab:001}.\newline
 
@@
 \end{figure}
+
+\begin{center}
+\begin{tabular}{lllll}
+Landscapes & Mountains & Rural & City & Industrial\\
+January & 1.5 & 2.1 & 3.1 & 4.1\\
+February & 1.6 & 2.2 & 3.2 & 4.3\\
+March & 1.8 & 2.5 & 3.5 & 4.7\\
+April & 1.9 & 2.9 & 4 & 5.3\\
+May & 2 & 3.2 & 4.2 & 5.5\\
+June & 2.3 & 3.4 & 4.3 & 5.7\\
+July & 2.3 & 3.5 & 4.4 & 5.8\\
+August & 2.3 & 3.3 & 4.3 & 5.7\\
+September & 2.1 & 2.9 & 4 & 5.3\\
+October & 1.8 & 2.6 & 3.6 & 4.9\\
+November & 1.6 & 2.3 & 3.3 & 4.5\\
+December & 1.5 & 2.2 & 3.1 & 4.2\\
+Annual & 1.9 & 2.75 & 3.75 & 5
+\end{tabular}
+\linebreak
+Table 1: Linke Turbidity Coefficient
+\end{center}
 
@@
 Global or total irradiance output file is a product of the three base outputs Beam irradiance, Diffuse irradiance and reflected irradiance.\newline
+To generate the output files for Mode 2, the r.sun must be run again and put all of the input files.
+In Output\_options the output files related to mode 2 or mod 1 and 2 must be filled (boxes 2 to 6) and the box 1 must be kept empty.
+In Optional label delete the local time which was mentioned for Mode 1 outputs in before.\newline
 
@@
    %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
-   \includegraphics[scale=0.4]{gipe025.png}
+   \includegraphics[scale=0.3]{gipe025.png}
    %caption of the figure
-   \caption{r.sun Module}
+   \caption{r.sun Mode 1}
    %label of the figure, which has to correspond to \ref{}:
@@
 
-To generate the output insolation time for Mode 2, the r.sun must be run again. And put all of the input files. In Output\_options the only output file in row 3 should be written.\newline\linebreak
-r.sun -s --overwrite elevin=dem90\newline
-aspin=\_aspect slopein=\_slop\newline
-albedo=L5162040\_04020090518.1Albedo\newline
-latin=latitude longin=Longitude\newline
-incidout=L5162040\_4020090518.2InAnMod1\newline
-beam\_rad=L5162040\_4020090518.2BeIr\newline
-insol\_time=L5162040\_04020090518.2InTiMod2\newline
-diff\_rad=L5162040\_04020090518.2DiIrMod1\newline
-refl\_rad=L5162040\_04020090518.2GReIrMod1\newline
-glob\_rad=L5162040\_04020090518.2TIrMod1\newline
-day=138 time=10
-\subsection{soil heat flux production}
+%\setkeys{Gin}{width=1\textwidth}
+\begin{figure}[htbp]
+   \centering
+   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
+   \includegraphics[scale=0.3]{gipe025a.png}
+   %caption of the figure
+   \caption{r.sun Mode 2}
+   %label of the figure, which has to correspond to \ref{}:
+   \label{fig:gipe025a}
+\end{figure}
+
+Incident angle raster map is computed using DEM, aspect, slope maps for the given julian day and local time. The figures ranges between 0 and 90.\newline
+Global or total irradiance output file is a product of the three basal outputs beam irradiance, diffuse irradiance and reflected irradiance. \newline
+The range of values of the products is dependent of many factors but some guidelines can be given as followings:\newline\linebreak
+The range of figures for Beam irradiance are normaly between 500 to 1000, diffuse irradiance between 70 to 150, and ground reflected irradiance between less than 1 to 100 all in (W/m2).\newline
+The summation of those basal products figures (global irradiance) for a given pixel must be less than actual instantaneous radiation at the atmosphere which ranged between 1361 to 1386 (W/M2).\newline\linebreak
+The net radiation (W/M2/day) value for each pixel can be computed by dividing the global irradiation mode 2 (Wh/M2/day) by the actual sunshine hours. It may be called Rnet.day product.\newline
+Sunshine hours is a weather station parameter and alternatively is possible to generate as a raster file by using the i.sunhours module.\newline\linebreak
+The r.sun command line for mode 1 and mode 2 are as followings and can be used for automated scripting.\newline\linebreak
+
+Mode 1
+\begin{smallverbatim}
+ r.sun elevin=dem90
+  aspin=_aspect slopein=_slop lin=3.2
+  albedo=L5162040_04020090518.1Albedo
+  latin=latitude longin=Longitude
+  incidout=_InAnM1 beam_rad=_BiIrM1
+  diff_rad=_DifIrM1 refl_rad=_GrRefIrM1
+  glob_rad=_GlIrrM1 day=138 time=10
+\end{smallverbatim}
+
+Mode 2
+\begin{smallverbatim}
+ r.sun elevin=dem90
+  aspin=_aspect slopein=_slop lin=3.2
+  albedo=L5162040_04020090518.1Albedo
+  latin=latitude longin=Longitude
+  beam_rad=_BiIrM2 insol_time=_InsTiM2
+  diff_rad=_DifIrM2 refl_rad=_GrRefIrM2
+  glob_rad=_GlIrrM2 day=138
+\end{smallverbatim}
+
+\subsection{soil heat flux}
 Soil heat flux can be computed with "i.eb.g0".\newline
@@
 
+\subsection{Sensible Heat Flux}
 Sensible heat flux can be calculated with "i.eb.h\_SEBAL01".\newline
@@
 
+\subsection{Evaporative Fraction}
 Evaporative fraction can be calculated by "i.eb.evapfr":\newline
@@
 
+\subsection{Evapotranspiration}
 Evapotranspiration can be computed from "i.eb.eta":\newline

### 2010-12-23 tutorials/grass_modis/article_GIPE.tex
Added Basic MODIS tutorial
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44678 15284696-431f-4ddb-bdfa-cd5b030d7da7

% Template GRASS newsletter - Article
% Language: Latex
%

% Head

\title{Basic MODIS preparation in GRASS GIS}
\subtitle{Manual}
\author{GRASS Development Team}

\maketitle
\section{Downloading free satellite data from Internet}
Downloading satellite imagery from Internet is now common. From 2009, Landsat-class satellites is having all its imagery freely downloadable online. Terra and Aqua satellites have always been freely downloadable since their launch. Typically, a safe way to start with is to reach the Warehouse Inventory Search Tool (WIST), a NASA website (\href{http://wist.echo.nasa.gov}{wist.echo.nasa.gov}) holding a large amount of free satellite imagery. Below is the initial choice available on WIST.
\begin{center}
 \includegraphics[scale=0.17]{WIST_datasets.png}
\end{center}
If you are downloading Modis images, be sure to have at hand a proper tool to manipulate the .hdf file format. The Modis Reprojection Tool (MRT) is such a tool and is available at (\href{http://lpdaac.usgs.gov/landdaac/tools/modis/index.asp}{lpdaac.usgs.gov/landdaac/tools/modis/}). MRT can convert to a more standard GeoTiff file format the Modis images. It can also reproject them to more common projection systems than its storage-purpose projection system the Integrated Sinusoidal. Alternatively, you can use a combination of tools from GDAL.\newline\linebreak
GDAL has a set of small tools that are practical to access information from header file and to perform repeated information on a dataset. You can use gdalinfo (\href{http://www.gdal.org/gdalinfo.html}{www.gdal.org/gdalinfo.html}) for extracting detailed information from the image file header, it extracts proper information about MODIS subdatasets and their naming conventions, add to it gdal\_translate (\href{http://www.gdal.org/gdal\_translate.html}{www.gdal.org/gdal\_translate.html}) to extract specific bands from the HDF format file into single bands common formats like GeoTiff. The script below automatically reads and exports each subdataset of any MODIS HDF file in the directory into a subdirectory called \textit{processed}.\newline
\begin{smallverbatim}
#This Unix Shell script automatically 
# extracts MODIS subdatasets into 
# processed/ subdirectory as GeoTiff 
# (*.tif) files
#-------------------------------------
mkdir processed
for file in *.hdf
do SDS_list=$(gdalinfo $file \
        | grep "SUBDATASET_.*_NAME.*")
	for subdataset in $SDS_list
	do echo ${subdataset#*=}.tif
	   gdal_translate -of GTiff \
	      ${subdataset#*=} processed/ \
	      ${subdataset#*=}.tif
	done
done
\end{smallverbatim}
Another tool, gdalwarp (\href{http://www.gdal.org/gdalwarp.html}{www.gdal.org/gdalwarp.html}) is dedicated to extract part of images and geolocate them properly. It would reproject the image data, it is useful to note that it also change the file format if you request it to do so. The script below does that with a target projection \textit{EPSG:4326} which actually means the following proj4 crs: \textit{+proj=longlat +ellps=WGS84 +datum=WGS84 +no\_defs}.
\begin{smallverbatim}
for file in *.hdf
do SDS_list=$(gdalinfo $file \
        | grep "SUBDATASET_.*_NAME.*")
	for subdataset in $SDS_list
	do echo ${subdataset#*=}.tif
	   gdalwarp -of GTiff \
	      -s_srs '+proj=sinu +R=6371007.181 \
	      +nadgrids=@null +wktext' \
	      -t_srs EPSG:4326 ${subdataset#*=} \
              processed/${subdataset#*=}.tif
	done
done
\end{smallverbatim}

\section{Renaming}
Most of the time you will want to reduce the size of the MODIS file names. As an example for MOD13Q1 NDVI layer remaning when converting from HDF to TIF, write the following script at the GRASS Command Line Interface:

\begin{smallverbatim}
root=~/MOD13Q1/2_PreProcessed
rootNDVI=$root/NDVI/
for file in MOD13Q1.A2010*.hdf
do 
	SDS_list_NDVI=$(gdalinfo $file \
		| grep "SUBDATASET_1_NAME")
	echo $file
	gdal_translate -of GTiff -quiet "${SDS_list_NDVI#*=}" \
	   $rootNDVI/$(echo ${SDS_list_NDVI#*=} \
	   | sed 's/\(.*\):\(.*\):"\(.*\).A\(.*\)\.\h \
	   \(.*\)\.\(.*\)\.\(.*\).hdf":\(.*\): \
	   \(.*\)/\3\_\4\_h\5\_\8\_250m_16_days_NDVI.tif/')
done
\end{smallverbatim}

\section{Importing in GRASS}
Once your files are prepared, they can be imported in GRASS.

\begin{smallverbatim}
cd $rootNDVI
for file in $rootNDVI
do
	r.in.gdal input=$file output=$file
done
\end{smallverbatim}

To access blindly an NDVI set of files, create a variable list from g.mlist:
\begin{smallverbatim}
listNDVI=$(g.mlist type=rast pattern=*NDVI*)
echo $listNDVI
\end{smallverbatim}

\section{QA Flags screening}
Use the \textit{i.modis.qc} module.

\begin{center}
 \includegraphics[scale=0.45]{i_modis_qc.png}
\end{center}

\address{GRASS Development Team\\
  \url{http://grass.osgeo.org}\\
  \email{tmitchell@osgeo.org}}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: main\_document.tex
%%% End:

### 2010-12-24 tutorials/grass_modis/article_GIPE.tex
Update
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44700 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \begin{smallverbatim}
+#This Unix Shell script automatically 
+# extracts and reprojects MODIS 
+# subdatasets into processed/ 
+# subdirectory as GeoTiff (*.tif) files
+#--------------------------------------
 for file in *.hdf
@@
 Most of the time you will want to reduce the size of the MODIS file names.
-As an example for MOD13Q1 NDVI layer remaning when converting from HDF to TIF, write the following script at the GRASS Command Line Interface:
+As an example for MOD13Q1 NDVI layer renaming when converting from HDF to TIF, write the following script at the GRASS Command Line Interface:
 
 \begin{smallverbatim}
+#This Unix Shell script automatically 
+# extracts MODIS NDVI subdatasets into 
+# GeoTiff (*.tif) files with a sed 
+# renaming scheme.
+#-------------------------------------
 root=~/MOD13Q1/2_PreProcessed
@@
 	echo $file
-	gdal_translate -of GTiff -quiet "${SDS_list_NDVI#*=}" \
+	gdal_translate -of GTiff "${SDS_list_NDVI#*=}" \
 	   $rootNDVI/$(echo ${SDS_list_NDVI#*=} \
@@
 
+If the later part of the code above is confusing, it may be a good idea to read about \href{http://www.gnu.org/software/sed/manual/sed.html}{sed} syntax.
+
 \section{Importing in GRASS}
@@
 \begin{smallverbatim}
+#Import all NDVI files in a directory
+# into GRASS GIS
+#--------------------------------
 cd $rootNDVI
@@
 \begin{smallverbatim}
+#Create a list of NDVI files available
+# in the current GRASS GIS Mapset
+#-------------------------------------
 listNDVI=$(g.mlist type=rast pattern=*NDVI*)

### 2011-01-03 tutorials/grass_landsat_ETa/article_GIPE.tex
Added Sensible Heat Flux module information
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44844 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \subtitle{Manual}
-\author{Pakparvar M. and GRASS Development Team}
+\author{Pakparvar M. (U. Ghent, Belgium) and GRASS Development Team}
 
@@
 \subsection{soil heat flux}
+The generic module "i.eb.soilheatflux" calculates the soil heat flux approximation (g0).
+It takes input of Albedo, NDVI, Surface Skin temperature, Net Radiation (see r.sun), and time of satellite overpass.\newline
+Surface temperature (LST) is directly relative to thermal radiation recorded in thermal band .
+So the the thermal band that has been converted to radiation (by i.landsat.toar) can be used as the input file for surface temperature raster map.\newline
+Net radiation is the global radiation product of mode1 of r.sun module.\newline
+Time raster map can be created by map calculation knowing the local time of satellite overpass.\newline
+
 Soil heat flux can be computed with "i.eb.g0".\newline
@@
 
-Note that some additional input should be created, including a ".time" raster.\newline
+The i.eb.soilheatflux command line is as followings and can be used for automated scripting.
+\begin{smallverbatim}
+i.eb.soilheatflux \
+    albedo="L5162040_04020090518.1Albedo" \
+    ndvi="L5162040_04020090518.1NDVI" \
+    tempk="L5162040_04020090518.toar.6" \
+    rnet="_GlIrrM1" time="time" output="_G0" 
+\end{smallverbatim}
 
 \subsection{Sensible Heat Flux}
+The Sensible heat flux (H) is calculated by "i.eb.h\_SEBAL01", given both maps of Net Radiation and soil Heat flux (Rn, G) at instantaneous time, the surface roughness (z0m), a map of the altitude corrected temperature (t0dem), a point data of the frictional velocity (u*), a value of actual vapour pressure (ea[KPa]) and the (x,y) pairs for wet and dry pixels.\newline
+Surface roughness (Z0m) is an dependent variable of vegetation hight.
+Generation of an accurate map of the vegetation inside the study area in the date of image acquisition will lead to increase the accuracy of H calculation.\newline
+\begin{smallverbatim}
+    Z0m=hveg * 0.136 
+\end{smallverbatim}
+hveg is the hight of vegetation (m).\newline
+Altitude corrected temperature map can be computed by using the toar thermal band and the DEM.\newline
+\begin{smallverbatim}
+    T0DEM=LST-(0.00627*DEM)
+\end{smallverbatim}
+The factor 0.00627 is the gradient of decreasing the temprature in relation to the decrease in hight (6.27 degree in each 1000 meter).\newline
+
+The U* (Called U star) is the friction velocity is computed by:\newline
+\begin{smallverbatim}
+    U*= 0.41*um/(ln(hu/Z0m) 
+\end{smallverbatim}
+um is wind speed in the time of satellite overpass (m/s), hu is the hight of wind measurement which is normally described as 5 (m).
+Z0m here is not the same as that is used in  U* calculation.
+The  hveg in this case is defined as the hight of vegetation around the weather station.\newline
+
+The value of actuale vapor pressure ea is calculated using the e0 for max and min tempreture.\newline
+\begin{smallverbatim}
+    e0=0.618*exp(17.27*T/(T+273.3))  
+\end{smallverbatim}
+e0 is the saturation vapor pressure at the air temperature. It must be calculated for Max and Min absolute tempreture.\newline
+ea is calculated using:\newline
+\begin{smallverbatim}
+    ea=RH*(e0Max=e0Min)/2))/100  
+\end{smallverbatim}
+RH is the measured relative humidity at the time of satellite overpass.\newline
+The location (row and column) of the wet (cold) and dry (hot) pixel must be found by the user.
+For wet pixel a place inside a water body and for dry pixel a place inside a bare and dry soil surface is recommended (SEBAL method is geographically dependent on extrem energy balance points).\newline
+
 Sensible heat flux can be calculated with "i.eb.h\_SEBAL01".\newline

### 2011-01-04 tutorials/grass_landsat_ETa/article_GIPE.tex
Added Energy Balance Intro
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44848 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \section{Energy balance terms}
+The energy-balance models use visible, infrared and thermal remotely sensed data for solving the main equation:\newline
+\begin{center}
+Rn-G-H-$\lambda$ET=0 \newline
+\end{center}
+Where the Rn is the net radiation, H is the sensible heat flux, G is the soil heat flux, and $\lambda$ET is the latent heat flux.\newline
 \subsection{Net Radiation}

### 2011-01-04 tutorials/grass_landsat_ETa/article_GIPE.tex
fixed typos
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44849 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
    %caption of the figure
-   \caption{r.sun Module}
+   \caption{r.sun Module, input options label}
    %label of the figure, which has to correspond to \ref{}:
@@
 
+Table 1: Linke Turbidity Coefficient
 \begin{center}
@@
 \linebreak
-Table 1: Linke Turbidity Coefficient
 \end{center}
@@
    %caption of the figure
-   \caption{r.sun Module}
+   \caption{r.sun Module, optional label}
    %label of the figure, which has to correspond to \ref{}:
@@
 The Sensible heat flux (H) is calculated by "i.eb.h\_SEBAL01", given both maps of Net Radiation and soil Heat flux (Rn, G) at instantaneous time, the surface roughness (z0m), a map of the altitude corrected temperature (t0dem), a point data of the frictional velocity (u*), a value of actual vapour pressure (ea[KPa]) and the (x,y) pairs for wet and dry pixels.\newline
-Surface roughness (Z0m) is an dependent variable of vegetation hight.
+Surface roughness (Z0m) is an dependent variable of vegetation height.
 Generation of an accurate map of the vegetation inside the study area in the date of image acquisition will lead to increase the accuracy of H calculation.\newline
@@
 \end{smallverbatim}
-hveg is the hight of vegetation (m).\newline
+hveg is the height of vegetation (m).\newline
 Altitude corrected temperature map can be computed by using the toar thermal band and the DEM.\newline
@@
 \end{smallverbatim}
-The factor 0.00627 is the gradient of decreasing the temprature in relation to the decrease in hight (6.27 degree in each 1000 meter).\newline
+The factor 0.00627 is the gradient of decreasing the temprature in relation to the increase in height (6.27 degree in each 1000 meter).\newline
 
@@
 \end{smallverbatim}
-um is wind speed in the time of satellite overpass (m/s), hu is the hight of wind measurement which is normally described as 5 (m).
+um is wind speed in the time of satellite overpass (m/s), hu is the height of wind measurement which is normally described as 5 (m).
 Z0m here is not the same as that is used in  U* calculation.
-The  hveg in this case is defined as the hight of vegetation around the weather station.\newline
+The  hveg in this case is defined as the height of vegetation around the weather station.\newline
 
@@
 \begin{smallverbatim}
-    ea=RH*(e0Max=e0Min)/2))/100  
+    ea=RH*(e0Max+e0Min)/2))/100  
 \end{smallverbatim}
@@
 For wet pixel a place inside a water body and for dry pixel a place inside a bare and dry soil surface is recommended (SEBAL method is geographically dependent on extrem energy balance points).\newline
-
-Sensible heat flux can be calculated with "i.eb.h\_SEBAL01".\newline
 

### 2011-01-04 tutorials/grass_modis/article_GIPE.tex
updated i.modis.qc section
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44852 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \section{QA Flags screening}
-Use the \textit{i.modis.qc} module.
+Use the \textit{i.modis.qc} module with MODIS Vegetation products (i.e. MOD13A2) as shown in the screenshot below:
+\begin{smallverbatim}
+MOD13A2: Mandatory QA Flags 1Km bits[0-1]
+* [00]= class 0: VI produced, good quality
+* [01]= class 1: VI produced, but check other QA
+* [10]= class 2: Pixel produced, but most probably cloud
+* [11]= class 3: Pixel not produced due to other \
+    reasons than clouds
+\end{smallverbatim}
 
@@
 \end{center}
+
+If you want to use shell scripting, the example below shows how to process Quality Assessment for Land Surface Temperature (i.e. MOD11A1):
+\begin{smallverbatim}
+
+MOD11A1: Mandatory QA Flags bits=[0-1]
+* [00]= class 0: LST produced, good quality, \
+    not necessary to examine more detailed QA
+* [01]= class 1: LST produced, other quality, \
+    recommend examination of more detailed QA
+* [10]= class 2: LST not produced due to cloud effects
+* [11]= class 3: LST not produced primarily due \
+    to reasons other than cloud
+
+for QC in mandatory_qa_11A1 data_quality_flag_11A1 \
+ emis_error_11A1 lst_error_11A1
+ do
+ i.modis.qc productname=mod11A1 qcname=$QC \
+ input=mod11A1.QC out=mod11A1_$QC
+done
+\end{smallverbatim}
 

### 2011-01-04 tutorials/grass_modis/article_GIPE.tex
Updated MCD43B3/B2 Quality processing info
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44874 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
+When Dealing with BRDF-Corrected Albedo product (i.e.
+MCD43B3), a complement quality product should be downloaded, MCD43B2.
+This product has two Sub-Datasets (SDS) that are not bit-packed, therefore can be read directly but r.mapcalc.
+These SDS are \textit{BRDF\_Albedo\_Quality} and \textit{Snow\_BRDF\_Albedo}.
+
+\begin{smallverbatim}
+BRDF_Albedo_Quality
+-------------------
+ Value 0: Processed, good quality \
+    (full BRDF inversion) 
+ Value 1: Processed, see other QA \
+    (magnitude BRDF inversions)
+ Value 255: Fill Value
+\end{smallverbatim}
+
+\begin{smallverbatim}
+Snow_BRDF_Albedo
+----------------
+ Value 0: Snow-free albedo retrieved  
+ Value 1: Snow albedo retrieved 
+ Value 255: Fill Value
+\end{smallverbatim}
+
 \address{GRASS Development Team\\

### 2011-01-05 tutorials/grass_modis/article_MODIS.tex
included MCD43B2 example
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44878 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2011-01-04 tutorials/grass_modis/article_GIPE.tex
@@
 
+In the case of BRDF\_Albedo\_Quality SDS (SDS\_BRDF), we may create an all BRDF levels inclusive mask with:
+
+\begin{smallverbatim}
+ r.mapcalc BRDFmask1=if(SDS_BRDF>1,null(),1)
+\end{smallverbatim}
+
+A more conservative version will be including only successful Full BRDF inversions:
+
+\begin{smallverbatim}
+ r.mapcalc BRDFmask2=if(SDS_BRDF>0,null(),1)
+\end{smallverbatim}
+
 \address{GRASS Development Team\\

### 2011-02-12 grassflyer/flyer1/en/grassflyer.tex
git-svn-id: https://svn.osgeo.org/grass/grass-promo@45389 15284696-431f-4ddb-bdfa-cd5b030d7da7

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%GRASS PROMOTION FLYER                                 %
%(c) 2007 GRASS PROMOTION TEAM                         %
%GNU Free Documentation License                        %
%Version 1.2                                           %
%Needs leaflet.cls				       %
%www.ctan.org/tex-archive/macros/latex/contrib/leaflet/%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Sometimes printing engines need the 2nd side upside down
%in this case, use tumble (which is default) instead of notumble
%If this causes problems, use notumble
%If you need a foldmark, delete nofoldmark
\documentclass[notumble,a4paper,10pt,nofoldmark]{leaflet}
\usepackage{helvet,courier,xcolor}

% Set Helvetica as the default font
\renewcommand*\familydefault\sfdefault
% Let LaTeX knows that pictures are found in ./pix
\graphicspath{{pix/}}

% Setting up things for the captions
\usepackage{caption}[2004/07/16]
\captionsetup{%
  font={small,it},%
  labelformat=empty,% Leaves out label: ``Figure 1''
  labelsep=none,%
  aboveskip=0pt%
}
% Defining a new 'figure' environment for the document
\newenvironment{myfig}[1][0pt plus 1.5ex minus .5ex]{\par\vspace*{#1}\begin{minipage}{\textwidth}\centering}{\end{minipage}}

% Defining the GRASS homepage
\newcommand{\GRASSurl}{\url{http://grass.osgeo.org}}

% Define a color for the URIs
\definecolor{darkblue}{RGB}{0,0,88}

\usepackage{hyperref}
% Setting up some document info
\hypersetup{%
  colorlinks=true,%
  urlcolor=darkblue,% Redefine this color to change URIs color
  pdfauthor={The GRASS Community},%
  pdftitle={GRASS GIS: Efficiency through Freedom \& Transparency},%
  pdfsubject={GRASS Promotion Flyer},%
  breaklinks=true,%
  plainpages=false%
}

% Title page stuff
\title{\textbf{\huge GRASS GIS}\\%
\textsl{Efficiency through Freedom \& Transparency}}
\author{The GRASS Community}
\date{\includegraphics[width=\textwidth]{grasslogo_vector}\\[2ex]
\large\GRASSurl}

\begin{document}

\maketitle
\thispagestyle{empty}% Necessary to leave out the page number on the first page

\newpage

\section{What is GRASS}

GRASS (Geographic Resources Analysis Support System) is Free and Open Source Software for performing spatial analysis. It consists of more than 350 modules for processing vector (2D/3D), raster and voxel data. Many interfaces to other programs in related domains like geostatistics, databases, mapserver and even other GIS software exist. It is the largest Open Source GIS. It can serve as a Desktop GIS and as the backbone of a complete GIS infrastructure.

\section{Where is GRASS used}

GRASS is used in scientific applications, commercial settings and by public authorities all over the world. GRASS has shown strong potential for solving geospatial problems in numerous situations world-wide.

\section{History}

GRASS was originally developed in the early 1980's by the US Army Construction Engineering Research Laboratories (USA-CERL) and was published as public domain software. When the USA-CERL withdrew from GRASS development, an international developer team assumed responsibility for the task. Since 1999, GRASS has been published as free software under the terms of the GNU General Public Licence.
\begin{myfig}[1.5ex]
\includegraphics[width=0.7\textwidth]{visibility}
\captionof{figure}{Viewshed analysis performed with GRASS}
\end{myfig}

\section{Open Source Philosophy}

The Open Source philosophy lets the user see the source code and structure of the program, which offers great transparency. Users can extend the program for their own needs. Immediate source code peer review increases the quality. With the help of the extension manager, new modules can be created without GRASS package source code.

\section{Technical Data Sheet}

\subsection{License}

GNU General Public License (Free Software Foundation)

\subsection{Supported platforms}

GRASS runs on nearly all platforms. It supports GNU/Linux, Posix compliant Unix Systems, MS-Windows and MacOS X.

\subsection{Design}

\begin{itemize}
\item Modular
\item Consists of more than 350 modules
\end{itemize}

\subsection{Programming languages}

\begin{itemize}
\item ANSI C
\item GRASS-SWIG interface
\item Python for WebGIS applications
\item Java Version: JGRASS
\end{itemize}

\subsection{Data management capabilities}

\begin{itemize}
\item Raster / Vector / Voxel data processing
\item 2D / 3D Raster / Vector modeling
\item Image manipulation
\item Vector topology / Network analysis
\item Geostatistics (Interface to R)
\end{itemize}

\begin{myfig}[1ex]
\includegraphics[width=0.7\textwidth]{trento3d}
\captionof{figure}{A flyby of the city of Trento, Italy}
\end{myfig}

\section{Supported file formats}

GRASS supports nearly all common GIS file formats through the use of the GDAL/OGR library. It also supports the Open GIS Consortium's Simple Features.

\subsection{Vector file formats}
ASCII, ARC/INFO ungenerate, ARC/INFO E00, Arc\-View SHAPE, BIL, DLG (U.S.), DXF, DXF3D, GMT, GPS-ASCII USGS-DEM, IDRISI, MOSS, MapInfo MIF, PostGIS, TIGER, VRML, \dots

\subsection{Raster file formats}
ASCII, ARC/GRID, E00, GIF, GMT, TIF, PNG, Vis5D, SURFER (.grd),\dots
\begin{myfig}
\includegraphics[width=0.7\textwidth]{isodist}
\captionof{figure}{Default GUI configuration showing GRASS network analysis capabilites}
\end{myfig}

\subsection{Image file formats}

CEOS (SAR, SRTM, LANDSAT7 etc.), ERDAS LAN / IMG, HDF, LANDSAT TM/MSS, NHAP aerial photos, SAR, SPOT, \dots
\begin{myfig}[1.5ex]
\includegraphics[width=0.7\textwidth]{ndvi}
\captionof{figure}{Image processing options in GRASS}
\end{myfig}

\subsection{Database support}

\begin{itemize}
\item PostgreSQL / PostGIS
\item MySQL
\item SQLite
\item ODBC
\item DBF
\end{itemize}

\subsection{Output}

\begin{itemize}
\item Mapping modules
\item NVIZ for visualization of 2.5D and 3D data (creation of animations \& flybys)
%\item{GMT export}
%item{VRML}
\item VTK, POVray
\item WebGIS via Mapserver, Python, etc.
\end{itemize}

\subsection{Interoperability with other GIS-related Software}

\begin{itemize}
\item Quantum GIS (Free geodata viewer and more)
\item R-Language (Statistics)
\item Gstat (Geostatistics)
\item UMN Mapserver (Webmapping)
\end{itemize}

\section{Where to find more information}

\begin{itemize}
%\begin{flushleft}
\item{Project Website: \\\GRASSurl}
\item{GRASS Wiki: \\\url{http://grass.osgeo.org/wiki}}
\item{GRASS Promotion Team: \\\url{malte@perlomat.de}}
\item{GRASS mailing lists: \\\url{http://grass.osgeo.org/community/support.php}}
%\end{flushleft}
\end{itemize}

\vfill
\section{OSGeo}

GRASS is a founding project of the Open Source Geospatial Foundation which has the aim to create high quality open source geospatial software. For further information visit the OSGeo homepage:
\begin{center}
\includegraphics[width=0.8\textwidth]{OSGeo_CMYK}\\
\url{http://www.osgeo.org}
\end{center}

\end{document}

### 2011-12-07 tutorials/grass_starter/article_GRASS.tex
Updated intro and RS, now version of GRASS is 6.4.1
git-svn-id: https://svn.osgeo.org/grass/grass-promo@49591 15284696-431f-4ddb-bdfa-cd5b030d7da7

% Template GRASS newsletter - Article
% Language: Latex
%

% Head

\title{Starter Manual to GRASS GIS}
\subtitle{GRASS Original}
\author{GRASS Development Team}

\maketitle

\section{Introduction}

This screenshot is GRASS GIS running on Ubuntu, it does seamlessly in MacOSX and Windows too.Fig.~\ref{fig:grass000}
%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.125]{grass000.png}
   %caption of the figure
   \caption{GRASS on Ubuntu}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass000}
\end{figure}

Starting GRASS GIS: Select Spearfish60 Location by a click on
``Enter GRASS'':Fig.~\ref{fig:grass001}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{grass001.png}
   %caption of the figure
   \caption{Welcome Screen}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass001}
\end{figure}

At this point it should (somewhat) look this way: Fig.~\ref{fig:grass002}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass002.png}
   %caption of the figure
   \caption{GIS Manager}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass002}
\end{figure}

Some more GRASS GUI information is found in Appendix A \ref{appendixA}.

Load the elevation.10m layer by clicking on the raster display button
(fifth button from left):Fig.~\ref{fig:grass003}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.5]{grass003.png}
   %caption of the figure
   \caption{Basic Display}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass003}
\end{figure}

Once selected, the main GRASS GUI will have a new layer like one of
these in Fig.~\ref{fig:grass004}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.5]{grass004.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass004}
\end{figure}

By selecting the new layer, you will be given a contextual menu below:Fig.~\ref{fig:grass005}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass005.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass005}
\end{figure}

Then add a vector using the 7th icon from the left. Fig.~\ref{fig:grass006}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.5]{grass006.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass006}
\end{figure}

Add a stream layer (blue color) and a road layer (brown color). Below is
the example for the streams Fig.~\ref{fig:grass007}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.45]{grass007.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass007}
\end{figure}

Result should look like this (somehow):Fig.~\ref{fig:grass008}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass008.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass008}
\end{figure}

\section{DEM MANIPULATIONS}
Remove the vector layers from the display, and the annotations too. Display only an elevation map as in Fig.~\ref{fig:grass009}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass009.png}
   %caption of the figure
   \caption{Display a DEM}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass009}
\end{figure}

\subsection{Compute slope and aspect}
Raster/Terrain Analysis/Slope and Aspect. Fig.~\ref{fig:grass010}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass010.png}
   %caption of the figure
   \caption{Slope}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass010}
\end{figure}

Compute a shaded relief map ( in Raster/Terrain Analysis/Shaded Relief).
The Shaded Relief map should be like this when a elevation.10m map is overlaid to it with 0.5 opacity (right-click on elevation.10m layer and change opacity level): Fig.~\ref{fig:grass011}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass011.png}
   %caption of the figure
   \caption{Shaded Relief}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass011}
\end{figure}

\subsection{Watershed Basin Analysis Program}
Raster/Hydrologic modeling/Watershed Analysis.
Fill in the Elevation input map with ``elevation.10m''. The minimum size of an exterior watershed basin should be 5000 cells. Fill up output names for all the output maps available (i.e. ``\_cells\_nbr'', ``\_drain\_dir'', ``\_basins'', ``\_streams'', ``\_half\_basins'', ``\_visual'', ``\_LS'', ``\_S'').

Output should state the following:

SECTION 1a (of 6): Initiating Memory.

SECTION 1b (of 6): Determining Offmap Flow.

SECTION 2: A * Search.

SECTION 3: Accumulating Surface Flow.

SECTION 4: Length Slope determination.

SECTION 5: Watershed determination.

SECTION 6: Closing Maps.

Output of ``\_basins'' should look like this:Fig.~\ref{fig:grass012}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass012.png}
   %caption of the figure
   \caption{Generated Basins}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass012}
\end{figure}

Output of ``\_streams'' should look like this: Fig.~\ref{fig:grass013} compare it with
the vector map ``streams''.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass013.png}
   %caption of the figure
   \caption{Generated streams}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass013}
\end{figure}

Relaunch with various values instead of 5000 cells, i.e. 2000 and 10000.
Compare by vectorizing the streams generated. Vectorization follows
these steps:\newline
1-Raster/Transform Features/Thin\newline
2-File/Map Type Conversion/Raster to Vector Map\newline
3-Vector/Develop Vector Map/Create or Rebuild Topology (optional)\newline

\subsection{Stream Pollution Monitoring Station site identification}
Assuming a Wood Processing Factory is requesting permit to setup a new processing plant in the country side. It is remote from major mapped streams (598713.35(E) 4920069.15(N)), the local council gave you a notice to assess the path of some minor effluents that may be draining to the major stream from the future factory, and especially their meeting point coordinates where the council will establish an automatic monitoring station.
Use Raster/Terrain Analysis/Least Cost Route Or Flow, your output should look like this: Fig.~\ref{fig:grass014}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass014.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass014}
\end{figure}

What is the location (Easting,Northing) of the generated stream crossing
the mapped stream where it is proposed to install a monitoring
station?

\section{GRASS GIS Habitat Analysis}
\subsection{Introduction}

http://www.udel.edu/johnmack/frec682/682proj2.html

This course is available online under the course name ``FREC 682 Spatial Analysis''. This material is a modified version to accommodate with GRASS 6.4.1+.

In this session, the features needed are the following essentially (look in RASTER from the main interface):
The BUFFERING Module:   Raster/Create buffers Fig.~\ref{fig:grass015}
The MAP CALCULATOR Module:   Raster/Map Calculator Fig.~\ref{fig:grass016}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass015.png}
   %caption of the figure
   \caption{BUFFERING}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass015}
\end{figure}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass016.png}
   %caption of the figure
   \caption{MAP CALCULATOR}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass016}
\end{figure}

Additional modules for the later part of the lab

Query map with mouse:
In the Map display window, look for:   Fig.~\ref{fig:grass017}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=1]{grass017.png}
   %caption of the figure
   \caption{Query Map with mouse}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass017}
\end{figure}

\textbf{NULL values:}\newline Raster/Develop raster Map/Manage Null values\newline
\textbf{CLUMP:}\newline Raster/Transform features/Clump\newline
\textbf{STATISTICS:}\newline Raster/Reports \& Statistics/General statistics\newline
\textbf{R2V:}\newline File/Map type Conversions/Raster to vector\newline
\textbf{Vector Build:}\newline Vector/Develop Map/Create or Rebuild Topology\newline
\textbf{Vector Export:}\newline File/Export/Vector map/Common export formats\newline
\textbf{Start New Display Window:}\newline
In the main GRASS GUI look for:    Fig.~\ref{fig:grass018}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=1]{grass018.png}
   %caption of the figure
   \caption{Launch New Display}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass018}
\end{figure}

Erase Display:
In the Map display window, look for:   Fig.~\ref{fig:grass019}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=1]{grass019.png}
   %caption of the figure
   \caption{Erase Display Icon}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass019}
\end{figure}

Redraw map:
In the Map display window, look for:   Fig.~\ref{fig:grass020}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=1]{grass020.png}
   %caption of the figure
   \caption{Redraw Icon}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass020}
\end{figure}

\subsection{Habitat Preservation Mission}
The pickled strumpet (Trollopensus bibulosa) has recently been added to the Endangered Species List, and the Fish and Wildlife Service is identifying likely habitat areas in the Spearfish area for protection from development. They have constructed the following habitat scoring system based on the species observed habitat preferences:

\subsection{Habitat Scoring System (from Fish and Wildlife Service) }

Map number Environmental conditions Score to be given
\begin{enumerate}
 \item within 500 meters of streams slope <= 5 degrees \textbf{+2 points} and within 500 meters of streams where slope >5 degrees \textbf{+5 points}
 \item within 500 meters of a road \textbf{-5 points}
 \item coniferous forest \textbf{+4 points}
 \item mixed forest \textbf{+1 point}
 \item northern exposure (aspect from NW to NE) \textbf{+3 points}
 \item western or eastern exposure (SW to NW or SE to NE) \textbf{+1 point}
 \item 1200-1400 meters elevation \textbf{+2 points}
 \item 1400-1600 meters elevation \textbf{+4 points}
 \item over 1600 meters elevation \textbf{+2 points}
\end{enumerate}

Use r.buffer (..=> Create buffers) and r.mapcalc (..=> Map calculator) to create an aggregate habitat score map of the entire area, summing all the partial scores as defined above. (hint: you have to convert all null values of buffer output maps into zero values)
When finished with numbers 1 to 10 above, sum all the maps in a map that you may call scoreindivsum. Then identify suitable habitat areas by converting to zeroes all cells with overall habitat scores below 9, and all cells within 100 meters of a road (hint: you have to make a new buffer map here, and remove its null values for calculations). Make a final scoring map that you may call scorefinal and change 0 values to NULL (..=>Manage null values) for next laboratory part.

\subsection{Process Scoring Maps}

In the processing of number 1 and 2, please use the Map Calculator with an input following an 'if statement'. The structure goes this
way:
\begin{smallverbatim}
if(condition, action_if_true, action_if_not_true)
\end{smallverbatim}
In the case of a map application use it this way:
\begin{smallverbatim}
if(MapA==value1, score_value1, score_value2)
\end{smallverbatim}
Since one may want to give two input maps together, a double if statement can be formulated this way:

A practical example for number 1:
\begin{smallverbatim}
if(stream_buff_500==2,if(slope=5,2,0),0)
\end{smallverbatim}
In case one wants to select a range of values (inclusive or exclusive), use of OR and AND is necessary. Query to check aspect map (..=>Query with mouse), East=1 and North=+90 degrees.

Practical examples for 7a and 7b:
\begin{smallverbatim}
7a) if(aspect<225 && aspect>135, 1, 0)

7b) if(aspect<45 || aspect>314 && aspect!=0, 1, 0)
\end{smallverbatim}
Example 7b has an added constraint ``\&\& aspect !=0'' because aspect value 0 means no aspect was calculated (usually out of data boundary in
the image).

This Set of instructions shows how GRASS GIS does the reclassification work under scripting mode. This is useful when you need to reuse the same set of GIS manipulations/models several times on different or new datasets.

\subsection{Scoring Script}

Map number Environmental conditions Score to be given:

\textbf{
1) within 500 meters of streams where slope <= 5 degrees: +2 points and within 500 meters of streams where slope >5 degrees: +5 points}
\begin{smallverbatim}
r.buffer input=streams output=streams500
 distances=500 units=meters --overwrite

r.null map=streams500 null=0

r.mapcalc score1="if(streams500>=1,if(
 slope<=5,2,5),0)"
\end{smallverbatim}

\textbf{
2) within 500 meters of a road: -5 points}
\begin{smallverbatim}
r.buffer input=roads output=_broads500
 distances=500 units=meters --overwrite

r.null map=_broads500 null=0

r.mapcalc score2="float(if(
 _broads500>=1,-5.0,0))"
\end{smallverbatim}

\textbf{
3) coniferous forest: +4 points}
\begin{smallverbatim}
r.mapcalc score3="if(vegcover==3,4,0)"
\end{smallverbatim}

\textbf{
4) mixed forest: +1 point}
\begin{smallverbatim}
r.mapcalc score4="if(vegcover==5,1,0)"
\end{smallverbatim}

\textbf{
5) northern exposure (aspect from NW to NE): +3 points}
\begin{smallverbatim}
r.mapcalc score5="if(aspect<=135.0 && aspect>=45.0
 && aspect != 0,3,0)"
\end{smallverbatim}

\textbf{
6) western or eastern exposure (SW to NW or SE to NE): +1 point}
\begin{smallverbatim}
r.mapcalc score61="if(aspect<45.0 ||
 aspect>314.0,1,0)"
r.mapcalc score62="if(aspect<225.0 &&
 aspect>135.0,1,0)"
\end{smallverbatim}

\textbf{
7) 1200-1400 meters elevation: +2 points}
\begin{smallverbatim}
r.mapcalc score7="if(elevation.10m<1400
 && elevation.10m>1200,2,0)"
\end{smallverbatim}

\textbf{
8) 1400-1600 meters elevation: +4 points}
\begin{smallverbatim}
r.mapcalc score8="if(elevation.10m<1600
 && elevation.10m>=1400,4,0)"
\end{smallverbatim}

\textbf{
9) over 1600 meters elevation: +2 points}
\begin{smallverbatim}
r.mapcalc score9="if(elevation.10m>=1600,2,0)"
\end{smallverbatim}

\subsection{Finalizing}

\begin{smallverbatim}
r.buffer input=roads output=roads100
 distances=100 units=meters --overwrite

r.null map=roads100 null=0

r.mapcalc score_temp="float(score1+score2+score3+
 score4+score5+score61+score62+score7+
score8+score9)"

r.mapcalc score_final="if(score_temp>9,1,null())"

r.mapcalc score_final_clean="if(score_final==1&&_br100==0,1,null())"
\end{smallverbatim}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass021.png}
   %caption of the figure
   \caption{Scoring Map before masking (ref as score\_temp above)}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass021}
\end{figure}

\subsection{Clumping Suitable Areas}
WARNING: This part of the Laboratory involves the use of the command line (command prompt).

What is ``clumping''?
Recategorizes data in a raster map layer by grouping cells that form physically discrete areas into unique categories.

Now find the discrete areas (clumps) of aggregated habitat scores.
Run \textit{r.clump (..=>Clump Small Areas) }on the ``\textit{class}'' map to give each clump its own category number. You may call the output ``\textit{class\_clumped}''.

\begin{smallverbatim}
r.clump input=score_final_clean
 output=score_clumped
\end{smallverbatim}

Display your newly clumped map ``\textit{score\_clumped}''. It should somewhat look like this one:Fig.~\ref{fig:grass022}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass022.png}
   %caption of the figure
   \caption{Clumped map}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass022}
\end{figure}

Since this species is most viable in larger clumps, extract the clumps greater than 50 hectares to a separate map. You may use the command line for reclassification by area threshold to select area superior to 50 hectares:

\begin{smallverbatim}
r.reclass.area input=score_clumped
 output=habitat_area greater=50
\end{smallverbatim}

Output ``habitat\_area'' at this level should be similar to this one:Fig.~\ref{fig:grass023}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass023.png}
   %caption of the figure
   \caption{Selected Habitat Areas}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass023}
\end{figure}

\subsection{Export Shapefile}
Since the users work in vector GIS, we are going to convert the results in vector format and export them from GRASS GIS to shapefile.

\begin{smallverbatim}
r.to.vect -s --overwrite input=habitat_area
 output=habitat_area feature=area
\end{smallverbatim}

Vectorize the habitat\_area map you just produced (\textbf{File/Map type conversion/raster to vector}) and check that you have effectively created a polygon vector map by displaying your vector using random colors.Fig.~\ref{fig:grass024}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass024.png}
   %caption of the figure
   \caption{Vector Export}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass024}
\end{figure}

Export this selected habitat vector file along with the ``\textit{roads}'' and ``\textit{streams}'' vector files into shapefile. Please be sure that you export the same type of vectors (areas for ``\textit{habitat\_area}'' and lines for ``\textit{roads}'' and ``\textit{streams}''). Display and query them using Quantum GIS.

\begin{smallverbatim}
v.out.ogr -c input=habitat_area type=area
 dsn=QGISDATA layer=1 format=ESRI_Shapefile

v.out.ogr input=roads type=line dsn=QGISDATA
 layer=1 format=ESRI_Shapefile

v.out.ogr input=streams type=line dsn=QGISDATA
 layer=1 format=ESRI_Shapefile
\end{smallverbatim}

Additional processing.....

The pickled strumpet is quite intolerant of edge disturbances, so you would like to weight interior areas of the habitat clumps more highly than edge areas. Create interior 100-meter-interval buffers within the large habitat clumps, where interior pixels within 100 meters of a clump edge have a weight of 1, interior pixels 100-200 meters from a clump edge have a weight of 2, interior pixels 200-300 meters from a clump edge have a weight of 3, etc., and pixels outside the largest clumps have a weight of zero.

Use \textit{r.mapcalc} to multiply the aggregate habitat score map by these interior buffer weights.
Now run \textit{r.volume }on this buffer-weighted habitat score map to obtain the sum and average of each clump s cell habitat scores.
Use \textit{awk} to create reclass rules files, then use \textit{r.reclass} to map the largest clumps by sum and average habitat scores.
Which clump has the highest weighted total habitat score? Which has the highest weighted average habitat score?
Use \textit{r.grow} to create a map of clump edges only (subtracting the input map from the output map).
Use the edge map to index the perimeter of each of the major clumps.
Calculate the compactness (area divided by perimeter squared) of each clump.
Map the largest clumps by compactness. Create a jazzy display script to demonstrate your procedures and explain your findings.
(See \href{http://www.udel.edu/johnmack/frec682/script_ideas.html})

A script for some parts of the Lab is in \textbf{Appendix B} \ref{appendixB}.

\newpage
\section{Remote sensing}
\label{remote_sensing}

\subsection{Import}
\label{Import}

Download from GLCF website a satellite image of Landsat 7 ETM+ covering your country, or area of interest. In this case it is p092r084 from year 2010 and Julian day 26, it is in the South-East Australia. We took a small geographical sample by this gdal shell script:

\begin{smallverbatim}
 #Uncompress the tarball
 tar xvf LE70920842010026ASN00.tar.gz
 cd LE70920842010026ASN00/

 #subset all Landsat 7 bands
 for file in *.TIF
   do gdalwarp -te 452274 -3855746 476447
      -3839082 $file new$file
   #remove quietly the $file
   rm -f $file
 done
\end{smallverbatim}

Start GRASS GIS. On opening, click on ``Location Wizard'', set your Location name, press ``Next'', then click on the third option ``Read projection and datum terms for a georeferenced data file'' button and select one of the Landsat TIF files. Then agree to all until completion.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass_rs000.png}
   %caption of the figure
   \caption{Start GRASS GIS}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs000}
\end{figure}

On launching the module, type in ``landsat'' or whatever name you created and load your landsat images into it.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass_rs001.png}
   %caption of the figure
   \caption{Set up the new Location name}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs001}
\end{figure}

Once setup from georeferenced file, launch GRASS GIS from this new Location called ''landsat''.

Identify with band number corresponding to which spectrum band, especially Red and Near-InfraRed spectra.

Once GRASS is loaded, import in GRASS GIS using r.in.gdal (File / import raster data / Common import formats).

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass_rs002.png}
   %caption of the figure
   \caption{import with r.in.gdal}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs002}
\end{figure}

Change the coloring of the bands R=3, G=2 and B=1 according to r.landsat.rgb:

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass_rs003.png}
   %caption of the figure
   \caption{Change RGB color table for Landsat}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs003}
\end{figure}

Load a RGB combination of band 4,3,2 by clicking the 8th button from the left near to th raster loading button, select there the RGB map.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.45]{grass_rs004.png}
   %caption of the figure
   \caption{Load a RGB band combination}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs004}
\end{figure}

Display the map (real color composite)

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass_rs005.png}
   %caption of the figure
   \caption{Display the RGB real colour composite}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs005}
\end{figure}

Change the coloring of the bands according to this (False Colour Composite).

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass_rs006.png}
   %caption of the figure
   \caption{Load NIR-R-B colour combination)}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs006}
\end{figure}

Display the map of the false color composite

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass_rs007.png}
   %caption of the figure
   \caption{Display the RGB FCC}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs007}
\end{figure}

\subsection{Classification}
\label{classification}

Create a group and subgroup with band 1-5.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.45]{grass_rs008.png}
   %caption of the figure
   \caption{Create image group and subgroup}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs008}
\end{figure}

Create a signature file.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass_rs009.png}
   %caption of the figure
   \caption{Create initial class statistics signature file}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs009}
\end{figure}

See the convergence happening...

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass_rs010.png}
   %caption of the figure
   \caption{Convergence of statistics}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs010}
\end{figure}

Run the Maximum Likelihood clustering classification.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass_rs011.png}
   %caption of the figure
   \caption{Create initial class statistics signature file}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs011}
\end{figure}

Display the result of unsupervised classification

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass_rs012.png}
   %caption of the figure
   \caption{Display classification result}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass_rs012}
\end{figure}

\subsection{Map Algebra}
\label{map_algebra}

Using r.mapcalc, calculate the difference vegetation index (dvi), the Normalized dvi (ndvi) and the soil-adjusted vegetation index (savi). Then calculate some uncorrected Albedo and the temperature.

\begin{enumerate}
 \item dvi=(NIR-RED)
 \item ndvi=dvi/(NIR+RED)
 \item savi=((1+0.5)*dvi)/(NIR+RED+0.5)
 \item Albedo=0.293*BLUE + 0.274*GREEN + 0.233*RED + 0.156*NIR + 0.033*band5 +0.011*band7
 \item temperature=1282.71 / (log ((666.09 / (band6)) + 1.0))
\end{enumerate}

Observe cities, roads, irrigation canals, rivers, wetlands, agricultural lands, forests and barren areas with each and all of these images, find out what defines best each land use.

\newpage
\section{3D Visualization}
\label{3D_visualization}

The N-Visualization tool in GRASS GIS takes care of 3D display of GIS data. Identify the 3 N-VIZ buttons in the GRASS GIS GUI. Click on the Left Side button. This will launch NVIZ.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{nviz000.png}
   %caption of the figure
   \caption{Find out the 3 NVIZ buttons}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz000}
\end{figure}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.2]{nviz001.png}
   %caption of the figure
   \caption{NVIZ Display}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz001}
\end{figure}

Open the Panel and detach it.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{nviz002.png}
   %caption of the figure
   \caption{NVIZ panel detached}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz002}
\end{figure}

Load a Raster by clicking on Raster surfaces

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.2]{nviz003.png}
   %caption of the figure
   \caption{Load a raster}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz003}
\end{figure}

In the Surface Panel, click on the NEW button,select NEW MAP.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.2]{nviz004.png}
   %caption of the figure
   \caption{Select New Map}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz004}
\end{figure}

This will load a mapset locator, select permanent, then in the coverage browser select elevation.10m.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.2]{nviz005.png}
   %caption of the figure
   \caption{Select elevation.10m}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz005}
\end{figure}

Accept for each open dialog. The raster will be loaded.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.2]{nviz006.png}
   %caption of the figure
   \caption{Load elevation.10m}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz006}
\end{figure}

Close the Surface Panel and Open the Vector Panel.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.2]{nviz007.png}
   %caption of the figure
   \caption{Open Vector Panel}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz007}
\end{figure}

Select NEW. This will open the mapset browser again, choose PERMANENT, select streams coverage.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.2]{nviz008.png}
   %caption of the figure
   \caption{Load Streams vector layer}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz008}
\end{figure}

Accept and click the button called DRAW CURRENT.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.2]{nviz009.png}
   %caption of the figure
   \caption{Draw Streams Layer}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz009}
\end{figure}

Close the vector panel and open the color panel from the main panel.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.2]{nviz010.png}
   %caption of the figure
   \caption{Open color panel}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz010}
\end{figure}

Select your color and CLOSE the color panel.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.2]{nviz011.png}
   %caption of the figure
   \caption{Select your color}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz011}
\end{figure}

Drag the directional ball-point to the Upper-left, closer to the center. Increase Height exaggeration to 3.0.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.2]{nviz012.png}
   %caption of the figure
   \caption{Change the z-exaggeration and camera settings}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:nviz012}
\end{figure}

\newpage
\subsection{Appendix A: Overview of Grass GUI}
\label{appendixA}

Overview of the available commands in the modules:Fig.~\ref{fig:grass025} Fig.~\ref{fig:grass026} Fig.~\ref{fig:grass027}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{grass025.png}
   %caption of the figure
   \caption{GRASS Menus (1/3)}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass025}
\end{figure}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{grass026.png}
   %caption of the figure
   \caption{GRASS Menus (2/3)}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass026}
\end{figure}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{grass027.png}
   %caption of the figure
   \caption{GRASS Menus (3/3)}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass027}
\end{figure}

\newpage

\subsection{Appendix B: GRASS SCRIPT}
\label{appendixB}

Please put this into a file that you may name \textit{script.sh}\textup{and from a }\textit{Terminal}\textup{ type: ``chmod 0755}\textit{script.sh''}\textup{. Then you can run the script }by typing the command: ``./script.sh''.

\begin{smallverbatim}
#!/bin/bash
# main map names variables
dem=elevation.dem
r=roads
s=streams
# buffer streams and roads variables
_bs=_bstreams500
_br=_broads500
# reclassed buffer streams and roads variables
_rbs=_rbstreams500
_rbr=_rbroads500
#--------------------------------------------------
# General Presentation: Start Monitor 0
#--------------------------------------------------
d.mon start=x0
d.erase color=grey
d.rast map=\$dem
sleep 1
d.vect map=\$r color=brown
sleep 1
d.vect map=\$s color=blue
sleep 1
d.barscale bcolor=white tcolor=black at=30.0,95.0
sleep 2
#--------------------------------------------------
# Buffering: Start Monitor 1
#--------------------------------------------------
d.mon start=x1
d.mon select=x1
d.erase color=grey
r.buffer input=\$s output=\$_bs distances=500
 units=meters --overwrite
r.null map=\$_bs null=0
d.rast map=\$_bs
d.vect map=\$s color=blue
d.barscale bcolor=white tcolor=black at=30.0,95.0
r.buffer input=\$r output=\$_br distances=500
 units=meters --overwrite
r.null map=\$_br null=0
d.rast map=\$_br
d.vect map=\$s color=blue
d.barscale bcolor=white tcolor=black at=30.0,95.0
#--------------------------------------------------
# Reclassification: Start Monitor 2
#--------------------------------------------------
d.mon start=x2
d.mon select=x2
d.erase color=grey
echo "...Reclassify..."
r.mapcalc \$_rbs="if(\$_bs==2,1,0)"
r.mapcalc _s_sl="if(\$_rbs==1,if(slope<=5,2,5),0)"
r.mapcalc \$_rbr="float(if(\$_br==2,-5.0,0))"
r.mapcalc _for="if(vegcover==3,4,0)"
r.mapcalc _for1="if(vegcover==5,1,0)"
r.mapcalc _exp1="if(aspect<45.0 || aspect>314.0 &&
 aspect != 0.0,1,0)"
r.mapcalc _exp2="if(aspect<225.0 && aspect>135.
 0,1,0)"
r.mapcalc _exp3="if(aspect<=135.0 && aspect>=45.0,
 3,0)"
r.mapcalc _elev1="if(\$dem<1400 &&\$dem>1200,2,0)"
r.mapcalc _elev2="if(\$dem<1600 &&\$dem>=1400,4,0)"
r.mapcalc _elev3="if(\$dem>=1600,2,0)"
#--------------------------------------------------
r.buffer input=\$r output=_br100 distances=100
 units=meters --overwrite
r.null map=\_br100 null=0
r.mapcalc _add="float(_s_sl+\$_rbr+_for+_for1+
 _exp1+_exp2+_exp3+_elev1+_elev2+_elev3)"
r.mapcalc _clas="if(_add{>9,1,null())"
r.mapcalc _class="if(_clas==1&&_br100==0,1,null())"
echo "Reclassification...done."
d.rast map="\$_rbs"
sleep 1
d.rast map="_s_sl"
d.rast map="\$_rbr"
d.rast map="_for"
d.rast map="_for1"
d.rast map="_exp1"
d.rast map="_exp2"
d.rast map="_exp3"
d.rast map="_elev1"
d.rast map="_elev2"
d.rast map="_elev3"
d.rast map="_br100"
sleep 1
#r.colors color=grey map="_add"
d.rast map="_add"
sleep 1
d.rast map="_class"
sleep 1
#d.erase
d.vect map="\$s" color=blue
d.vect map="\$r" color=brown
d.barscale bcolor=white tcolor=black at=30.0,95.0
sleep 5
g.remove
rast="\$_rbs,_s_sl,\$_rbr,_for,_for1"}
g.remove
rast="_exp1,_exp2,_exp3,_elev1"}
g.remove
rast="_elev2,_elev3,_br100,_add"}
g.remove rast="\$_bs,\$_br,_clas"}
sleep 1
echo ""
echo "finished"
sleep 1
#--------------------------------------------------
# Clumping: Start Monitor 3
#--------------------------------------------------
d.mon start=x3
d.mon select=x3
d.erase color=grey
g.remove rast=_clump.clump._rclumpnew
r.clump input=_class output=_clump --overwrite
r.colors color=gyr map="_clump"
d.rast map="_clump"
sleep 1
r.reclass.area input=_clump greater=50
 output=_rclumpnew --overwrite
r.colors color=gyr map="_rclumpnew"
d.erase color=white
d.rast map="_rclumpnew"
sleep 1
d.vect map="streams" color=blue
d.vect map="roads" color=brown
d.barscale bcolor=white tcolor=black at=30.0,95.0
sleep 1
g.remove rast="_clump,_class"
#--------------------------------------------------
# R2V and Export: Start Monitor 4
#--------------------------------------------------
d.mon start=x4
d.mon select=x4
d.erase color=white
r.to.vect -s input=_rclumpnew output=rclump
 feature=area --overwrite
d.vect -c map=rclump type=area color=black
d.vect map="streams" color=blue
d.vect map="roads" color=brown
d.barscale bcolor=white tcolor=black at=30.0,95.0
sleep 1
v.out.ogr input=rclump type=area dsn=QGISDATA
 layer=1 format=ESRI_Shapefile --overwrite
g.remove rast="_rclumpnew"
g.remove vect="rclump"
d.mon stop=x4
d.mon stop=x3
d.mon stop=x2
d.mon stop=x1
d.mon stop=x0
\end{smallverbatim}

\address{GRASS Development Team\\
  \url{http://grass.itc.it}\\
  \email{weblist@grass.itc.it}}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: main_document.tex
%%% End:

### 2012-06-17 tutorials/grass_starter/FR_article_GRASS.tex
move images into subdirectory
git-svn-id: https://svn.osgeo.org/grass/grass-promo@52098 15284696-431f-4ddb-bdfa-cd5b030d7da7

% Template GRASS newsletter - Article
% Language: Latex
%

% Head
\graphicspath{{./images/}}

\title{Manuel pour d\'ebuter avec le SIG GRASS}
\subtitle{GRASS en version originale}
\author{GRASS Development Team}

\maketitle

\section{Introduction}

Cette capture d'\'ecran est le SIG GRASS en version original sous Windows
(http://geni.ath.cx/grass.html).Fig.~\ref{fig:grass000}
%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.15]{grass000.png}
   %caption of the figure
   \caption{GRASS en version original sous Windows}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass000}
\end{figure}

Lancer le SIG GRASS: S\'electionnez la Location Spearfish60 et cliquez sur
``Enter GRASS'':Fig.~\ref{fig:grass001}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.3]{grass001.png}
   %caption of the figure
   \caption{Ecran d'acceuil}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass001}
\end{figure}

A ce moment cel\`a devrait ressembler \`a: Fig.~\ref{fig:grass002}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass002.png}
   %caption of the figure
   \caption{Gestionnaire du SIG}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass002}
\end{figure}

Plus d'information sur le GUI se trouve dans l'appendice A \ref{appendixA}.

Chargez la couche elevation.10m en cliquant sur le bouton de d'affichage raster (second bouton \`a partir de gauche):Fig.~\ref{fig:grass003}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.5]{grass003.png}
   %caption of the figure
   \caption{Affichage \'el\'ementaire}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass003}
\end{figure}

Une fois s\'electionn\'e, l'interface d'utilisation de GRASS aura une nouvelle couche comme cell-ci:Fig.~\ref{fig:grass004}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass004.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass004}
\end{figure}

En s\'electionnant la nouvelle couche, vous aurez acc\`es \`a un menu contextuel comme ceci:Fig.~\ref{fig:grass005}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass005.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass005}
\end{figure}

Ajoutez une couche vectorielle en utilisant la 8\`eme ic\^one \`a partir de la gauche. Fig.~\ref{fig:grass006}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.5]{grass006.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass006}
\end{figure}

Ajoutez une couche vectorielle "stream" (de couleur bleue) et "road" de couleur amrron. Ci-dessous est l'exemple pour "stream" Fig.~\ref{fig:grass007}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.45]{grass007.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass007}
\end{figure}

Le r\'esultat devrait \^etre comme ceci (plus ou moins):Fig.~\ref{fig:grass008}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass008.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass008}
\end{figure}

\section{MANIPULATIONS DE DEM}
Affichage du dem:Fig.~\ref{fig:grass009}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass009.png}
   %caption of the figure
   \caption{Affichage du DEM}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass009}
\end{figure}

\subsection{Calcul de pente et d'aspect}
Raster/Terrain Analysis/Slope and Aspect. Fig.~\ref{fig:grass010}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass010.png}
   %caption of the figure
   \caption{Pente}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass010}
\end{figure}

Calcul de carte de relief ombrag\'e ( prenez Raster/Terrain Analysis/Shaded Relief Map).
La carte de relief ombrag\'e devrait \^etre comme ceci quand la carte "elevation.10m" est superimpos\'ee dessus avec une opacit\'e de 0.75: Fig.~\ref{fig:grass011}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass011.png}
   %caption of the figure
   \caption{Relief Ombrag\'e}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass011}
\end{figure}

\subsection{Programme d'analyse de basin versant}
Raster/Hydrologic modeling/Watershed Analysis.
Remplissezs les param\`etres d'entr\'e de la carte d'altitude avec ``elevation.10m''. La taille minimum de l'ext\'erieur d'un bassin versant doit \^etre de 5000 pixels. Remplissez les param\`etres de sortie pour toutes les cartes disponibles (i.e. ``\_cells\_nbr'', ``\_drain\_dir'', ``\_drain\_dir'', ``\_basins'', ``\_streams'', ``\_half\_basins'', ``\_visual'', ``\_LS'', ``\_S'').

Voici ce que doit dire l' ex\'ecution du module:

SECTION 1a (of 6): Initiating Memory.

SECTION 1b (of 6): Determining Offmap Flow.

SECTION 2: A * Search.

SECTION 3: Accumulating Surface Flow.

SECTION 4: Length Slope determination.

SECTION 5: Watershed determination.

SECTION 6: Closing Maps.

La carte r\'esultante ``\_basins'' devrait ressembler \`a cel\`a:Fig.~\ref{fig:grass012}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass012.png}
   %caption of the figure
   \caption{Carte de basins versants}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass012}
\end{figure}

La carte r\'esultante ``\_streams'' devrait ressembler \`a cel\`a: Fig.~\ref{fig:grass013} comparez-l\`a avec la carte vectorielle ``streams''.

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass013.png}
   %caption of the figure
   \caption{Carte de r\'eseau hydrologique}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass013}
\end{figure}

Relancez avec des valuers diff\'erentes au lieu de 5000 pixels, i.e. 2000 et 10000.
Comparez en vectorisant les r\'eseaux hydrologiques g\'en\'er\'es. La vectorisation suit ces \'etapes:
1-Raster/Neighborhood Analysis/Thin Linear Features
2-File/Map Type Conversion/Raster to Vector Map
3-Vector/Develop Map/Create-Rebuild Topology (optional)

\subsection{Identification de site de station de suivit de la Pollution d'un ruisseau}
En consid\'erant qu'une usine de transformation/traitement de bois fasse une demande de permis pour mettre en place une nouvelle usine dans le basin versant. La localisation est distante du r\'eseau hydrologique majeur cartographi\'e (598713.35(E) 4920069.15(N)), le conseil local vous a employ\'e pour \'evaluer le chemin de quelques effluents mineurs qui pourraient se retrouver dans le r\'eseau majeur \`a partir de l'usine qui va \^etre install\'ee, et sp\'ecialement leurs coordonn\'ees g\'eographiques du point de rencontre o\`u le conseil va mettre en place une station de suivit automatique.
Utilisez Raster/Terrain Analysis/Least Cost Route Or Flow, v\^otre r\'esultat devrait ressembler a cel\`a: Fig.~\ref{fig:grass014}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass014.png}
   %caption of the figure
   \caption{}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass014}
\end{figure}

Quelle est la localisation (Est,Nord) du chemin hydrologique g\'en\'er\'e rejoignant la rivi\`ere cartographi\'ee, et donc lieu propos\'e pour installer une station de suivit?

\section{Analyse d'habitat avec le SIG GRASS}
\subsection{Introduction}

http://www.udel.edu/johnmack/frec682/682proj2.html

Ce cours est disponible en ligne sous le nom ``FREC 682 Spatial Analysis''. Ce mat\'eriel a \'et\'e modifi\'e pour r\'epondre aux changements venant avec GRASS  version 6.3 et additionnelles.

Dans cette session, les \'el\'ements dont vous aurez besoins sont essentiellement (regardez dans la partie RASTER de l'interface principale): 
Le module BUFFERING:   Raster/Create buffers Fig.~\ref{fig:grass015}
Le module MAP CALCULATOR:   Raster/Map Calculator Fig.~\ref{fig:grass016}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass015.png}
   %caption of the figure
   \caption{BUFFERING}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass015}
\end{figure}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass016.png}
   %caption of the figure
   \caption{MAP CALCULATOR}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass016}
\end{figure}

Certains modules additionnels pour plus tard

Questionner une carte avec la souris:   
Dans la fen\^etre d'affichage, cherchez:   Fig.~\ref{fig:grass017}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=1]{grass017.png}
   %caption of the figure
   \caption{Questionner une carte avec la souris}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass017}
\end{figure}

Valeurs NULL dans les cartes: Raster/Develop Map/Manage Null values

CLUMP: Raster/Transform features/Clump small Areas

STATISTIQUES: Raster/Reports \& Statistics = General statistics

R2V: File/Map type Conversions/Raster to vector

Construction Vectorielle: Vector/Develop Map/Create/Rebuild Topology

Export Vectoriel: File/Export/Vector map/Various format using OGR (SHAPE, etc)

Lanc\'e une nouvelle fen\^etre:
Dans l'interface principal de GRASS, cherchez :    Fig.~\ref{fig:grass018}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=1]{grass018.png}
   %caption of the figure
   \caption{Lanacer une nouvelle fen\^etre d'affichage}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass018}
\end{figure}

Effacer l'affichage:
Dans la fen\^etre d'affichage, cherchez:   Fig.~\ref{fig:grass019}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=1]{grass019.png}
   %caption of the figure
   \caption{Ic\^one d'effacement d'affichage}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass019}
\end{figure}

Redessiner la carte:
Dans la fen\^etre d'affichage, cherchez:   Fig.~\ref{fig:grass020}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=1]{grass020.png}
   %caption of the figure
   \caption{Ic\^one de redessinage}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass020}
\end{figure}

\subsection{MISSION DE PRESERVATION D'UN HABITAT}
La Trollopensus bibulosa a recemment \'et\'e ajout\'ee sur la liste des esp\`eces en danger, et le service en charge de la faune sauvage est en train d'identifier des habitats probables dans la zone sp\'eciale de Spearfish pour prot\'eger contre le d\'eveloppement. Ils ont construit le syst\`emes de points suivant pour cet habitat bas\'e sur les statistiques de pr\'ef\'erences des esp\`eces observ\'ees:

\subsection{SYSTEME DE POINTS POUR L'HABITAT (venant du service de la faune sauvage) }

Num\'ero de carte Conditions environnementales Score \`a donner
1 dans 500 m\`etres d'un cours d'eau o\` la pente <= 5 degr\'es +2 points
2 dans 500 m\`etres d'un cours d'eau o\` la pente >5 degr\'es +5 points
3 dans 500 m\`etres d'une route -5 points
4 for\^et de conif\`eres +4 points
5 for\^et mixte +1 point
6 exposition au Nord (aspect de NO \`a NE) +3 points
7 exposition \`a l'Ouest ou l'Est (SO au NO ou SE to NE) +1 point
8 1200-1400 m\`etres d'altitude +2 points
9 1400-1600 m\`etres d'altitude +4 points
10 over 1600 m\`etres d'altitude +2 points

Utilisez r.buffer (..=> Create buffers) et r.mapcalc (..=> Map calculator) pour cr\'eer une carte de score d'habitat pour toute la zone, en additionnant tous les scores partiels comme d\'efinis ci-dessus. (conseil: vous devez convertir toutes les valuers nulles des cartes de r\'esultats de buffer en valuers z\'ero)
Quand vous serez termin\'e avec les cartes 1 \`a 10 ci-dessus, additionnez-les toutes en une seule carte que vous pourriez appeler "scoreindivsum". Ensuite, identifiez une zone d'habitat souhaitable en convertissant les valeurs z\'ero des pixels pour tout r\'esultat inf\'erieur \`a 9, et tout pixel dans les 100 m\`etres d'une route (conseil: vous devz faire une nouvelle carte de buffer ici, et enlever ses valeurs nulles pour les calculs). Faites une carte finale que vous pourriez appeler "scorefinal" et changez en les valeurs z\'ero en NULL (..=>Manage null values) pour atteindre la prochaine partie de cet exercice.

\subsection{PREPARATION DES CARTES DE SCORE}

Pour calculer les cartes 1 et 2, utilisez le "Map Calculator" avec un syntaxte comprenant une structure conditionnelle (if). Cel\`a se trouve \^etre dans l'exemple suivant:
\begin{smallverbatim}
if(condition, action_si_vrai, action_si_faux)
\end{smallverbatim}
Dans le cas d'une carte:
\begin{smallverbatim}
if(CarteA==valeur1, score_valeur1, score_valeur2)
\end{smallverbatim}
Dans le cas ou deux cartes sont utilis\'ees ensemble, un syst\`eme conditionnel double peut \^etre d\'ecrit comme ceci:

Un exemple pratique pour la carte num\'ero 1:
\begin{smallverbatim}
if(stream_buff_500==2,if(slope=5,2,0),0)
\end{smallverbatim}
Dans le cas o\'u l'on voudrait s\'electionner une gamme de valeurs (inclusive ou exclusive), utilisez les op\'erants "OR" et "AND". Questionnez la carte d'aspect (..=>Query with mouse), Est=1 et Nord=+90 degr\'es.

Exemples practiques pour 7a et 7b:
\begin{smallverbatim}
7a) if(aspect<225 && aspect>135, 1, 0)

7b) if(aspect<45 || aspect>314 && aspect!=0, 1, 0)
\end{smallverbatim}
L'exemple 7b a une contrainte additionnelle ``\&\& aspect !=0'' car la valeur d'aspect 0 veut dire pas d'aspect calcul\'e (g\'en\'eralement en dehors de la zone de donn\'ees de l'image).

Ce jeu d'instructions montre comment le SIG GRASS produit une reclassification en mode "script". Ceci devient tr\`es utile quand vous avez besoin de r\'e-utiliser une analyse SIG complex plusieurs fois de suite sur d'autre jeux de donn\'ees par exemple.

\subsection{HABITAT SCORING SCRIPT}

Num\'ero de carte Conditions environnementales Score \`a donner:

\textbf{
1) Dans 500 m\`etres des cours d'eau o\`u la pente <= 5 degr\'es: +2 points}
\begin{smallverbatim}
r.buffer input=streams output=_bstreams500
 distances=500 units=meters --overwrite

r.null map=_bstreams500 null=0

r.mapcalc _rbstreams500="if(_bstreams500==2,1,0)"

r.null map=_rbstreams500 null=0
\end{smallverbatim}

\textbf{
2) Dans 500 m\`etres des cours d'eau o\`u la pente >5 degr\'es: +5 points}
\begin{smallverbatim}
r.buffer input=roads output=_broads500 distances=500
 units=meters --overwrite

r.mapcalc _s_sl="if(_rbstreams500==1,if(
 slope<=5,2,5),0)"
\end{smallverbatim}

\textbf{
3) Dans 500 m\`etres d'une route: -5 points}
\begin{smallverbatim}
r.mapcalc _rbroads500="float(if(
 _broads500==2,-5.0,0))"
\end{smallverbatim}

\textbf{
4) for\^et de conif\`eres: +4 points}
\begin{smallverbatim}
r.mapcalc _for="if(vegcover==3,4,0)"
\end{smallverbatim}

\textbf{
5) for\^et mixte: +1 point}
\begin{smallverbatim}
r.mapcalc _for1="if(vegcover==5,1,0)"
\end{smallverbatim}

\textbf{
6) Exposition Nord (aspect de NO \`a NE): +3 points}
\begin{smallverbatim}
r.mapcalc _exp3="if(aspect<=135.0 && aspect>=45.0
 && aspect != 0,3,0)"
\end{smallverbatim}

\textbf{
7a) Exposition Ouest ou Est (SO \`a NO ou SE \`a NE): +1 point}
\begin{smallverbatim}
r.mapcalc _exp1="if(aspect<45.0 || aspect>314.0,1,0)"
r.mapcalc _exp2="if(aspect<225.0 && aspect>135.0,1,0)"
\end{smallverbatim}

\textbf{
7b) 1200-1400 m\`etres d'altitude: +2 points}
\begin{smallverbatim}
r.mapcalc _elev1="if(elevation.10m<1400
 && elevation.10m>1200,2,0)"
\end{smallverbatim}

\textbf{
8) 1400-1600 m\`etres d'altitude: +4 points}
\begin{smallverbatim}
r.mapcalc _elev2="if(elevation.10m<1600
 && elevation.10m>=1400,4,0)"
\end{smallverbatim}

\textbf{
9) plus de 1600 m\`etres d'altitude: +2 points}
\begin{smallverbatim}
r.mapcalc _elev3="if(elevation.10m>=1600,2,0)"
\end{smallverbatim}

\subsection{FINALISATION DE LA CARTE DE SCORE}

\begin{smallverbatim}
r.buffer input=roads output=_br100
 distances=100 units=meters --overwrite

r.null map=_br100 null=0

r.mapcalc _add="float(_s_sl+_rbroads500+_for+
 _for1+_exp1+_exp2+_exp3+_elev1+_elev2+_elev3)"

r.mapcalc _clas="if(_add>9,1,null())"

r.mapcalc _class="if(_clas==1&&_br100==0,1,null())"
\end{smallverbatim}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass021.png}
   %caption of the figure
   \caption{Carte de score}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass021}
\end{figure}

\subsection{METTRE EN BLOC LES ZONES SOUHAITABLES}
ATTENTION: Cette partie demande l'utilisation du prompt/terminal avec des commandes en ligne.

Qu'est-ce que ``mettre en bloc''?
Re-cat\'egoriser les donn\'ees dans une carte raster en groupant les pixels qui form des surfaces continues physiquement en d'uniques cat\'egories.

Maintenant, trouvez les zones discr\`etes/continues (ou clumps) des scores d'aggr\'egation d'habitat. 
Lancez \textit{r.clump (..=>Clump Small Areas) }sur la carte ``\textit{score\_final}'' pour donner \`a chaque bloc son propre num\'ero de cat\'egorie. Vous pourriez appeler la carte r\'esultante ``\textit{score\_clumped}''.

\begin{smallverbatim}
r.clump input=score_final output=score_clumped 
\end{smallverbatim}

Affichez votre nouvelle carte de blocs ``\textit{score\_clumped}''. Elle devrait plus ou moins ressembler \`a cel\`a:Fig.~\ref{fig:grass022}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass022.png}
   %caption of the figure
   \caption{Carte des blocs}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass022}
\end{figure}

Puisque cette esp\`ece est mieux dans de larges blocs, faites une extraction des blocs sup\'erieurs a 50 hectares dans une carte sp\'epar\'ee. Vous pourriez utilisez le terminal pour reclassifier par seuil de surface sup\'erieur \`a 50 hectares:

\begin{smallverbatim}
r.reclass.area input = score_final greater=50 
 output=selected_habitat_area
\end{smallverbatim}

R\'esultat ``selected\_habitat\_area'' \`a ce niveau devrait \^etre similaire \`a ceci:Fig.~\ref{fig:grass023}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass023.png}
   %caption of the figure
   \caption{Zones d'habitat s\'electionn\'ees}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass023}
\end{figure}

\subsection{EXPORT DES RESULTATS SOUS FORMAT VECTORIEL}
Puisque nos clients travaillent sous SIG \`a format vectoriel, nous allons convertir les r\'esultats en format vectoriel et les exporter de GRASS \`a ESRI shapefile.

Vectorisez larte de blocs que vous venez de produire (File/Map type conversion/raster to vector) et v\'erifiez que vous avez effectivement cr\'ee une carte vectorielle \`a \'el\'ements de type polygones en affichant votre couche vectorielle avec des couleurs al\'eatoires.Fig.~\ref{fig:grass024}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.35]{grass024.png}
   %caption of the figure
   \caption{Export de fichier vectoriel}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass024}
\end{figure}

Exportez ce fichier vectoriel d'habitat avec ``\textit{roads}'' et ``\textit{streams}'' aussi en format shapefile. Soyez s\^ur que vous exportez le m\^eme type d'\'el\'ements vectoriels (area pour ``\textit{selected\_habitat\_area}'' et lines pour ``\textit{roads}'' et ``\textit{streams}''). Affichez et questionnez ces fichiers dans le SIG Quantum.

\begin{smallverbatim}
v.out.ogr input=selected_habitat_area type=area
 dsn=QGISDATA layer=1 format=ESRI_Shapefile

v.out.ogr input=roads type=line dsn=QGISDATA
 layer=1 format=ESRI_Shapefile

v.out.ogr input=streams type=line dsn=QGISDATA
 layer=1 format=ESRI_Shapefile
\end{smallverbatim}

Bonus de traitement de donn\'ees.....

Cette esp\`ece est assez intol\'erante des perturbations aux fronti\`eres de zones, donc vous devriez faire un poids plus lourd pour les zones internes que frontali\`eres des blocs d'habitat. Cr\'eez des buffers internes concentriques de 100 m\`etres pour chaque bloc, avec un poids de 1 pour le premier buffer en fronti\`ere (0-100 m\`etres internes), 2 pour le second vers l'interieur (100-200 m\`etres), 3 pour 200-300 m\`etres, etc..., quand aux pixels en dehors des blocs, leurs valeurs sont de z\'ero.

Utilisez \textit{r.mapcalc} pour multiplier la carte d'habitat par les poids des buffers internes.
Maintenant lancez \textit{r.volume }sur cette carte r\'esultante pour obtenir la somme et la moyenne de chaque bloc.
Utilisez  \textit{awk} pour cr\'eer des fichiers de r\`egles de r\'eclassification, puis utilisez \textit{r.reclass} pour cartographier les blocs par somme et moyenne.
Quel bloc a le nouveau total maximum? Lequel a la nouvelle moyenne maximum?
Utilisez \textit{r.grow} pour cr\'eer une carte de fronti\`eres de blocs (soustraire les cartes d'origines aux cartes r\'esultantes).
Utilisez les cartes de fronti\`eres de blocs pour indexer le p\'erimetre de chaque bloc majeur. 
Calculez la compacit\'e (surface divis\'ee par le carr\'e du p\'erimetre) de chaque bloc. 
Cartographiez les blocs par compacit\'e. Cr\'eez un script d'affichage cool pour d\'emontrer vos proc\'edures et expliquez ce que vous avez trouv\'e.
(Pour cel\`a voyez: \href{http://www.udel.edu/johnmack/frec682/script_ideas.html})

Un script de quelques pqrties de cet exercice est dans l'\textbf{Appendice B} \ref{appendixB}.

\newpage

\subsection{Appendice A: SUrvol de l'interface principale de GRASS}
\label{appendixA}

Survol des commandes disponibles dans les modules:Fig.~\ref{fig:grass025} Fig.~\ref{fig:grass026} Fig.~\ref{fig:grass027}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{grass025.png}
   %caption of the figure
   \caption{GRASS Menus (1/3)}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass025}
\end{figure}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{grass026.png}
   %caption of the figure
   \caption{GRASS Menus (2/3)}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass026}
\end{figure}

%\setkeys{Gin}{width=1\textwidth}
\begin{figure}[htbp]
   \centering
   %name of your graphic, without the path AND in PNG (screnshots etc)/PDF (drawings) format:
   \includegraphics[scale=0.4]{grass027.png}
   %caption of the figure
   \caption{GRASS Menus (3/3)}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:grass027}
\end{figure}

\newpage

\subsection{Appendice B: SCRIPT dans GRASS}
\label{appendixB}

Veuillez mettre ceci dans un fichier \textit{script.sh}\textup{et dans un }\textit{Terminal}\textup{ \'ecrivez: ``chmod 0755}\textit{script.sh''}\textup{. Ensuite vous pouvez lancer le script }en \'ecrivant la commande: ``./script.sh''.

\begin{smallverbatim}
#!/bin/bash
# Noms des variables de cartes
dem=elevation.dem
r=roads
s=streams
# buffer cours d'eau et routes
_bs=_bstreams500
_br=_broads500
# reclassement des buffer cours d'eau et routes
_rbs=_rbstreams500
_rbr=_rbroads500
#--------------------------------------------------
# Pr\'esentation g\'en\'erale: D\'ebut Affichage 0
#--------------------------------------------------
d.mon start=x0
d.erase color=grey
d.rast map=\$dem
sleep 1
d.vect map=\$r color=brown
sleep 1
d.vect map=\$s color=blue
sleep 1
d.barscale bcolor=white tcolor=black at=30.0,95.0
sleep 2
#--------------------------------------------------
# Cr\'eation de buffer: D\'ebut Affichage 1
#--------------------------------------------------
d.mon start=x1
d.mon select=x1
d.erase color=grey
r.buffer input=\$s output=\$_bs distances=500
 units=meters --overwrite
r.null map=\$_bs null=0
d.rast map=\$_bs
d.vect map=\$s color=blue
d.barscale bcolor=white tcolor=black at=30.0,95.0
r.buffer input=\$r output=\$_br distances=500
 units=meters --overwrite
r.null map=\$_br null=0
d.rast map=\$_br
d.vect map=\$s color=blue
d.barscale bcolor=white tcolor=black at=30.0,95.0
#--------------------------------------------------
# Reclassification: D\'ebut Affichage 2
#--------------------------------------------------
d.mon start=x2
d.mon select=x2
d.erase color=grey
echo "...Reclassification..."
r.mapcalc \$_rbs="if(\$_bs==2,1,0)"
r.mapcalc _s_sl="if(\$_rbs==1,if(slope<=5,2,5),0)"
r.mapcalc \$_rbr="float(if(\$_br==2,-5.0,0))"
r.mapcalc _for="if(vegcover==3,4,0)"
r.mapcalc _for1="if(vegcover==5,1,0)"
r.mapcalc _exp1="if(aspect<45.0 || aspect>314.0 &&
 aspect != 0.0,1,0)"
r.mapcalc _exp2="if(aspect<225.0 && aspect>135.
 0,1,0)"
r.mapcalc _exp3="if(aspect<=135.0 && aspect>=45.0,
 3,0)"
r.mapcalc _elev1="if(\$dem<1400 &&\$dem>1200,2,0)"
r.mapcalc _elev2="if(\$dem<1600 &&\$dem>=1400,4,0)"
r.mapcalc _elev3="if(\$dem>=1600,2,0)"
#--------------------------------------------------
r.buffer input=\$r output=_br100 distances=100
 units=meters --overwrite
r.null map=\_br100 null=0
r.mapcalc _add="float(_s_sl+\$_rbr+_for+_for1+
 _exp1+_exp2+_exp3+_elev1+_elev2+_elev3)"
r.mapcalc _clas="if(_add{>9,1,null())"
r.mapcalc _class="if(_clas==1&&_br100==0,1,null())"
echo "Reclassification...Fin."
d.rast map="\$_rbs"
sleep 1
d.rast map="_s_sl"
d.rast map="\$_rbr"
d.rast map="_for"
d.rast map="_for1"
d.rast map="_exp1"
d.rast map="_exp2"
d.rast map="_exp3"
d.rast map="_elev1"
d.rast map="_elev2"
d.rast map="_elev3"
d.rast map="_br100"
sleep 1
#r.colors color=grey map="_add"
d.rast map="_add"
sleep 1
d.rast map="_class"
sleep 1
#d.erase
d.vect map="\$s" color=blue
d.vect map="\$r" color=brown
d.barscale bcolor=white tcolor=black at=30.0,95.0
sleep 5
g.remove
rast="\$_rbs,_s_sl,\$_rbr,_for,_for1"}
g.remove
rast="_exp1,_exp2,_exp3,_elev1"}
g.remove
rast="_elev2,_elev3,_br100,_add"}
g.remove rast="\$_bs,\$_br,_clas"}
sleep 1
echo ""
echo "fin"
sleep 1
#--------------------------------------------------
# Mettre en bloc: D\'ebut Affichage 3
#--------------------------------------------------
d.mon start=x3
d.mon select=x3
d.erase color=grey
g.remove rast=_clump.clump._rclumpnew
r.clump input=_class output=_clump --overwrite
r.colors color=gyr map="_clump"
d.rast map="_clump"
sleep 1
r.reclass.area input=_clump greater=50
 output=_rclumpnew --overwrite
r.colors color=gyr map="_rclumpnew"
d.erase color=white
d.rast map="_rclumpnew"
sleep 1
d.vect map="streams" color=blue
d.vect map="roads" color=brown
d.barscale bcolor=white tcolor=black at=30.0,95.0
sleep 1
g.remove rast="_clump,_class"
#--------------------------------------------------
# R2V et Export: D\'ebut Affichage 4
#--------------------------------------------------
d.mon start=x4
d.mon select=x4
d.erase color=white
r.to.vect -s input=_rclumpnew output=rclump
 feature=area --overwrite
d.vect -c map=rclump type=area color=black
d.vect map="streams" color=blue
d.vect map="roads" color=brown
d.barscale bcolor=white tcolor=black at=30.0,95.0
sleep 1
v.out.ogr input=rclump type=area dsn=QGISDATA
 layer=1 format=ESRI_Shapefile --overwrite
g.remove rast="_rclumpnew"
g.remove vect="rclump"
d.mon stop=x4
d.mon stop=x3
d.mon stop=x2
d.mon stop=x1
d.mon stop=x0
\end{smallverbatim}

\address{GRASS Development Team\\
  \url{http://grass.itc.it}\\
  \email{weblist@grass.itc.it}}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: main_document.tex
%%% End:

### 2012-06-17 tutorials/batch_processing/earthquakes/php_demo/grass_earthquakes.sh
+ Markus N's Earthquake PHP demo
git-svn-id: https://svn.osgeo.org/grass/grass-promo@52104 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@ -1,0 +1,110 @@
+#!/bin/sh
+
+# 2006 Markus Neteler
+#
+#      This program is free software under the GNU General Public
+#      License (>=v2). Read the file COPYING that comes with GRASS
+#      for details.
+#######
+# Script to launch GRASS, fetch the USGS list of recent
+# earthquakes, generate map, leave GRASS.
+#
+# Inspired by
+#   http://grass.itc.it/spearfish/php_grass_earthquakes.php
+#
+# Requirements:
+# - grass6 installation
+# - latitude-longitude GRASS location (= GRASS project)
+#######################################################
+
+# some settings:
+TMPDIR=/tmp
+
+# directory of our software and grassdata:
+MAINDIR=/asd0/ssi/neteler_grid/software
+# our private /usr/ directory:
+MYUSER=$MAINDIR/myusr
+
+# path to GRASS binaries and libraries:
+export GISBASE=$MYUSER/grass-6.1.cvs
+
+# generate GRASS settings file:
+# the file contains the GRASS variables which define the LOCATION etc.
+echo "GISDBASE: $MAINDIR/grassdata
+LOCATION_NAME: latlong
+MAPSET: PERMANENT
+" > $TMPDIR/.grassrc6_earthquakes
+
+# path to GRASS settings file:
+export GISRC=$TMPDIR/.grassrc6_earthquakes
+
+# first our GRASS, then the rest
+export PATH=$GISBASE/bin:$GISBASE/scripts:$PATH
+#first have our private libraries:
+export LD_LIBRARY_PATH=$MYUSER/lib:$GISBASE/lib:$LD_LIBRARY_PATH
+
+# settings for graphical output
+PNGOUTPUTDIR=$TMPDIR
+# current date
+DATE=`LC_ALL=C date -R | tr -s ' ' ' ' | cut -d' ' -f2,3,4 | tr -s ' ' '_'`
+export GRASS_PNGFILE=$PNGOUTPUTDIR/grass6_recent_earthquakes_${DATE}.png
+export GRASS_TRUECOLOR=TRUE
+export GRASS_WIDTH=900
+export GRASS_PNG_COMPRESSION=1
+
+# use process ID (PID) as lock file number:
+export GIS_LOCK=$$
+
+
+##### the algorithms goes here
+
+error_routine () {
+ echo "ERROR: $1"
+ exit 1
+}
+
+# fetch last earthquake bulletin:
[…]

### 2012-06-17 tutorials/batch_processing/earthquakes/NZ/do_quakes_NZTM_ChCh.sh
+ earthquake demo scripts from adhoc VM: fetch XML data from GNS NZ & plot from LCC and TMerc loc'ns
git-svn-id: https://svn.osgeo.org/grass/grass-promo@52106 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@ -1,0 +1,266 @@
+#!/bin/sh
+#
+# script to download, import, and plot earthquakes from the last week.
+#  modified version to plot around the city of Christchurch, New Zealand
+#   using the NZTM projection (epsg:2193)
+#
+# (c) 2011 Hamish Bowman, and the GRASS Development Team
+# Based on earlier version by Markus Neteler, which in turn was based on
+#  comments from Sharyn Namnath and Glynn Clements.
+#
+# This script is licensed under the GPL >=2. See GPL.TXT which comes with
+#  the GRASS source code for details.
+#
+# World DTM picture is from the ETOPO1 dataset,
+#   http://www.ngdc.noaa.gov/mgg/global/global.html
+# Nice colors were done in GMT by J. Varner and E. Lim, CIRES, University
+#  of Colorado at Boulder.
+#
+# Earthquake data is downloaded from GNS NZ
+#  http://www.geonet.org.nz/resources/earthquake/quake-web-services.html
+#
+
+if  [ -z "$GISBASE" ] ; then
+    echo "You must be in GRASS GIS to run this program." >&2
+    exit 1
+fi
+
+#for filenames, etc:
+PROJ_SHORT_NAME=NZTM_ChCh
+WEB_DIR=/var/www/grass/earthquakes
+
+GRASS_PNGFILE=earthquakes.png
+#GRASS_PNGFILE=earthquakes.ppm
+#GRASS_WIDTH=1024
+#GRASS_HEIGHT=845
+GRASS_WIDTH=1102
+GRASS_HEIGHT=882
+GRASS_TRUECOLOR=TRUE
+GRASS_PNG_COMPRESSION=9
+GRASS_VERBOSE=0
+export GRASS_WIDTH GRASS_HEIGHT GRASS_TRUECOLOR GRASS_PNG_COMPRESSION \
+   GRASS_VERBOSE GRASS_PNGFILE
+
+TMPDIR="/var/tmp/grass"
+if [ ! -d "$TMPDIR" ] ; then
+   mkdir -p "$TMPDIR"
+fi
+cd "$TMPDIR"
+
+# remove old stuff
+g.remove vect=recent_earthquakes --quiet
+
+
+### download and import
+DATAFILE="$TMPDIR/latest_gns_quakes.csv"
+
+fetch_gns_earthquakes.sh "$DATAFILE" 2>&1
+if [ $? -ne 0 ] ; then
[…]

### 2012-06-17 tutorials/batch_processing/earthquakes/NZ/do_quakes_NZ_lcc.sh

@@ -1,0 +1,219 @@
+#!/bin/sh
+#
+# script to download, import, and plot earthquakes from the last week.
+#  modified version to plot around New Zealand using the LCC projection (epsg:3851)
+#
+# (c) 2011 Hamish Bowman, and the GRASS Development Team
+# Based on earlier version by Markus Neteler, which in turn was based on
+#  comments from Sharyn Namnath and Glynn Clements.
+#
+# This script is licensed under the GPL >=2. See GPL.TXT which comes with
+#  the GRASS source code for details.
+#
+# World DTM picture is from the ETOPO1 dataset,
+#   http://www.ngdc.noaa.gov/mgg/global/global.html
+# Nice colors were done in GMT by J. Varner and E. Lim, CIRES, University
+#  of Colorado at Boulder.
+#
+# Earthquake data is downloaded from GNS NZ
+#  http://www.geonet.org.nz/resources/earthquake/quake-web-services.html
+#
+
+if  [ -z "$GISBASE" ] ; then
+    echo "You must be in GRASS GIS to run this program." >&2
+    exit 1
+fi
+
+
+PROJ_SHORT_NAME=NZ_lcc
+WEB_DIR=/var/www/grass/earthquakes
+
+GRASS_PNGFILE=earthquakes.png
+#GRASS_PNGFILE=earthquakes.ppm
+GRASS_WIDTH=738
+GRASS_HEIGHT=600
+GRASS_TRUECOLOR=TRUE
+GRASS_PNG_COMPRESSION=9
+GRASS_VERBOSE=0
+export GRASS_WIDTH GRASS_HEIGHT GRASS_TRUECOLOR GRASS_PNG_COMPRESSION \
+   GRASS_VERBOSE GRASS_PNGFILE
+
+TMPDIR="/var/tmp/grass"
+if [ ! -d "$TMPDIR" ] ; then
+   mkdir -p "$TMPDIR"
+fi
+cd "$TMPDIR"
+
+# remove old stuff
+g.remove vect=recent_earthquakes --quiet
+
+
+### download and import
+DATAFILE="$TMPDIR/latest_gns_quakes.csv"
+
+fetch_gns_earthquakes.sh "$DATAFILE" 2>&1
+if [ $? -ne 0 ] ; then
+   echo "Failed to download data from GNS." >&2
+   exit 1
+fi
+
[…]

### 2012-06-17 tutorials/batch_processing/earthquakes/NZ/fetch_gns_earthquakes.sh

@@ -1,0 +1,60 @@
+#!/bin/sh
+
+# Script to fetch NZ earthquakes from GNS's geonet SOAP interface
+#  H. Bowman 20 Jan 2011, released to the public domain
+#
+#  http://www.geonet.org.nz/resources/earthquake/quake-web-services.html
+#  "GeoNet is a collaboration between the Earthquake Commission and GNS Science."
+#  "The Website: The GeoNet website provides public access to hazards information,
+#   including earthquake reports and Volcanic Alert Bulletins. It also allows the
+#   retrieval of fundamental data sets, such as GPS Rinex files, earthquake
+#   hypocentres and instrument waveform data. These data are made freely available
+#   to the research community."
+
+# requires wget and xml2 to be installed
+
+
+if [ -n "$1" ] ; then
+   OUTFILE="$1"
+else
+   OUTFILE=latest_gns_quakes.csv
+fi
+XMLNAME="$OUTFILE.tmp_$$"
+
+URL="http://magma.geonet.org.nz/services/quake/quakeml/1.0.1/query?"
+#startDate and endDate (mandatory): format is yyyy-mm-ddThh:MM:ss and times are in UTC (GMT)
+#latLower, latUpper, longLower and longUpper (optional, but if present, all must be specified): values should be in decimal degrees
+
+
+END_DATE=`date --utc +%FT%T`
+START_DATE=`date --utc --date="last week" +%FT%T`
+#START_DATE=`date --utc --date="2 weeks ago" +%FT%T`
+#START_DATE=`date --utc --date="last month" +%FT%T`
+#START_DATE=`date --utc --date="6 months ago" +%FT%T`
+#START_DATE=`date --utc --date="last year" +%FT%T`
+
+DATE_STR="startDate=$START_DATE&endDate=$END_DATE"
+ 
+
+wget -nv -O "$XMLNAME" "${URL}startDate=$START_DATE&endDate=$END_DATE"
+
+
+BASE="quakeml/eventParameters/event"
+FIELDS="
+origin/time/value
+origin/longitude/value
+origin/latitude/value
+magnitude/mag/value
+origin/depth/value
+"
+
+echo "#date_utc|time_utc|longitude|latitude|magnitude|depth_km" \
+   > "$OUTFILE"
+
+xml2 < "$XMLNAME" | \
+   2csv -d'|' $BASE $FIELDS | \
[…]

### 2012-06-17 tutorials/batch_processing/earthquakes/earthquake_plot_job.sh
add missing name
git-svn-id: https://svn.osgeo.org/grass/grass-promo@52109 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@ -2,7 +2,7 @@
 ############################################################################
 #
 # MODULE:       earthquake_plot_job.sh
-# AUTHOR:       M. Hamish Bowman, Depts.of Marine Science and Geology,
+# AUTHOR:       M. Hamish Bowman, Depts. of Marine Science and Geology,
 #                 Otago Univeristy, New Zealand
 # PURPOSE:      Wrapper script to launch GRASS batch job
 #                 (perhaps called by cron)
@@ -14,7 +14,7 @@
 #
 #############################################################################
 # Inspired by Markus Neteler's PHP demo, which in turn was seeded from the ideas
-#    of [...] and Glynn Clements
+#    of Sharyn Namnath and Glynn Clements
 # Adjust paths etc. to suit.
 
 ## sample crontab:

### 2012-06-17 tutorials/batch_processing/earthquakes/do_quakes_latlon.sh
merge in changes from adhoc
git-svn-id: https://svn.osgeo.org/grass/grass-promo@52110 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@ -15,13 +15,19 @@
 #  of Colorado at Boulder.
 #
 # Earthquake data is downloaded from the USGS
-#  http://neic.usgs.gov/neis/gis/bulletin.asc
+#  http://neic.usgs.gov/neis/gis/bulletin.asc (defunct)
+#  new1:  http://earthquake.usgs.gov/earthquakes/catalogs/eqs7day-M2.5.txt
+#  new2:  http://earthquake.usgs.gov/earthquakes/feed/csv/2.5/week
 #
 
 if  [ -z "$GISBASE" ] ; then
     echo "You must be in GRASS GIS to run this program." >&2
     exit 1
 fi
+
+
+PROJ_SHORT_NAME=world_ll
+WEB_DIR=/var/www/grass/earthquakes
 
 #GRASS_PNGFILE=earthquakes.png
 GRASS_PNGFILE=earthquakes.ppm
@@ -33,7 +39,7 @@ GRASS_VERBOSE=0
 export GRASS_WIDTH GRASS_HEIGHT GRASS_TRUECOLOR GRASS_PNG_COMPRESSION \
    GRASS_VERBOSE GRASS_PNGFILE
 
-TMPDIR="/var/local/grass/tmp"
+TMPDIR="/var/tmp/grass"
 if [ ! -d "$TMPDIR" ] ; then
    mkdir -p "$TMPDIR"
 fi
@@ -42,7 +48,9 @@ cd "$TMPDIR"
 
 ### download and import
 
-wget -nv -O "$TMPDIR/bulletin.tmp" http://neic.usgs.gov/neis/gis/bulletin.asc 2>&1
+wget -nv -O "$TMPDIR/bulletin.tmp" \
+   "http://neic.usgs.gov/neis/gis/bulletin.asc" 2>&1
+
 if [ $? -ne 0 ] ; then
    echo "Failed to download data from the USGS." >&2
    exit 1
@@ -86,13 +94,18 @@ v.db.addcol recent_earthquakes column="magn_energy DOUBLE PRECISION"
 # how to do POW(x,n) in SQLite?
 #v.db.update recent_earthquakes column=magn_energy value="POW(magnitude,10) * 1e-7" --verbose
 
-v.db.select recent_earthquakes column=cat,magnitude | awk -F'|' \
-  '{printf("UPDATE recent_earthquakes SET magn_energy=%f WHERE cat=%d;\n", ($2^10)*1e-7, $1)}' | db.execute
[…]

### 2012-06-17 tutorials/batch_processing/earthquakes/do_quakes_wintri.sh
merge in changes from adhoc
git-svn-id: https://svn.osgeo.org/grass/grass-promo@52111 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@ -16,13 +16,19 @@
 #  of Colorado at Boulder.
 #
 # Earthquake data is downloaded from the USGS
-#  http://neic.usgs.gov/neis/gis/bulletin.asc
+#  http://neic.usgs.gov/neis/gis/bulletin.asc (defunct)
+#  new1:  http://earthquake.usgs.gov/earthquakes/catalogs/eqs7day-M2.5.txt
+#  new2:  http://earthquake.usgs.gov/earthquakes/feed/csv/2.5/week
 #
 
 if  [ -z "$GISBASE" ] ; then
     echo "You must be in GRASS GIS to run this program." >&2
     exit 1
 fi
+
+
+PROJ_SHORT_NAME=world_wintri
+WEB_DIR=/var/www/grass/earthquakes
 
 #GRASS_PNGFILE=earthquakes.png
 GRASS_PNGFILE=earthquakes.ppm
@@ -34,19 +40,18 @@ GRASS_VERBOSE=0
 export GRASS_WIDTH GRASS_HEIGHT GRASS_TRUECOLOR GRASS_PNG_COMPRESSION \
    GRASS_VERBOSE GRASS_PNGFILE
 
-TMPDIR="/var/local/grass/tmp"
+TMPDIR="/var/tmp/grass"
 if [ ! -d "$TMPDIR" ] ; then
    mkdir -p "$TMPDIR"
 fi
 cd "$TMPDIR"
 
-# remove old stuff
-g.remove vect=recent_earthquakes --quiet
-
 
 ### download and import
 
-wget -nv -O "$TMPDIR/bulletin.tmp" http://neic.usgs.gov/neis/gis/bulletin.asc 2>&1
+wget -nv -O "$TMPDIR/bulletin.tmp" \
+   "http://neic.usgs.gov/neis/gis/bulletin.asc" 2>&1
+
 if [ $? -ne 0 ] ; then
    echo "Failed to download data from the USGS." >&2
    exit 1
@@ -101,13 +106,18 @@ v.db.addcol recent_earthquakes column="magn_energy DOUBLE PRECISION"
 # how to do POW(x,n) in SQLite?
 #v.db.update recent_earthquakes column=magn_energy value="POW(magnitude,10) * 1e-7" --verbose
 
-v.db.select recent_earthquakes column=cat,magnitude | awk -F'|' \
[…]

### 2012-06-18 tutorials/batch_processing/earthquakes/do_quakes_latlon.sh
update for new USGS bulletin format, use csv_dequote.pl
git-svn-id: https://svn.osgeo.org/grass/grass-promo@52116 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@ -48,22 +48,31 @@ cd "$TMPDIR"
 
 ### download and import
 
-wget -nv -O "$TMPDIR/bulletin.tmp" \
-   "http://neic.usgs.gov/neis/gis/bulletin.asc" 2>&1
+wget -nv -O "eqs7day-M2.5.csv" \
+   "http://earthquake.usgs.gov/earthquakes/catalogs/eqs7day-M2.5.txt" 2>&1
 
 if [ $? -ne 0 ] ; then
    echo "Failed to download data from the USGS." >&2
    exit 1
 fi
 
-# bulletin.asc format:
-#Date,TimeUTC,Latitude,Longitude,Magnitude,Depth
-# date is yy/mm/dd so not SQL Date type!
+#convert commas+quoting to pipe delims:
+csv_dequote.pl eqs7day-M2.5.csv
 
-COL_DEF="e_date varchar(8), e_time varchar(10), latitude double precision, \
-  longitude double precision, magnitude double precision, depth double precision"
+# add a '#' at the start of the first line and remove spurious whitespace
+sed -i -e '0,/^/s//#/' \
+       -e 's+| \([0-9]\)|+|\1|+' eqs7day-M2.5.psv
 
-INPUT="$TMPDIR/bulletin.tmp"
+# eqs7day-M2.5.txt format:
+#Src,EqId,Version,Datetime,Lat,Lon,Magnitude,Depth,NST,Region
+
+COL_DEF="data_source varchar(4), eq_id varchar(10), version varchar(3),
+   eq_time varchar(50), latitude double precision, longitude double precision, \
+   magnitude double precision, depth double precision, num_stations_obs integer,
+   region varchar(255)"
+
+INPUT="$TMPDIR/eqs7day-M2.5.psv"
+ 
 
 db.connect -c
 DBDRIVER=`db.connect -p | grep '^driver:' | cut -f2 -d:`
@@ -74,7 +83,7 @@ if [ "$DBDRIVER" != 'sqlite' ] ; then
 fi
 
 v.in.ascii in="$INPUT" out=recent_earthquakes skip=1 \
-    fs=',' y=3 x=4 z=6 column="$COL_DEF" --overwrite
+    fs='|' y=5 x=6 z=8 column="$COL_DEF" --overwrite
 
 
 ### unlog & scale magnitude
[…]

### 2012-06-18 tutorials/batch_processing/earthquakes/do_quakes_wintri.sh

@@ -49,33 +49,40 @@ cd "$TMPDIR"
 
 ### download and import
 
-wget -nv -O "$TMPDIR/bulletin.tmp" \
-   "http://neic.usgs.gov/neis/gis/bulletin.asc" 2>&1
+wget -nv -O "eqs7day-M2.5.csv" \
+   "http://earthquake.usgs.gov/earthquakes/catalogs/eqs7day-M2.5.txt" 2>&1
 
 if [ $? -ne 0 ] ; then
    echo "Failed to download data from the USGS." >&2
    exit 1
 fi
 
-# bulletin.asc format:
-#Date,TimeUTC,Latitude,Longitude,Magnitude,Depth
-# date is yy/mm/dd so not SQL Date type!
+#convert commas+quoting to pipe delims:
+csv_dequote.pl eqs7day-M2.5.csv
 
-INPUT="$TMPDIR/bulletin.tmp"
+INPUT="$TMPDIR/eqs7day-M2.5.psv"
 
-sed -i -e 's/^Date/#Date/' "$INPUT"
+# add a '#' at the start of the first line and remove spurious whitespace
+sed -i -e '0,/^/s//#/' \
+       -e 's+| \([0-9]\)|+|\1|+' "$INPUT"
 
-cut -f3,4 -d, "$INPUT" | awk -F, '{print $2 "\t" $1}' | \
-   m.proj -ig fs=, | cut -f1,2 -d, | \
-   awk '{if (NR!=1) {print} else {print "easting,northing"}}' \
-  > "$INPUT.wintri.coord"
+# eqs7day-M2.5.txt format:
+#Src,EqId,Version,Datetime,Lat,Lon,Magnitude,Depth,NST,Region
+ 
+COL_DEF="data_source varchar(4), eq_id varchar(10), version varchar(3),
+   eq_time varchar(50), latitude double precision, longitude double precision, \
+   magnitude double precision, depth double precision, num_stations_obs integer,
+   region varchar(255)"
 
-paste -d, "$INPUT" "$INPUT.wintri.coord" > "$INPUT.wintri"
+cut -f5,6 -d'|' "$INPUT" | awk -F'|' '{print $2 "\t" $1}' | \
+   m.proj -ig fs='|' | cut -f1,2 -d'|' | \
+   awk '{if (NR!=1) {print} else {print "easting|northing"}}' \
+   > "$INPUT.wintri.coord"
 
[…]

### 2013-03-13 grassposter/2013_EGU_G7/poster.tex
added poster for EGU 2013 on image processing in Grass 7
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55346 15284696-431f-4ddb-bdfa-cd5b030d7da7

\documentclass{a0poster}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikzposter} % here most of the things are defined
% change parameters only after this line You can also start a new column with an arbitrary 
% x-coordinate by specifying explicitly the coordinate of the new block node as follows:
\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage{wrapfig}
\usepackage{url}

\usepackage[margin=\margin cm, paperwidth=84.1cm, paperheight=118.9cm]{geometry}

% \setbackgrounddarkcolor{ForestGreen!70!black}
% \setbackgroundlightcolor{YellowGreen!90!}

% \setfirstcolor{YellowGreen!80!}
% \setsecondcolor{gray!80!}
% \setthirdcolor{red!80!black}

\title{GRASS image processing environment\\ Gearing towards GRASS 7}
\author{Yann Chemin\\
International Water Management Institute}

\usetemplate{1}
\setinstituteshift{1}

\setblocktitleheight{2}
\setblockspacing{1}

\begin{document}
\ClearShipoutPicture
\AddToShipoutPicture{\BackgroundPicture}
\noindent
\tikzstyle{every picture}+=[remember picture]
\begin{tikzpicture}
\initializesizeandshifts
\titleblock{73.8}{1}
% \setblocktitleheight{1}

\addlogo[north west]{(2,-1)}{9cm}{./images/Grass_GIS.png}
\addlogo[north east]{(-2,-2.5)}{11cm}{./images/iwmi.png}

\blocknode{Abstract}{
\small GRASS 7 started its development by the branching out of GRASS 6.x from the main trunk of code (rev 31142).
This was done on 27th of April 2008, and a large amount of changes took place since that date, more 
are still underway.
\begin{itemize}
 \item Display library in GRASS 7 (planning \& ongoing)
 \item Raster library in GRASS 7 (planning \& ongoing)
 \item Vector library in GRASS 7 (planning \& ongoing)
 \item G3d (volume) library and modules in GRASS 7 (finished)
 \item Temporal extension for GRASS 7 (planning state) 
\end{itemize}

GRASS GIS capacity in remote sensing has also been under great changes and additions for version 7.
}

\blocknode{Linear features extraction}{
\small
An edge is considered as a change in image digital values.
Edge detection \& extraction in i.canny is done by a Canny edge detector [1]. 
The Canny edge detector encompasses Gaussian smoothing, 
gradient computation \& non-maximum suppression. \newline
This creates thin edges and thresholding with hysteresis which
preserves only important edges. Thus, no pre- or post-processing is required.
The produced binary image shows boundaries of areas in the input image
which is usually a gray scale image e.g., intensity channel or the
result of PCA.\newline
The i.edge module is suitable as a first step in building or road detection.
The level of details of the output image is easily customizable.
\begin{center}
 \includegraphics[width=0.48\textwidth]{./images/imagery_spot_original}
 \hspace{10mm}
 \includegraphics[width=0.48\textwidth]{./images/imagery_spot_edge_1}
 \newline
 Figure 1: Canny edge detector on a road network [1]
\end{center}
}

\blocknode{Object recognition}{
\small The module i.segment is a region growing image segmentation algorithm [2].
It produces a raster map with segments (objects), and optionally other maps with segments statistics 
(mean/variance/range/etc.). 
\begin{center}
 \includegraphics[width=0.48\textwidth]{./images/sltsu.png}
 \hspace{10mm}
 \includegraphics[width=0.48\textwidth]{./images/sltsu_seg.png}
 \newline
 Figure 2: Image segmentation (2.4x2.4m) of the 2004 tsunami wave, West Coast Sri Lanka
\end{center}
}

\blocknode{Satellite imagery products}{
\innerblockplain[colortwo!80!]{
\small
\begin{itemize}
 \item {\bf i.vi} 15 vegetation indices available
 \item {\bf i.albedo} Broadband Albedo (snow \~= 0.6-0.8, water=0.05)
 \item {\bf i.emissivity} Emissivity approximation from vegetation index
 \item {\bf i.biomass} biomass growth for crop yield
\end{itemize}

{\bf Reference/Potential ET: i.evapo.* modules}

\begin{itemize}
 \item {\bf i.evapo.mh} ETo Hargreaves, modified-Hargreaves \& Hargreaves-Samani 
 \item {\bf i.evapo.pm} ETo Penman-Monteith
 \item {\bf i.evapo.pt} ETpot Priestley-Taylor
\end{itemize}

{\bf Actual ET: i.eb.* modules using thermodynamic heat flux modeling}

% \begin{equation}\label{eq1}
% \Lambda = \frac {Rn - G - H} {Rn - G}
% \end{equation}
% 
% \begin{equation}\label{eq2}
% ET_a = \Lambda \, ET_{potential}
% \end{equation}

\begin{center}
 \includegraphics[width=0.38\textwidth]{./images/slet2005}
 \hspace{20mm}
 \includegraphics[width=0.38\textwidth]{./images/slet2010}
 \newline
 Figure 3: Actual evapotranspiration (i.eb.*) for water monitoring and management [3]
\end{center}
}
\vspace*{-25pt}
}

\startsecondcolumn

\blocknode{Interactive supervised classification}{
\innerblockplain[colortwo!80!]{
\small 
This interactive tool [4], aims at greatly simplifying quantitative surpervised class training areas creation.
It calculates the spectral signatures based on the cells within the specified areas. 
The resulting signature file can be used by a maximum likelihood classification module (i.maxlik). 
During the process the user is shown a histogram of the area cell values for each image band, 
and coincident plot which shows the separability of classes.\newline
Another way the user can inspect the suitability of the created training areas 
is by displaying the cells of the image bands which fall within a user-specified 
number of standard deviations from the means in the spectral signature. This
helps to estimate how much of the image is likely to be classified as a particular class.\newline
\begin{center}
 \includegraphics[width=0.47\textwidth]{./images/wxiclass1.png}
 \hspace{10mm}
 \includegraphics[width=0.47\textwidth]{./images/wxiclass2.png}
 \newline
 Figure 4: Interactive image classification with coincidence plots (left side) \& histograms (right side)
\end{center}
}
\hspace*{-25pt}
}

\blocknode{Lidar}{
\medskip
\innerblockplain[colortwo!80!]{
\small The Lidar library ({\url {www.liblas.org}}) included in GRASS GIS permits the import of Lidar (.las)
data in raster (r.in.lidar using statistics of choice) or in vector format (v.in.lidar). 
Author Markus Metz tested r.in.lidar with a 705Gb .las file. \newline
On-farm water storage study with lidar data in NSW (Australia) permitted to develop the 
first full remote sensing monitoring methodology of water availability by a combination of 
lidar-based bathymetric survey and multi-source remote sensing water area regular survey [5].\newline
\begin{center}
 \includegraphics[width=0.4\textwidth]{./images/ofs1}
 \hspace{10mm}
 \includegraphics[width=0.275\textwidth]{./images/ofs2}
 \newline
 Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [5]
\end{center}
}
\vspace*{-25pt}
}
\blocknode{Other Improvements \& Additions}{
\medskip
\innerblockplain[colortwo!80!]{
\small

{\bf Remanufacturing, performance improvement}

\begin{itemize}
 \item {\bf i.ortho.rectify} new rewritten \& optimized version of i.ortho.photo
 \item {\bf i.atcorr} atmospheric correction, more satellite sensors configured, faster
 \item {\bf i.pca} backward modeling implemented 
\end{itemize}
\vspace{15pt}
{\bf Preparing Landsat, Aster and MODIS datasets}

\begin{itemize}
 \item {\bf i.landsat.toar} TOA reflectance correction for Landsat satellite series
 \item {\bf i.aster.toar} TOA reflectance correction for Terra-ASTER
 \item {\bf i.modis.qc} Quality flag interpretation for Terra/Aqua MODIS
\end{itemize}
\vspace{15pt}
{\bf Geographical and astronomic functions}

\begin{itemize}
 \item {\bf i.latlong} maps latitude or longitude (dd.ddd)
 \item {\bf i.sunhours} maps potential hours of sunshine in a day at a given location (hh.hhh)
\end{itemize}
\vspace{15pt}
{\bf Temporal cleaning and smoothing}

A dedicated time-series environment (modules starting with t.*) is being developed for GRASS 7, 
the following functions initially developed for NDVI temporal interpolation and maximization might 
find their way in the t.* modules.
\begin{itemize}
 \item {\bf r.hants} Fourier temporal smoothing
 \item {\bf i.lmf} Local maximum fitting of temporal data
\end{itemize}
}
\vspace*{-25pt}
}

% \initializesizeandshifts
\getcurrentrow{box}
\coordinate (funkcionalita) at (box.south west);
\coordinate (funkcionalitaeast) at (box.east);
\coordinate (screenshot) at (box.north west);
% \getcurrentrow{box}
\blocknodew[($(funkcionalita)+(25,-1)$)]{25}{References}{
\scriptsize
\begin{center}
\begin{tabular}{rp{0.8\textwidth}}
[1] & Petráš, 2012. M.Sc. Thesis, OSGeoREL, FCE CTU, Prague.\\{}
[2] & Momsen \& Metz, 2012. i.segment module. Geographic Resources
Analysis Support System (GRASS GIS) Software, Version 7.\\{}
[3] & Chemin, 2012. Chapter 19, DOI: 10.5772/23571 ({\url {http://bit.ly/16qJOep}})\\{}
[4] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
[5] & Chemin \& Rabbani, 2011. International Journal of Geoinformatics,  7(3):1-6pp.
\end{tabular}
\end{center}
\smallskip
\hrulefill
\vspace{-5pt}

\begin{center}
\begin{tabular}{cp{0.9\textwidth}}
\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/iwmiqr.png}
\end{minipage}

\begin{minipage}{0.3\textwidth}
\small {\url{www.iwmi.org}}
\end{minipage}

\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/Grass_qr.png}
\end{minipage}

\begin{minipage}{0.3\textwidth}
\small {\url{grass.osgeo.org}}
\end{minipage}
\end{tabular}
\end{center}

\hrulefill
\vspace{14pt}

\newcommand{\logowidth}{0.65em}
\newcommand{\logospace}{\hspace{0.1em}}
\noindent
\includegraphics[width=\logowidth]{./images/public_domain_logo.png}
\logospace Public Domain 2013 GRASS Development Team
}

\end{tikzpicture}

\end{document}

### 2013-03-13 grassposter/2013_EGU_G7/poster.tex
pdf qr codes instead of png
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55349 15284696-431f-4ddb-bdfa-cd5b030d7da7
Modified the status of temporal GIS to -finished-
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55351 15284696-431f-4ddb-bdfa-cd5b030d7da7
2013_EGU_G7: use vector logos
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55352 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-\addlogo[north west]{(2,-1)}{9cm}{./images/Grass_GIS.png}
-\addlogo[north east]{(-2,-2.5)}{11cm}{./images/iwmi.png}
+\addlogo[north west]{(2,-1)}{9cm}{./images/Grass_GIS.pdf}
+\addlogo[north east]{(-2,-2.5)}{11cm}{./images/IWMI_logo.pdf}
 
@@
  \item G3d (volume) library and modules in GRASS 7 (finished)
- \item Temporal extension for GRASS 7 (planning state) 
+ \item Temporal extension for GRASS 7 (finished) 
 \end{itemize}
@@
 \begin{minipage}{0.15\textwidth}
-\includegraphics[width=0.7in]{./images/iwmiqr.png}
+\includegraphics[width=0.7in]{./images/iwmi_qr.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.15\textwidth}
-\includegraphics[width=0.7in]{./images/Grass_qr.png}
+\includegraphics[width=0.7in]{./images/grass_qr.pdf}
 \end{minipage}

### 2013-03-13 grassposter/2013_EGU_G7/poster.tex
2013_EGU_G7: converting svg to pdf in Makefile; added public domain logo
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55353 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-\addlogo[north west]{(2,-1)}{9cm}{./images/Grass_GIS.pdf}
-\addlogo[north east]{(-2,-2.5)}{11cm}{./images/IWMI_logo.pdf}
+\addlogo[north west]{(2,-1)}{9cm}{./svg_images/Grass_GIS.pdf}
+\addlogo[north east]{(-2,-2.5)}{11cm}{./svg_images/IWMI_logo.pdf}
 
@@
 \vspace{14pt}
-
-\newcommand{\logowidth}{0.65em}
+\begin{center}
+\newcommand{\logowidth}{5em}
 \newcommand{\logospace}{\hspace{0.1em}}
 \noindent
-\includegraphics[width=\logowidth]{./images/public_domain_logo.png}
-\logospace Public Domain 2013 GRASS Development Team
+\includegraphics[width=\logowidth]{./svg_images/public_domain_logo.pdf}
+\raisebox{0.7\height}{\logospace 2013 GRASS Development Team}
+\end{center}
 }

### 2013-03-13 grassposter/2013_EGU_G7/poster.tex
2013_EGU_G7: cleaning from negative vspaces and innerblocks
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55354 15284696-431f-4ddb-bdfa-cd5b030d7da7
GRASS -> GRASS GIS in titles
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55365 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-\title{GRASS image processing environment\\ Gearing towards GRASS 7}
+\title{GRASS GIS image processing environment\\ Gearing towards GRASS GIS 7}
 \author{Yann Chemin\\
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \blocknode{Abstract}{
-\small GRASS 7 started its development by the branching out of GRASS 6.x from the main trunk of code (rev 31142).
+\small GRASS GIS 7 started its development by the branching out of GRASS GIS 6.x from the main trunk of code (rev 31142).
 This was done on 27th of April 2008, and a large amount of changes took place since that date, more 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \blocknode{Linear features extraction}{
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \blocknode{Object recognition}{
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \blocknode{Satellite imagery products}{
-\innerblockplain[colortwo!80!]{
 \small
@@
 }
-\vspace*{-25pt}
-}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \blocknode{Interactive supervised classification}{
-\innerblockplain[colortwo!80!]{
 \small 
@@
 }
-\hspace*{-25pt}
-}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \blocknode{Lidar}{
 \medskip
-\innerblockplain[colortwo!80!]{
 \small The Lidar library ({\url {www.liblas.org}}) included in GRASS GIS permits the import of Lidar (.las)
@@
 }
-\vspace*{-25pt}
-}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \blocknode{Other Improvements \& Additions}{
 \medskip
-\innerblockplain[colortwo!80!]{
 \small
@@
 }
-\vspace*{-25pt}
-}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % \initializesizeandshifts

### 2013-03-13 grassposter/2013_EGU_G7/poster.tex
+Intro; +i.spec.unmix
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55368 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \blocknode{Abstract}{
-\small GRASS GIS 7 started its development by the branching out of GRASS GIS 6.x from the main trunk of code (rev 31142).
+\small GRASS GIS, commonly referred to as GRASS (Geographic Resources Analysis Support System), is a free Geographic Information System (GIS) software used for geospatial data management and analysis, image processing, graphics/maps production, spatial modeling, and visualization [1].
+
+GRASS GIS 7 started its development by the branching out of GRASS GIS 6.x from the main trunk of code (rev 31142).
 This was done on 27th of April 2008, and a large amount of changes took place since that date, more 
@@
 \begin{itemize}
- \item Display library in GRASS 7 (planning \& ongoing)
- \item Raster library in GRASS 7 (planning \& ongoing)
- \item Vector library in GRASS 7 (planning \& ongoing)
- \item G3d (volume) library and modules in GRASS 7 (finished)
+% commented, not that important
+% \item Display library in GRASS 7 (planning \& ongoing)
+ \item Raster library in GRASS 7 (ongoing)
+ \item Vector library in GRASS 7 (ongoing)
+ \item Raster3D (volume) library and modules in GRASS 7 (finished)
  \item Temporal extension for GRASS 7 (finished) 
@@
 
-GRASS GIS capacity in remote sensing has also been under great changes and additions for version 7.
+GRASS GIS' capacity in remote sensing has also been greatly improved with additions for version 7.
 }
@@
 An edge is considered as a change in image digital values.
-Edge detection \& extraction in i.canny is done by a Canny edge detector [1]. 
+Edge detection \& extraction in i.canny is done by a Canny edge detector [2]. 
 The Canny edge detector encompasses Gaussian smoothing, 
@@
  \newline
- Figure 1: Canny edge detector on a road network [1]
+ Figure 1: Canny edge detector on a road network [2]
 \end{center}
@@
 \blocknode{Object recognition}{
-\small The module i.segment is a region growing image segmentation algorithm [2].
+\small The module i.segment is a region growing image segmentation algorithm [3].
 It produces a raster map with segments (objects), and optionally other maps with segments statistics 
@@
 \begin{center}
- \includegraphics[width=0.38\textwidth]{./images/slet2005}
+ \includegraphics[width=0.32\textwidth]{./images/slet2005}
  \hspace{20mm}
- \includegraphics[width=0.38\textwidth]{./images/slet2010}
+ \includegraphics[width=0.32\textwidth]{./images/slet2010}
  \newline
- Figure 3: Actual evapotranspiration (i.eb.*) for water monitoring and management [3]
+ Figure 3: Actual evapotranspiration (i.eb.*) for water monitoring and management [4]
 \end{center}
@@
 \small 
-This interactive tool [4], aims at greatly simplifying quantitative surpervised class training areas creation.
+This interactive tool [5], aims at greatly simplifying quantitative surpervised class training areas creation.
 It calculates the spectral signatures based on the cells within the specified areas. 
@@
 first full remote sensing monitoring methodology of water availability by a combination of 
-lidar-based bathymetric survey and multi-source remote sensing water area regular survey [5].\newline
+lidar-based bathymetric survey and multi-source remote sensing water area regular survey [6].\newline
 \begin{center}
@@
  \newline
- Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [5]
+ Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [6]
 \end{center}
@@
 
-A dedicated time-series environment (modules starting with t.*) is being developed for GRASS 7, 
-the following functions initially developed for NDVI temporal interpolation and maximization might 
-find their way in the t.* modules.
+%%% Since being the only comment, taken out to gain vertical space:
+% A dedicated time-series environment (modules starting with t.*) is being developed for GRASS 7, 
+% the following functions initially developed for NDVI temporal interpolation and maximization might 
+% find their way in the t.* modules.
 \begin{itemize}
@@
  \item {\bf i.lmf} Local maximum fitting of temporal data
+\end{itemize}
+\vspace{15pt}
+{\bf Multi- and hyperspectral data analysis}
+
+\begin{itemize}
+ \item {\bf i.spec.unmix} Spectral Unmixing
 \end{itemize}
@@
 % \getcurrentrow{box}
-\blocknodew[($(funkcionalita)+(25,-1)$)]{25}{References}{
+\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
 \scriptsize
 \begin{center}
-\begin{tabular}{rp{0.8\textwidth}}
-[1] & Petráš, 2012. M.Sc. Thesis, OSGeoREL, FCE CTU, Prague.\\{}
-[2] & Momsen \& Metz, 2012. i.segment module. Geographic Resources
+\begin{tabular}{rp{0.9\textwidth}}
+[1] & Neteler \& Bowman \&  Landa \& Metz, 2012: GRASS GIS: a multi-purpose
+Open Source GIS. Environ Model Soft, 31:124-130\\{}
+% , DOI: 10.1016/j.envsoft.2011.11.014.\\{}
+[2] & Petráš, 2012. M.Sc. Thesis, OSGeoREL, FCE CTU, Prague.\\{}
+[3] & Momsen \& Metz, 2012. i.segment module. Geographic Resources
 Analysis Support System (GRASS GIS) Software, Version 7.\\{}
-[3] & Chemin, 2012. Chapter 19, DOI: 10.5772/23571 ({\url {http://bit.ly/16qJOep}})\\{}
-[4] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
-[5] & Chemin \& Rabbani, 2011. International Journal of Geoinformatics,  7(3):1-6pp.
+[4] & Chemin, 2012. Chapter 19, DOI: 10.5772/23571 ({\url {http://bit.ly/16qJOep}})\\{}
+[5] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
+[6] & Chemin \& Rabbani, 2011. International Journal of Geoinformatics,  7(3):1-6pp.
 \end{tabular}

### 2013-03-14 grassposter/2013_EGU_G7/poster.tex
Segmentation text and references addition, clean up
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55373 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \blocknode{Abstract}{
-\small GRASS GIS, commonly referred to as GRASS (Geographic Resources Analysis Support System), is a free Geographic Information System (GIS) software used for geospatial data management and analysis, image processing, graphics/maps production, spatial modeling, and visualization [1].
+\small GRASS GIS, commonly referred to as GRASS (Geographic Resources Analysis Support System),
+is a free Geographic Information System (GIS) software used for geospatial data management and analysis,
+image processing, graphics/maps production, spatial modeling, and visualization [1].
 
@@
 \begin{itemize}
-% commented, not that important
-% \item Display library in GRASS 7 (planning \& ongoing)
  \item Raster library in GRASS 7 (ongoing)
@@
 \blocknode{Object recognition}{
-\small The module i.segment is a region growing image segmentation algorithm [3].
-It produces a raster map with segments (objects), and optionally other maps with segments statistics 
-(mean/variance/range/etc.). 
+\small The module i.segment [3] is using a region growing algorithm [4], some ideas 
+have also been implemented from [5]. It produces a raster map with segments (objects), 
+and optionally other maps with segments statistics (mean/variance/range/etc.). 
 \begin{center}
@@
 
-% \begin{equation}\label{eq1}
-% \Lambda = \frac {Rn - G - H} {Rn - G}
-% \end{equation}
-% 
-% \begin{equation}\label{eq2}
-% ET_a = \Lambda \, ET_{potential}
-% \end{equation}
-
 \begin{center}
- \includegraphics[width=0.32\textwidth]{./images/slet2005}
+ \includegraphics[width=0.315\textwidth]{./images/slet2005}
  \hspace{20mm}
- \includegraphics[width=0.32\textwidth]{./images/slet2010}
+ \includegraphics[width=0.315\textwidth]{./images/slet2010}
  \newline
- Figure 3: Actual evapotranspiration (i.eb.*) for water monitoring and management [4]
+ Figure 3: Actual evapotranspiration (i.eb.*) for water monitoring and management [6]
 \end{center}
@@
 \small 
-This interactive tool [5], aims at greatly simplifying quantitative surpervised class training areas creation.
+This interactive tool [7], aims at greatly simplifying quantitative surpervised class training areas creation.
 It calculates the spectral signatures based on the cells within the specified areas. 
@@
 Author Markus Metz tested r.in.lidar with a 705Gb .las file. \newline
-On-farm water storage study with lidar data in NSW (Australia) permitted to develop the 
-first full remote sensing monitoring methodology of water availability by a combination of 
-lidar-based bathymetric survey and multi-source remote sensing water area regular survey [6].\newline
+On-farm water storage study with lidar data in NSW (Australia) developed a full remote sensing monitoring methodology
+of water availability with lidar-based bathymetric survey and multi-source remote sensing survey [8].\newline
 \begin{center}
@@
  \newline
- Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [6]
+ Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]
 \end{center}
@@
 \blocknode{Other Improvements \& Additions}{
-\medskip
+\smallskip
 \small
@@
 \end{itemize}
-\vspace{15pt}
+
 {\bf Preparing Landsat, Aster and MODIS datasets}
@@
 \end{itemize}
-\vspace{15pt}
+
 {\bf Geographical and astronomic functions}
@@
  \item {\bf i.sunhours} maps potential hours of sunshine in a day at a given location (hh.hhh)
+ \item {\bf r.sun.angle} maps the sun elevation and sun azimuth angles for the given time of day
 \end{itemize}
-\vspace{15pt}
+
 {\bf Temporal cleaning and smoothing}
 
-%%% Since being the only comment, taken out to gain vertical space:
-% A dedicated time-series environment (modules starting with t.*) is being developed for GRASS 7, 
-% the following functions initially developed for NDVI temporal interpolation and maximization might 
-% find their way in the t.* modules.
 \begin{itemize}
@@
 \end{itemize}
-\vspace{15pt}
+
 {\bf Multi- and hyperspectral data analysis}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \initializesizeandshifts
 \getcurrentrow{box}
@@
 \coordinate (screenshot) at (box.north west);
-% \getcurrentrow{box}
 \blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
@@
 \begin{tabular}{rp{0.9\textwidth}}
-[1] & Neteler \& Bowman \&  Landa \& Metz, 2012: GRASS GIS: a multi-purpose
-Open Source GIS. Environ Model Soft, 31:124-130\\{}
-% , DOI: 10.1016/j.envsoft.2011.11.014.\\{}
+[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
 [2] & Petráš, 2012. M.Sc. Thesis, OSGeoREL, FCE CTU, Prague.\\{}
-[3] & Momsen \& Metz, 2012. i.segment module. Geographic Resources
-Analysis Support System (GRASS GIS) Software, Version 7.\\{}
-[4] & Chemin, 2012. Chapter 19, DOI: 10.5772/23571 ({\url {http://bit.ly/16qJOep}})\\{}
-[5] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
-[6] & Chemin \& Rabbani, 2011. International Journal of Geoinformatics,  7(3):1-6pp.
+[3] & Momsen \& Metz, 2012. i.segment module. GRASS GIS Software, Version 7.\\{}
+[4] & Sant'Anna Bins \& Fonseca \& Erthal \& Misuo, 1996. Anais VIII Simpósio Brasileiro de Sensoria.
+Rem., Salvador, Brasil, INPE, 677-680.\\{}
+[5] & Athelogou \& Schmidt \& Schäpe \& Baatz \& Binnig, 2007. Imaging Cellular \& Molecular Biological
+Functions, 407-422.\\{}
+[6] & Chemin, 2012. Chapter 19, DOI: 10.5772/23571 ({\url {http://bit.ly/16qJOep}})\\{}
+[7] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
+[8] & Chemin \& Rabbani, 2011. International Journal of Geoinformatics,  7(3):1-6.
 \end{tabular}

### 2013-03-18 grassposter/2013_EGU_G7_Landscape/poster.tex
Rotated poster enabled tikzposter was indeed very designed...
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55375 15284696-431f-4ddb-bdfa-cd5b030d7da7
4 columns done, not nice code but it works
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55414 15284696-431f-4ddb-bdfa-cd5b030d7da7
Added temporal cleaning section
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55418 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2013-03-14 grassposter/2013_EGU_G7/poster.tex
@@
-\documentclass{a0poster}
+\documentclass[landscape,a0,final]{a0poster}
 \usepackage[dvipsnames,svgnames]{xcolor}
@@
 
-\usepackage[margin=\margin cm, paperwidth=84.1cm, paperheight=118.9cm]{geometry}
+\usepackage[margin=\margin cm, paperwidth=197cm, paperheight=100cm]{geometry}
 
@@
 
+\startsecondcolumn
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Interactive supervised classification}{
+\small 
+This interactive tool [7], aims at greatly simplifying quantitative surpervised class training areas creation.
+It calculates the spectral signatures based on the cells within the specified areas. 
+The resulting signature file can be used by a maximum likelihood classification module (i.maxlik). 
+During the process the user is shown a histogram of the area cell values for each image band, 
+and coincident plot which shows the separability of classes.\newline
+Another way the user can inspect the suitability of the created training areas 
+is by displaying the cells of the image bands which fall within a user-specified 
+number of standard deviations from the means in the spectral signature. This
+helps to estimate how much of the image is likely to be classified as a particular class.\newline
+\begin{center}
+ \includegraphics[width=0.47\textwidth]{./images/wxiclass1.png}
+ \hspace{10mm}
+ \includegraphics[width=0.47\textwidth]{./images/wxiclass2.png}
+ \newline
+ Figure 3: Interactive image classification with coincidence plots (left side) \& histograms (right side)
+\end{center}
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{center}
- \includegraphics[width=0.315\textwidth]{./images/slet2005}
+ \includegraphics[width=0.4\textwidth]{./images/slet2005}
  \hspace{20mm}
- \includegraphics[width=0.315\textwidth]{./images/slet2010}
+ \includegraphics[width=0.4\textwidth]{./images/slet2010}
  \newline
- Figure 3: Actual evapotranspiration (i.eb.*) for water monitoring and management [6]
+ Figure 4: Actual evapotranspiration (i.eb.*) for water monitoring and management [6]
 \end{center}
@@
 
-\startsecondcolumn
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Interactive supervised classification}{
-\small 
-This interactive tool [7], aims at greatly simplifying quantitative surpervised class training areas creation.
-It calculates the spectral signatures based on the cells within the specified areas. 
-The resulting signature file can be used by a maximum likelihood classification module (i.maxlik). 
-During the process the user is shown a histogram of the area cell values for each image band, 
-and coincident plot which shows the separability of classes.\newline
-Another way the user can inspect the suitability of the created training areas 
-is by displaying the cells of the image bands which fall within a user-specified 
-number of standard deviations from the means in the spectral signature. This
-helps to estimate how much of the image is likely to be classified as a particular class.\newline
-\begin{center}
- \includegraphics[width=0.47\textwidth]{./images/wxiclass1.png}
- \hspace{10mm}
- \includegraphics[width=0.47\textwidth]{./images/wxiclass2.png}
- \newline
- Figure 4: Interactive image classification with coincidence plots (left side) \& histograms (right side)
-\end{center}
-}
-
+\startthirdcolumn
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\blocknode{Temporal signature cleaning}{
+\medskip
+\begin{itemize}
+ \item r.hants produces a harmonic analysis through incomplete returned Fourier inversion.
+ \item i.lmf computes a temporal Local Maximum Fitting with Akaike Information Content.
+\end{itemize}
+
+\begin{center}
+ \includegraphics[width=0.8\textwidth]{./images/lmf0}\newline
+ \vspace{10mm}
+ \includegraphics[width=0.8\textwidth]{./images/lmf1}
+ \newline
+ Figure 6: pre and post LMF temporal filter
+\end{center}
+}
+
+\startfourthcolumn
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \coordinate (screenshot) at (box.north west);
+
 \blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{

### 2013-03-19 grassposter/2013_EGU_G7_Landscape/poster.tex
Added two blocks: unmix and floodrisk
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55434 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-\startsecondcolumn
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Interactive supervised classification}{
-\small 
-This interactive tool [7], aims at greatly simplifying quantitative surpervised class training areas creation.
-It calculates the spectral signatures based on the cells within the specified areas. 
-The resulting signature file can be used by a maximum likelihood classification module (i.maxlik). 
-During the process the user is shown a histogram of the area cell values for each image band, 
-and coincident plot which shows the separability of classes.\newline
-Another way the user can inspect the suitability of the created training areas 
-is by displaying the cells of the image bands which fall within a user-specified 
-number of standard deviations from the means in the spectral signature. This
-helps to estimate how much of the image is likely to be classified as a particular class.\newline
-\begin{center}
- \includegraphics[width=0.47\textwidth]{./images/wxiclass1.png}
- \hspace{10mm}
- \includegraphics[width=0.47\textwidth]{./images/wxiclass2.png}
- \newline
- Figure 3: Interactive image classification with coincidence plots (left side) \& histograms (right side)
-\end{center}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Satellite imagery products}{
-\small
-\begin{itemize}
- \item {\bf i.vi} 15 vegetation indices available
- \item {\bf i.albedo} Broadband Albedo (snow \~= 0.6-0.8, water=0.05)
- \item {\bf i.emissivity} Emissivity approximation from vegetation index
- \item {\bf i.biomass} biomass growth for crop yield
-\end{itemize}
-
-{\bf Reference/Potential ET: i.evapo.* modules}
-
-\begin{itemize}
- \item {\bf i.evapo.mh} ETo Hargreaves, modified-Hargreaves \& Hargreaves-Samani 
- \item {\bf i.evapo.pm} ETo Penman-Monteith
- \item {\bf i.evapo.pt} ETpot Priestley-Taylor
-\end{itemize}
-
-{\bf Actual ET: i.eb.* modules using thermodynamic heat flux modeling}
-
-\begin{center}
- \includegraphics[width=0.4\textwidth]{./images/slet2005}
- \hspace{20mm}
- \includegraphics[width=0.4\textwidth]{./images/slet2010}
- \newline
- Figure 4: Actual evapotranspiration (i.eb.*) for water monitoring and management [6]
-\end{center}
-}
-
-\startthirdcolumn
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Lidar}{
-\medskip
-\small The Lidar library ({\url {www.liblas.org}}) included in GRASS GIS permits the import of Lidar (.las)
-data in raster (r.in.lidar using statistics of choice) or in vector format (v.in.lidar). 
-Author Markus Metz tested r.in.lidar with a 705Gb .las file. \newline
-On-farm water storage study with lidar data in NSW (Australia) developed a full remote sensing monitoring methodology
-of water availability with lidar-based bathymetric survey and multi-source remote sensing survey [8].\newline
-\begin{center}
- \includegraphics[width=0.4\textwidth]{./images/ofs1}
- \hspace{10mm}
- \includegraphics[width=0.275\textwidth]{./images/ofs2}
- \newline
- Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]
-\end{center}
-}
-
-\blocknode{Temporal signature cleaning}{
-\medskip
-\begin{itemize}
- \item r.hants produces a harmonic analysis through incomplete returned Fourier inversion.
- \item i.lmf computes a temporal Local Maximum Fitting with Akaike Information Content.
-\end{itemize}
-
-\begin{center}
- \includegraphics[width=0.8\textwidth]{./images/lmf0}\newline
- \vspace{10mm}
- \includegraphics[width=0.8\textwidth]{./images/lmf1}
- \newline
- Figure 6: pre and post LMF temporal filter
-\end{center}
-}
-
-\startfourthcolumn
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Other Improvements \& Additions}{
-\smallskip
-\small
-
-{\bf Remanufacturing, performance improvement}
-
-\begin{itemize}
- \item {\bf i.ortho.rectify} new rewritten \& optimized version of i.ortho.photo
- \item {\bf i.atcorr} atmospheric correction, more satellite sensors configured, faster
- \item {\bf i.pca} backward modeling implemented 
-\end{itemize}
-
-{\bf Preparing Landsat, Aster and MODIS datasets}
-
-\begin{itemize}
- \item {\bf i.landsat.toar} TOA reflectance correction for Landsat satellite series
- \item {\bf i.aster.toar} TOA reflectance correction for Terra-ASTER
- \item {\bf i.modis.qc} Quality flag interpretation for Terra/Aqua MODIS
-\end{itemize}
-
-{\bf Geographical and astronomic functions}
-
-\begin{itemize}
- \item {\bf i.latlong} maps latitude or longitude (dd.ddd)
- \item {\bf i.sunhours} maps potential hours of sunshine in a day at a given location (hh.hhh)
- \item {\bf r.sun.angle} maps the sun elevation and sun azimuth angles for the given time of day
-\end{itemize}
-
-{\bf Temporal cleaning and smoothing}
-
-\begin{itemize}
- \item {\bf r.hants} Fourier temporal smoothing
- \item {\bf i.lmf} Local maximum fitting of temporal data
-\end{itemize}
-
-{\bf Multi- and hyperspectral data analysis}
-
-\begin{itemize}
- \item {\bf i.spec.unmix} Spectral Unmixing
-\end{itemize}
-}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 [7] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
-[8] & Chemin \& Rabbani, 2011. International Journal of Geoinformatics,  7(3):1-6.
+[8] & Chemin \& Rabbani, 2011. International Journal of Geoinformatics,  7(3):1-6.\\{}
+[9] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. 
+International Journal of Geoinformatics, 1(1): 51-61.\\{}
+[10] & Chemin \& Phuphak \& Asilo \& Hijmans, 2012. International Journal of GeoInformatics. 8(1):1-12.
 \end{tabular}
@@
 
+\startsecondcolumn
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Interactive supervised classification}{
+This interactive tool [7], aims at greatly simplifying quantitative surpervised class training areas creation.
+It calculates the spectral signatures based on the cells within the specified areas. 
+The resulting signature file can be used by a maximum likelihood classification module (i.maxlik). 
+During the process the user is shown a histogram of the area cell values for each image band, 
+and coincident plot which shows the separability of classes.\newline\linebreak
+Another way the user can inspect the suitability of the created training areas 
+is by displaying the cells of the image bands which fall within a user-specified 
+number of standard deviations from the means in the spectral signature. This
+helps to estimate how much of the image is likely to be classified as a particular class.\newline
+\begin{center}
+ \includegraphics[width=0.47\textwidth]{./images/wxiclass1.png}
+ \hspace{10mm}
+ \includegraphics[width=0.47\textwidth]{./images/wxiclass2.png}
+ \newline
+ Figure 3: Interactive image classification with coincidence plots (left side) \& histograms (right side)
+\end{center}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Satellite imagery products}{
+\begin{itemize}
+ \item {\bf i.vi} 15 vegetation indices available
+ \item {\bf i.albedo} Broadband Albedo (snow \~= 0.6-0.8, water=0.05)
+ \item {\bf i.emissivity} Emissivity approximation from vegetation index
+ \item {\bf i.biomass} biomass growth for crop yield
+\end{itemize}
+
+{\bf Reference/Potential ET: i.evapo.* modules}
+
+\begin{itemize}
+ \item {\bf i.evapo.mh} ETo Hargreaves, modified-Hargreaves \& Hargreaves-Samani 
+ \item {\bf i.evapo.pm} ETo Penman-Monteith
+ \item {\bf i.evapo.pt} ETpot Priestley-Taylor
+\end{itemize}
+
+{\bf Actual ET: i.eb.* modules using thermodynamic heat flux modeling}
+
+\begin{center}
+ \includegraphics[width=0.45\textwidth]{./images/slet2005}
+ \hspace{20mm}
+ \includegraphics[width=0.45\textwidth]{./images/slet2010}
+ \newline
+ Figure 4: Actual evapotranspiration (i.eb.*) for water monitoring and management [6]
+\end{center}
+}
+
+\startthirdcolumn
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Lidar}{
+\smallskip
+The Lidar library ({\url {www.liblas.org}}) included in GRASS GIS permits the import of Lidar (.las)
+data in raster (r.in.lidar using statistics of choice) or in vector format (v.in.lidar). 
+Author Markus Metz tested r.in.lidar with a 705Gb .las file. \newline
+On-farm water storage study with lidar data in NSW (Australia) developed a full remote sensing monitoring methodology
+of water availability with lidar-based bathymetric survey and multi-source remote sensing survey [8].\newline
+\begin{center}
+ \includegraphics[width=0.4\textwidth]{./images/ofs1}
+ \hspace{10mm}
+ \includegraphics[width=0.275\textwidth]{./images/ofs2}
+ \newline
+ Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]
+\end{center}
+}
+
+\blocknode{Temporal signature cleaning}{
+\smallskip
+\begin{itemize}
+ \item r.hants produces a harmonic analysis through incomplete returned Fourier inversion.
+ \item i.lmf computes a temporal Local Maximum Fitting with Akaike Information Content.
+\end{itemize}
+
+\begin{center}
+ \includegraphics[width=0.8\textwidth]{./images/lmf0}\newline
+ \vspace{10mm}
+ \includegraphics[width=0.8\textwidth]{./images/lmf1}
+ \newline
+ Figure 6: pre and post LMF temporal filter
+\end{center}
+}
+
+\blocknode{Other Improvements \& Additions}{
+\smallskip
+
+{\bf Remanufacturing, performance improvement}
+
+\begin{itemize}
+ \item {\bf i.ortho.rectify} new rewritten \& optimized version of i.ortho.photo
+ \item {\bf i.atcorr} atmospheric correction, more satellite sensors configured, faster
+ \item {\bf i.pca} backward modeling implemented 
+\end{itemize}
+
+{\bf Preparing Landsat, Aster and MODIS datasets}
+
+\begin{itemize}
+ \item {\bf i.landsat.toar} TOA reflectance correction for Landsat satellite series
+ \item {\bf i.aster.toar} TOA reflectance correction for Terra-ASTER
+ \item {\bf i.modis.qc} Quality flag interpretation for Terra/Aqua MODIS
+\end{itemize}
+
+{\bf Geographical and astronomic functions}
+
+\begin{itemize}
+ \item {\bf i.latlong} maps latitude or longitude (dd.ddd)
+ \item {\bf i.sunhours} maps potential hours of sunshine in a day at a given location (hh.hhh)
+ \item {\bf r.sun.angle} maps the sun elevation and sun azimuth angles for the given time of day
+\end{itemize}
+}
+
+\startfourthcolumn
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Multi- and hyperspectral data analysis}{
+\smallskip
+{\bf Unmixing mixed pixels (i.spec.unmix [9]) is based upon identifying orignal spectral signatures
+that ideally come from a land cover that is covering at least one full pixel in the image
+studied.}
+
+\begin{center}
+ \includegraphics[width=0.4\textwidth]{./images/unmix1.png}
+ \hspace{10mm}
+ \includegraphics[width=0.5\textwidth]{./images/unmix.png}
+\end{center}
+\begin{center}
+ \includegraphics[width=0.5\textwidth]{./images/unmix2.png}
+ \newline
+ Figure 7: Unmixing principle (left), end-members selection (right), error space (below)
+\end{center}
+}
+
+\blocknode{Spatio-temporal Analysis}{
+\smallskip
+Repetitive daily open water mapping (i.wi), provides with the probability 
+of flood destruction on rice crop area in Thailand [10].\newline
+
+\begin{center}
+ \includegraphics[width=0.75\textwidth]{./images/floodrisk}
+ \newline
+ Figure 8: Flood risk on Eastern Thailand analysed with ~9 years daily MODIS data
+\end{center}
+}
+
 \end{tikzpicture}

### 2013-03-19 grassposter/2013_EGU_G7_Landscape/poster.tex
unmix images replaced with high-res PDF version
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55435 15284696-431f-4ddb-bdfa-cd5b030d7da7
Remove Bold on paragraph
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55436 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \smallskip
-{\bf Unmixing mixed pixels (i.spec.unmix [9]) is based upon identifying orignal spectral signatures
+Unmixing mixed pixels (i.spec.unmix [9]) is based upon identifying orignal spectral signatures
 that ideally come from a land cover that is covering at least one full pixel in the image
-studied.}
+studied.
 
 \begin{center}
- \includegraphics[width=0.4\textwidth]{./images/unmix1.png}
+ \includegraphics[width=0.4\textwidth]{./images/unmix_pixels_spectrum.pdf}
  \hspace{10mm}
- \includegraphics[width=0.5\textwidth]{./images/unmix.png}
+ \includegraphics[width=0.5\textwidth]{./images/unmix_xgobi_supersession.pdf}
 \end{center}
 \begin{center}
- \includegraphics[width=0.5\textwidth]{./images/unmix2.png}
+ \includegraphics[width=0.5\textwidth]{./images/unmix_errorfunction.pdf}
  \newline

### 2013-04-05 grasslecture/20130416_Trento_G7/crowdsourceET.tex
Trento 2013Apr16 talk upload
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55636 15284696-431f-4ddb-bdfa-cd5b030d7da7

\documentclass[xcolor=dvipsnames,beamer]{beamer} %handout,notes=show

\usepackage{textcomp}
\usepackage[utf8]{inputenc}
% \usepackage{default}
\usepackage{graphicx}
%  \usepackage[pdftex]{hyperref}
\usepackage{url}
\usepackage{amsmath}

% frames have to be fragile
\newif\ifnotes
\input{tmpnotessettings}
%\notestrue

\ifnotes
%\setbeamertemplate{note page}[plain]
\setbeamertemplate{note page}[compress]
\setbeamerfont{note page}{size=\large}
\setbeameroption{show only notes}
%\setbeameroption{show notes}
\usepackage{pgfpages}
\pgfpagesuselayout{2 on 1}[a4paper,border shrink=5mm]%
\else
%\setbeameroption{hide notes}
\fi
%\notesfalse

% nastaveni TypeWriter
%\usepackage{courier}
%\usepackage{lmodern}
%\renewcommand*\ttdefault{txtt}
\DeclareFontShape{OT1}{cmtt}{bx}{n}{<5><6><7><8><9><10><10.95><12><14.4><17.28><20.74><24.88>cmttb10}{}

% \usepackage{verbatim}
\usepackage[absolute,overlay]{textpos}

\usepackage{listings}
% \usepackage{courier}
\definecolor{grey}{RGB}{70,70,70}
\definecolor{green}{RGB}{0,255,0}
\definecolor{red}{RGB}{202,53,53}
\definecolor{lightGrey}{RGB}{250,250,250}
\definecolor{darkGrey}{RGB}{50,50,50}

\usepackage{color}
\definecolor{lightgray}{rgb}{.9,.9,.9}
\definecolor{darkgray}{rgb}{.4,.4,.4}
\definecolor{purple}{rgb}{0.65, 0.12, 0.82}

% \usetheme{Warsaw}
\usetheme{Madrid}
% \usetheme{Szeged}
% \useoutertheme{infolines}
\usecolortheme[named=MidnightBlue]{structure}
% \usecolortheme[named=PineGreen]{structure}
% \setbeamertemplate{navigation symbols}{}

\title[crowdsourcing ET calibration]
{GRASS GIS crowdsourcing of the local calibration of ETa models to improve on public domain Global ET products}
%\subtitle{SVO\v{C}}
%\pdforstring{}{}
\author[Yann Chemin]
{Yann Chemin}

\institute[IWMI]
{International Water Management Institute\\
\vspace{20pt}
% \includegraphics[width=1cm]{iwmi}
}
\date{April 16, 2013}

%\AtBeginSection[]{\begin{frame}\frametitle{Obsah}%
%\tableofcontents[currentsection ]\end{frame}}
%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>
%  \frametitle{Obsah}
%  \tableofcontents[currentsection,currentsubsection]
%  \end{frame}
%}

\setbeamercovered{transparent}

\hypersetup{%
	pdfauthor={Yann Chemin},%
	pdfsubject={Presentation},%
    pdfkeywords={GRASS, GIS, Evapotranspiration, crowdsourcing}
}

\input{nastavenilst}

\newcommand{\overovaciref}[1]{{\scriptsize(\ref{#1})}}

\usepackage{tipa}
\newcommand{\pron}[2]{#1 [#2]}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\frame{
\titlepage
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Contents}
\tableofcontents
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Overview}

Evapotranspiration is the largest transiting quantity in the daily 
hydrological cycle along with rain. It is used by scientists and
managers in:
\newline\linebreak

\begin{itemize}
 \item Irrigation systems performance
 \item Crop water productivity
 \item Water accounting
 \item Wetlands-agriculture interface
 \item Basin water uses quantification
 \item Climate change on water cycle \& users
\end{itemize}

\end{frame}

\section{Evapotranspiration Modeling}
\subsection{Overview}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Overview}

There are several types of evapotranspiration modeling methods:\\

\begin{itemize}
 \item Reference ET: Hargreaves, Penman-Monteith
 \item Potential ET: Priestley-Taylor, astronomical
 \item Actual ET: Thermodynamic/energy balance (mostly)
\end{itemize}

\end{frame}

\subsection{ETo \& ETpot}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Reference \& potential ET}

\begin{block}{Trunk (G7)}
\begin{itemize}
 \item i.evapo.mh: ETo Hargreaves, Modified H., H.-Samani 
 \item i.evapo.pm: ETo Penman-Monteith (PM, 1972)
 \item i.evapo.pt: ETpot Priestley-Taylor (PT, 1970s)
 \item i.evapo.potrad: ETpot astronomical (WB, 1995)
\end{itemize}
\end{block}

\begin{block}{Add-ons (G7)}
\begin{itemize}
 \item i.evapo.senay: ET \textit{regional} (Senay, 2007)
 \item i.evapo.zk: ET \textit{biome} (ZK, 2010)
\end{itemize}
\end{block}
\end{frame}

\subsection{ETa definition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Actual ET}

Actual ET: thermodynamic heat flux modeling\\

\begin{equation}\label{eq1}
\Lambda = \frac {Rn - G - H} {Rn - G}
\end{equation}

\begin{equation}\label{eq2}
ET_a = \Lambda \, ET_{potential}
\end{equation}

\begin{block}{i.eb.* modules (G7 main) using thermodynamic heat flux modeling}
\begin{itemize}
 \item i.eb.netrad: Net radiation (Rn in \ref{eq1}) 
 \item i.eb.h\_*: Sensible heat flux (H in \ref{eq1})
 \item i.eb.evapfr: Evaporative fraction ($\Lambda$ in \ref{eq2})
 \item i.eb.eta: Evapotranspiration (ETa in \ref{eq2})
\end{itemize}
\end{block}
\end{frame}

\subsection{ETa examples 1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Evapotranspiration @ country level}

Actual evapotranspiration\\ 
for water resources monitoring \& management.\\

\begin{center}
 \includegraphics[width=5cm]{slet2005}
 \hspace{10mm}
 \includegraphics[width=5cm]{slet2010}
\end{center}

\end{frame}

\subsection{ETa examples 2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Equity of water use in irrigation systems}

Irrigation water monitoring \& management
\begin{itemize}
 \item Map: Uniform colour is equity of water distribution
 \item Graph: irrigation system equity in time (daily, 12 years)
\end{itemize}

\begin{columns}[l]
\column{0.2\textwidth}
\begin{center}
\includegraphics[width=4cm]{fess2012ef}
\end{center}

\column{0.8\textwidth}
\begin{flushright}
  \includegraphics[width=8cm]{fess2012meaneftemporal}
\end{flushright}
\end{columns}

\end{frame}

\subsection{ETa examples 3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Crop water consumption in irrigation systems}

Actual evapotranspiration (mm/d)\\ 
for agricultural water performance management.\\

\begin{center}
 \includegraphics[width=9.5cm]{ciameanet}\\
 \includegraphics[width=9.5cm]{ciaminmaxet}
\end{center}

\end{frame}

\subsection{Chain processing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Chain processing}

Chain processing has a fundamental impact on remote sensing work:\\

\begin{itemize}
 \item Standardization limits bugs
 \item Less prone to human error
 \item Simpler parameterization access
 \item Permits to apply any number of modules to all target images
 \item Ensures maximum quality of generated images
\end{itemize}

\begin{block}{Concept}
\begin{itemize}
 \item META Module, a module using modules
 \item Prototype, shell script, then grass.script
 \item Actually moving to pygrass (Genoa CS2013)
\end{itemize}
\end{block}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Chain processing}

The development of pyGRASS is maturing,\\
META Modules arise from vertical integration.

\begin{center}
 \includegraphics[width=7.5cm]{chain0}
\end{center}

\end{frame}

\subsection{MOD 16}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{MOD16 MODIS product}

Global monthly (MOD16A2) and yearly (MOD16A3) dataset
\begin{center}
 \includegraphics[width=10.5cm]{MOD16_2000.png}
\end{center}
8km parameterization, validated on Fluxnet data.\\
Not validated daily.
\end{frame}

\section{Crowdsourcing}
\subsection{Rationale}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Rationale for crowdsourcing}

\begin{columns}[l]
\column{0.7\textwidth}
Local parameterization of ET models is necessary\newline\linebreak

\begin{block}{because the end-user is:}
\begin{itemize}
 \item in a better position for QC in/out
 \item interested in both upstream/downstream
\end{itemize}
\end{block}

\begin{block}{but the constraints are:}
\begin{itemize}
 \item using ET models
 \item using GIS, FOSSGIS
\end{itemize}
\end{block}
\column{0.3\textwidth}
\begin{center}
 \includegraphics[width=3.5cm]{crowdsourcing}
\end{center}
\end{columns}

\end{frame}

\subsection{Year 1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{set up for year 1: Kick the geek}

Scientists on all continents
\begin{itemize}
 \item Background in RS/ET/FOSS (pick any to all)
 \item Interested to publish their calibration of ET models
 \item Willing to be trained on GRASS GIS v7
\end{itemize}

\begin{block}{Year 1 Goals}
\begin{itemize}
 \item Training a core of interested scientists
 \item GRASS GIS modules for ET modeling taken over by users
\end{itemize}
\end{block}

\end{frame}

\subsection{Year 2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{set up for year 2: Bring the bee}

Any interested person on all continents
\begin{itemize}
 \item Background in science
 \item Interested to learn that knowledge
 \item Willing to be trained on GRASS GIS
 \item Interested in simple GRASS GIS raster programming
\end{itemize}

\begin{block}{Year 2 Goals}
\begin{itemize}
 \item Year 1 articles in press, local calibration in svn
 \item HPC FOSS source code online
 \item GRASS GIS ET modules used by Year 2 community
\end{itemize}
\end{block}

\end{frame}

\subsection{Year 3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{set up for year 3: Ubergeek upgrade}

Any intensely interested person on all continents
\begin{itemize}
 \item Background in C programming, ET models
 \item Interested to process all MODIS archives
 \item Willing to learn and contribute distributed modeling
\end{itemize}

\begin{block}{Year 3 Goals}
\begin{itemize}
 \item Year 1/2 articles in press
 \item Local calibration in svn
 \item HPC FOSS source code taken over by community
\end{itemize}
\end{block}

\end{frame}

\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Conclusions}

One for all
\begin{itemize}
 \item Crowdsourcing of science should be possible
 \item But needs supporting efforts in terms of training
 \item Realizing this makes the science uptake more robust
\end{itemize}

\begin{block}{All for all}
\begin{itemize}
 \item Returning local parameterization from local to svn
 \item Permits local QC improvement of global ET data generation
 \item Anybody can model ET anywhere/anywhen they want
\end{itemize}
\end{block}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Thank You}

\begin{center}
 \includegraphics[width=5cm]{crowdsourcing}
\end{center}

\end{frame}

\end{document}

### 2013-04-19 grasslecture/20130416_Trento_G7/crowdsourceET.tex
Final version from the FEM talk
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55905 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \end{frame}
+
+\subsection{Blueprint}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}[fragile]{Blueprint}
+
+\begin{center}
+ \includegraphics[width=8cm]{chain0}
+\end{center}
+
+\begin{itemize}
+ \item GDAL+[C+OpenMP]
+ \item GRASSGIS+pyGRASS+[C+OpenMP]
+\end{itemize}
+
+\end{frame}
+
+\subsection{GDAL}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}[fragile]{HPC GDAL framework}
+
+\begin{columns}[l]
+\column[t]{0.6\textwidth}
+\begin{center}
+ GDAL+[C+OpenMP]
+ \includegraphics[width=7.5cm]{chain2}
+\end{center}
+\column[t]{0.4\textwidth}
+\begin{center}
+ OpenMP distribution
+ \includegraphics[width=5cm]{chain1}
+\end{center}
+\end{columns}
+\end{frame}
+
+\subsection{GRASS GIS}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}[fragile]{GRASS GIS framework}
+
+\begin{center}
+ \includegraphics[width=7.5cm]{architecture_implementation}
+\end{center}
+
+\begin{block}{metaModule concept}
+{\bf pyGRASS:} vertical integration of GRASS GIS modules\\
+{\bf GRASS GIS modules:} [C+OpenMP] any multi-core PC \\
+{\bf GRASS GIS modules:} [C+MPIch?] in FEM - GISCluster \\
+{\bf GRASS GIS modules:} [C+CUDA/GPGPU?] in FEM - Tesla
+\end{block}
+
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{center}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}[fragile]{Initial results of ET Models comparison}
+
+\begin{center}
+ Average ET for Sri Lanka, Daily 2000-2012 (mm/d, daily, 12.3 years)
+ \includegraphics[width=12cm]{sltemporaletb}
+\end{center}
+
+\begin{block}{Comparison}
+\begin{itemize}
+ \item ETo \& ETpot (rad) are similar, expected.
+ \item ETa models are not so similar, expected.
+ \item ETo \& ETpot (rad) are higher than ETa models, expected.
+\end{itemize}
+
+\end{block}
 
@@
 
-\subsection{Year 1}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Year 2}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Year 3}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-10-09 grassposter/2014_EGU_G7_Landscape/poster.tex
First changes to the poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@57965 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2013-03-19 grassposter/2013_EGU_G7_Landscape/poster.tex
@@
 
-\title{GRASS GIS image processing environment\\ Gearing towards GRASS GIS 7}
-\author{Yann Chemin\\
-International Water Management Institute}
+\title{GRASS GIS Vector state of the art\\ Gearing towards GRASS GIS 7}
+\author{Markus Neteler, ...\\
+GRASS GIS Development Team}
 
@@
 \smallskip
-Unmixing mixed pixels (i.spec.unmix [9]) is based upon identifying orignal spectral signatures
-that ideally come from a land cover that is covering at least one full pixel in the image
-studied.
+Unmixing of mixed pixels (i.spec.unmix [9]) is based on the identification of original
+spectral signatures that are ideally derived from land covers that cover at least one
+full pixel in the image (pure endmembers).
 
@@
 \begin{center}
- \includegraphics[width=0.75\textwidth]{./images/floodrisk}
+ \includegraphics[width=0.7\textwidth]{./images/floodrisk}
  \newline

### 2014-04-10 grassposter/2014_EGU_WD_Landscape/poster.tex
Added draft Water Dynamics poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59661 15284696-431f-4ddb-bdfa-cd5b030d7da7

\documentclass[landscape,a0,final]{a0poster}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikzposter} % here most of the things are defined
% change parameters only after this line You can also start a new column with an arbitrary 
% x-coordinate by specifying explicitly the coordinate of the new block node as follows:
\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage{wrapfig}
\usepackage{url}

%Used for better control on code display

\usepackage[margin=\margin cm, paperwidth=197cm, paperheight=100cm]{geometry}

% \setbackgrounddarkcolor{ForestGreen!70!black}
% \setbackgroundlightcolor{YellowGreen!90!}

% \setfirstcolor{YellowGreen!80!}
% \setsecondcolor{gray!80!}
% \setthirdcolor{red!80!black}

\title{From Water Dynamics to Rainfed Landscapes\\ with GRASS GIS}
\author{Yann Chemin$^1$, Martin van Brakel$^2$, Robyn Johnston$^1$, Jayne Curnow$^1$\\
$^1$International Water Management Institute\\
$^2$CRP on Water, Land and Ecosystems (WLE)}

\usetemplate{1}
\setinstituteshift{1}

\setblocktitleheight{2}
\setblockspacing{1}

\begin{document}
\ClearShipoutPicture
\AddToShipoutPicture{\BackgroundPicture}
\noindent
\tikzstyle{every picture}+=[remember picture]
\begin{tikzpicture}
\initializesizeandshifts
\titleblock{90}{1}
% \setblocktitleheight{1}

\addlogo[north west]{(2,-1)}{9cm}{./svg_images/Grass_GIS.pdf}
\addlogo[north east]{(-2,-2.5)}{11cm}{./svg_images/IWMI_logo.pdf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Abstract}{
\small \noindent Variability in water availability is a key determinant of risk and constraint to productivity in rainfed agricultural systems. Understanding the dynamics of water availability across both spatial and temporal scales is essential to managing water and optimize production. This research proposes to look at both the physical measurement of water availability and water user perceptions of landscapes and water availability.\newline\linebreak
\noindent Evapotranspiration makes up about three quarters of the transiting water in a landscape, it is composed of evaporation (water bodies, soil) and transpiration, the vegetation biomass growing quantity. This work will develop a methodology for defining landscapes based on water dynamics to be used at the interface of WLE research. The GRASS GIS [1] Imagery (i.*), Landscape (r.li.*) and Temporal (t.*) toolkits form the basis of the methodological development, from evapotranspiration modeling and landscape analysis to spatio-temporal analysis.\newline\linebreak
The methodology will be complemented by time series analysis spanning 14 years up to near real-time (2000-2014) of MODIS vegetation index data, capable of distinguishing seasonal and long term land use and land cover trends in these landscapes. This analysis will be developed into a routine that can be executed in open source GIS (GDAL [2] tools and GRASS GIS [1]), providing a robust and readily available application for monitoring medium to large scale land use and land cover change over any desired area.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Transpiration and the search for rainfed landscapes}{
\smallskip
\begin{center}
	\begin{tabular}{c p{0.5\textwidth}}
	 \raisebox{-0.9\totalheight}{\includegraphics[width=0.45\textwidth]{./images/Yann_flowchart}}
	&
	The transpiration data is created from energy balance modelling [3] modules (i.eb.*, i.evapo.*) within GRASS GIS version 7, by partitioning the net radiation (r.sun) into soil heat flux (i.eb.soilheatflux), sensible heat flux (i.eb.h\_*) and the residual being the energy needed to evaporate water (i.eb.evapfr, i.eb.eta). This information is then fractionated into biotic (transpiration) and abiotic (evaporation) parts using vegetation fraction.\newline\linebreak
The accumulated transpiration (t.rast.aggregate) is subjected to Landscape analysis (r.li.*) for search of patchiness and diversity indices [4]. Further analysis of transpiration is also done with the object oriented classifier (i.segment) for spatiotemporal objects within the transpiration original dataset, the accumulated one and the Landscape indices, respectively.\newline
 	\end{tabular}\newline
\end{center}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\getcurrentrow{box}
\coordinate (funkcionalita) at (box.south west);
\coordinate (funkcionalitaeast) at (box.east);
\coordinate (screenshot) at (box.north west);

\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
\scriptsize
\begin{center}
\begin{tabular}{rp{0.9\textwidth}}
[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
[2] & GDAL, 2014. {\url {http://gdal.osgeo.org}}\\{}
[3] & Chemin, 2012. Chapter 19, DOI: 10.5772/23571 ({\url {http://bit.ly/16qJOep}})\\{}
[4] & McGarigal \& Marks, 1995. FRAGSTATS. USDA For. Serv. Gen. Tech. Rep. PNW-351.\\{}
[5] & Momsen \& Metz, 2012. GSoC project: Segmentation algorithm.
\end{tabular}
\end{center}
\smallskip
\hrulefill
\vspace{-5pt}

\begin{center}
\begin{tabular}{cp{0.9\textwidth}}
\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/iwmi_qr.pdf}
\end{minipage}

\begin{minipage}{0.3\textwidth}
\small {\url{www.iwmi.org}}
\end{minipage}

\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/grass_qr.pdf}
\end{minipage}

\begin{minipage}{0.3\textwidth}
\small {\url{grass.osgeo.org}}
\end{minipage}
\end{tabular}
\end{center}

\hrulefill
\vspace{14pt}
\begin{center}
\newcommand{\logowidth}{5em}
\newcommand{\logospace}{\hspace{0.1em}}
\noindent
\includegraphics[width=\logowidth]{./svg_images/public_domain_logo.pdf}
\raisebox{0.7\height}{\logospace 2013 GRASS Development Team}
\end{center}
}

\startsecondcolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Temporal PCA-based classification}{
\smallskip
\begin{center}
	\begin{tabular}{c p{0.5\textwidth}}
	\raisebox{-0.9\totalheight}{\includegraphics[width=0.45\textwidth]{./images/Martin_flowchart}}
	&
	A summary of the code needed to reach this point of analysis is here.\newline
	{\footnotesize \fontfamily{pcr}\selectfont i.group \textcolor{blue}{group}=pca\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=*h28v07*EVI)\newline
	i.pca \textcolor{blue}{input}=pca\_group \textcolor{blue}{output\_prefix}=pca\_ \textcolor{blue}{percent}=99 --o\newline}
 	\end{tabular}\newline
\end{center}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Temporal PCA-based classification}{
Balaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa
aaaaaaaaaaaaaaaaaaaaaaaaaaaaaa\newline
\begin{center}
	\begin{tabular}{cc}
 	\raisebox{-0.5\totalheight}{\includegraphics[width=0.45\textwidth]{./images/MSUBAS_MD}}
 	& 
 	\begin{tabular}{c}
 	\includegraphics[width=0.45\textwidth]{./images/cl2_DoY}\\
 	\includegraphics[width=0.45\textwidth]{./images/cl12_DoY}
	\end{tabular}
	\end{tabular}\newline
	Figure 2: Temporal 
\end{center}

}

\startthirdcolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Temporal patterns of recession cropping \& natural vegetation}{

\begin{center}
	\begin{tabular}{cc}
	\raisebox{-0.7\totalheight}{\includegraphics[width=0.45\textwidth]{./images/MSUBAS_TS}}
	&
	\begin{tabular}{c}
 	\includegraphics[width=0.45\textwidth]{./svg_images/EVI_distance_from_tonle_sap}\\
	bllaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa
	\end{tabular}
 	\end{tabular}\newline
\end{center}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Recession cropping \& natural vegetation}{
\begin{center}
	\begin{tabular}{cc}
 	\begin{tabular}{c}
 	\includegraphics[width=0.5\textwidth]{./images/cl3_avg}\\
 	\includegraphics[width=0.5\textwidth]{./images/cl65_avg}
	\end{tabular}
 	& 
 	\begin{tabular}{c}
 	\includegraphics[width=0.5\textwidth]{./images/cl45_avg}\\
 	\includegraphics[width=0.5\textwidth]{./images/cl10_avg}
	\end{tabular}
	\end{tabular}\newline
\end{center}

}

\startfourthcolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Euclidian Distance plotting}{
\smallskip

\begin{center}
	\includegraphics[width=0.75\textwidth]{./images/msubas65}
\end{center}

}

\end{tikzpicture}

\end{document}

### 2014-04-10 grassposter/2014_EGU_G7_Landscape/poster.tex
Starting the G7 Vector poster modifications
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59663 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2013-03-19 grassposter/2013_EGU_G7_Landscape/poster.tex
@@
 
-\title{GRASS GIS image processing environment\\ Gearing towards GRASS GIS 7}
-\author{Yann Chemin\\
-International Water Management Institute}
+\title{\bigskip GRASS GIS Vector State of the Art  -  Gearing towards GRASS GIS 7 \bigskip}
+\author{Markus Metz$^1$, Martin Landa$^2$, Anna Petrasova$^3$, Vaclav Petras$^3$, Yann Chemin$^4$, Markus Neteler$^1$ and The GRASS GIS Development Team\\ \bigskip
+$^1$ CRI, FEM, Italy, $^2$ CTU, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka}
 
@@
 \initializesizeandshifts
-\titleblock{73.8}{1}
+\titleblock{123.8}{1}
 % \setblocktitleheight{1}
@@
 \addlogo[north west]{(2,-1)}{9cm}{./svg_images/Grass_GIS.pdf}
-\addlogo[north east]{(-2,-2.5)}{11cm}{./svg_images/IWMI_logo.pdf}
+%Please insert your institution logo here
+\addlogo[north east]{(-2,-2.5)}{4cm}{./svg_images/IWMI_logo.pdf}
+\addlogo[north east]{(-2,-6.5)}{4cm}{./svg_images/IWMI_logo.pdf}
+\addlogo[north east]{(-8,-2.5)}{4cm}{./svg_images/IWMI_logo.pdf}
+\addlogo[north east]{(-8,-6.5)}{4cm}{./svg_images/IWMI_logo.pdf}
 
@@
 \small
-An edge is considered as a change in image digital values.
-Edge detection \& extraction in i.canny is done by a Canny edge detector [2]. 
-The Canny edge detector encompasses Gaussian smoothing, 
-gradient computation \& non-maximum suppression. \newline
-This creates thin edges and thresholding with hysteresis which
-preserves only important edges. Thus, no pre- or post-processing is required.
-The produced binary image shows boundaries of areas in the input image
-which is usually a gray scale image e.g., intensity channel or the
-result of PCA.\newline
-The i.edge module is suitable as a first step in building or road detection.
-The level of details of the output image is easily customizable.
+blabla
 \begin{center}
- \includegraphics[width=0.48\textwidth]{./images/imagery_spot_original}
- \hspace{10mm}
- \includegraphics[width=0.48\textwidth]{./images/imagery_spot_edge_1}
- \newline
+ %\includegraphics[width=0.48\textwidth]{./images/imagery_spot_original}
+ %\hspace{10mm}
+ %\includegraphics[width=0.48\textwidth]{./images/imagery_spot_edge_1}
+ %\newline
  Figure 1: Canny edge detector on a road network [2]
-\end{center}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Object recognition}{
-\small The module i.segment [3] is using a region growing algorithm [4], some ideas 
-have also been implemented from [5]. It produces a raster map with segments (objects), 
-and optionally other maps with segments statistics (mean/variance/range/etc.). 
-\begin{center}
- \includegraphics[width=0.48\textwidth]{./images/sltsu.png}
- \hspace{10mm}
- \includegraphics[width=0.48\textwidth]{./images/sltsu_seg.png}
- \newline
- Figure 2: Image segmentation (2.4x2.4m) of the 2004 tsunami wave, West Coast Sri Lanka
 \end{center}
@@
 [2] & Petráš, 2012. M.Sc. Thesis, OSGeoREL, FCE CTU, Prague.\\{}
-[3] & Momsen \& Metz, 2012. i.segment module. GRASS GIS Software, Version 7.\\{}
-[4] & Sant'Anna Bins \& Fonseca \& Erthal \& Misuo, 1996. Anais VIII Simpósio Brasileiro de Sensoria.
-Rem., Salvador, Brasil, INPE, 677-680.\\{}
-[5] & Athelogou \& Schmidt \& Schäpe \& Baatz \& Binnig, 2007. Imaging Cellular \& Molecular Biological
-Functions, 407-422.\\{}
-[6] & Chemin, 2012. Chapter 19, DOI: 10.5772/23571 ({\url {http://bit.ly/16qJOep}})\\{}
-[7] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
-[8] & Chemin \& Rabbani, 2011. International Journal of Geoinformatics,  7(3):1-6.\\{}
-[9] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. 
-International Journal of Geoinformatics, 1(1): 51-61.\\{}
-[10] & Chemin \& Phuphak \& Asilo \& Hijmans, 2012. International Journal of GeoInformatics. 8(1):1-12.
+[3] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
+[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. 
+International Journal of Geoinformatics, 1(1): 51-61.
 \end{tabular}
@@
 \includegraphics[width=\logowidth]{./svg_images/public_domain_logo.pdf}
-\raisebox{0.7\height}{\logospace 2013 GRASS Development Team}
+\raisebox{0.7\height}{\logospace 2014 GRASS Development Team}
 \end{center}
@@
 \blocknode{Interactive supervised classification}{
-This interactive tool [7], aims at greatly simplifying quantitative surpervised class training areas creation.
-It calculates the spectral signatures based on the cells within the specified areas. 
-The resulting signature file can be used by a maximum likelihood classification module (i.maxlik). 
-During the process the user is shown a histogram of the area cell values for each image band, 
-and coincident plot which shows the separability of classes.\newline\linebreak
-Another way the user can inspect the suitability of the created training areas 
-is by displaying the cells of the image bands which fall within a user-specified 
-number of standard deviations from the means in the spectral signature. This
-helps to estimate how much of the image is likely to be classified as a particular class.\newline
+This
 \begin{center}
- \includegraphics[width=0.47\textwidth]{./images/wxiclass1.png}
- \hspace{10mm}
- \includegraphics[width=0.47\textwidth]{./images/wxiclass2.png}
- \newline
+ %\includegraphics[width=0.47\textwidth]{./images/wxiclass1.png}
+ %\newline
  Figure 3: Interactive image classification with coincidence plots (left side) \& histograms (right side)
@@
 \blocknode{Satellite imagery products}{
-\begin{itemize}
- \item {\bf i.vi} 15 vegetation indices available
- \item {\bf i.albedo} Broadband Albedo (snow \~= 0.6-0.8, water=0.05)
- \item {\bf i.emissivity} Emissivity approximation from vegetation index
- \item {\bf i.biomass} biomass growth for crop yield
-\end{itemize}
-
-{\bf Reference/Potential ET: i.evapo.* modules}
-
-\begin{itemize}
- \item {\bf i.evapo.mh} ETo Hargreaves, modified-Hargreaves \& Hargreaves-Samani 
- \item {\bf i.evapo.pm} ETo Penman-Monteith
- \item {\bf i.evapo.pt} ETpot Priestley-Taylor
-\end{itemize}
-
-{\bf Actual ET: i.eb.* modules using thermodynamic heat flux modeling}
-
-\begin{center}
- \includegraphics[width=0.45\textwidth]{./images/slet2005}
- \hspace{20mm}
- \includegraphics[width=0.45\textwidth]{./images/slet2010}
- \newline
- Figure 4: Actual evapotranspiration (i.eb.*) for water monitoring and management [6]
-\end{center}
+blabla
 }
@@
 \begin{center}
- \includegraphics[width=0.4\textwidth]{./images/ofs1}
- \hspace{10mm}
- \includegraphics[width=0.275\textwidth]{./images/ofs2}
- \newline
+ %\includegraphics[width=0.4\textwidth]{./images/ofs1}
+ %\newline
  Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]
-\end{center}
-}
-
-\blocknode{Temporal signature cleaning}{
-\smallskip
-\begin{itemize}
- \item r.hants produces a harmonic analysis through incomplete returned Fourier inversion.
- \item i.lmf computes a temporal Local Maximum Fitting with Akaike Information Content.
-\end{itemize}
-
-\begin{center}
- \includegraphics[width=0.8\textwidth]{./images/lmf0}\newline
- \vspace{10mm}
- \includegraphics[width=0.8\textwidth]{./images/lmf1}
- \newline
- Figure 6: pre and post LMF temporal filter
 \end{center}
@@
 
-\begin{itemize}
- \item {\bf i.ortho.rectify} new rewritten \& optimized version of i.ortho.photo
- \item {\bf i.atcorr} atmospheric correction, more satellite sensors configured, faster
- \item {\bf i.pca} backward modeling implemented 
-\end{itemize}
-
-{\bf Preparing Landsat, Aster and MODIS datasets}
+{\bf Other functions}
 
 \begin{itemize}
- \item {\bf i.landsat.toar} TOA reflectance correction for Landsat satellite series
- \item {\bf i.aster.toar} TOA reflectance correction for Terra-ASTER
- \item {\bf i.modis.qc} Quality flag interpretation for Terra/Aqua MODIS
-\end{itemize}
-
-{\bf Geographical and astronomic functions}
-
-\begin{itemize}
- \item {\bf i.latlong} maps latitude or longitude (dd.ddd)
- \item {\bf i.sunhours} maps potential hours of sunshine in a day at a given location (hh.hhh)
- \item {\bf r.sun.angle} maps the sun elevation and sun azimuth angles for the given time of day
+ \item {\bf v.} blabla
+ \item {\bf v.} blabla
+ \item {\bf v.} blabla
+ \item {\bf v.} blabla
+ \item {\bf v.} blabla
 \end{itemize}
@@
 \smallskip
-{\bf Unmixing mixed pixels (i.spec.unmix [9]) is based upon identifying orignal spectral signatures
-that ideally come from a land cover that is covering at least one full pixel in the image
-studied.}
+Unmixing
 
 \begin{center}
- \includegraphics[width=0.4\textwidth]{./images/unmix1.png}
- \hspace{10mm}
- \includegraphics[width=0.5\textwidth]{./images/unmix.png}
-\end{center}
-\begin{center}
- \includegraphics[width=0.5\textwidth]{./images/unmix2.png}
- \newline
+ %\includegraphics[width=0.4\textwidth]{./images/unmix_pixels_spectrum.pdf}
+ %\newline
  Figure 7: Unmixing principle (left), end-members selection (right), error space (below)
-\end{center}
-}
-
-\blocknode{Spatio-temporal Analysis}{
-\smallskip
-Repetitive daily open water mapping (i.wi), provides with the probability 
-of flood destruction on rice crop area in Thailand [10].\newline
-
-\begin{center}
- \includegraphics[width=0.75\textwidth]{./images/floodrisk}
- \newline
- Figure 8: Flood risk on Eastern Thailand analysed with ~9 years daily MODIS data
 \end{center}

### 2014-04-10 grassposter/2014_EGU_G7_Landscape/poster.tex
updating posters
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59664 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \blocknode{Abstract}{
-\small GRASS GIS, commonly referred to as GRASS (Geographic Resources Analysis Support System),
-is a free Geographic Information System (GIS) software used for geospatial data management and analysis,
-image processing, graphics/maps production, spatial modeling, and visualization [1].
-
-GRASS GIS 7 started its development by the branching out of GRASS GIS 6.x from the main trunk of code (rev 31142).
-This was done on 27th of April 2008, and a large amount of changes took place since that date, more 
-are still underway.
-\begin{itemize}
- \item Raster library in GRASS 7 (ongoing)
- \item Vector library in GRASS 7 (ongoing)
- \item Raster3D (volume) library and modules in GRASS 7 (finished)
- \item Temporal extension for GRASS 7 (finished) 
-\end{itemize}
-
-GRASS GIS' capacity in remote sensing has also been greatly improved with additions for version 7.
+\small The upcoming GRASS GIS 7 release improves not only raster processing and general design but the vector processing in the first place.
+GRASS GIS, as a topological GIS, recognizes that the topology plays the key role in the vector processing and analysis.\newline
+Topology ensures that adjacent geographic components in a single vector map are related.
+In contrast to non-topological GIS, a border common to two areas exists only once and is shared between the two areas.
+Topological representation of vector data helps to produce and maintain vector maps with clean geometry as well as enables the user to perform certain analyses that can not be conducted with non-topological or spaghetti data.
+Non-topological vector data are automatically converted to a topological representation upon import.
+Further more, various cleaning tools exist to remove non-trivial topological errors.\newline
+In the upcoming GRASS GIS 7 release the vector library was particularly improved to make it faster and more efficient with an improved internal vector file format.
+This new topological format reduces memory and disk space requirements, leading to a generally faster processing.
+Opening an existing vector requires less memory providing additionally support for large files.
+The new spatial index performs queries faster (compared to GRASS GIS 6 more than 10 times for large vectors).
+As a new option the user can select a file-based version of the spatial index for large vector data.
+All topological cleaning tools have been optimized with regard to processing speed, robustness, and system requirements.\newline
+The topological engine comes with a new prototype for direct read/write support of Simple Features API/OGR. \newline
+Additionally vector data can be directly exchanged with topological PostGIS 2 databases.\newline
+Considering the wide spread usage of ESRI Shapefile, a non-topological format for vector data exchange, it is particularly advantageous that GRASS GIS 7 offers advanced cleaning tools.\newline
+For power users and programmers, the new Python interface allows to directly access functions provided by the underlying C library; this combines the ease of writing Python scripts with the power of optimized C functionality in the library backend.
 }

### 2014-04-10 grassposter/2014_EGU_WD_Landscape/poster.tex
trying to add code highlighting
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59662 15284696-431f-4ddb-bdfa-cd5b030d7da7
updating posters
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59664 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \usepackage[dvipsnames,svgnames]{xcolor}
+\usepackage{minted} %code highlighting, not working yet
 \usepackage{tikzposter} % here most of the things are defined
@@
 
-\title{From Water Dynamics to Rainfed Landscapes\\ with GRASS GIS}
+\title{From Water Dynamics to Rainfed Landscapes with GRASS GIS\bigskip}
 \author{Yann Chemin$^1$, Martin van Brakel$^2$, Robyn Johnston$^1$, Jayne Curnow$^1$\\
-$^1$International Water Management Institute\\
-$^2$CRP on Water, Land and Ecosystems (WLE)}
+\bigskip
+\\ $^1$International Water Management Institute, $^2$CRP on Water, Land and Ecosystems (WLE)}
 
@@
 \initializesizeandshifts
-\titleblock{90}{1}
+\titleblock{120}{1}
 % \setblocktitleheight{1}
-
 \addlogo[north west]{(2,-1)}{9cm}{./svg_images/Grass_GIS.pdf}
-\addlogo[north east]{(-2,-2.5)}{11cm}{./svg_images/IWMI_logo.pdf}
+\addlogo[north west]{(13,-3)}{19cm}{./svg_images/OSGeo_logo.pdf}
+\addlogo[north east]{(-2,-4.5)}{30cm}{./images/CR10583_1wle-iwmi_logo}
 
@@
 
+%Minted version Not working (+ compile needs -shell-escape)
+%\begin{minted}[frame=single,linenos,mathescape,fontsize=\small]{sh}
+%	i.group group=pca_group input=$(g.mlist type=rast pattern=*h28v07*EVI)
+%	i.pca input=pca_group output_prefix=pca_ percent=99 --o
+%\end{minted}
 }

### 2014-04-10 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: FEM logo added
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59665 15284696-431f-4ddb-bdfa-cd5b030d7da7
czech update
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59666 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 % x-coordinate by specifying explicitly the coordinate of the new block node as follows:
+% not needed:
 \usepackage[czech]{babel}
@@
 \title{\bigskip GRASS GIS Vector State of the Art  -  Gearing towards GRASS GIS 7 \bigskip}
-\author{Markus Metz$^1$, Martin Landa$^2$, Anna Petrasova$^3$, Vaclav Petras$^3$, Yann Chemin$^4$, Markus Neteler$^1$ and The GRASS GIS Development Team\\ \bigskip
+\author{Markus Metz$^1$, Martin Landa$^2$, Anna Petrášova$^3$, Vaclav Petráš$^3$, Yann Chemin$^4$, Markus Neteler$^1$ and The GRASS GIS Development Team\\ \bigskip
 $^1$ CRI, FEM, Italy, $^2$ CTU, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka}
@@
 %Please insert your institution logo here
-\addlogo[north east]{(-2,-2.5)}{4cm}{./svg_images/IWMI_logo.pdf}
+\addlogo[north east]{(-2,-2.5)}{4cm}{./svg_images/logo_FEM_CRI.pdf}
 \addlogo[north east]{(-2,-6.5)}{4cm}{./svg_images/IWMI_logo.pdf}

### 2014-04-10 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: add which texlive packages are needed
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59667 15284696-431f-4ddb-bdfa-cd5b030d7da7
Added some figures from Martin's PhD
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59672 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 % x-coordinate by specifying explicitly the coordinate of the new block node as follows:
-% not needed:
+% needed for authors:
 \usepackage[czech]{babel}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Linear features extraction}{
+\blocknode{Topology support}{
 \small
@@
 \begin{center}
- %\includegraphics[width=0.48\textwidth]{./images/imagery_spot_original}
- %\hspace{10mm}
- %\includegraphics[width=0.48\textwidth]{./images/imagery_spot_edge_1}
- %\newline
- Figure 1: Canny edge detector on a road network [2]
+ \includegraphics[width=0.48\textwidth]{./svg_images/grass6-topo}
+ \hspace{10mm}
+ \includegraphics[width=0.48\textwidth]{./svg_images/grass7-topo}
+ \newline
+ Figure 1: Topology changes from version 6 to 7 after [5]
 \end{center}
@@
 [3] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
-[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. 
+[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005.\\{}
+[5] & Landa, 2013. PhD thesis, CTU, Czech Republic.
 International Journal of Geoinformatics, 1(1): 51-61.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Interactive supervised classification}{
+\blocknode{Data Sources}{
 This
 \begin{center}
- %\includegraphics[width=0.47\textwidth]{./images/wxiclass1.png}
- %\newline
- Figure 3: Interactive image classification with coincidence plots (left side) \& histograms (right side)
+ \includegraphics[width=0.47\textwidth]{./images/grass-data-sources}
+  \newline
+ Figure 3: Data sources
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Satellite imagery products}{
-blabla
+\blocknode{Topology structure}{
+
+\begin{center}
+ \includegraphics[width=0.47\textwidth]{./images/topo-geo-grass}
+  \newline
+ Figure 3: Topology structure
+\end{center}
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Multi- and hyperspectral data analysis}{
+\blocknode{3D}{
 \smallskip
@@
 \begin{center}
- %\includegraphics[width=0.4\textwidth]{./images/unmix_pixels_spectrum.pdf}
- %\newline
- Figure 7: Unmixing principle (left), end-members selection (right), error space (below)
+ \includegraphics[width=0.4\textwidth]{./images/grass7-3d}
+ \newline
+ Figure 7: 3D handling
 \end{center}

### 2014-04-11 grassposter/2014_EGU_G7_Landscape/poster.tex
All Institutions Logo are there now
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59680 15284696-431f-4ddb-bdfa-cd5b030d7da7
GRASS & LAS screenshot added; avoid too small poster font
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59687 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \addlogo[north east]{(-2,-2.5)}{4cm}{./svg_images/logo_FEM_CRI.pdf}
-\addlogo[north east]{(-2,-6.5)}{4cm}{./svg_images/IWMI_logo.pdf}
-\addlogo[north east]{(-8,-2.5)}{4cm}{./svg_images/IWMI_logo.pdf}
+\addlogo[north east]{(-2,-6.5)}{4cm}{./svg_images/NC_State_Seal.pdf}
+\addlogo[north east]{(-8,-2.5)}{4cm}{./images/Logo_cvut.jpg}
 \addlogo[north east]{(-8,-6.5)}{4cm}{./svg_images/IWMI_logo.pdf}
@@
 \blocknode{Abstract}{
-\small The upcoming GRASS GIS 7 release improves not only raster processing and general design but the vector processing in the first place.
+% \small <<- too small for a poster!
+The upcoming GRASS GIS 7 release improves not only raster processing and general design but the vector processing in the first place.
 GRASS GIS, as a topological GIS, recognizes that the topology plays the key role in the vector processing and analysis.\newline
@@
 \blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
-\scriptsize
+% \scriptsize <<- too small for a poster!
 \begin{center}
@@
  %\newline
- Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]
+ %Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]
+
+ \includegraphics[width=0.4\textwidth]{./images/grass7_las_support}
+ %\newline
+ Figure 5: Example for LAS support in GRASS GIS 7: rapid LAS data assessment through binning
 \end{center}
@@
 \smallskip
-Unmixing
+Faces
 

### 2014-04-12 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape poster: more on topology added
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59697 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-\addlogo[north west]{(2,-1)}{9cm}{./svg_images/Grass_GIS.pdf}
+\addlogo[north west]{(2,-1)}{9cm}{svg_images/Grass_GIS.pdf}
 %Please insert your institution logo here
-\addlogo[north east]{(-2,-2.5)}{4cm}{./svg_images/logo_FEM_CRI.pdf}
-\addlogo[north east]{(-2,-6.5)}{4cm}{./svg_images/NC_State_Seal.pdf}
-\addlogo[north east]{(-8,-2.5)}{4cm}{./images/Logo_cvut.jpg}
-\addlogo[north east]{(-8,-6.5)}{4cm}{./svg_images/IWMI_logo.pdf}
+\addlogo[north east]{(-2,-2.5)}{4cm}{svg_images/logo_FEM_CRI.pdf}
+\addlogo[north east]{(-2,-6.5)}{4cm}{svg_images/NC_State_Seal.pdf}
+\addlogo[north east]{(-8,-2.5)}{4cm}{images/Logo_cvut.jpg}
+\addlogo[north east]{(-8,-6.5)}{4cm}{svg_images/IWMI_logo.pdf}
 
@@
 All topological cleaning tools have been optimized with regard to processing speed, robustness, and system requirements.\newline
-The topological engine comes with a new prototype for direct read/write support of Simple Features API/OGR. \newline
+The topological engine comes with a new prototype for direct read/write support of Simple Features API/OGR.\newline
 Additionally vector data can be directly exchanged with topological PostGIS 2 databases.\newline
@@
 \small
-blabla
+The GRASS GIS native vector format stores objects in a topology format.
+The OGC Simple Features can be imported into and exported from the GRASS GIS format through topological vector conversion.
+For attribute management several database management system (DBMS) with SQL support are supported including SQLite (default DB backend), PostgreSQL + PostGIS, MySQL, ODBC.
+
+The following \textbf{basic geometry types} can be edited directly: point, centroid, line, and boundary. A GRASS vector map can contain a combination of several different types.
+From these basic geometry types the following \textbf{derived geometry types} can be generated: area (closed ring of boundaries + centroid), isle (closed ring of boundaries, no centroid), and node (at both ends of lines/boundaries).
+Isles and Nodes are not visible to the user.
+
+% TODO: point to http://grass.osgeo.org/programming7/
+
+% TODO: 2. explain topology changes <<- needed?
+
+% TODO: show the internal format change or rather the actual model?
 \begin{center}
- \includegraphics[width=0.48\textwidth]{./svg_images/grass6-topo}
+ \includegraphics[width=0.48\textwidth]{odp_slides/grass7_basic_vector_types_digitizer}
  \hspace{10mm}
- \includegraphics[width=0.48\textwidth]{./svg_images/grass7-topo}
+ \includegraphics[width=0.48\textwidth]{odp_slides/grass7_derived_vector_types}
  \newline
- Figure 1: Topology changes from version 6 to 7 after [5]
+ Figure 1a: Basic and derived vector geometry types in GRASS GIS 7
+\end{center}
+
+\begin{center}
+ \includegraphics[width=0.48\textwidth]{svg_images/grass6-topo}
+ \hspace{10mm}
+ \includegraphics[width=0.48\textwidth]{svg_images/grass7-topo}
+ \newline
+ Figure 1b: Topology changes from version 6 to 7 after [5]
 \end{center}
@@
 [3] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
-[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005.\\{}
+[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1): 51-61.\\{}
 [5] & Landa, 2013. PhD thesis, CTU, Czech Republic.
-International Journal of Geoinformatics, 1(1): 51-61.
 \end{tabular}
@@
 \begin{minipage}{0.15\textwidth}
-\includegraphics[width=0.7in]{./images/iwmi_qr.pdf}
+\includegraphics[width=0.7in]{images/iwmi_qr.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.15\textwidth}
-\includegraphics[width=0.7in]{./images/grass_qr.pdf}
+\includegraphics[width=0.7in]{images/grass_qr.pdf}
 \end{minipage}
@@
 \noindent
-\includegraphics[width=\logowidth]{./svg_images/public_domain_logo.pdf}
+\includegraphics[width=\logowidth]{svg_images/public_domain_logo.pdf}
 \raisebox{0.7\height}{\logospace 2014 GRASS Development Team}
@@
 \begin{center}
- \includegraphics[width=0.47\textwidth]{./images/grass-data-sources}
+ \includegraphics[width=0.47\textwidth]{images/grass-data-sources}
   \newline
@@
 \begin{center}
- \includegraphics[width=0.47\textwidth]{./images/topo-geo-grass}
+ \includegraphics[width=0.47\textwidth]{images/topo-geo-grass}
   \newline
@@
 \begin{center}
- %\includegraphics[width=0.4\textwidth]{./images/ofs1}
+ %\includegraphics[width=0.4\textwidth]{images/ofs1}
  %\newline
@@
 
- \includegraphics[width=0.4\textwidth]{./images/grass7_las_support}
+ \includegraphics[width=0.4\textwidth]{images/grass7_las_support}
  %\newline
@@
 \begin{center}
- \includegraphics[width=0.4\textwidth]{./images/grass7-3d}
+ \includegraphics[width=0.4\textwidth]{images/grass7-3d}
  \newline

### 2014-04-12 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape poster: +PostGIS 2 support
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59698 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 All topological cleaning tools have been optimized with regard to processing speed, robustness, and system requirements.\newline
-The topological engine comes with a new prototype for direct read/write support of Simple Features API/OGR.\newline
+The topological engine comes with a new prototype for direct read/write support of OGR Simple Features API.\newline
 Additionally vector data can be directly exchanged with topological PostGIS 2 databases.\newline
@@
 Isles and Nodes are not visible to the user.
+Furthermore face, kernel (3D centroid) and volume (3D area) as defined in the format.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\getcurrentrow{box}
-\coordinate (funkcionalita) at (box.south west);
-\coordinate (funkcionalitaeast) at (box.east);
-\coordinate (screenshot) at (box.north west);
-
-\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
-% \scriptsize <<- too small for a poster!
-\begin{center}
-\begin{tabular}{rp{0.9\textwidth}}
-[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
-[2] & Petráš, 2012. M.Sc. Thesis, OSGeoREL, FCE CTU, Prague.\\{}
-[3] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
-[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1): 51-61.\\{}
-[5] & Landa, 2013. PhD thesis, CTU, Czech Republic.
-\end{tabular}
-\end{center}
-\smallskip
-\hrulefill
-\vspace{-5pt}
-
-\begin{center}
-\begin{tabular}{cp{0.9\textwidth}}
-\begin{minipage}{0.15\textwidth}
-\includegraphics[width=0.7in]{images/iwmi_qr.pdf}
-\end{minipage}
-
-\begin{minipage}{0.3\textwidth}
-\small {\url{www.iwmi.org}}
-\end{minipage}
-
-\begin{minipage}{0.15\textwidth}
-\includegraphics[width=0.7in]{images/grass_qr.pdf}
-\end{minipage}
-
-\begin{minipage}{0.3\textwidth}
-\small {\url{grass.osgeo.org}}
-\end{minipage}
-\end{tabular}
-\end{center}
-
-\hrulefill
-\vspace{14pt}
-\begin{center}
-\newcommand{\logowidth}{5em}
-\newcommand{\logospace}{\hspace{0.1em}}
-\noindent
-\includegraphics[width=\logowidth]{svg_images/public_domain_logo.pdf}
-\raisebox{0.7\height}{\logospace 2014 GRASS Development Team}
-\end{center}
-}
+% ref was here, moved to last column
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{GRASS GIS-PostGIS data provider: PostGIS 2 support}{
+\smallskip
+
+% TODO: finalize
+The native GRASS-PostGIS data provider supports
+
+PostGIS 2 Topology.
+It allows the GRASS vector library to read and write PostGIS data directly without any external library.
+The GRASS-PostGIS data provider has been implemented using \textit{libpq} library.
+
+%See also \url{http://trac.osgeo.org/grass/wiki/Grass7/VectorLib/PostGISInterface}
+
+% http://grasswiki.osgeo.org/wiki/PostGIS_Topology
+The support of PostGIS 2 Topology in GRASS GIS 7 is as follows:
+\begin{itemize}
+\item Points are stored as isolated nodes (\textit{containing\_face} is null),
+\item Centroids are stored as isolated nodes (\textit{containing\_face} is not null),
+\item Lines are stored as edges (\textit{left\_face} and \textit{right\_face} is 0),
+\item Boundaries are stored as edges,
+\item Areas are stored as faces (with id > 0),
+\item Isles are stored as faces (with id <= 0) (including universal face defined by PostGIS Topology).
+\end{itemize}
+
+Additional topological data related to nodes, lines, areas, and isles are stored in separated tables.
+
+{\bf Dedicated modules}
+
+\begin{itemize}
+ \item {\bf v.out.postgis:} Exports a vector map layer to PostGIS feature table.
+ \item {\bf v.} blabla
+\end{itemize}
+}
+
 \blocknode{Lidar}{
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\getcurrentrow{box}
+\coordinate (funkcionalita) at (box.south west);
+\coordinate (funkcionalitaeast) at (box.east);
+\coordinate (screenshot) at (box.north west);
+
+\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
+% \scriptsize <<- too small for a poster!
+\begin{center}
+\begin{tabular}{rp{0.9\textwidth}}
+[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
+[2] & Petráš, 2012. M.Sc. Thesis, OSGeoREL, FCE CTU, Prague.\\{}
+[3] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
+[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1): 51-61.\\{}
+[5] & Landa, 2013. PhD thesis, CTU, Czech Republic.
+\end{tabular}
+\end{center}
+\smallskip
+\hrulefill
+\vspace{-5pt}
+
+\begin{center}
+\begin{tabular}{cp{1.9\textwidth}}
+\begin{minipage}{0.25\textwidth}
+\includegraphics[width=2in]{svg_images/OSGeo_project.pdf}
+\end{minipage}
+
+\begin{minipage}{0.3\textwidth}
+%\small{\url{www.osgeo.org}}
+\url{www.osgeo.org}
+\end{minipage}
+
+\begin{minipage}{0.15\textwidth}
+\includegraphics[width=1.2in]{images/grass_qr.pdf}
+\end{minipage}
+
+\begin{minipage}{0.3\textwidth}
+%\small {\url{grass.osgeo.org}}
+\url{grass.osgeo.org}
+\end{minipage}
+\end{tabular}
+\end{center}
+
+\hrulefill
+\vspace{14pt}
+\begin{center}
+\newcommand{\logowidth}{5em}
+\newcommand{\logospace}{\hspace{0.1em}}
+\noindent
+\includegraphics[width=\logowidth]{svg_images/public_domain_logo.pdf}
+\raisebox{0.7\height}{\logospace 2014 GRASS Development Team}
+\end{center}
+}
+
 \end{tikzpicture}

### 2014-04-16 grassposter/2014_EGU_WD_Landscape/poster.tex
updated poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59744 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \end{center}
-
+\begin{center}
+	\begin{tabular}{cc}
+ 	\includegraphics[width=0.45\textwidth]{./images/RGB321_PCA_Ta_2000}
+ 	& 
+ 	\includegraphics[width=0.45\textwidth]{./images/SEG_PCA_Ta_2000}
+	\end{tabular}
+\end{center}
+Using the 50 first PCA components of the Transpiration data for year 2000, the object types that can be extracted by object-based classification were analysed.
+It turns out that the recession cropping around Tonle Sap and the rainfed cropping systems of Eastern Thailand are clearly extracted.
+However, the recession cropping in Tonle Sap only has one main class, which is different when using 2000-2014 EVI PCA classification (central part of the poster).
+It is thought that both the 500x500m resolution and the yearly changes in flooding height in Tonle Sap are driving the separation of the recession cropping area, thus not seen here with one year (2000) and 1x1km pixel size.\newline
 }
@@
 [4] & McGarigal \& Marks, 1995. FRAGSTATS. USDA For. Serv. Gen. Tech. Rep. PNW-351.\\{}
-[5] & Momsen \& Metz, 2012. GSoC project: Segmentation algorithm.
+[5] & Momsen \& Metz, 2012. GSoC project: Segmentation algorithm.\\{}
+[6] & Eastman \& Fulk, 1993. Photogramm. Eng. Remote Sens. 59(8), 1307-1312.
 \end{tabular}
@@
 	&
-	A summary of the code needed to reach this point of analysis is here.\newline
-	{\footnotesize \fontfamily{pcr}\selectfont i.group \textcolor{blue}{group}=pca\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=*h28v07*EVI)\newline
-	i.pca \textcolor{blue}{input}=pca\_group \textcolor{blue}{output\_prefix}=pca\_ \textcolor{blue}{percent}=99 --o\newline}
+	Long sequence time series PCA provides a comprehensive indicator of change events in time series of spatial environmental data (Eastman \& Fulk 1993)1.
+Principal Components Analysis undertakes linear transformation of a set of image bands to create a new set of images that are uncorrelated.
+This set of principal component images can be considered equivalent to bands of a multi-spectral image.
+Each image represents a different portion of spectral variability in the original image data set.
+The clusters yielded by subjecting the PCA component images to iterative self-organising cluster routine each express a particular signature, corresponding to a unique combination of characteristics in terms of the environmental variable under study.\newline
  	\end{tabular}\newline
 \end{center}
+The methodology involves the following steps: 1) a time series of EVI composites is subjected to PCA; 2) the Principal Component images explaining most (ca.
+95\%) of spatio-temporal variation in the time series, are used as input layers or ‘bands’ in the iterative self-organising cluster routine; 3) for each spatial cluster in the image output a Boolean mask is created and 4) overlaid (multiplied) with the original time series, which results in 5) a VI time series for each cluster in the output.
+Analysis of the temporal signature for each cluster reveals seasonal or long-term trends in VI that occur within the system.
+%A summary of the code needed to reach this point of analysis is here.\newline
+%{\footnotesize \fontfamily{pcr}\selectfont i.group \textcolor{blue}{group}=pca\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=*h28v07*EVI)\newline
+%i.pca \textcolor{blue}{input}=pca\_group \textcolor{blue}{output\_prefix}=pca\_ \textcolor{blue}{percent}=99 --o\newline}
 
@@
 \blocknode{Temporal PCA-based classification}{
-Balaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa
-aaaaaaaaaaaaaaaaaaaaaaaaaaaaaa\newline
 \begin{center}
@@
 	\end{tabular}
-	\end{tabular}\newline
-	Figure 2: Temporal 
+	\end{tabular}
 \end{center}
-
+This application employs a time series of MODIS EVI 16-day composites at 500 m resolution (MOD13A1) running over 14 years (2000 to near real-time).
+The h28v07 tile covers large part of the Mekong River Basin in Southeast Asia.
+We analyse a subset covering the Vietnamese Mekong Delta (VMD) and the Tonle Sap in Cambodia (TSC).
+\newline
+The results discern large areas in VMD dominated by irrigated triple crop rice agro-ecosystems, followed by seasonal flooding near the end of each year, as well as long-term change from double cropping to triple cropping in adjacent areas from 2008 onward.\newline
 }
@@
 	\begin{tabular}{cc}
-	\raisebox{-0.7\totalheight}{\includegraphics[width=0.45\textwidth]{./images/MSUBAS_TS}}
+	\raisebox{-0.5\totalheight}{\includegraphics[width=0.45\textwidth]{./images/MSUBAS_TS}}
 	&
-	\begin{tabular}{c}
+	\begin{tabular}{p{0.5\textwidth}}
  	\includegraphics[width=0.45\textwidth]{./svg_images/EVI_distance_from_tonle_sap}\\
-	bllaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa
+	The results for TSC show that the range between $EVI_{min}$ and $EVI_{max}$ in floodplains surrounding the Tonle Sap Lake decreases spatially with distance from dry season margins of the lake.
+This pattern is indicative of flood recession cropping systems and seasonally flooded natural vegetation around the lake, which expands dramatically in size during the wet season each year, inundating large areas of floodplain, which drain towards the dry season.
+We used the blue band of MOD13 to provide an additional indicator of flooding, handling the assumption of seasonal flood occurrence if ‘Blue’ approaches or exceeds ‘EVI’.
+The results in TSC do not discern any long-term trends in land cover and land use.\newline
 	\end{tabular}
@@
 \smallskip
-
+The Euclidian distance plot depicts graphically the resemblance between spatio-temporal signatures of the systems under study.
+Similar landscape groups can be distinguished at Euclidean distance of 2.1 or less.
+Euclidean distance of 1.1 or less assumes that dissimilarity between systems is not statistically significant at that level.
+\newline
 \begin{center}
@@
 }
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Biotic Zoning}{
+\smallskip
+Object based classification (\textit{i.segment}) of the sum transpiration for each year has been done and merged, resulting areas were clumped (\textit{r.clump}) and averaged statistics of yearly transpiration extracted (\textit{r.stats.zonal}).\newline
+\begin{center}
+	\includegraphics[width=0.45\textwidth]{./images/seg_ta_years_clump_reclass_ta_avg}
+\end{center}
+This perspective proposes that irrigated areas along the Mekong may not be transpiring as much as the recession cropping areas around Tonle Sap.
+Whether the transpiration in recession zones is actually used by crops all the time depends on the opportunity of farming intensification and risk avoidance.\newline
+}
 

### 2014-04-16 grassposter/2014_EGU_WD_Landscape/poster.tex
Updated poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59745 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 Object based classification (\textit{i.segment}) of the sum transpiration for each year has been done and merged, resulting areas were clumped (\textit{r.clump}) and averaged statistics of yearly transpiration extracted (\textit{r.stats.zonal}).\newline
+Rainfed cropping in Isarn (Part 1) is clearly identified as low transpiration signal (red colour), Recession cropping areas around Tonle Sap (Part 2 \& 3) are high signals (Blue and green) with both noise and a negative impact on transpiration in Part 2 around mid-year (Green signal drop).
+A southern area (Part 4) of most probably rainfed benefiting from flood to some extent to propose some kind of recession cropping with a mid-year transpiration raise signal (Violet).\newline
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{./images/seg_ta_years_clump_reclass_ta_avg}
-\end{center}
+	\begin{tabular}{cc}
+ 	\begin{tabular}{p{0.5\textwidth}}
+ 	\includegraphics[width=0.45\textwidth]{./images/seg_ta_years_clump_reclass_ta_avg}\\
+ 	\vspace{5mm}
  	This perspective proposes that irrigated areas along the Mekong may not be transpiring as much as the recession cropping areas around Tonle Sap.
 Whether the transpiration in recession zones is actually used by crops all the time depends on the opportunity of farming intensification and risk avoidance.\newline
+	\end{tabular}
+ 	& 
+ 	\begin{tabular}{c}
+ 	\includegraphics[width=0.45\textwidth]{./images/Ta_loc}\\
+ 	\includegraphics[width=0.45\textwidth]{./images/Ta}
+	\end{tabular}
+	\end{tabular}
+\end{center}
 }

### 2014-04-16 grassposter/2014_EGU_WD_Landscape/poster.tex
update poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59746 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Acknowledgements}{
+\smallskip
+The authors would like to acknowledge the WLE Seed funding for innovative research.\newline
+}
+
 \startthirdcolumn
@@
 Object based classification (\textit{i.segment}) of the sum transpiration for each year has been done and merged, resulting areas were clumped (\textit{r.clump}) and averaged statistics of yearly transpiration extracted (\textit{r.stats.zonal}).\newline
-Rainfed cropping in Isarn (Part 1) is clearly identified as low transpiration signal (red colour), Recession cropping areas around Tonle Sap (Part 2 \& 3) are high signals (Blue and green) with both noise and a negative impact on transpiration in Part 2 around mid-year (Green signal drop).
-A southern area (Part 4) of most probably rainfed benefiting from flood to some extent to propose some kind of recession cropping with a mid-year transpiration raise signal (Violet).\newline
+Rainfed cropping in Isarn (Part 1) is clearly identified from the low transpiration signal (red colour), recession cropping areas around Tonle Sap (Part 2 \& 3) have high signals (blue and green) with both noise and a negative impact on transpiration in Part 2 around mid-year (green signal drop).
+A southern area (Part 4), most probably rainfed, benefits from flood to some extent, it is proposed that some kind of recession cropping is practised, as there is a mid-year transpiration signal raise (violet).
 \begin{center}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Conclusions}{
+\smallskip
+The last ten years have seen intensification of cropping systems in the lower Mekong, where some triple cropping started to be practised.
+Landscapes relating to non-irrigated cropping systems are rainfed (as found in Isarn) or recession cropping (as found around Tonle Sap).
+There is a decrease of vegetation index range proportionally to the distance from Tonle Sap, interpreted as the transient surface water creating a reduction of the signal.
+\newline
+}
+
 \end{tikzpicture}

### 2014-04-16 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape poster: ref fix
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59699 15284696-431f-4ddb-bdfa-cd5b030d7da7
2014_EGU_G7_Landscape: standard box for references and PyGRASS and TGRASS added
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59747 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
+% \blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{ % special smaller box
+\blocknode{References}{
 % \scriptsize <<- too small for a poster!
@@
 [1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
-[2] & Petráš, 2012. M.Sc. Thesis, OSGeoREL, FCE CTU, Prague.\\{}
-[3] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
-[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1): 51-61.\\{}
-[5] & Landa, 2013. PhD thesis, CTU, Czech Republic.
+[2] & Gebbert \& Pebesma, 2014. TGRASS: A temporal GIS for field based environmental modeling, Environmental Modelling \& Software 53:1–12.\\{}
+[3] & Zambelli \& Gebbert \& Ciolli, 2013. PyGRASS: An Object Oriented Python API for GRASS GIS. ISPRS International Journal of Geo-Information 2.1:201-219.\\{}
+[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1):51-61.\\{}
+[5] & Landa, 2013. Vektorová architektura systému GRASS GIS [GRASS GIS Vector Architecture]. PhD thesis, CTU, Czech Republic.
 \end{tabular}

### 2014-04-16 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: added 3D house to 3D section
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59752 15284696-431f-4ddb-bdfa-cd5b030d7da7
2014_EGU_G7_Landscape: boxes for TGRASS and PyGRASS, PyGRASS Point and Line code, references with names
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59753 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-\title{\bigskip GRASS GIS Vector State of the Art  -  Gearing towards GRASS GIS 7 \bigskip}
+\title{\bigskip GRASS GIS Vector State of the Art  --  Gearing towards GRASS GIS 7 \bigskip}
 \author{Markus Metz$^1$, Martin Landa$^2$, Anna Petrášova$^3$, Vaclav Petráš$^3$, Yann Chemin$^4$, Markus Neteler$^1$ and The GRASS GIS Development Team\\ \bigskip
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{PyGRASS: fast Python API}{
+[Zambelli 2013]
+
+>>> from grass.pygrass.vector.geometry import Point, Line
+
+>>> point = Point()
+>>> point.x = 150.65
+>>> point.y = 368.50
+>>> point
+>>> Point(150.650000, 368.500000)
+>>> point.distance(Point(160.2, 372.6))
+10.39290623454286
+%%%%>>> point.get_wkt()
+'POINT(150.650000 368.500000)'
+
+>>> line = Line([(5, 12), (6, 13), (4, 19)])
+>>> line.bbox()
+Bbox(19.0, 12.0, 6.0, 4.0)
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{TGRASS: temporal framework}{
+[Gebbert 2014]
+}
+
 \startthirdcolumn
@@
 \begin{center}
- \includegraphics[width=0.4\textwidth]{images/grass7-3d}
- \newline
- Figure 7: 3D handling
+\begin{tabular}{lcr}
+\includegraphics[width=0.28\textwidth]{images/grass7-3d}
+& ~ &
+\includegraphics[width=0.49\textwidth]{images/house3D}\\
+ Figure X: 3D handling & & Figure X: Chancellor's House, North Carolina State University
+\end{tabular}
 \end{center}
@@
 \begin{center}
-\begin{tabular}{rp{0.9\textwidth}}
-[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
-[2] & Gebbert \& Pebesma, 2014. TGRASS: A temporal GIS for field based environmental modeling, Environmental Modelling \& Software 53:1–12.\\{}
-[3] & Zambelli \& Gebbert \& Ciolli, 2013. PyGRASS: An Object Oriented Python API for GRASS GIS. ISPRS International Journal of Geo-Information 2.1:201-219.\\{}
-[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1):51-61.\\{}
-[5] & Landa, 2013. Vektorová architektura systému GRASS GIS [GRASS GIS Vector Architecture]. PhD thesis, CTU, Czech Republic.
+\begin{tabular}{rp{0.8\textwidth}}
+[Neteler 2012] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
+[Gebbert 2014] & Gebbert \& Pebesma, 2014. TGRASS: A temporal GIS for field based environmental modeling, Environmental Modelling \& Software 53:1–12.\\{}
+[Zambelli 2013] & Zambelli \& Gebbert \& Ciolli, 2013. PyGRASS: An Object Oriented Python API for GRASS GIS. ISPRS International Journal of Geo-Information 2.1:201-219.\\{}
+[Neteler 2005] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1):51-61.\\{}
+[Landa 2013] & Landa, 2013. Vektorová architektura systému GRASS GIS [GRASS GIS Vector Architecture]. PhD thesis, CTU, Czech Republic.
 \end{tabular}

### 2014-04-17 grassposter/2014_EGU_WD_Landscape/poster.tex
update poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59754 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 This information is then fractionated into biotic (transpiration) and abiotic (evaporation) parts using vegetation fraction.\newline\linebreak
-The accumulated transpiration (t.rast.aggregate) is subjected to Landscape analysis (r.li.*) for search of patchiness and diversity indices [4].
+The accumulated transpiration (t.rast.aggregate) is subjected to Landscape analysis (r.li.*, inspired from [4]) for search of patchiness and diversity indices (not shown).
 Further analysis of transpiration is also done with the object oriented classifier (i.segment) for spatiotemporal objects within the transpiration original dataset, the accumulated one and the Landscape indices, respectively.\newline
@@
 Analysis of the temporal signature for each cluster reveals seasonal or long-term trends in VI that occur within the system.
-%A summary of the code needed to reach this point of analysis is here.\newline
-%{\footnotesize \fontfamily{pcr}\selectfont i.group \textcolor{blue}{group}=pca\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=*h28v07*EVI)\newline
-%i.pca \textcolor{blue}{input}=pca\_group \textcolor{blue}{output\_prefix}=pca\_ \textcolor{blue}{percent}=99 --o\newline}
 
-%Minted version Not working (+ compile needs -shell-escape)
-%\begin{minted}[frame=single,linenos,mathescape,fontsize=\small]{sh}
-%	i.group group=pca_group input=$(g.mlist type=rast pattern=*h28v07*EVI)
-%	i.pca input=pca_group output_prefix=pca_ percent=99 --o
-%\end{minted}
 }
@@
 \smallskip
-The authors would like to acknowledge the WLE Seed funding for innovative research.\newline
+The authors would like to acknowledge the WLE  (\url{wle.cgiar.org}) Seed funding for innovative research.\newline
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Recession cropping \& natural vegetation}{
+\blocknode{From recession cropping (UL) to natural vegetation (LR)}{
 \begin{center}
@@
 
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{GRASS GIS script for MODIS PCA \& segmentation of PCA}{
+\smallskip
+{\footnotesize \fontfamily{pcr}\selectfont 
+\textbf{\#Select MODIS EVI archive\newline} 
+i.group \textcolor{blue}{group}=pca\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=*h28v07*EVI)\newline
+\textbf{\#Run the PCA on the EVI archive\newline}
+i.pca \textcolor{blue}{input}=pca\_group \textcolor{blue}{output\_prefix}=pca \textcolor{blue}{percent}=99 --o\newline
+\textbf{\#As an example, you can select the 1$^{st}$ to the 9$^{th}$ PCA members\newline}
+i.group \textcolor{blue}{group}=ta\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=pca.[123456789] sep=,) \newline
+\textbf{\#and run an object-based classification analysis on them\newline}
+i.segment \textcolor{blue}{group}=ta\_group \textcolor{blue}{output}=seg\_ta \textcolor{blue}{threshold}=0.9 \textcolor{blue}{memory}=5000 \textcolor{blue}{iterations}=50 --o \& \newline}
+
+%Minted version Not working (+ compile needs -shell-escape)
+%\begin{minted}[frame=single,linenos,mathescape,fontsize=\small]{sh}
+%	i.group group=pca_group input=$(g.mlist type=rast pattern=*h28v07*EVI)
+%	i.pca input=pca_group output_prefix=pca_ percent=99 --o
+%\end{minted}
 }

### 2014-04-17 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: using listings package in a separate document
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59755 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \usepackage[margin=\margin cm, paperwidth=197cm, paperheight=100cm]{geometry}
+
+\usepackage{listings}
 
@@
  \newline
- Figure 1b: Topology changes from version 6 to 7 after [5]
+ Figure 1b: Topology changes from version 6 to 7 after [Landa 2013]
 \end{center}
@@
 \blocknode{PyGRASS: fast Python API}{
-[Zambelli 2013]
+PyGRASS [Zambelli 2013] is an object-oriented Python API which allows efficient manipulation with vectors.
+It is easy-to-use but its performance is comparable to C code since it calls GRASS C API behind the scenes.
 
->>> from grass.pygrass.vector.geometry import Point, Line
-
->>> point = Point()
->>> point.x = 150.65
->>> point.y = 368.50
->>> point
->>> Point(150.650000, 368.500000)
->>> point.distance(Point(160.2, 372.6))
-10.39290623454286
-%%%%>>> point.get_wkt()
-'POINT(150.650000 368.500000)'
-
->>> line = Line([(5, 12), (6, 13), (4, 19)])
->>> line.bbox()
-Bbox(19.0, 12.0, 6.0, 4.0)
+\includegraphics[width=0.9\textwidth]{texpdfs/pygrass_code}
 

### 2014-04-17 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: added TGRASS content
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59756 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \usepackage{url}
+\usepackage{alltt}
+\usepackage{textcomp}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{TGRASS: temporal framework}{
-[Gebbert 2014]
-}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\blocknode{TGRASS: temporal framework}{
+TGRASS [Gebbert 2014] provides support for large spatio-temporal data handling and analysis, and is fully integrated into GRASS GIS 7.
+It introduces the concept of space-time dataset as a series of vector, raster, or 3D raster data with temporal metadata.
+In the simple example below, we computed a series of vector data representing particles in a water flow simulation,
+created a space-time dataset and registered the vectors to this dataset based on time stamps assigned during the vector creation.
+The result can be then quickly visualized using GRASS GIS Animation Tool.
+
+{\small
+\begin{alltt}
+r.sim.water -t elevation=elev\_lid792\_1m dx=dx dy=dy depth=depth outwalk=walker outiter=1
+
+\textcolor{DarkGreen}{t.create} output=particles type=stvds temporaltype=relative semantictype=mean title="Particles"~desc="Particles"
+
+\textcolor{DarkGreen}{t.register} input=particles maps=\textasciigrave g.mlist --q type=vect pattern=walker* separator=,\textasciigrave{} type=vect
+
+g.gui.animation stvds=particles
+\end{alltt}}
+
+\begin{center}
+\includegraphics[width=\textwidth]{images/particles}
+\end{center}
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \getcurrentrow{box}

### 2014-04-17 grassposter/2014_EGU_WD_Landscape/poster.tex
final version
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59760 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \usepackage[dvipsnames,svgnames]{xcolor}
+\usepackage{tikzposter} % here most of the things are defined
 \usepackage{minted} %code highlighting, not working yet
-\usepackage{tikzposter} % here most of the things are defined
 % change parameters only after this line You can also start a new column with an arbitrary 
@@
 [5] & Momsen \& Metz, 2012. GSoC project: Segmentation algorithm.\\{}
-[6] & Eastman \& Fulk, 1993. Photogramm. Eng. Remote Sens. 59(8), 1307-1312.
+[6] & Eastman \& Fulk, 1993. Photogramm. Eng. Remote Sens. 59(8), 1307-1312.\\{}
+[7] & Clarke, 1993. Aust. J. Ecol. 18, 117-143.
 \end{tabular}
@@
 \smallskip
-The authors would like to acknowledge the WLE  (\url{wle.cgiar.org}) Seed funding for innovative research.\newline
+The authors would like to acknowledge the CGIAR Research Program on Water, Land and Ecosystems (WLE ; \url{wle.cgiar.org}) Innovation Fund.\newline
 }
@@
 %\begin{minted}[frame=single,linenos,mathescape,fontsize=\small]{sh}
+%	#Select MODIS EVI archive
 %	i.group group=pca_group input=$(g.mlist type=rast pattern=*h28v07*EVI)
+%	#Run the PCA on the EVI archive
 %	i.pca input=pca_group output_prefix=pca_ percent=99 --o
+%	#As an example, you can select the 1$^{st}$ to the 9$^{th}$ PCA members
+%	i.group group=ta_group input=\$(g.mlist type=rast pattern=pca.[123456789] sep=,)
+%	#and run an object-based classification analysis on them
+%	i.segment group=ta_group output=seg_ta threshold=0.9 memory=5000 iterations=50 --o \&
 %\end{minted}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Euclidian Distance plotting}{
+\blocknode{Non-metric multidimensional scaling}{
 \smallskip
-The Euclidian distance plot depicts graphically the resemblance between spatio-temporal signatures of the systems under study.
-Similar landscape groups can be distinguished at Euclidean distance of 2.1 or less.
-Euclidean distance of 1.1 or less assumes that dissimilarity between systems is not statistically significant at that level.
-\newline
 \begin{center}
@@
 \end{center}
-
+We employ a non-parametric multivariate method to display the relative dissimilarity between these a priori defined clusters [7].
+This non-metric multidimensional scaling (MDS) configuration depicts graphically the dissimilarity between spatio-temporal signatures of the systems under study, from which distinct clusters of landscapes emerge.
+Similar landscape groups can be distinguished at Euclidean distance of 2.1 or less.
+\newline
 }

### 2014-04-17 grassposter/2014_EGU_WD_Landscape/poster.tex
update credits
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59761 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \smallskip
-The authors would like to acknowledge the CGIAR Research Program on Water, Land and Ecosystems (WLE ; \url{wle.cgiar.org}) Innovation Fund.\newline
+\begin{tabular}{p{0.70\textwidth} c}
+	The authors would like to acknowledge the CGIAR Research Program on Water, Land and Ecosystems (WLE ; \url{wle.cgiar.org}) Innovation Fund.
+	&
+	\hspace{3mm}
+	\raisebox{-0.5\totalheight}{\includegraphics[width=0.27\textwidth]{./images/WLE}}
+\end{tabular}
 }
@@
 \startthirdcolumn
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{From recession cropping (UL) to natural vegetation (LR)}{
+\begin{center}
+	\begin{tabular}{cc}
+ 	\begin{tabular}{c}
+ 	\includegraphics[width=0.5\textwidth]{./images/cl3_avg}\\
+ 	\includegraphics[width=0.5\textwidth]{./images/cl65_avg}
+	\end{tabular}
+ 	& 
+ 	\begin{tabular}{c}
+ 	\includegraphics[width=0.5\textwidth]{./images/cl45_avg}\\
+ 	\includegraphics[width=0.5\textwidth]{./images/cl10_avg}
+	\end{tabular}
+	\end{tabular}\newline
+\end{center}
+
+}
 
@@
 The results in TSC do not discern any long-term trends in land cover and land use.\newline
-	\end{tabular}
- 	\end{tabular}\newline
-\end{center}
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{From recession cropping (UL) to natural vegetation (LR)}{
-\begin{center}
-	\begin{tabular}{cc}
- 	\begin{tabular}{c}
- 	\includegraphics[width=0.5\textwidth]{./images/cl3_avg}\\
- 	\includegraphics[width=0.5\textwidth]{./images/cl65_avg}
-	\end{tabular}
- 	& 
- 	\begin{tabular}{c}
- 	\includegraphics[width=0.5\textwidth]{./images/cl45_avg}\\
- 	\includegraphics[width=0.5\textwidth]{./images/cl10_avg}
 	\end{tabular}

### 2014-04-17 grassposter/2014_EGU_M3_Landscape/poster.tex
Submitting Moon poster draft
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59768 15284696-431f-4ddb-bdfa-cd5b030d7da7

\documentclass[landscape,a0,final]{a0poster}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikzposter} % here most of the things are defined
% change parameters only after this line You can also start a new column with an arbitrary 
% x-coordinate by specifying explicitly the coordinate of the new block node as follows:
\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage{wrapfig}
\usepackage{url}

%Used for better control on code display

\usepackage[margin=\margin cm, paperwidth=197cm, paperheight=100cm]{geometry}

% \setbackgrounddarkcolor{ForestGreen!70!black}
% \setbackgroundlightcolor{YellowGreen!90!}

% \setfirstcolor{YellowGreen!80!}
% \setsecondcolor{gray!80!}
% \setthirdcolor{red!80!black}

\title{Improving the Apollo 12 landing site mapping\\with Chandrayaan $M^3$ data}
\author{Yann Chemin$^{1,2}$, Ian Crawford$^1$, Roberto Bugiolacchi$^1$, Huma Irfan$^1$ and Louise Alexander$^1$\\
$^1$Birkbeck College, University of London, U.K. ~ $^2$IWMI, Pelawatte, Sri Lanka}

\usetemplate{1}
\setinstituteshift{1}

\setblocktitleheight{2}
\setblockspacing{1}

\begin{document}
\ClearShipoutPicture
\AddToShipoutPicture{\BackgroundPicture}
\noindent
\tikzstyle{every picture}+=[remember picture]
\begin{tikzpicture}
\initializesizeandshifts
\titleblock{90}{1}
% \setblocktitleheight{1}

%\addlogo[north west]{(2,-1)}{9cm}{./svg_images/Grass_GIS.pdf}
%\addlogo[north east]{(-2,-2.5)}{11cm}{./svg_images/IWMI_logo.pdf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Abstract}{
\small \noindent The geology of the Apollo 12 landing site has been the subject of many studies, including recently by Korotev et al. (2011) and Snape et al. (2013). This research attempts to bring additional understanding from a remote sensing perspective using the Moon Mineralogy Mapper ($M^3$) sensor data, onboard the Chandrayaan lunar orbiter. This has a higher spatial-spectral resolution sensor than the Clementine UV-Vis sensor and provides the opportunity to study the lunar surface with detailed spectral signatures.\newline

Mapping of FeO (wt\%) and TiO 2 (wt\%) is done using the methods of Lucey et al. (2000) and Wilcox et
al. (2005). A FeO \& TiO 2 processing module (i.feotio2) is made specifically for this research within the Free \& Open Source Software GRASS GIS (Neteler et al., 2012). Attempts will be made to estimate the lava flow thickness using the method of Bugiolacchi et al. (2006) and individual lava layers thicknesses (Weider et al., 2010). Integration of this new information will be put in perspective and integrated with previous work. Analysis from the combined higher spatial and spectral resolutions will improve the accuracy of the geological mapping at the Apollo 12 landing site.\newline
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Previous interpretations}{
Korotev et al. (2011) reviewed the lunar research done until recently, with a special interest in the Apollo 12 landing site and its vicinity. Among the information newly deducted, are a geological context block diagram 1 (Figure below) along with an Apollo 12 landing site interpretive cross-section. Fortezzo and Hare (2013) completed the digital renovation of the 1:5,000,000 lunar geological maps series, enhanced with LOLA-LRO information.\newline
\begin{center}
	\begin{tabular}{cc}
		\includegraphics[width=0.45\textwidth]{./images/Korotev_block}
		&
		\includegraphics[width=0.45\textwidth]{./images/A12region}
	\end{tabular}\newline
Figure 2: a) Korotev et al (2011) geological block of Apollo 12 landing site\\
b)  Fortezzo and Hare (2013) geological maps series with moon nomenclature.
\end{center}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\getcurrentrow{box}
\coordinate (funkcionalita) at (box.south west);
\coordinate (funkcionalitaeast) at (box.east);
\coordinate (screenshot) at (box.north west);

\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
\scriptsize
\begin{flushleft}
\begin{tabular}{rp{0.9\textwidth}}
Bugiolacchi et al. (2006) &  Planetary Science. 41(2):285-304.\\{}
Fortezzo et al. (2013) & LPI Contributions, 1719:2114.\\{}
Korotev et al. (2011) & Geochimica et Cosmochimica Acta. 75(6):1540-1573.\\{}
Lucey et al. (2000) & J. Geophys. Res. 105(E8): 20297-20305.\\{}
Neteler et al. (2012) & Environment \& Modeling Software, 31:124-130.\\{}
Snape et al. (2013) & LPSC Abstracts 44:1044.\\{}
Weider et al. (2010) & Icarus, 209, 323-336.\\{}
Wilcox et al. (2005) & J. Geophys. Res. 110(E11):2156-2202.\\{}
\end{tabular}
\end{flushleft}
\smallskip
\hrulefill
\vspace{-5pt}

\begin{center}
\begin{tabular}{cp{0.9\textwidth}}
\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/grass_qr.pdf}
\end{minipage}

\begin{minipage}{0.3\textwidth}
\small {\url{www.bbk.ac.uk}}
\end{minipage}

\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/grass_qr.pdf}
\end{minipage}

\begin{minipage}{0.3\textwidth}
\small {\url{grass.osgeo.org}}
\end{minipage}
\end{tabular}
\end{center}

\hrulefill
\vspace{14pt}
\begin{center}
\newcommand{\logowidth}{5em}
\newcommand{\logospace}{\hspace{0.1em}}
\noindent
\includegraphics[width=\logowidth]{./svg_images/public_domain_logo.pdf}
%\raisebox{0.7\height}{\logospace 2013 GRASS Development Team}
\end{center}
}

\startsecondcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Clementine data}{
\smallskip

\begin{center}
 \includegraphics[width=0.75\textwidth]{./images/Clementine}
 \newline
 Figure 1: Clementine RGB153, segmentation and FeO (wt\%) per segmentation class.
\end{center}
}

\startthirdcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{$M^3$ data analysis}{
nn
\newline

\begin{center}
 \includegraphics[width=0.5\textwidth]{./images/M3FEOlarge}
 \newline
 Figure 3: FeO
\end{center}

}

\startfourthcolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Segmentation of PCA elements}{
GRASS GIS segmentation of the PCA of the full temporal archive of MODIS EVI.
\newline

A summary of the code needed to reach this point of analysis is here.\newline
\hrule
{\footnotesize \fontfamily{pcr}\selectfont i.group \textcolor{blue}{group}=pca\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=*h28v07*EVI)\newline
i.pca \textcolor{blue}{input}=pca\_group \textcolor{blue}{output\_prefix}=pca\_ \textcolor{blue}{percent}=99 --o\newline
\#Here, run {\it i.group} interactively to add the PCA output files you want to use for segmentation\newline
i.segment \textcolor{blue}{group}=seg\_group \textcolor{blue}{output}=seg \textcolor{blue}{threshold}=0.9 \textcolor{blue}{memory}=3000 \textcolor{blue}{iterations}=100 --o\newline}
\hrule
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Temporal PCA-based classification}{
Classes found to follow one crop per year
\newline

\begin{center}
 \includegraphics[width=0.55\textwidth]{./images/startup_banner_isis}\newline
 \newline
 Figure 4: Single-crop classes from PCA.
\end{center}

}

\end{tikzpicture}

\end{document}

### 2014-04-18 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: added qr code to gif
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59759 15284696-431f-4ddb-bdfa-cd5b030d7da7
Lidar, improved vector modules
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59781 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \smallskip
-The Lidar library ({\url {www.liblas.org}}) included in GRASS GIS permits the import of Lidar (.las)
-data in raster (r.in.lidar using statistics of choice) or in vector format (v.in.lidar). 
-Author Markus Metz tested r.in.lidar with a 705Gb .las file. \newline
+The Lidar library ({\url {www.liblas.org}}) used by GRASS GIS permits the import of LAS Lidar
+data. The imported data can be in raster (r.in.lidar using statistics of choice) or in vector format (v.in.lidar). \newline
 On-farm water storage study with lidar data in NSW (Australia) developed a full remote sensing monitoring methodology
@@
 \begin{itemize}
- \item {\bf v.} blabla
- \item {\bf v.} blabla
- \item {\bf v.} blabla
- \item {\bf v.} blabla
- \item {\bf v.} blabla
+ \item {\bf v.distance:} Calculates distances from points, lines, or areas to points, lines, or areas.
+ \item {\bf v.overlay:} The processing speed has been substantially improved.
+ \item {\bf v.net.*:} All vector network analysis tools provide now fine control over node costs.
+ \item {\bf v.voronoi:} New option to create Voronoi diagrams for areas.
+ \item {\bf v.rectify:} Vector data can now be georeferenced using various methods for 2D and 3D coordinate transformation.
 \end{itemize}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{images/particles}
+\includegraphics[width=\textwidth]{images/particles}%
+\raisebox{0pt}[0pt][0pt]{\hspace{-3cm}\colorbox{white}{\includegraphics[width=3cm]{images/particles_qr_short}}}
 \end{center}

### 2014-04-19 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: text for animation qr code, remove unused code
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59792 15284696-431f-4ddb-bdfa-cd5b030d7da7
pg modifications, various cosmetics
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59801 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \author{Markus Metz$^1$, Martin Landa$^2$, Anna Petrášova$^3$, Vaclav Petráš$^3$, Yann Chemin$^4$, Markus Neteler$^1$ and The GRASS GIS Development Team\\ \bigskip
-$^1$ CRI, FEM, Italy, $^2$ CTU, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka}
+$^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka}
 
@@
 All topological cleaning tools have been optimized with regard to processing speed, robustness, and system requirements.\newline
-The topological engine comes with a new prototype for direct read/write support of OGR Simple Features API.\newline
-Additionally vector data can be directly exchanged with topological PostGIS 2 databases.\newline
-Considering the wide spread usage of ESRI Shapefile, a non-topological format for vector data exchange, it is particularly advantageous that GRASS GIS 7 offers advanced cleaning tools.\newline
-For power users and programmers, the new Python interface allows to directly access functions provided by the underlying C library; this combines the ease of writing Python scripts with the power of optimized C functionality in the library backend.
+The vector engine comes with a new prototype for direct read/write support of OGR Simple Features API.\newline
+Additionally vector data can be directly exchanged with topological PostGIS 2 databases.
+This enables GRASS to read and write topological primitives beside native file-based format also to the topological PostGIS 2 databases.
+\newline
+Considering the wide spread usage of Esri Shapefile, a non-topological format for vector data exchange, it is particularly advantageous that GRASS GIS 7 offers advanced cleaning tools.\newline
+For power users and programmers, the new Python interface allows to directly access functions provided by the underlying C libraries; this combines the ease of writing Python scripts with the power of optimized C functionality in the library backend.
 }
@@
 The OGC Simple Features can be imported into and exported from the GRASS GIS format through topological vector conversion.
-For attribute management several database management system (DBMS) with SQL support are supported including SQLite (default DB backend), PostgreSQL + PostGIS, MySQL, ODBC.
+For attribute management several database management system (DBMS) with SQL support are supported including SQLite (default DB backend), DBF, PostgreSQL, MySQL, ODBC.
 
-The following \textbf{basic geometry types} can be edited directly: point, centroid, line, and boundary. A GRASS vector map can contain a combination of several different types.
-From these basic geometry types the following \textbf{derived geometry types} can be generated: area (closed ring of boundaries + centroid), isle (closed ring of boundaries, no centroid), and node (at both ends of lines/boundaries).
+The following \textbf{basic topological elements} can be edited directly: point, centroid, line, and boundary. A GRASS vector map can contain a~combination of several different types of the elements.
+From these basic geometry types the following \textbf{derived topological elements} can be generated: area (closed ring of boundaries + centroid), isle (closed ring of boundaries, no centroid), and node (at both ends of lines/boundaries).
 Isles and Nodes are not visible to the user.
@@
  \newline
- Figure 1a: Basic and derived vector geometry types in GRASS GIS 7
+ Figure 1a: Basic and derived topological elements in GRASS GIS 7
 \end{center}
@@
 \begin{center}
- \includegraphics[width=0.48\textwidth]{svg_images/grass6-topo}
+ \includegraphics[width=0.38\textwidth]{svg_images/grass6-topo}
  \hspace{10mm}
- \includegraphics[width=0.48\textwidth]{svg_images/grass7-topo}
+ \includegraphics[width=0.38\textwidth]{svg_images/grass7-topo}
  \newline
- Figure 1b: Topology changes from version 6 to 7 after [Landa 2013]
+ Figure 1b: Topology changes from version 6 to 7 after (points and centroids are represented by the nodes) [Landa 2013]
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Topology structure}{
-
-\begin{center}
- \includegraphics[width=0.47\textwidth]{images/topo-geo-grass}
-  \newline
- Figure 3: Topology structure
-\end{center}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \blocknode{PyGRASS: fast Python API}{
-PyGRASS [Zambelli 2013] is an object-oriented Python API which allows efficient manipulation with vectors.
+PyGRASS [Zambelli 2013] is an object-oriented Python API which allows efficient manipulation with GRASS rasters and vectors.
 It is easy-to-use but its performance is comparable to C code since it calls GRASS C API behind the scenes.
@@
 % TODO: finalize
-The native GRASS-PostGIS data provider supports
+The native GRASS-PostGIS data provider allows the GRASS vector library
+to read and write PostGIS data directly without any external
+geospatial library. Beside simple features the provider also allows to work with
+topological elements through PostGIS Topology extension.\newline
 
-PostGIS 2 Topology.
-It allows the GRASS vector library to read and write PostGIS data directly without any external library.
-The GRASS-PostGIS data provider has been implemented using \textit{libpq} library.
+%The GRASS-PostGIS data provider has been implemented using
+%\textit{libpq} library.
 
@@
 \item Boundaries are stored as edges,
-\item Areas are stored as faces (with id > 0),
-\item Isles are stored as faces (with id <= 0) (including universal face defined by PostGIS Topology).
+\item Areas are stored as faces (with id $>$ 0),
+\item Isles are stored as faces (with id $<=$ 0) (including universal face defined by PostGIS Topology).
 \end{itemize}
 
-Additional topological data related to nodes, lines, areas, and isles are stored in separated tables.
+Additional topological data related to nodes, lines, areas, and isles are stored in separated tables (see figure bellow).
+
+\begin{center}
+  \includegraphics[width=0.47\textwidth]{images/topo-geo-grass}
+  \newline
+ Figure 3: Extended PostGIS Topology structure
+\end{center}
 
@@
  \item {\bf v.out.postgis:} Exports a vector map layer to PostGIS feature table.
- \item {\bf v.} blabla
+ \item {\bf v.external:} Creates a new pseudo-vector map as a link to a PostGIS feature table. 
+ \item {\bf v.external.out:} Defines vector output format.
 \end{itemize}
@@
 The Lidar library ({\url {www.liblas.org}}) used by GRASS GIS permits the import of LAS Lidar
-data. The imported data can be in raster (r.in.lidar using statistics of choice) or in vector format (v.in.lidar). \newline
+data. The imported data can be in raster ({\bf r.in.lidar} using statistics of choice) or in vector format ({\bf v.in.lidar}). \newline
 On-farm water storage study with lidar data in NSW (Australia) developed a full remote sensing monitoring methodology
@@
  \includegraphics[width=0.4\textwidth]{images/grass7_las_support}
- %\newline
+ \newline
  Figure 5: Example for LAS support in GRASS GIS 7: rapid LAS data assessment through binning
@@
 \includegraphics[width=\textwidth]{images/particles}%
-\raisebox{0pt}[0pt][0pt]{\hspace{-3cm}\colorbox{white}{\includegraphics[width=3cm]{images/particles_qr_short}}}
+\raisebox{0pt}[0pt][0pt]{\hspace{-3cm}\colorbox{white}{\includegraphics[width=3cm]{images/particles_qr_short}}}%
+\newcommand{\seeanimtext}{see animation online}%
+\newlength{\myl}%
+\settowidth{\myl}{\small\seeanimtext}%
+\raisebox{-2ex}[0pt][0pt]{\hspace{-\myl}\colorbox{white}{\small\seeanimtext}}%
 \end{center}
 }
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\getcurrentrow{box}
-\coordinate (funkcionalita) at (box.south west);
-\coordinate (funkcionalitaeast) at (box.east);
-\coordinate (screenshot) at (box.north west);
-
-% \blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{ % special smaller box
 \blocknode{References}{
@@
 [Neteler 2005] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1):51-61.\\{}
-[Landa 2013] & Landa, 2013. Vektorová architektura systému GRASS GIS [GRASS GIS Vector Architecture]. PhD thesis, CTU, Czech Republic.
+[Landa 2013] & Landa, 2013. Vektorová architektura systému GRASS GIS [GRASS GIS Vector Architecture]. PhD thesis, CTU in Prague, Czech Republic.
 \end{tabular}

### 2014-04-20 grassposter/2014_EGU_M3_Landscape/poster.tex
Update poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59837 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 Wilcox et al. (2005) & J. Geophys. Res. 110(E11):2156-2202.\\{}
+Zhang et al. (2013) & LPSC Abstracts 44:374.\\{}
 \end{tabular}
@@
  \newline
- Figure 1: Clementine RGB153, segmentation and FeO (wt\%) per segmentation class.
+ Figure 1: Clementine RGB153 (top), segmentation (middle) and FeO (wt\%) per segmentation class (bottom).
 \end{center}
@@
 \startthirdcolumn
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{$M^3$ data analysis}{
-nn
-\newline
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{M$^3$ Signal at Apollo 12 landing site}{
+\smallskip
 \begin{center}
- \includegraphics[width=0.5\textwidth]{./images/M3FEOlarge}
- \newline
- Figure 3: FeO
+\begin{tabular}{ c p{0.45\textwidth}}
+ \raisebox{-1.2\totalheight}{\includegraphics[width=0.5\textwidth]{./images/M3_A12_craters_signal}}\newline
+ %\caption{Spectral signature of $M^3$ from four craters}
+ \label{fig:specsignature4craters}
+ &
+ \noindent Chandrayaan $M^3$ data was  downloaded from PDS \url{http://pds-imaging.jpl.nasa.gov/}{pds-imaging.jpl.nasa.gov}.
+The tile \textit{M3G20090111T013904\_V01\_RFL.IMG} was imported in GRASS GIS, resulting in 85 bands.
+The spectrum for four craters where extracted in the Figure \ref{fig:specsignature4craters}.
+Bench and Surveyor are both together in the lower reflectance curves.
+On the higher side, Sharp and Middle Crescent are consistently above the two others.
+This higher broadband Albedo is increasing towards the West, where one of the ray is clearly drawn (Oblique white strip in the middle of The Clementine upper map.
+Compared to the spectral data from Figure ~\ref{fig:specsignatureASTERlib} the reflectance is overall lower and the obvious shape differences are there.
+ \end{tabular}
  \end{center}
+ \begin{flushleft}
+ \hspace{22mm}
+ \includegraphics[width=0.45\textwidth]{./images/Apollo12_signatures}
+ %\caption{Spectral signature from Apollo 12 (ASTER library)}
+ \label{fig:specsignatureASTERlib}
+ \end{flushleft}
 
@@
 \startfourthcolumn
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Segmentation of PCA elements}{
-GRASS GIS segmentation of the PCA of the full temporal archive of MODIS EVI.
-\newline
-
-A summary of the code needed to reach this point of analysis is here.\newline
-\hrule
-{\footnotesize \fontfamily{pcr}\selectfont i.group \textcolor{blue}{group}=pca\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=*h28v07*EVI)\newline
-i.pca \textcolor{blue}{input}=pca\_group \textcolor{blue}{output\_prefix}=pca\_ \textcolor{blue}{percent}=99 --o\newline
-\#Here, run {\it i.group} interactively to add the PCA output files you want to use for segmentation\newline
-i.segment \textcolor{blue}{group}=seg\_group \textcolor{blue}{output}=seg \textcolor{blue}{threshold}=0.9 \textcolor{blue}{memory}=3000 \textcolor{blue}{iterations}=100 --o\newline}
-\hrule
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Temporal PCA-based classification}{
-Classes found to follow one crop per year
-\newline
+\blocknode{M$^3$ derived FeO from standard equations}{
+\noindent The wt\%FeO equations have a large range of results when used with $M^3$ data:
+\begin{center}
+\begin{tabular}{ l r r}
+\hline
+Authors & Bench & Surveyor\\
+\hline
+Lucey et al. (2000) & -26.64 & -23.32 \\
+Lawrence et al. (2002) & 4.72 & 6.38 \\
+Wilcox et al. (2005) & 22.28 & 21.82 \\
+Zhang et al. (2013) & 19.74 & 19.49 \\
+\hline
+\end{tabular}
+\end{center}
+\bigskip
 
 \begin{center}
- \includegraphics[width=0.55\textwidth]{./images/startup_banner_isis}\newline
- \newline
- Figure 4: Single-crop classes from PCA.
+\begin{tabular}{ c p{0.45\textwidth}}
+ \raisebox{-0.8\totalheight}{\includegraphics[width=0.5\textwidth]{./code/code1}}
+ %\caption{Testing FeO algorithms.}
+ \label{fig:FeOtesting}
+ &
+ \noindent It is known that the local range of FeO is below 10wt\% from UVVIS data (see Figure on the lower left), only the Lawrence et al.
+(2002) equation is giving an appropriate range.
+Lucey et al.
+(2000) equation fails because of the offset of uvvis4/uvvis2(=1.15 vs offset = 1.19) and the one for uvvis2(=0.05 vs offset = 0.08), as both of the parts are negative thus giving a positive division output, their interplay should bring a negative number for the arctangent negative sign to compensate.
+This clearly does not happen with $M^3$ data in the Bench and Surveyor craters, the results from the arctangent being positive, and the sign change brings the main part of the equation to a negative, further reduced by the negative final offset.\newline
+\end{tabular}
 \end{center}
+\noindent Upon using the  Lawrence et al.
+(2002) equation, it turned out that though the wt\%FeO range was satisfactory for few crater points, the rate of change was actually reverse to the expected one, reducing to null towards the South of the landing site and increasing towards the North.\newline
+\noindent The equation from Zhang et al. (2013) is giving an appropriate rate of change, however, the local values are too large compared to the Clementine derived FeO values.\newline
 

### 2014-04-20 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: update figure captions, adjust logos position
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59865 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \addlogo[north east]{(-2,-2.5)}{4cm}{svg_images/logo_FEM_CRI.pdf}
-\addlogo[north east]{(-2,-6.5)}{4cm}{svg_images/NC_State_Seal.pdf}
+\addlogo[north east]{(-2,-5.5)}{4cm}{svg_images/NC_State_Seal.pdf}
 \addlogo[north east]{(-8,-2.5)}{4cm}{images/Logo_cvut.jpg}
@@
   \newline
- Figure 3: Data sources
+ Figure 2: Data sources
 \end{center}
@@
  \newline
- Figure 5: Example for LAS support in GRASS GIS 7: rapid LAS data assessment through binning
+ Figure 4: Example for LAS support in GRASS GIS 7: rapid LAS data assessment through binning
 \end{center}
@@
 \begin{center}
-\begin{tabular}{lcr}
-\includegraphics[width=0.28\textwidth]{images/grass7-3d}
-& ~ &
-\includegraphics[width=0.49\textwidth]{images/house3D}\\
- Figure X: 3D handling & & Figure X: Chancellor's House, North Carolina State University
+\begin{tabular}{ll}
+\includegraphics[width=0.30\textwidth]{images/grass7-3d}
+& 
+\includegraphics[width=0.55\textwidth]{images/house3D}\\
+ Figure 5a: 3D object with a hole &  Figure 5b: 3D model of Chancellor's House (NC State University)\\
+ in GRASS GIS topology model& visualized in GRASS GIS
+
 \end{tabular}

### 2014-04-21 grassposter/2014_EGU_G7_Landscape/poster.tex
add some text to 'data sources' box
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59866 15284696-431f-4ddb-bdfa-cd5b030d7da7
updated poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59867 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 The upcoming GRASS GIS 7 release improves not only raster processing and general design but the vector processing in the first place.
-GRASS GIS, as a topological GIS, recognizes that the topology plays the key role in the vector processing and analysis.\newline
+GRASS GIS, as a topological GIS, recognizes that the topology plays the key role in the vector processing and analysis.\newline\linebreak
 Topology ensures that adjacent geographic components in a single vector map are related.
@@
 Non-topological vector data are automatically converted to a topological representation upon import.
-Further more, various cleaning tools exist to remove non-trivial topological errors.\newline
+Further more, various cleaning tools exist to remove non-trivial topological errors.\newline\linebreak
 In the upcoming GRASS GIS 7 release the vector library was particularly improved to make it faster and more efficient with an improved internal vector file format.
@@
 As a new option the user can select a file-based version of the spatial index for large vector data.
-All topological cleaning tools have been optimized with regard to processing speed, robustness, and system requirements.\newline
+All topological cleaning tools have been optimized with regard to processing speed, robustness, and system requirements.\newline\linebreak
 The vector engine comes with a new prototype for direct read/write support of OGR Simple Features API.\newline
@@
 \newline
-Considering the wide spread usage of Esri Shapefile, a non-topological format for vector data exchange, it is particularly advantageous that GRASS GIS 7 offers advanced cleaning tools.\newline
+Considering the wide spread usage of Esri Shapefile, a non-topological format for vector data exchange, it is particularly advantageous that GRASS GIS 7 offers advanced cleaning tools.\newline\linebreak
 For power users and programmers, the new Python interface allows to directly access functions provided by the underlying C libraries; this combines the ease of writing Python scripts with the power of optimized C functionality in the library backend.
@@
 
-The following \textbf{basic topological elements} can be edited directly: point, centroid, line, and boundary. A GRASS vector map can contain a~combination of several different types of the elements.
-From these basic geometry types the following \textbf{derived topological elements} can be generated: area (closed ring of boundaries + centroid), isle (closed ring of boundaries, no centroid), and node (at both ends of lines/boundaries).
-Isles and Nodes are not visible to the user.
-Furthermore face, kernel (3D centroid) and volume (3D area) as defined in the format.
-
 % TODO: point to http://grass.osgeo.org/programming7/
-
 % TODO: 2. explain topology changes <<- needed?
-
 % TODO: show the internal format change or rather the actual model?
@@
 \end{center}
+
+The following \textbf{basic topological elements} can be edited directly: point, centroid, line, and boundary. A GRASS vector map can contain a~combination of several different types of the elements.
+From these basic geometry types the following \textbf{derived topological elements} can be generated: area (closed ring of boundaries + centroid), isle (closed ring of boundaries, no centroid), and node (at both ends of lines/boundaries).
+Isles and Nodes are not visible to the user.
+Furthermore face, kernel (3D centroid) and volume (3D area) as defined in the format.\newline
 
@@
 \blocknode{Data Sources}{
-This
+
+  GRASS GIS 7 supports various data sources in read and write
+  access. Beside native file-based raster and vector format GRASS
+  allows to specify external data sources through GDAL/OGR
+  library. GRASS GIS 7 also natively supports PostGIS database
+  including its topological extension.
+
 \begin{center}
@@
   \newline
- Figure 2: Data sources
+ Figure 2: Supported data sources
 \end{center}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Other Improvements \& Additions}{
+\smallskip
+
+{\bf Remanufacturing, performance improvement}
+
+{\bf Other functions}
+
+\begin{itemize}
+ \item {\bf v.distance:} Calculates distances from points, lines, or areas to points, lines, or areas.
+ \item {\bf v.overlay:} The processing speed has been substantially improved.
+ \item {\bf v.net.*:} All vector network analysis tools provide now fine control over node costs.
+ \item {\bf v.voronoi:} New option to create Voronoi diagrams for areas.
+ \item {\bf v.rectify:} Vector data can now be georeferenced using various methods for 2D and 3D coordinate transformation.
+\end{itemize}
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 data. The imported data can be in raster ({\bf r.in.lidar} using statistics of choice) or in vector format ({\bf v.in.lidar}). \newline
-On-farm water storage study with lidar data in NSW (Australia) developed a full remote sensing monitoring methodology
-of water availability with lidar-based bathymetric survey and multi-source remote sensing survey [8].\newline
 \begin{center}
- %\includegraphics[width=0.4\textwidth]{images/ofs1}
- %\newline
- %Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]
-
- \includegraphics[width=0.4\textwidth]{images/grass7_las_support}
+ \includegraphics[width=0.7\textwidth]{images/grass7_las_support}
  \newline
@@
 \end{center}
-}
 
-\blocknode{Other Improvements \& Additions}{
-\smallskip
-
-{\bf Remanufacturing, performance improvement}
-
-{\bf Other functions}
-
-\begin{itemize}
- \item {\bf v.distance:} Calculates distances from points, lines, or areas to points, lines, or areas.
- \item {\bf v.overlay:} The processing speed has been substantially improved.
- \item {\bf v.net.*:} All vector network analysis tools provide now fine control over node costs.
- \item {\bf v.voronoi:} New option to create Voronoi diagrams for areas.
- \item {\bf v.rectify:} Vector data can now be georeferenced using various methods for 2D and 3D coordinate transformation.
-\end{itemize}
+On-farm water storage study with lidar data in NSW (Australia) developed a full remote sensing monitoring methodology of water availability with lidar-based bathymetric survey and multi-source remote sensing survey [Chemin 2011].\newline
+\begin{center}
+\includegraphics[width=0.4\textwidth]{images/ofs1}
+\hspace{5mm}
+\includegraphics[width=0.3\textwidth]{images/ofs2}
+\newline
+Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]
+\end{center}
 }
@@
 \begin{tabular}{rp{0.8\textwidth}}
+[Chemin 2011] & Chemin \& Rabbani, 2011. International Journal of Geoinformatics,  7(3):1-6.\\{}
+[Gebbert 2014] & Gebbert \& Pebesma, 2014. TGRASS: A temporal GIS for field based environmental modeling, Environmental Modelling \& Software 53:1–12.\\{}
+[Landa 2013] & Landa, 2013. Vektorová architektura systému GRASS GIS [GRASS GIS Vector Architecture]. PhD thesis, CTU in Prague, Czech Republic.\\{}
+[Neteler 2005] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1):51-61.\\{}
 [Neteler 2012] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
-[Gebbert 2014] & Gebbert \& Pebesma, 2014. TGRASS: A temporal GIS for field based environmental modeling, Environmental Modelling \& Software 53:1–12.\\{}
 [Zambelli 2013] & Zambelli \& Gebbert \& Ciolli, 2013. PyGRASS: An Object Oriented Python API for GRASS GIS. ISPRS International Journal of Geo-Information 2.1:201-219.\\{}
-[Neteler 2005] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1):51-61.\\{}
-[Landa 2013] & Landa, 2013. Vektorová architektura systému GRASS GIS [GRASS GIS Vector Architecture]. PhD thesis, CTU in Prague, Czech Republic.
 \end{tabular}

### 2014-04-21 grassposter/2014_EGU_G7_Landscape/poster.tex
fixed reference
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59868 15284696-431f-4ddb-bdfa-cd5b030d7da7
updated poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59869 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \newline
-Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]
+Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [Chemin 2011]
 \end{center}
@@
 \smallskip
-Faces
+GRASS 7 has 3D topological capabilities, as described in Figure 5a. An application to buildings is found in Figure 5b.
 
@@
 \begin{minipage}{0.25\textwidth}
+\hspace{15mm}
 \includegraphics[width=2in]{svg_images/OSGeo_project.pdf}

### 2014-04-21 grassposter/2014_EGU_M3_Landscape/poster.tex
updated poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59877 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
  \newline
- Figure 1: Clementine RGB153 (top), segmentation (middle) and FeO (wt\%) per segmentation class (bottom).
+ Figure 2: Clementine RGB153 (top), segmentation (middle) and FeO (wt\%) per segmentation class (bottom).
 \end{center}
@@
 (2002) equation, it turned out that though the wt\%FeO range was satisfactory for few crater points, the rate of change was actually reverse to the expected one, reducing to null towards the South of the landing site and increasing towards the North.\newline
-\noindent The equation from Zhang et al. (2013) is giving an appropriate rate of change, however, the local values are too large compared to the Clementine derived FeO values.\newline
+\noindent The equation from Zhang et al.
+(2013) is giving an appropriate rate of change, however, the local values are too large compared to the Clementine derived FeO values.
+Comparing the zonal contrast between Clementine FeO map from Lucey et al.
+(2000) the $M^3$ from Zhang et al.
+(2013) leads to an interesting prospect as even the shapes are not consistent (see Figures ~\ref{fig:subfeoclem} \& ~\ref{fig:subfeoM3}).
+This indicates that the inner work of the angle equation is not sensitive to the same type of distance between R950 and R750 as they are in Clementine and in $M^3$.
+In an ideal condition, the calibration of both sensor bands would be identical, and the sensor response for each band would also be the same.
+This is not a reality, from the design and manufacture inheritance of multi-spectral sensors and hyperspectral sensors, to the data collection flight and its environment.
+Finally, some accident or issues can damage the operation.\newline
+
+\begin{center}
+ \includegraphics[width=0.4\textwidth,keepaspectratio=true]{./images/Clem_FeO_area}
+% \caption{Subset of Clementine FeO using \citep{lucey2000lunar}}
+ \label{fig:subfeoclem}
+\hspace{5mm}
+ \includegraphics[width=0.435\textwidth,keepaspectratio=true]{./images/M3_Zhang_FeO_area}
+% \caption{Subset of $M^3$ FeO using \cite{zhang2013mapping}}
+ \label{fig:subfeoM3}
+\end{center}
 

### 2014-05-14 grassposter/2014_EGU_M3_Landscape/poster.tex
Update poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59883 15284696-431f-4ddb-bdfa-cd5b030d7da7
Update poster tex+bib
git-svn-id: https://svn.osgeo.org/grass/grass-promo@60236 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \usepackage{url}
+
+% For blibliography styling
+\usepackage{natbib}
 
@@
 \blocknode{Abstract}{
-\small \noindent The geology of the Apollo 12 landing site has been the subject of many studies, including recently by Korotev et al.
-(2011) and Snape et al.
-(2013).
+\small \noindent The geology of the Apollo 12 landing site has been the subject of many studies, including recently by \cite{korotev2011apollo} and \cite{Snape2013basaltic}.
 This research attempts to bring additional understanding from a remote sensing perspective using the Moon Mineralogy Mapper ($M^3$) sensor data, onboard the Chandrayaan lunar orbiter.
@@
 
-Mapping of FeO (wt\%) and TiO 2 (wt\%) is done using the methods of Lucey et al. (2000) and Wilcox et
-al.
-(2005).
-A FeO \& TiO 2 processing module (i.feotio2) is made specifically for this research within the Free \& Open Source Software GRASS GIS (Neteler et al., 2012).
-Attempts will be made to estimate the lava flow thickness using the method of Bugiolacchi et al.
-(2006) and individual lava layers thicknesses (Weider et al., 2010).
+Mapping of FeO (wt\%) and TiO 2 (wt\%) is done using the methods of \cite{lucey2000lunar} and \cite{wilcox2005mapping}.
+A FeO \& TiO 2 processing module (i.feotio2) is made specifically for this research within the Free \& Open Source Software GRASS GIS \cite{neteler2012grass}.
+Attempts will be made to estimate the lava flow thickness using the method of \cite{bugiolacchi2006stratigraphy} and individual lava layers thicknesses from \cite{weider2010individual}.
 Integration of this new information will be put in perspective and integrated with previous work.
@@
 \blocknode{Previous interpretations}{
-Korotev et al.
-(2011) reviewed the lunar research done until recently, with a special interest in the Apollo 12 landing site and its vicinity.
+\cite{korotev2011apollo} reviewed the lunar research done until recently, with a special interest in the Apollo 12 landing site and its vicinity.
 Among the information newly deducted, are a geological context block diagram 1 (Figure below) along with an Apollo 12 landing site interpretive cross-section.
-Fortezzo and Hare (2013) completed the digital renovation of the 1:5,000,000 lunar geological maps series, enhanced with LOLA-LRO information.\newline
+\cite{fortezzo2013completed} completed the digital renovation of the 1:5,000,000 lunar geological maps series, enhanced with LOLA-LRO information.
 \begin{center}
 	\begin{tabular}{cc}
-		\includegraphics[width=0.45\textwidth]{./images/Korotev_block}
+		\includegraphics[width=0.45\textwidth]{./images/Korotev_block}\hspace{20mm}
 		&
@@
 	\end{tabular}\newline
-Figure 2: a) Korotev et al (2011) geological block of Apollo 12 landing site\\
-b)  Fortezzo and Hare (2013) geological maps series with moon nomenclature.
+Figure 1: a) Geological block of Apollo 12 landing site from \cite{korotev2011apollo}.\\
+b) Geological maps series with moon nomenclature from \cite{fortezzo2013completed}.
+\end{center}
+
+\begin{center}
+	\begin{tabular}{c}
+		\includegraphics[width=0.75\textwidth]{./images/2013_lpsc_Snape_et_al}
+	\end{tabular}\newline
+Figure 2: Interpretive cross-section of Apollo 12 landing site from \cite{Snape2013basaltic}. 
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\getcurrentrow{box}
-\coordinate (funkcionalita) at (box.south west);
-\coordinate (funkcionalitaeast) at (box.east);
-\coordinate (screenshot) at (box.north west);
+%\getcurrentrow{box}
+%\coordinate (funkcionalita) at (box.south west);
+%\coordinate (funkcionalitaeast) at (box.east);
+%\coordinate (screenshot) at (box.north west);
+%
+%\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
+\blocknode{References}{
+\smallskip
+\scriptsize
 
-\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
-\scriptsize
-\begin{flushleft}
-\begin{tabular}{rp{0.9\textwidth}}
-Bugiolacchi et al. (2006) &  Planetary Science. 41(2):285-304.\\{}
-Fortezzo et al. (2013) & LPI Contributions, 1719:2114.\\{}
-Korotev et al. (2011) & Geochimica et Cosmochimica Acta. 75(6):1540-1573.\\{}
-Lucey et al. (2000) & J. Geophys. Res. 105(E8): 20297-20305.\\{}
-Neteler et al. (2012) & Environment \& Modeling Software, 31:124-130.\\{}
-Snape et al. (2013) & LPSC Abstracts 44:1044.\\{}
-Weider et al. (2010) & Icarus, 209, 323-336.\\{}
-Wilcox et al. (2005) & J. Geophys. Res. 110(E11):2156-2202.\\{}
-Zhang et al. (2013) & LPSC Abstracts 44:374.\\{}
-\end{tabular}
-\end{flushleft}
-\smallskip
+\begingroup
+\renewcommand{\section}[2]{}%
+\bibliographystyle{plain}
+\bibliography{poster}
+\endgroup
+
 \hrulefill
@@
 \begin{center}
-\begin{tabular}{cp{0.9\textwidth}}
-\begin{minipage}{0.15\textwidth}
+\begin{tabular}{c}
+\hspace{5mm}
+\begin{minipage}{0.2\textwidth}
 \includegraphics[width=0.7in]{./images/grass_qr.pdf}
@@
 
-\begin{minipage}{0.3\textwidth}
+\begin{minipage}{0.25\textwidth}
 \small {\url{www.bbk.ac.uk}}
@@
 \begin{minipage}{0.15\textwidth}
-\includegraphics[width=0.7in]{./images/grass_qr.pdf}
+\includegraphics[width=0.7in]{./svg_images/public_domain_logo.pdf}
 \end{minipage}
@@
 \end{minipage}
+
+\begin{minipage}{0.2\textwidth}
+\includegraphics[width=0.7in]{./images/grass_qr.pdf}
+\end{minipage}
+
 \end{tabular}
@@
 \hrulefill
-\vspace{14pt}
-\begin{center}
-\newcommand{\logowidth}{5em}
-\newcommand{\logospace}{\hspace{0.1em}}
-\noindent
-\includegraphics[width=\logowidth]{./svg_images/public_domain_logo.pdf}
-%\raisebox{0.7\height}{\logospace 2013 GRASS Development Team}
-\end{center}
 }
@@
  \newline
- Figure 2: Clementine RGB153 (top), segmentation (middle) and FeO (wt\%) per segmentation class (bottom).
+ Figure 3: Clementine RGB153 (top), segmentation (middle) and FeO (wt\%) per segmentation class (bottom).
 \end{center}
@@
 \startthirdcolumn
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{M$^3$ derived FeO from standard equations}{
+\bigskip
+
+\begin{center}
+\begin{tabular}{ c p{0.45\textwidth}}
+ \raisebox{-1.1\totalheight}{\includegraphics[width=0.5\textwidth]{./code/code1}}
+ %\caption{Testing FeO algorithms.}
+ \label{fig:FeOtesting}
+ &
+\noindent The wt\%FeO equations have a large range of results when used with $M^3$ data:\newline
+\begin{center}
+\begin{tabular}{ l r r}
+\hline
+Authors & Bench & Surveyor\\
+\hline
+\cite{lucey2000lunar} & -26.64 & -23.32 \\
+\cite{lawrence2002iron} & 4.72 & 6.38 \\
+\cite{wilcox2005mapping} & 22.28 & 21.82 \\
+\cite{zhang2013mapping} & 19.74 & 19.49 \\
+\hline
+\end{tabular}
+\end{center}
+\bigskip
+ \noindent It is known that the local range of FeO is below 10wt\% from UVVIS data (see Figure on the lower left), only the \cite{lawrence2002iron} equation is giving an appropriate range.
+\cite{lucey2000lunar} equation fails because of the offset of uvvis4/uvvis2(=1.15 vs offset = 1.19) and the one for uvvis2(=0.05 vs offset = 0.08), as both of the parts are negative thus giving a positive division output, their interplay should bring a negative number for the arctangent negative sign to compensate.
+This clearly does not happen with $M^3$ data in the Bench and Surveyor craters, the results from the arctangent being positive, and the sign change brings the main part of the equation to a negative, further reduced by the negative final offset.\newline
+\end{tabular}
+\end{center}
+\noindent Upon using the equation from \cite{lawrence2002iron}, it turned out that though the wt\%FeO range was satisfactory for few crater points, the rate of change was actually reverse to the expected one, reducing to null towards the South of the landing site and increasing towards the North.\newline
+\noindent The equation from \cite{zhang2013mapping} is giving an appropriate rate of change, however, the local values are too large compared to the Clementine derived FeO values.
+Comparing the zonal contrast between Clementine FeO map from \cite{lucey2000lunar} the $M^3$ from \cite{zhang2013mapping} leads to an interesting prospect as even the shapes are not consistent (see Figures ~\ref{fig:subfeoclem} \& ~\ref{fig:subfeoM3}).
+This indicates that the inner work of the angle equation is not sensitive to the same type of distance between R950 and R750 as they are in Clementine and in $M^3$.
+In an ideal condition, the calibration of both sensor bands would be identical, and the sensor response for each band would also be the same.
+This is not a reality, from the design and manufacture inheritance of multi-spectral sensors and hyperspectral sensors, to the data collection flight and its environment.
+Finally, some accident or issues can damage the operation.\newline
+\noindent After Contacting W.
+Zhang of \cite{zhang2013mapping} about the issue in its algorithm, he promptly answered that the article had a typo in the equation.
+After correction, the output were in a better range (about 15 for the two craters in the table above).\newline
+
+\begin{center}
+\begin{tabular}{ c c }
+ \raisebox{0.0\totalheight}{ 
+ \begin{tabular}{ p{0.45\textwidth} }
+  \includegraphics[width=0.45\textwidth,keepaspectratio=true]{./images/Clem_FeO_area}
+% \caption{Subset of Clementine FeO using \citep{lucey2000lunar}}
+ \label{fig:subfeoclem}
+ Figure 4: Subset of Clementine FeO using \cite{lucey2000lunar}.
+ \newline\linebreak
+\vspace{10mm}\\
+ \includegraphics[width=0.45\textwidth,keepaspectratio=true]{./images/M3_Zhang_FeO_area}
+% \caption{Subset of $M^3$ FeO using \cite{zhang2013mapping}}
+ \label{fig:subfeoM3}
+ Figure 5: Subset of $M^3$ FeO using \cite{zhang2013mapping}.
+ \newline
+ \end{tabular}
+ }
+ &
+ \begin{tabular}{ p{0.45\textwidth} }
+  \includegraphics[width=0.45\textwidth,keepaspectratio=true]{./images/M3_Zhang_FeO_region}
+% \caption{Region of $M^3$ FeO using \cite{zhang2013mapping} corrected}
+ \label{fig:subfeoM3corr}
+ Figure 6: Region of $M^3$ FeO using \cite{zhang2013mapping} corrected.
+  \end{tabular}
+\end{tabular}
+\end{center}
+
+}
+
+\startfourthcolumn
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{center}
-\begin{tabular}{ c p{0.45\textwidth}}
- \raisebox{-1.2\totalheight}{\includegraphics[width=0.5\textwidth]{./images/M3_A12_craters_signal}}\newline
- %\caption{Spectral signature of $M^3$ from four craters}
- \label{fig:specsignature4craters}
+\begin{tabular}{ c p{0.45\textwidth} }
+ \raisebox{-0.40\totalheight}{ 
+ \begin{tabular}{ c }
+ \includegraphics[width=0.5\textwidth]{./images/M3_A12_craters_signal}
+  \label{fig:specsignature4craters}\\
+  \vspace{5mm}
+  \includegraphics[width=0.5\textwidth]{./images/A12_spectrum}
+  \label{fig:specsignaturespeclibv2}\\
+  \vspace{5mm}
+  \includegraphics[width=0.5\textwidth]{./images/Apollo12_signatures}
+  \label{fig:specsignatureASTERlib}
+ \end{tabular} 
+ }%End of tabular
  &
@@
 Compared to the spectral data from Figure ~\ref{fig:specsignatureASTERlib} the reflectance is overall lower and the obvious shape differences are there.
+Additional spectrum signature data from \cite{clark2007usgs} is in the process of being extracted for analysis.\newline\linebreak
+ \noindent Figure 8: \newline Spectral signature of $M^3$ from four craters.
+ \newline\linebreak 
+ \noindent Figure 9: \newline Spectral signature from Apollo 12 (Speclib v2.0).
+ \newline\linebreak 
+ \noindent Figure 10: \newline Spectral signature from Apollo 12 from \cite{Baldridge2009711}.
+ \newline\linebreak 
 \end{tabular}
 \end{center}
- \begin{flushleft}
- \hspace{22mm}
- \includegraphics[width=0.45\textwidth]{./images/Apollo12_signatures}
- %\caption{Spectral signature from Apollo 12 (ASTER library)}
- \label{fig:specsignatureASTERlib}
- \end{flushleft}
+}%End of Block
 
-}
-
-\startfourthcolumn
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{M$^3$ derived FeO from standard equations}{
-\noindent The wt\%FeO equations have a large range of results when used with $M^3$ data:
-\begin{center}
-\begin{tabular}{ l r r}
-\hline
-Authors & Bench & Surveyor\\
-\hline
-Lucey et al. (2000) & -26.64 & -23.32 \\
-Lawrence et al. (2002) & 4.72 & 6.38 \\
-Wilcox et al. (2005) & 22.28 & 21.82 \\
-Zhang et al. (2013) & 19.74 & 19.49 \\
-\hline
-\end{tabular}
-\end{center}
-\bigskip
-
-\begin{center}
-\begin{tabular}{ c p{0.45\textwidth}}
- \raisebox{-0.8\totalheight}{\includegraphics[width=0.5\textwidth]{./code/code1}}
- %\caption{Testing FeO algorithms.}
- \label{fig:FeOtesting}
- &
- \noindent It is known that the local range of FeO is below 10wt\% from UVVIS data (see Figure on the lower left), only the Lawrence et al.
-(2002) equation is giving an appropriate range.
-Lucey et al.
-(2000) equation fails because of the offset of uvvis4/uvvis2(=1.15 vs offset = 1.19) and the one for uvvis2(=0.05 vs offset = 0.08), as both of the parts are negative thus giving a positive division output, their interplay should bring a negative number for the arctangent negative sign to compensate.
-This clearly does not happen with $M^3$ data in the Bench and Surveyor craters, the results from the arctangent being positive, and the sign change brings the main part of the equation to a negative, further reduced by the negative final offset.\newline
-\end{tabular}
-\end{center}
-\noindent Upon using the  Lawrence et al.
-(2002) equation, it turned out that though the wt\%FeO range was satisfactory for few crater points, the rate of change was actually reverse to the expected one, reducing to null towards the South of the landing site and increasing towards the North.\newline
-\noindent The equation from Zhang et al.
-(2013) is giving an appropriate rate of change, however, the local values are too large compared to the Clementine derived FeO values.
-Comparing the zonal contrast between Clementine FeO map from Lucey et al.
-(2000) the $M^3$ from Zhang et al.
-(2013) leads to an interesting prospect as even the shapes are not consistent (see Figures ~\ref{fig:subfeoclem} \& ~\ref{fig:subfeoM3}).
-This indicates that the inner work of the angle equation is not sensitive to the same type of distance between R950 and R750 as they are in Clementine and in $M^3$.
-In an ideal condition, the calibration of both sensor bands would be identical, and the sensor response for each band would also be the same.
-This is not a reality, from the design and manufacture inheritance of multi-spectral sensors and hyperspectral sensors, to the data collection flight and its environment.
-Finally, some accident or issues can damage the operation.\newline
-
-\begin{center}
- \includegraphics[width=0.4\textwidth,keepaspectratio=true]{./images/Clem_FeO_area}
-% \caption{Subset of Clementine FeO using \citep{lucey2000lunar}}
- \label{fig:subfeoclem}
-\hspace{5mm}
- \includegraphics[width=0.435\textwidth,keepaspectratio=true]{./images/M3_Zhang_FeO_area}
-% \caption{Subset of $M^3$ FeO using \cite{zhang2013mapping}}
- \label{fig:subfeoM3}
-\end{center}
-
+\blocknode{Conclusions}{
+\smallskip
+Conclusions
 }

### 2014-07-14 tutorials/batch_processing/earthquakes/NZ/fetch_gns_earthquakes.sh
adjust for upstream WFS changes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@61249 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@ -23,8 +23,8 @@ fi
 XMLNAME="$OUTFILE.tmp_$$"
 
 
-URL="http://wfs-beta.geonet.org.nz/geoserver/geonet/ows?"
-REQUEST="service=WFS&version=1.1.0&request=GetFeature&typeName=geonet:quake&outputFormat=text/xml; subtype=gml/3.2"
+URL="http://wfs.geonet.org.nz/geonet/ows?"
+REQUEST="service=WFS&version=1.1.0&request=GetFeature&typeName=geonet:quake_search_v1&outputFormat=text/xml; subtype=gml/3.2"
 
 START_DATE=`date --utc --date="last week" +%F`
 #START_DATE=`date --utc --date="2 weeks ago" +%F`
@@ -42,7 +42,7 @@ if [ $? -ne 0 ] ; then
 fi
 
 
-BASE="wfs:FeatureCollection/wfs:member/geonet:quake"
+BASE="wfs:FeatureCollection/wfs:member/geonet_search_v1:quake"
 FIELDS="
 geonet:origintime
 geonet:longitude

### 2014-07-16 grassposter/2014_EGU_M3_Landscape/poster.tex
Updated poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@61258 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 This research attempts to bring additional understanding from a remote sensing perspective using the Moon Mineralogy Mapper ($M^3$) sensor data, onboard the Chandrayaan lunar orbiter.
-This has a higher spatial-spectral resolution sensor than the Clementine UV-Vis sensor and provides the opportunity to study the lunar surface with detailed spectral signatures.\newline
-
+This has a higher spatial-spectral resolution sensor than the Clementine UV-Vis sensor and provides the opportunity to study the lunar surface with detailed spectral signatures.\vspace{5mm}\newline
 Mapping of FeO (wt\%) and TiO 2 (wt\%) is done using the methods of \cite{lucey2000lunar} and \cite{wilcox2005mapping}.
@@
 Integration of this new information will be put in perspective and integrated with previous work.
-Analysis from the combined higher spatial and spectral resolutions will improve the accuracy of the geological mapping at the Apollo 12 landing site.\newline
+Analysis from the combined higher spatial and spectral resolutions will improve the accuracy of the geological mapping at the Apollo 12 landing site.
 }
@@
 
-\hrulefill
-\vspace{-5pt}
+%\hrulefill
+%\vspace{-5pt}
 
@@
 \begin{minipage}{0.2\textwidth}
-\includegraphics[width=0.7in]{./images/grass_qr.pdf}
+\includegraphics[width=0.5in]{./images/grass_qr.pdf}
 \end{minipage}
@@
 
-\hrulefill
 }
@@
 \startsecondcolumn
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Clementine data}{
-\smallskip
 
-\begin{center}
- \includegraphics[width=0.75\textwidth]{./images/Clementine}
- \newline
- Figure 3: Clementine RGB153 (top), segmentation (middle) and FeO (wt\%) per segmentation class (bottom).
-\end{center}
-}
-
-\startthirdcolumn
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{tabular}{ c p{0.45\textwidth}}
- \raisebox{-1.1\totalheight}{\includegraphics[width=0.5\textwidth]{./code/code1}}
+ \raisebox{-1.1\totalheight}{\includegraphics[width=0.5\textwidth]{./code/code1.pdf}}
  %\caption{Testing FeO algorithms.}
@@
 \cite{zhang2013mapping} & 19.74 & 19.49 \\
+\cite{zhang2013mapping} (corrected) & 15.65 & 14.76 \\
 \hline
@@
 \end{center}
-\noindent Upon using the equation from \cite{lawrence2002iron}, it turned out that though the wt\%FeO range was satisfactory for few crater points, the rate of change was actually reverse to the expected one, reducing to null towards the South of the landing site and increasing towards the North.\newline
+\noindent Upon using the equation from \cite{lawrence2002iron}, it turned out that though the wt\%FeO range was satisfactory for few crater points, the rate of change was actually reverse to the expected one, reducing to null towards the South of the landing site and increasing towards the North.\vspace{5mm}\newline
 \noindent The equation from \cite{zhang2013mapping} is giving an appropriate rate of change, however, the local values are too large compared to the Clementine derived FeO values.
@@
 This is not a reality, from the design and manufacture inheritance of multi-spectral sensors and hyperspectral sensors, to the data collection flight and its environment.
-Finally, some accident or issues can damage the operation.\newline
+Finally, some accident or issues can damage the operation.\vspace{5mm}\newline
 \noindent After Contacting W.
-Zhang of \cite{zhang2013mapping} about the issue in its algorithm, he promptly answered that the article had a typo in the equation.
+Zhang of \citep{zhang2013mapping} about the issue in its algorithm, he promptly answered that the article had a typo in the equation.
 After correction, the output were in a better range (about 15 for the two craters in the table above).\newline
@@
 \end{center}
+\vspace{2mm}
+}
 
+\startthirdcolumn
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Lava Flow Depth}{
+\smallskip
+
+\noindent Isolating the 95\% top and 5\% bottom of the destriped FeO image brought the possibility to suggest the Fresh Crater Ejecta (FCE) values.
+The FCE was found near Lansberg P in the surroundings of (-22.8215621403E,-2.09875487116N) with 11 samples averaging to 17.87 FeO wt\%.\newline
+
+\begin{center}
+	\begin{tabular}{cc}
+		\includegraphics[width=0.42\textwidth]{./images/mdi_high}\hspace{20mm}
+		&
+		\includegraphics[width=0.47\textwidth]{./images/mdi_low}
+	\end{tabular}\newline
+Figure 3 (left): Locating FCE above Lansberg P, with the upper 95\% FeO wt\%\\
+Figure4 (right): Locating lowest E Westward Copernicus, with the lower 5\% FeO wt\%.
+\end{center}
+
+\noindent The H value is the lower boundary of the FeO wt\% in the region, typically found in the nearest highland region.
+There are two solid constraints to it value.
+H should be strictly less than E and strictly more than zero ($0<H<E$).
+The E value was found in Copernicus ejecta ring and actually taken from the FeO wt\% map.
+The minimum value found in the FeO\_M3G20090111T013904.destripe map is 3.88 wt\%, belonging to the ejecta ring of Copernicus.
+Thus it can be inferred that $0<H<3.88$, strictly, in this Copernican work.
+Looking at over M$^3$ FeO tiles, there is no lower value to the crater ejecta of Copernicus.
+Some Alpes Formation and Dark Mantling Material in the vicinity of Gay Lussac do not go lower than this.\newline
+
+\noindent This is obviously shows the limit of this statistical search method.
+Another attempt was undertaken using the original tile FeO\_M320090610T113334 a visual search for H in the vicinity of Montes Carpatus (Northwestern of Copernicus with -23.6070634574E, 14.571534275N) was done and from 14 samples found $\overline{H}=5.88$.
+Another visual search in the ejecta blanket of Copernicus for a FCE value, 22 samples were collected, giving an average FCE value of 7.16.
+Thus, it is found that $0 < \overline H < \overline{FCE}$, which is a logical outcome.
+It is thus proposed to carry forward this parametrisation for mapping the depth of the Copernican lava flow with the following equation ~\ref{eq:NewMareDepthVal}.\newline
+\begin{equation}\label{eq:NewMareDepthVal}
+Mh = \frac {D_*} {8} \times \frac {E-\overline{H}} {\overline{FCE}-\overline{H}} = \frac {117000}{8} \times \frac {E-5.88}{17.87-5.88} [m]
+\end{equation}
+\noindent Which realizes as the following equation.\newline
+\begin{equation}\label{eq:NewMareDepthValCoef}
+Mh = (E-5.88) \times 1219.77 [m]
+\end{equation} 
+}
+
+\blocknode{Conclusions}{
+\smallskip
+Conclusions
 }
@@
 \startfourthcolumn
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Clementine data}{
+\smallskip
 
+\begin{center}
+ \includegraphics[width=0.45\textwidth]{./images/Clementine}
+ \newline
+ Figure 3: Clementine RGB153 (top), segmentation (middle) and FeO (wt\%) per segmentation class (bottom).
+\end{center}
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
  &
- \noindent Chandrayaan $M^3$ data was  downloaded from PDS \url{http://pds-imaging.jpl.nasa.gov/}{pds-imaging.jpl.nasa.gov}.
+ \noindent Chandrayaan $M^3$ data was  downloaded from PDS \url{http://pds-imaging.jpl.nasa.gov/}.
 The tile \textit{M3G20090111T013904\_V01\_RFL.IMG} was imported in GRASS GIS, resulting in 85 bands.
@@
 
-\blocknode{Conclusions}{
-\smallskip
-Conclusions
-}
-
 \end{tikzpicture}

### 2014-07-16 grassposter/2014_EGU_M3_Landscape/poster.tex
Updated poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@61259 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 	\end{tabular}\newline
-Figure 3 (left): Locating FCE above Lansberg P, with the upper 95\% FeO wt\%\\
-Figure4 (right): Locating lowest E Westward Copernicus, with the lower 5\% FeO wt\%.
+Figure 7 (left): Locating FCE above Lansberg P, with the upper 95\% FeO wt\%\\
+Figure 8 (right): Locating lowest E Westward Copernicus, with the lower 5\% FeO wt\%.
 \end{center}
 
+\smallskip
+
+\begin{center}
+\begin{tabular}{ c p{0.45\textwidth}}
+ \raisebox{-0.95\totalheight}{\includegraphics[width=0.45\textwidth]{./images/MariaDepthm}}\hspace{10mm}
+ %\caption{Testing FeO algorithms.}
+ \label{fig:MariaDepthm}
+ &
 \noindent The H value is the lower boundary of the FeO wt\% in the region, typically found in the nearest highland region.
@@
 Some Alpes Formation and Dark Mantling Material in the vicinity of Gay Lussac do not go lower than this.\newline
-
 \noindent This is obviously shows the limit of this statistical search method.
@@
 \begin{equation}\label{eq:NewMareDepthVal}
-Mh = \frac {D_*} {8} \times \frac {E-\overline{H}} {\overline{FCE}-\overline{H}} = \frac {117000}{8} \times \frac {E-5.88}{17.87-5.88} [m]
+Mh = \frac {D_*} {8} \times \frac {E-\overline{H}} {\overline{FCE}-\overline{H}} [m]
 \end{equation}
-\noindent Which realizes as the following equation.\newline
+\noindent Which realizes as the following equation ~\ref{eq:NewMareDepthValCoef}.\newline
 \begin{equation}\label{eq:NewMareDepthValCoef}
-Mh = (E-5.88) \times 1219.77 [m]
+Mh = \frac {117000}{8} \times \frac {E-5.88}{17.87-5.88} [m]
 \end{equation} 
+Figure 9: Attempt at Maria Depth mapping\newline
+\end{tabular}
+\end{center}
+
 }
@@
 \smallskip
-Conclusions
+Some attempts at using M$^3$ data to assess Apollo 12 landing site properties has proven to be constrained at every steps of the study.
+The cartographic, radiometric and data noise issues were of the most difficult to address.
+Combined, these issues reduced the mosaicking potential, thus the area covered.\newline
+
+The Lava Flow Depth estimation, to this date is still very doubtful and has to be research from scratch.
+Differences in estimation of FeO (wt\%) from M$^3$ and UVVis are not negligible.
+This is particularly troublesome.
 }
@@
 \begin{center}
- \includegraphics[width=0.45\textwidth]{./images/Clementine}
- \newline
- Figure 3: Clementine RGB153 (top), segmentation (middle) and FeO (wt\%) per segmentation class (bottom).
+\begin{tabular}{ c p{0.35\textwidth}}
+ \raisebox{-0.95\totalheight}{\includegraphics[width=0.5\textwidth]{./images/Clementine}}\hspace{10mm}
+  \label{fig:FeOClem}
+ &
+\noindent Clementine data was downloaded from \url{pdsimage.wr.usgs.gov}, UV-Vis 5 bands covering tiles \textit{ui03s333.img} and \textit{ui03s339.img}, both 3 degrees South and surrounding the 336E meridian.
+Ingestion of UV-Vis 5 bands in Isis (\url{isis.astrogeology.usgs.gov}) was done by using the \textit{pds2isis} conversion module, and import in GRASS GIS done by \textit{r.in.gdal}.
+This can be done in ISIS-GRASS bridge mode.\newline
+
+\noindent An object-based classification is run using the \textit{i.segment} module on the UVVis dataset.
+The output is vectorized with \textit{r.to.vect} and FeO statistics are extracted per vector polygons (also called zonal statistics) using \textit{v.rast.stats}.
+The mean zonal FeO statistics indicate a very clear threshold increase South of Apollo 12 landing site.\newline
+
+Figure 10 a): UVVIS RGB composite\newline
+
+Figure 10 b): Object-oriented classification (\textit{i.segment})\newline
+
+Figure 10 c): Zonal statistics (\textit{v.rast.stats})\newline
+
+\end{tabular}
 \end{center}
@@
 Additional spectrum signature data from \cite{clark2007usgs} is in the process of being extracted for analysis.\newline\linebreak
- \noindent Figure 8: \newline Spectral signature of $M^3$ from four craters.
+ \noindent Figure 11: \newline Spectral signature of $M^3$ from four craters.
  \newline\linebreak 
- \noindent Figure 9: \newline Spectral signature from Apollo 12 (Speclib v2.0).
+ \noindent Figure 12: \newline Spectral signature from Apollo 12 (Speclib v2.0).
  \newline\linebreak 
- \noindent Figure 10: \newline Spectral signature from Apollo 12 from \cite{Baldridge2009711}.
+ \noindent Figure 13: \newline Spectral signature from Apollo 12 from \cite{Baldridge2009711}.
  \newline\linebreak 

### 2015-03-01 grassposter/2015_EGU_Python/main.tex
python poster: template, logos, authors, abstract (Makefile is missing)
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64772 15284696-431f-4ddb-bdfa-cd5b030d7da7

\documentclass[innermargin=10mm]{tikzposter}
\usepackage{enumitem}
\geometry{paperwidth=63in,paperheight=42in}
\usepackage{url}

\title{
  \begin{minipage}{\textwidth}
    \centering
    Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7
  \end{minipage}
}
\author{
V\'{a}clav Petr\'{a}\v{s} (1), Anna Petr\'{a}\v{s}ov\'{a} (1), Yann Chemin (2), Pietro Zambelli (3), Martin Landa (4), \\
S\"{o}ren Gebbert (5), Markus Neteler (6), and Peter L\"{o}we (7)
}
\institute{
\large  % using smaller size of font than default because the list is long
(1) North Carolina State University, Raleigh, USA (wenzeslaus@gmail.com, vpetras@ncsu.edu), (2) International Water Management Institute,
Pelawatta, Sri Lanka, (3) EURAC Research, Institute for Renewable Energy, Bolzano/Bozen, Italy, (4) Faculty of Civil
Engineering, Czech Technical University in Prague, Czech Republic, (5) Th\"{u}nen Institute of Climate-Smart Agriculture,
Braunschweig, Germany, (6) Research and Innovation Centre, Fondazione Edmund Mach, San Michele all'Adige, Italy, (7)
German National Library for Science and Technology, Hanover, Germany
}
% \titlegraphic{}

\pdfinfo{
   /Author (Vaclav Petras, Anna Petrasova, Yann Chemin, Pietro Zambelli, Martin Landa, Soeren Gebbert, Markus Neteler, and Peter Loewe)
   /Title  (Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7)
%    /Subject (ensuring reproducibility of scientific geospatial computing - this is from testing poster)
   /Keywords (GIS, API, algorithms, open science, reproducibility)
}

\definecolor{textcolor}{HTML}{000000}

\definecolorpalette{sampleColorPalette} {
  \definecolor{colorOne}{HTML}{419041}
  % \definecolor{colorTwo}{HTML}{cccccc}
  \definecolor{colorTwo}{HTML}{dddddd}
  \definecolor{colorThree}{HTML}{F1B52D}
  % \definecolor{colorThree}{HTML}{EFA126}
}

\usetheme{Rays}
\usecolorstyle[colorPalette=sampleColorPalette]{Britain}
\useblockstyle{Default} % Basic
% \usecolorpalette{e}

\makeatletter
\renewcommand\TP@maketitle{%
    \begin{minipage}{0.2\linewidth}
       \centering

       % TODO: get other logos
       \includegraphics[width=0.2\textwidth]{ncstate}
       \hspace{2ex}
       \includegraphics[width=0.2\textwidth]{iwmi}

       \vspace{4ex}

       \includegraphics[width=0.2\textwidth]{ncstate}
       \hspace{2ex}
       \includegraphics[width=0.2\textwidth]{ctu_prague}
       \hspace{2ex}
       \includegraphics[width=0.2\textwidth]{ncstate}

       \vspace{4ex}

       \includegraphics[width=0.2\textwidth]{fem_cri}
       \hspace{2ex}
       \includegraphics[width=0.2\textwidth]{ncstate}
    \end{minipage}%
    \hfill
   \begin{minipage}{0.6\linewidth}
        \centering
        \color{titlefgcolor}
        {\bfseries  \sc {\fontsize{85}{60}\selectfont \@title}  \par}
        \vspace*{1em}
        {\huge \@author \par}
        \vspace*{1em}
        {\LARGE \@institute}
    \end{minipage}%
    \hfill
    \begin{minipage}{0.2\linewidth}
       \centering
       \includegraphics[width=0.39\textwidth]{grass}\\
       \LARGE \textbf{\textsf{GRASS GIS}}
    \end{minipage}
}
\setlength{\TP@visibletextwidth}{\textwidth-3\TP@innermargin}
\setlength{\TP@visibletextheight}{\textheight-3\TP@innermargin}

\makeatother

\setlength{\parskip}{1ex}

\graphicspath{{images/}{logos/}{qrcodes/}{listings/}}

\newcommand{\partitle}[1]{\bigskip \textbf{#1}\\[1ex]}
\newcommand{\parinlinetitle}[1]{\bigskip \textbf{#1}\ }
\newcommand{\textfontsize}{\LARGE}

\newcommand{\gmodule}[1]{\emph{#1}}
\newcommand{\rafun}[1]{\texttt{#1()}}

\begin{document}
\maketitle[width=0.95\textwidth]

\begin{columns}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\column{0.25}

% Abstract from http://meetingorganizer.copernicus.org/EGU2015/EGU2015-8142.pdf
%
% GRASS GIS 7 is a free and open source GIS software developed and used by many scientists (Neteler et al., 2012).
% While some users of GRASS GIS prefer its graphical user interface, significant part of the scientific community
% takes advantage of various scripting and programing interfaces offered by GRASS GIS to develop new models and
% algorithms. Here we will present different interfaces added to GRASS GIS 7 and available in Python, a popular
% programming language and environment in geosciences. These Python interfaces are designed to satisfy the needs
% of scientists and programmers under various circumstances.
% 
% PyGRASS (Zambelli et al., 2013) is a new object-oriented interface to GRASS GIS modules and libraries.
% The GRASS GIS libraries are implemented in C to ensure maximum performance and the PyGRASS interface
% provides an intuitive, pythonic access to their functionality. GRASS GIS Python scripting library is another way of
% accessing GRASS GIS modules. It combines the simplicity of Bash and the efficiency of the Python syntax. When
% full access to all low-level and advanced functions and structures from GRASS GIS library is required, Python
% programmers can use an interface based on the Python ctypes package. Ctypes interface provides complete, direct
% access to all functionality as it would be available to C programmers.
%
% GRASS GIS provides specialized Python library for managing and analyzing spatio-temporal data (Gebbert and
% Pebesma, 2014). The temporal library introduces space time datasets representing time series of raster, 3D raster
% or vector maps and allows users to combine various spatio-temporal operations including queries, aggregation,
% sampling or the analysis of spatio-temporal topology.
% 
% We will also discuss the advantages of implementing scientific algorithm as a GRASS GIS module and we will
% show how to write such module in Python. To facilitate the development of the module, GRASS GIS provides
% a Python library for testing (Petras and Gebbert, 2014) which helps researchers to ensure the robustness of the
% algorithm, correctness of the results in edge cases as well as the detection of changes in results due to new
% development. For all modules GRASS GIS automatically creates standardized command line and graphical user
% interfaces and documentation. Finally, we will show how GRASS GIS can be used together with powerful Python
% tools such as the NumPy package and the IPython Notebook.

% TODO: the two blocks below are just taken from testing poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Highlights}{
% \setlength{\parskip}{1em}
\textfontsize
% \begin{itemize}
\renewcommand{\item}{\par\vspace{0.8ex}}
\item GRASS GIS is a platform for geospatial computations.
\item The framework supports code maintenance which results in long term preservation of algorithms.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Description}{
% \textfontsize
\Large
\newcommand{\intropartitle}[1]{\parinlinetitle{#1}}
% \setlength{\parskip}{1em}

\intropartitle{Motivation}
GRASS GIS \cite{Neteler2012}, a free and open source GIS, is used by many scientists directly or through other projects such as R or QGIS to perform geoprocessing tasks.
Thus, a large number of scientific geospatial computations depend on quality and correct functionality of GRASS GIS.
Automatic functionality testing is therefore necessary to ensure software reliability.

\intropartitle{Unique features}
We present a testing framework for GRASS GIS which addresses different needs of GRASS GIS and geospatial software in general.
It tests GRASS tools (referred to as GRASS modules) and
examines outputs including large raster and vector maps as well as temporal datasets.
Furthermore, it enables to test all levels of GRASS GIS architecture including C and Python application programming interface and GRASS modules invoked as subprocesses.

\intropartitle{Audience}
Since GRASS GIS is used as a platform for development of geospatial algorithms and models,
the testing framework allows not only to test GRASS GIS core functionality but also tools developed by scientists as a part of their research.

\intropartitle{Scientific impact}
}

\block{More information}{
\newcommand{\qrcodewidth}{1\linewidth}
\hspace{-0.02\linewidth}
\begin{tabular}{lll}
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{grass_osgeo_org}
\end{minipage}
\begin{minipage}{0.27\linewidth}
GRASS GIS website
\end{minipage}
&
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{python_doc}
\end{minipage}
\begin{minipage}{0.45\linewidth}
GRASS GIS Python libraries documentation
\end{minipage}
\\
% http://grass.osgeo.org/
\url{grass.osgeo.org}
&
% http://grass.osgeo.org/grass71/manuals/libpython/
\url{grass.osgeo.org/grass71/manuals/libpython}
\end{tabular}

% qrcode -t EPS -o grass-user.eps "http://lists.osgeo.org/listinfo/grass-user"
% epstopdf grass-user.eps
% rm grass-user.eps

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\column{0.25}

\block{Example of including code generated aside}{

% listings package does not work well with the tikzposter class,
% so we need to include pdf
\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{sample}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\column{0.25}

\block{Sample block}{
\textfontsize

See abstact for topics which can become blocks.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\column{0.25}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Acknowledgements}{
\begin{tabular}{cp{28em}}
\raisebox{-.4\height}{
\includegraphics[width=0.2\linewidth]{osgeo}
}
& GRASS GIS is a OSGeo project. OSGeo provides infrastructure for websites and source code management.
\\
\raisebox{-.8\height}{
\includegraphics[width=0.2\linewidth]{google}
}
& Initial development of pygrass and gunittest packages was done during Google Summer of Code.
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{References}{

% disable the title
\renewcommand{\section}[2]{}
\begin{thebibliography}{9}

\bibitem{Neteler2012}
  Neteler, M., Bowman, M. H., Landa, M., Metz, M., 2012.
  \emph{GRASS GIS: A multi-purpose open source GIS.}
  Environmental Modelling \& Software, 31(0), 124-130.

\bibitem{Gebbert2014}
  Gebbert, S., Pebesma, E., 2014. A temporal GIS for field based environmental modeling. Environmental
  Modelling \& Software 53, 1-12.

\bibitem{Petras2014}
  Petras, V., Gebbert, S., 2014. Testing framework for GRASS GIS: ensuring reproducibility of scientific
  geospatial computing. Poster presented at: AGU Fall Meeting, December 15-19, 2014, San Francisco, USA.

\bibitem{Zambelli2013}
  Zambelli, P., Gebbert, S., Ciolli, M., 2013. Pygrass: An Object Oriented Python Application Programming
  Interface (API) for Geographic Resources Analysis Support System (GRASS) Geographic Information System
  (GIS). ISPRS International Journal of Geo-Information 2, 201-219.

\end{thebibliography}
}

\end{columns}
\end{document}

### 2015-03-03 grassposter/2015_EGU_WD_Ethiopia/poster.tex
Added 2015_EGU_WD_Ethiopia poster draft
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64791 15284696-431f-4ddb-bdfa-cd5b030d7da7

\documentclass[landscape,a0,final]{a0poster}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikzposter} % here most of the things are defined
\usepackage{minted} %code highlighting, not working yet
% change parameters only after this line You can also start a new column with an arbitrary 
% x-coordinate by specifying explicitly the coordinate of the new block node as follows:
\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage{wrapfig}
\usepackage{url}

%Used for better control on code display

\usepackage[margin=\margin cm, paperwidth=197cm, paperheight=100cm]{geometry}

% \setbackgrounddarkcolor{ForestGreen!70!black}
% \setbackgroundlightcolor{YellowGreen!90!}

% \setfirstcolor{YellowGreen!80!}
% \setsecondcolor{gray!80!}
% \setthirdcolor{red!80!black}

\title{Water Dynamics in Fogera and the Upper Blue Nile\\Farmers perspectives and remote sensing\bigskip}
\author{Yann Chemin, Mengistu Dessalegn, Jayne Curnow\\
\bigskip
\\ International Water Management Institute}

\usetemplate{1}
\setinstituteshift{1}

\setblocktitleheight{2}
\setblockspacing{1}

\begin{document}
\ClearShipoutPicture
\AddToShipoutPicture{\BackgroundPicture}
\noindent
\tikzstyle{every picture}+=[remember picture]
\begin{tikzpicture}
\initializesizeandshifts
\titleblock{120}{1}
% \setblocktitleheight{1}
\addlogo[north west]{(2,-1)}{9cm}{./svg_images/Grass_GIS.pdf}
\addlogo[north west]{(13,-3)}{19cm}{./svg_images/OSGeo_logo.pdf}
\addlogo[north east]{(-2,-4.5)}{30cm}{./images/CR10583_1wle-iwmi_logo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Abstract}{
\small \noindent This research work is about finding the connection between farmers perspectives on changes of water conditions in their socio-agricultural environment and satellite remote sensing analysis.\newline
Key informant surveys were conducted to investigate localised views on water scarcity as a counterpoint to the physical measurement of water availability. Does a numerical or mapped image identifying water scarcity always equate to a dearth of water for agriculture? To push the limits of the relationship between human and physical data we sought to ground-truth GIS results with the practical experience and knowledge of people living in the area.\newline\linebreak
\noindent We data-mined public domain satellite data with FOSS (GDAL[2], GRASS GIS[1]) and produced water-related spatio-temporal domains for our study area and the larger Upper Nile Basin.\newline\linebreak
Accumulated remote sensing information was then cross-referenced with informant’s accounts of water availability for the same space and time. During the survey fieldwork the team also took photographs electron- ically stamped with GPS coordinates to compare and contrast the views of informants and the remote sensing information with high resolution images of the landscape.\newline\linebreak
We found that farmers perspective on the Spring maize crop sensibility to variability of rainfall can be quantified in space and time by remote sensing cumulative transpiration. A crop transpiration gap of 1-2.5 mm/day for about 20 days is to be overcome, a full amount of 20 to 50 mm, depending on the type of year deficit. Such gap can be overcome, even by temporary supplemental irrigation practices, however, the economical and cultural set up is already developed in another way, as per sesonal renting of higher soil profile water retention capacity fields.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Transpiration of Fogera crops}{
\smallskip
\begin{center}
	\begin{tabular}{c p{0.5\textwidth}}
	 \raisebox{-0.9\totalheight}{\includegraphics[width=0.45\textwidth]{./images/fig1}}
	&
	The transpiration data is created from energy balance modelling [3] modules (i.eb.*, i.evapo.*) within GRASS GIS version 7, by partitioning the net radiation (r.sun) into soil heat flux (i.eb.soilheatflux), sensible heat flux (i.eb.h\_*) and the residual being the energy needed to evaporate water (i.eb.evapfr, i.eb.eta). This information is then fractionated into biotic (transpiration) and abiotic (evaporation) parts using vegetation fraction.\newline\linebreak
The accumulated transpiration is subjected to temporal scrutiny ...\newline
 	\end{tabular}\newline
\end{center}
\begin{center}
	\begin{tabular}{cc}
 	\includegraphics[width=0.45\textwidth]{./images/fig1}
 	& 
 	\includegraphics[width=0.45\textwidth]{./images/fig1}
	\end{tabular}
\end{center}

More info here...\newline

}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Acknowledgements}{
\smallskip
\begin{tabular}{p{0.70\textwidth} c}
	The authors would like to acknowledge the CGIAR Research Program on Water, Land and Ecosystems (WLE ; \url{wle.cgiar.org}) Innovation Fund.
	&
	\hspace{3mm}
	\raisebox{-0.5\totalheight}{\includegraphics[width=0.27\textwidth]{./images/WLE}}
\end{tabular}
}

\startsecondcolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Farmer's perspectives on changes of water conditions}{
\smallskip
Farmer’s perspectives on changes of water conditions is tied to the socio-agricultural environment. Localised views on water scarcity is a counterpoint to the physical measurement of water availability.\newline\linebreak
Scholars have raised the concern that conventional approaches are driven largely by biophysical crop data, disregarding farmers’ behaviours, responses and strategies (Hurd, 2008). Likewise, the persistent view that risk should be determined “scientifically” and “objectively” relegated community perceptions and assessments to be uninformed, false, illusory, or irrational (Oliver-Smith, 1996). This study aims at listening to people's perspectives and support it from remote sensing.\newline\linebreak
The practical experience and knowledge of people living in an area is driving decision-making and is a lever for assessing improvement of social and economic well-being.\newline
Farmers in Fogera, Ethiopia depend on rainfed agriculture for their livelihoods using ox-drawn ploughs. Crop production largely depends on mono-modal rainfall which starts in May and extends from June to September. The wet season crop calendar, i.e. planting and harvesting, starts in May and ends by December, depending on the type of crop (see Table 1).\newline\linebreak
\begin{center}
\includegraphics[width=0.6\textwidth]{./images/table1}
\end{center}
Key informants in Fogera described how rainfall patterns have become more irregular over the last two decades. Farmers we interviewed also indicated that the rain comes irregularly or at times, fails. There is a common agreement by farmers that years of sufficient rainfall, without hail or frost, providing good harvest have become less. Mostly increased variability and hazard are the new norm in recent decades (Wakjira and Gizaw, 2008).\newline\linebreak
We data-mined public domain satellite data and produced water-related spatio-temporal domains that was then cross-referenced with informant’s accounts of water availability for the same space and time.\newline
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Spring Maize and food security}{
\begin{center}
	\begin{tabular}{c p{0.5\textwidth}}
 	\raisebox{-0.9\totalheight}{\includegraphics[width=0.45\textwidth]{./images/fig1}}
	&
	We found that in one case (figure 1), farmers perspective on the Spring maize crop sensibility to variability of rainfall can be quantified in space and time by remote sensing cumulative transpiration. A crop transpiration gap of 1-2.5 mm/day for about 20 days is to be overcome, a full amount of 20 to 50 mm, depending on the type of year deficit. Such gap can be overcome, even by temporary supplemental irrigation practices.\newline
We argue that a better understanding of the dynamics of water variability and the implications on water management, agricultural production and livelihoods should consider small-holder farmers’ perceptions, concerns and responses. This is essential to devise well-targeted policies and interventions that can improve livelihoods, as well as optimising water management and agricultural production.\newline\linebreak
	\end{tabular}
\end{center}
Cumulative transpiration on a yearly basis highlights different years, and heterogeneity periods (breaks) in the growing curve. Looking closely into the May-July period, one can identified the transpiration gap found most of the time for the early Maize crop much discussed by farmers. Out of 14 years, only 4 seem to have made the transpiration leap above the others (red ellipse in Figure 1). The leap can be quantified by an average of 20mm of rainfall over a period of 20 days, 1 mm of transpiration per day is missing at minimum (red ellipse) and 2.5mm/day at maximum (yellow ellipse) from mid-June to early July.\newline\linebreak

}

\startthirdcolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{May rainfall deficit perceived water scarcity}{
Farmers in upland Fogera associate the failure of the May rains with “drought”. For instance, a male farmer stated that, “When it is drought, it is the season of millet (teff).” A female farmer stressed this seasonal scarcity in water availability by insisting that “It is this drought that hinders crop production.” However, if the rain fails in May, it does not necessarily represent an inevitable drought year, in that rain can be available in the subsequent months. Nevertheless, rainfed maize and millet planting in May is a central concern as it provides food and fodder for season, buffering household food security and reducing stress on further crop-related decision-making.\newline\linebreak
Rainfall variability has been one of the important factors impeding sustained implementation of intensification strategies, and particularly the use of fertilisers. Key informants indicated that rainfall variability has been discouraging the use of fertiliser due to risk of unsuccessful crop production which exacerbates farmers’ indebtedness besides losing production.i\newline\linebreak
Vulnerability and capacity to respond to rainfall variability differs depending on individual natural, financial and social assets, as well as gender and socio-cultural variables. Farmers in Fogera have been attempting to respond to problems related to water availability based on adaptation, indigenous knowledge, practicing available options. Responses undertaken by individual farmers and communities include: adjusting planting times and cropping pattern; deploying traditional ecological knowledge of soil to mitigate risk associated with water availability, expanding traditional and motor-pump irrigation (Dessalegn and Merry 2014); and sponsoring religious figures to ameliorate the violation of spiritual sanctions that are transgressed in contemporary agricultural production.\newline\linebreak
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{GRASS GIS script}{
\smallskip
{\footnotesize \fontfamily{pcr}\selectfont 
\textbf{\#Select MODIS EVI archive\newline} 
i.group \textcolor{blue}{group}=pca\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=*h28v07*EVI)\newline
\textbf{\#Run the PCA on the EVI archive\newline}
i.pca \textcolor{blue}{input}=pca\_group \textcolor{blue}{output\_prefix}=pca \textcolor{blue}{percent}=99 --o\newline
\textbf{\#As an example, you can select the 1$^{st}$ to the 9$^{th}$ PCA members\newline}
i.group \textcolor{blue}{group}=ta\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=pca.[123456789] sep=,) \newline
\textbf{\#and run an object-based classification analysis on them\newline}
i.segment \textcolor{blue}{group}=ta\_group \textcolor{blue}{output}=seg\_ta \textcolor{blue}{threshold}=0.9 \textcolor{blue}{memory}=5000 \textcolor{blue}{iterations}=50 --o \& \newline}

%Minted version Not working (+ compile needs -shell-escape)
%\begin{minted}[frame=single,linenos,mathescape,fontsize=\small]{sh}
%	#Select MODIS EVI archive
%	i.group group=pca_group input=$(g.mlist type=rast pattern=*h28v07*EVI)
%	#Run the PCA on the EVI archive
%	i.pca input=pca_group output_prefix=pca_ percent=99 --o
%	#As an example, you can select the 1$^{st}$ to the 9$^{th}$ PCA members
%	i.group group=ta_group input=\$(g.mlist type=rast pattern=pca.[123456789] sep=,)
%	#and run an object-based classification analysis on them
%	i.segment group=ta_group output=seg_ta threshold=0.9 memory=5000 iterations=50 --o \&
%\end{minted}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\getcurrentrow{box}
\coordinate (funkcionalita) at (box.south west);
\coordinate (funkcionalitaeast) at (box.east);
\coordinate (screenshot) at (box.north west);

\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
\scriptsize
\begin{center}
\begin{tabular}{rp{0.9\textwidth}}
[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
[2] & GDAL, 2014. {\url {http://gdal.osgeo.org}}\\{}
[3] & Chemin, 2012. Chapter 19, DOI: 10.5772/23571 ({\url {http://bit.ly/16qJOep}})\\{}
\end{tabular}
\end{center}
\smallskip
\hrulefill
\vspace{-5pt}

\begin{center}
\begin{tabular}{cp{0.9\textwidth}}
\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/iwmi_qr.pdf}
\end{minipage}

\begin{minipage}{0.3\textwidth}
\small {\url{www.iwmi.org}}
\end{minipage}

\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/grass_qr.pdf}
\end{minipage}

\begin{minipage}{0.3\textwidth}
\small {\url{grass.osgeo.org}}
\end{minipage}
\end{tabular}
\end{center}

\hrulefill
\vspace{14pt}
\begin{center}
\newcommand{\logowidth}{5em}
\newcommand{\logospace}{\hspace{0.1em}}
\noindent
\includegraphics[width=\logowidth]{./svg_images/public_domain_logo.pdf}
\raisebox{0.7\height}{\logospace 2015 GRASS Development Team}
\end{center}
}

\startfourthcolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{TBC...}{
\smallskip
TBC...\newline\linebreak

Object based classification (\textit{i.segment}) of the sum transpiration for each year has been done and merged, resulting areas were clumped (\textit{r.clump}) and averaged statistics of yearly transpiration extracted (\textit{r.stats.zonal}).\newline
\begin{center}
	\begin{tabular}{cc}
 	\begin{tabular}{p{0.5\textwidth}}
 	\includegraphics[width=0.45\textwidth]{./images/fig1}\\
 	\vspace{5mm}
 	This perspective proposes that irrigated areas along the Mekong may not be transpiring as much as the recession cropping areas around Tonle Sap. Whether the transpiration in recession zones is actually used by crops all the time depends on the opportunity of farming intensification and risk avoidance.\newline 
	\end{tabular}
 	& 
 	\begin{tabular}{c}
 	\includegraphics[width=0.45\textwidth]{./images/fig1}\\
 	\includegraphics[width=0.45\textwidth]{./images/fig1}
	\end{tabular}
	\end{tabular}
\end{center}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Conclusions}{
\smallskip
Space science (i.e. remote sensing plant transpiration data and analysis) complements and augments farmer’s responses to rainfall variability. In such marginal landscapes access to this information can mean the difference between seasonal hunger and food security.
}

\end{tikzpicture}

\end{document}

### 2015-03-03 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
Added 2015_EGU_G7_PeerReview_SciPlatform draft
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64792 15284696-431f-4ddb-bdfa-cd5b030d7da7

\documentclass[landscape,a0,final]{a0poster}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikzposter} % here most of the things are defined
% change parameters only after this line You can also start a new column with an arbitrary 
% x-coordinate by specifying explicitly the coordinate of the new block node as follows:
\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage{wrapfig}
\usepackage{url}

% For blibliography styling
\usepackage{natbib}

%Used for better control on code display

\usepackage[margin=\margin cm, paperwidth=197cm, paperheight=100cm]{geometry}

% \setbackgrounddarkcolor{ForestGreen!70!black}
% \setbackgroundlightcolor{YellowGreen!90!}

% \setfirstcolor{YellowGreen!80!}
% \setsecondcolor{gray!80!}
% \setthirdcolor{red!80!black}

\title{\bigskip GRASS GIS: a peer-reviewed scientific platform and future research repository\bigskip}
\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$,Soeren Gebbert$^5$, Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Magherita di Leo$^8$\\ \bigskip
$^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, $^5$ TICSA, Germany, $^6$ EURAC, Italy, $^7$ GNLST, Germany, $^8$ EC-JRC, Itlay}

\usetemplate{1}
\setinstituteshift{1}

\setblocktitleheight{2}
\setblockspacing{1}

\begin{document}
\ClearShipoutPicture
\AddToShipoutPicture{\BackgroundPicture}
\noindent
\tikzstyle{every picture}+=[remember picture]
\begin{tikzpicture}
\initializesizeandshifts
\titleblock{90}{1}
% \setblocktitleheight{1}

\addlogo[north west]{(2,-1)}{9cm}{svg_images/Grass_GIS.pdf}
%Please insert your institution logo here
\addlogo[north east]{(-2,-2.5)}{4cm}{svg_images/logo_FEM_CRI.pdf}
\addlogo[north east]{(-2,-5.5)}{4cm}{svg_images/NC_State_Seal.pdf}
\addlogo[north east]{(-8,-2.5)}{4cm}{images/Logo_cvut.jpg}
\addlogo[north east]{(-8,-6.5)}{4cm}{svg_images/IWMI_logo.pdf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Abstract}{
\small \noindent Geographical Information Systems (GIS) is known for its capacity to spatially enhance the capacity of man- agement of natural resources. While being often used as an analytical tool, it also represents a collaborative scientific platform to develop new algorithms. GRASS GIS \cite{neteler2012grass}, a free and open source GIS, is used by many scientists directly or through other projects such as R or QGIS to perform geoprocessing tasks. Thus, a large number of scientific geospatial computations depend on quality and correct functionality of GRASS GIS. Integrating scientific algorithms into GRASS GIS helps to preserve reproducibility of scientific results over time as the original author designed it \cite{rocchini2012let}. Moreover, subsequent improvements are tracked in the source code versioning system and are immediately available to the public (Petras, 2014). Thus, GRASS GIS acts as a repository of scientific peer-reviewed code and algorithm/knowledge hub for future generation of scientists.\vspace{5mm}\newline
With the various types of actual ET models being developed in the last 20 years, it becomes necessary to inter-compare methods. Most of already published ETa models comparisons address few number of models, and small to medium areas (\cite{chemin2012distributed}; \cite{gao2008intercomparison}; \cite{garcia2007comparison}; \cite{suleiman2008intercomparison}; \cite{timmermans2007intercomparison}). With the large amount of remote sensing data covering the Earth, and the daily information available for the past ten years (i.e. Aqua/Terra-MODIS) for each pixel location, it becomes paramount to have a more complete comparison, in space and time.\vspace{5mm}\newline
To address this new experimental requirement, a distributed computing framework was designed, and created \cite{chemin2012distributed}. The design architecture was built from original satellite datasets to various levels of processing until reaching the requirement of various ETa models input dataset. Each input product is computed once and reused in all ETa models requiring such input. This permits standardization of inputs as much as possible to zero-in variations of models to the models internals/specificities. All of the ET models are available in the new GRASS GIS version 7 as imagery modules and replicability is complete for future research.\vspace{5mm}\newline
A set of modules for multiscale analysis of landscape structure was added in 1992 by \cite{baker1992r} who developed the r.le model similar to FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually improved to become r.li in 2006. Further development continued, with a significant speed up (Trac1, 2014) and new interactive user interface.\vspace{5mm}\newline
The module v.surf.rst for spatial interpolation was developed approximately 12 years ago, since then it was improved several times (Trac2, 2014). It is an important part of GRASS GIS and is even taught at geospatial modeling courses, for example http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html.\vspace{5mm}\newline
GRASS GIS entails several modules that constitute the result of active research on natural hazard. The r.sim.water simulation model (Mitas and Mitasova, 1998) for overland flow under rainfall excess conditions was integrated into the Emergency Routing Decision Planning system as a WPS \cite{raghavan2014deploying}. It was also modified by Petrasova et al. (2014) and is now part of a specialised software called Tangible Landscape (previously Tangible GIS), which also incorporated the r.damflood module.\vspace{5mm}\newline
The wildfire simulation toolset, firstly developed by \cite{xu1994simulating}, implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS functions r.ros and r.spread, is object of active research. It has been exten- sively tested and recently adapted to European fuel types (\cite{rodriguez2013data} ; \cite{derigo2013architecture} ; Di Leo et al., 2013).
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\getcurrentrow{box}
%\coordinate (funkcionalita) at (box.south west);
%\coordinate (funkcionalitaeast) at (box.east);
%\coordinate (screenshot) at (box.north west);
%
%\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
\blocknode{References}{
\smallskip
\scriptsize

\begingroup
\renewcommand{\section}[2]{}%
\bibliographystyle{plain}
\bibliography{poster}
\endgroup

%\hrulefill
%\vspace{-5pt}

\begin{center}
\begin{tabular}{c}
\hspace{5mm}
\begin{minipage}{0.2\textwidth}
\includegraphics[width=0.5in]{./images/grass_qr.pdf}
\end{minipage}

\begin{minipage}{0.25\textwidth}
\small {\url{www.bbk.ac.uk}}
\end{minipage}

\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./svg_images/public_domain_logo.pdf}
\end{minipage}

\begin{minipage}{0.3\textwidth}
\small {\url{grass.osgeo.org}}
\end{minipage}

\begin{minipage}{0.2\textwidth}
\includegraphics[width=0.5in]{./images/grass_qr.pdf}
\end{minipage}

\end{tabular}
\end{center}

}

\startsecondcolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{}{
\bigskip

\startthirdcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{}{
\smallskip

}

\blocknode{Conclusions}{
\smallskip
}

\startfourthcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{}{
\smallskip

}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{}{

}%End of Block

\end{tikzpicture}

\end{document}

### 2015-03-04 grassposter/2015_EGU_WD_Ethiopia/poster.tex
update drafts
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64796 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 To push the limits of the relationship between human and physical data we sought to ground-truth GIS results with the practical experience and knowledge of people living in the area.\newline\linebreak
-\noindent We data-mined public domain satellite data with FOSS (GDAL[2], GRASS GIS[1]) and produced water-related spatio-temporal domains for our study area and the larger Upper Nile Basin.\newline\linebreak
+\noindent We data-mined public domain satellite data with FOSS (GDAL \cite{GDAL}, GRASS GIS \cite{neteler2012grass}) and produced water-related spatio-temporal domains for our study area and the larger Upper Nile Basin.\newline\linebreak
 Accumulated remote sensing information was then cross-referenced with informant’s accounts of water availability for the same space and time.
-During the survey fieldwork the team also took photographs electron- ically stamped with GPS coordinates to compare and contrast the views of informants and the remote sensing information with high resolution images of the landscape.\newline\linebreak
+During the survey fieldwork the team also took photographs electronically stamped with GPS coordinates to compare and contrast the views of informants and the remote sensing information with high resolution images of the landscape.\newline\linebreak
 We found that farmers perspective on the Spring maize crop sensibility to variability of rainfall can be quantified in space and time by remote sensing cumulative transpiration.
 A crop transpiration gap of 1-2.5 mm/day for about 20 days is to be overcome, a full amount of 20 to 50 mm, depending on the type of year deficit.
-Such gap can be overcome, even by temporary supplemental irrigation practices, however, the economical and cultural set up is already developed in another way, as per sesonal renting of higher soil profile water retention capacity fields.
+Such gap can be overcome, even by temporary supplemental irrigation practices, however, the economical and cultural set up is already developed in another way, as per seasonal renting of higher soil profile water retention capacity fields.
 }
@@
 	&
-	The transpiration data is created from energy balance modelling [3] modules (i.eb.*, i.evapo.*) within GRASS GIS version 7, by partitioning the net radiation (r.sun) into soil heat flux (i.eb.soilheatflux), sensible heat flux (i.eb.h\_*) and the residual being the energy needed to evaporate water (i.eb.evapfr, i.eb.eta).
+	The transpiration data is created from energy balance modelling \citep{chemin2012distributed} modules (i.eb.*, i.evapo.*) within GRASS GIS version 7, by partitioning the net radiation (r.sun) into soil heat flux (i.eb.soilheatflux), sensible heat flux (i.eb.h\_*) and the residual being the energy needed to evaporate water (i.eb.evapfr, i.eb.eta).
 This information is then fractionated into biotic (transpiration) and abiotic (evaporation) parts using vegetation fraction.\newline\linebreak
@@
 Localised views on water scarcity is a counterpoint to the physical measurement of water availability.\newline\linebreak
-Scholars have raised the concern that conventional approaches are driven largely by biophysical crop data, disregarding farmers’ behaviours, responses and strategies (Hurd, 2008).
-Likewise, the persistent view that risk should be determined “scientifically” and “objectively” relegated community perceptions and assessments to be uninformed, false, illusory, or irrational (Oliver-Smith, 1996).
+Scholars have raised the concern that conventional approaches are driven largely by biophysical crop data, disregarding farmers’ behaviours, responses and strategies \citep{hurd2008challenges}.
+Likewise, the persistent view that risk should be determined “scientifically” and “objectively” relegated community perceptions and assessments to be uninformed, false, illusory, or irrational \citep{oliver1996anthropological}.
 This study aims at listening to people's perspectives and support it from remote sensing.\newline\linebreak
@@
 There is a common agreement by farmers that years of sufficient rainfall, without hail or frost, providing good harvest have become less.
-Mostly increased variability and hazard are the new norm in recent decades (Wakjira and Gizaw, 2008).\newline\linebreak
+Mostly increased variability and hazard are the new norm in recent decades \citep{wakjira2008diversifying}.\newline\linebreak
 We data-mined public domain satellite data and produced water-related spatio-temporal domains that was then cross-referenced with informant’s accounts of water availability for the same space and time.\newline
@@
 Farmers in Fogera have been attempting to respond to problems related to water availability based on adaptation, indigenous knowledge, practicing available options.
-Responses undertaken by individual farmers and communities include: adjusting planting times and cropping pattern; deploying traditional ecological knowledge of soil to mitigate risk associated with water availability, expanding traditional and motor-pump irrigation (Dessalegn and Merry 2014); and sponsoring religious figures to ameliorate the violation of spiritual sanctions that are transgressed in contemporary agricultural production.\newline\linebreak
+Responses undertaken by individual farmers and communities include: adjusting planting times and cropping pattern; deploying traditional ecological knowledge of soil to mitigate risk associated with water availability, expanding traditional and motor-pump irrigation \citep{dessalegn2014is}; and sponsoring religious figures to ameliorate the violation of spiritual sanctions that are transgressed in contemporary agricultural production.\newline\linebreak
 }
@@
 
-%Minted version Not working (+ compile needs -shell-escape)
-%\begin{minted}[frame=single,linenos,mathescape,fontsize=\small]{sh}
-%	#Select MODIS EVI archive
-%	i.group group=pca_group input=$(g.mlist type=rast pattern=*h28v07*EVI)
-%	#Run the PCA on the EVI archive
-%	i.pca input=pca_group output_prefix=pca_ percent=99 --o
-%	#As an example, you can select the 1$^{st}$ to the 9$^{th}$ PCA members
-%	i.group group=ta_group input=\$(g.mlist type=rast pattern=pca.[123456789] sep=,)
-%	#and run an object-based classification analysis on them
-%	i.segment group=ta_group output=seg_ta threshold=0.9 memory=5000 iterations=50 --o \&
-%\end{minted}
 }
@@
 \scriptsize
-\begin{center}
-\begin{tabular}{rp{0.9\textwidth}}
-[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
-[2] & GDAL, 2014. {\url {http://gdal.osgeo.org}}\\{}
-[3] & Chemin, 2012. Chapter 19, DOI: 10.5772/23571 ({\url {http://bit.ly/16qJOep}})\\{}
-\end{tabular}
-\end{center}
-\smallskip
-\hrulefill
-\vspace{-5pt}
+\begingroup
+\renewcommand{\section}[2]{}%
+\bibliographystyle{plain}
+\bibliography{poster}
+\endgroup
+
+%\smallskip
+%\hrulefill
+%\vspace{-5pt}
 
@@
  	\vspace{5mm}
- 	This perspective proposes that irrigated areas along the Mekong may not be transpiring as much as the recession cropping areas around Tonle Sap.
-Whether the transpiration in recession zones is actually used by crops all the time depends on the opportunity of farming intensification and risk avoidance.\newline
+blablablablablabla
 	\end{tabular}

### 2015-03-04 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
update
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64797 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-\title{\bigskip GRASS GIS: a peer-reviewed scientific platform and future research repository\bigskip}
-\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$,Soeren Gebbert$^5$, Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Magherita di Leo$^8$\\ \bigskip
+\title{\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip}
+\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$, Soeren Gebbert$^5$, \\Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Magherita di Leo$^8$\\ \bigskip
 $^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, $^5$ TICSA, Germany, $^6$ EURAC, Italy, $^7$ GNLST, Germany, $^8$ EC-JRC, Itlay}
@@
 \begin{minipage}{0.25\textwidth}
-\small {\url{www.bbk.ac.uk}}
+\small {\url{grasswiki.osgeo.org}}
 \end{minipage}
@@
 \bigskip
+
+}
 

### 2015-03-04 grassposter/2015_EGU_Python/listings/grass_module_cli.tex
python poster: blocks for outline, bash in documentation to python block, generated interface block, width according to other EGU posters
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64799 15284696-431f-4ddb-bdfa-cd5b030d7da7

% taken from grass-promo/grassposter, written by me I think

\documentclass{standalone}

\usepackage[active,tightpage]{preview}
\usepackage{listings}
\PreviewEnvironment{lstlisting}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\input{listings_settings}

\begin{document}

% do some trim here, do more trim when including if needed
\begin{lstlisting}[linewidth=34.2em]
Description:
 Adds the values of two rasters (A + B)

Keywords:
 raster, algebra, sum

Usage:
 r.plus araster=name braster=name output=name [--overwrite] [--help]
   [--verbose] [--quiet] [--ui]

Flags:
 --o   Allow output files to overwrite existing files
 --h   Print usage summary
 --v   Verbose module output
 --q   Quiet module output
 --ui  Force launching GUI dialog

Parameters:
  araster   Name of input raster A in an expression A + B
  braster   Name of input raster B in an expression A + B
   output   Name for output raster map
\end{lstlisting}
\end{document}

### 2015-03-04 grassposter/2015_EGU_Python/main.tex
python poster: blocks for outline, bash in documentation to python block, generated interface block, width according to other EGU posters
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64799 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \usepackage{enumitem}
-\geometry{paperwidth=63in,paperheight=42in}
+\geometry{paperwidth=197cm,paperheight=100cm}
 \usepackage{url}
+
+\usepackage{alltt}
+
+\newcommand{\inst}[1]{\hspace{2pt}$^{\mbox{\normalsize#1}}$\hspace{-7pt}}
+\newcommand{\instlist}[1]{\hspace{1pt}$^{#1}$}
 
@@
     Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7
+    \bigskip
   \end{minipage}
@@
 \author{
-V\'{a}clav Petr\'{a}\v{s} (1), Anna Petr\'{a}\v{s}ov\'{a} (1), Yann Chemin (2), Pietro Zambelli (3), Martin Landa (4), \\
-S\"{o}ren Gebbert (5), Markus Neteler (6), and Peter L\"{o}we (7)
+V\'{a}clav Petr\'{a}\v{s}\inst{1},
+Anna Petr\'{a}\v{s}ov\'{a}\inst{1},
+Yann Chemin\inst{2},
+Pietro Zambelli\inst{3},
+Martin Landa\inst{4},
+S\"{o}ren Gebbert\inst{5},
+Markus Neteler\inst{6}, and
+Peter L\"{o}we\inst{7}
 }
 \institute{
-\large  % using smaller size of font than default because the list is long
-(1) North Carolina State University, Raleigh, USA (wenzeslaus@gmail.com, vpetras@ncsu.edu), (2) International Water Management Institute,
-Pelawatta, Sri Lanka, (3) EURAC Research, Institute for Renewable Energy, Bolzano/Bozen, Italy, (4) Faculty of Civil
-Engineering, Czech Technical University in Prague, Czech Republic, (5) Th\"{u}nen Institute of Climate-Smart Agriculture,
-Braunschweig, Germany, (6) Research and Innovation Centre, Fondazione Edmund Mach, San Michele all'Adige, Italy, (7)
-German National Library for Science and Technology, Hanover, Germany
+\large
+\instlist{1}North Carolina State University, Raleigh, USA (wenzeslaus@gmail.com, vpetras@ncsu.edu),
+\instlist{2}International Water Management Institute, Pelawatta, Sri Lanka,
+\instlist{3}EURAC Research, Institute for Renewable Energy, Bolzano/Bozen, Italy,
+\instlist{4}Faculty of Civil Engineering, Czech Technical University in Prague, Czech Republic,
+\instlist{5}Th\"{u}nen Institute of Climate-Smart Agriculture, Braunschweig, Germany,
+\instlist{6}Research and Innovation Centre, Fondazione Edmund Mach, San Michele all'Adige, Italy,
+\instlist{7}German National Library for Science and Technology, Hanover, Germany
 }
@@
 \definecolor{textcolor}{HTML}{000000}
+
+\definecolor{titleTextColor}{HTML}{2E652E}
 
@@
 \renewcommand\TP@maketitle{%
-    \begin{minipage}{0.2\linewidth}
+    \begin{minipage}{0.12\linewidth}
        \centering
 
+       \newcommand{\logowidth}{0.17\textwidth}
+       \newcommand{\logovspace}{\vspace{3ex}}
+       \newcommand{\logohspace}{\hspace{1ex}}
+
        % TODO: get other logos
-       \includegraphics[width=0.2\textwidth]{ncstate}
-       \hspace{2ex}
-       \includegraphics[width=0.2\textwidth]{iwmi}
+       \includegraphics[width=\logowidth]{ncstate}
+       \logohspace
+       \includegraphics[width=\logowidth]{iwmi}
 
-       \vspace{4ex}
+       \logovspace
 
-       \includegraphics[width=0.2\textwidth]{ncstate}
-       \hspace{2ex}
-       \includegraphics[width=0.2\textwidth]{ctu_prague}
-       \hspace{2ex}
-       \includegraphics[width=0.2\textwidth]{ncstate}
+       \includegraphics[width=\logowidth]{ncstate}
+       \logohspace
+       \includegraphics[width=\logowidth]{ctu_prague}
+       \logohspace
+       \includegraphics[width=\logowidth]{ncstate}
 
-       \vspace{4ex}
+       \logovspace
 
-       \includegraphics[width=0.2\textwidth]{fem_cri}
-       \hspace{2ex}
-       \includegraphics[width=0.2\textwidth]{ncstate}
+       \includegraphics[width=\logowidth]{fem_cri}
+       \logohspace
+       \includegraphics[width=\logowidth]{ncstate}
     \end{minipage}%
     \hfill
-   \begin{minipage}{0.6\linewidth}
+   \begin{minipage}{0.74\linewidth}
         \centering
         \color{titlefgcolor}
-        {\bfseries  \sc {\fontsize{85}{60}\selectfont \@title}  \par}
+        {\textcolor{titleTextColor}{\textsf{\textbf{{\fontsize{85}{60}\selectfont \@title}}}}  \par}
         \vspace*{1em}
@@
     \hfill
-    \begin{minipage}{0.2\linewidth}
+    \begin{minipage}{0.12\linewidth}
        \centering
-       \includegraphics[width=0.39\textwidth]{grass}\\
-       \LARGE \textbf{\textsf{GRASS GIS}}
+       \includegraphics[width=0.35\textwidth]{grass}\\
+       \Large \textbf{\textsf{GRASS GIS}}
     \end{minipage}
@@
 
+% listings package does not work well with the tikzposter class,
+% so we need to include PDFs with code generated separately
+
 \newcommand{\partitle}[1]{\bigskip \textbf{#1}\\[1ex]}
@@
 
+% GRASS module
 \newcommand{\gmodule}[1]{\emph{#1}}
+
 \newcommand{\rafun}[1]{\texttt{#1()}}
+
+% GRASS Python package
+\newcommand{\pkg}[1]{\emph{#1}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \block{Highlights}{
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\block{Example of including code generated aside}{
+\block{GRASS Scripting library interface to GRASS GIS modules}{
 
-% listings package does not work well with the tikzposter class,
-% so we need to include pdf
-\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{sample}
+The same applies to \pkg{grass.pygrass} syntax:
+
+\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{script_doc_syntax}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{PyGRASS interface to GRASS GIS modules}{
+
+The same applies to \pkg{grass.pygrass} syntax:
+
+\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{Using documentation for GRASS GIS modules}{
+
+Documentation of GRASS GIS modules usually use Bash syntax for examples:
+
+\begin{alltt}
+r.neighbors input=elevation output=elevation\_smooth method=median -c
+\end{alltt}
+
+This can be easily rewritten to \pkg{grass.script} syntax:
+
+\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{script_doc_syntax}
+
+The same applies to \pkg{grass.script} syntax:
+
+\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\pkg{ctypes} interface to C libraries}{
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{Using NumPy}{
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{Using IPython Notebook}{
 
@@
 
-\block{Sample block}{
-\textfontsize
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{Automatic creation of GUI and CLI}{
 
-See abstact for topics which can become blocks.
+\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{grass_module}
+
+\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{grass_module_gui}
+\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{grass_module_cli}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{PyGRASS interface to C libraries}{
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{Python script versus GRASS GIS module}{
+and running code from IDE
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{Temporal framework}{
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{Testing the code}{
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{GRASS GIS Addons}{
+The GRASS GIS Addons ensures long-term preservation of the code.
+Well maintained modules in Addons can be moved to GRASS GIS itself.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{Alternatives to Python}{
+GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
+and as subprocesses virtually any language as long as proper environment is set.
+
+The GRASS GIS library has a C API which is often used to create GRASS modules in C and C++.
+
+GRASS GIS modules can be used in R using \pkg{rgrass7} package.
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \block{Acknowledgements}{
-\begin{tabular}{cp{28em}}
+\begin{tabular}{cp{0.75\linewidth}}
 \raisebox{-.4\height}{
@@
 }
-& Initial development of pygrass and gunittest packages was done during Google Summer of Code.
+& Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code.
 \end{tabular}

### 2015-03-04 grassposter/2015_EGU_Python/main.tex
change style for block titles, make cli listing show whole lines
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64800 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
+% License: CC0
+% The license is CC0 but you can acknowledge the authors if you want to. See their names bellow.
+
 \documentclass[innermargin=10mm]{tikzposter}
@@
 \newcommand{\textfontsize}{\LARGE}
+\newcommand{\blocktitlewrap}[1]{\textsf{\textbf{\LARGE#1}}}
+% it is not possible (?) to change block title in the class, using wrapper
+% the command introduced using:
+%   sed -i 's/\\block{\([^}]*\)}/\\block{\\blocktitlewrap{\1}}/g' main.tex
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{Highlights}{
+\block{\blocktitlewrap{Highlights}}{
 % \setlength{\parskip}{1em}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{Description}{
+\block{\blocktitlewrap{Description}}{
 % \textfontsize
@@
 
-\block{More information}{
+\block{\blocktitlewrap{More information}}{
 \newcommand{\qrcodewidth}{1\linewidth}
@@
 
-\block{GRASS Scripting library interface to GRASS GIS modules}{
+\block{\blocktitlewrap{GRASS Scripting library interface to GRASS GIS modules}}{
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{PyGRASS interface to GRASS GIS modules}{
+\block{\blocktitlewrap{PyGRASS interface to GRASS GIS modules}}{
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{Using documentation for GRASS GIS modules}{
+\block{\blocktitlewrap{Using documentation for GRASS GIS modules}}{
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\pkg{ctypes} interface to C libraries}{
+\block{\blocktitlewrap{ctypes interface to C libraries}}{
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{Using NumPy}{
+\block{\blocktitlewrap{Using NumPy}}{
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{Using IPython Notebook}{
+\block{\blocktitlewrap{Using IPython Notebook}}{
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{Automatic creation of GUI and CLI}{
+\block{\blocktitlewrap{Automatic creation of GUI and CLI}}{
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{PyGRASS interface to C libraries}{
+\block{\blocktitlewrap{PyGRASS interface to C libraries}}{
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{Python script versus GRASS GIS module}{
+\block{\blocktitlewrap{Python script versus GRASS GIS module}}{
 and running code from IDE
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{Temporal framework}{
+\block{\blocktitlewrap{Temporal framework}}{
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{Testing the code}{
+\block{\blocktitlewrap{Testing the code}}{
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{GRASS GIS Addons}{
+\block{\blocktitlewrap{GRASS GIS Addons}}{
 The GRASS GIS Addons ensures long-term preservation of the code.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{Alternatives to Python}{
+\block{\blocktitlewrap{Alternatives to Python}}{
 GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{Acknowledgements}{
-\begin{tabular}{cp{0.75\linewidth}}
-\raisebox{-.4\height}{
-\includegraphics[width=0.2\linewidth]{osgeo}
-}
-& GRASS GIS is a OSGeo project. OSGeo provides infrastructure for websites and source code management.
-\\
-\raisebox{-.8\height}{
-\includegraphics[width=0.2\linewidth]{google}
-}
-& Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code.
-\end{tabular}
+\block{\blocktitlewrap{Acknowledgements}}{
+
+\newcommand{\listhspace}{\hspace{0.005\linewidth}}
+\newcommand{\listlogowidth}{0.22\linewidth}
+\newcommand{\listtextwidth}{0.76\linewidth}
+
+\begin{minipage}{\listlogowidth}
+\includegraphics[width=\linewidth]{osgeo}
+\end{minipage}
+\listhspace
+\begin{minipage}{\listtextwidth}
+GRASS GIS is a OSGeo project. OSGeo provides infrastructure for websites and source code management.
+\end{minipage}
+
+\bigskip
+
+\begin{minipage}{\listlogowidth}
+\includegraphics[width=\linewidth]{google}
+\end{minipage}
+\listhspace
+\begin{minipage}{\listtextwidth}
+Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code.
+\end{minipage}
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{References}{
+\block{\blocktitlewrap{References}}{
 

### 2015-03-05 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
JRC logo added, some other small modifications
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64803 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \title{\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip}
-\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$, Soeren Gebbert$^5$, \\Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Magherita di Leo$^8$\\ \bigskip
-$^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, $^5$ TICSA, Germany, $^6$ EURAC, Italy, $^7$ GNLST, Germany, $^8$ EC-JRC, Itlay}
+\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$, Soeren Gebbert$^5$, 
+\\Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Magherita di Leo$^8$\\ \bigskip
+$^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, 
+$^5$ TICSA, Germany, $^6$ EURAC, Italy, $^7$ GNLST, Germany, $^8$ EC-JRC, Italy}
 
@@
 
-\addlogo[north west]{(2,-1)}{9cm}{svg_images/Grass_GIS.pdf}
+\addlogo[north west]{(2,-1)}{9cm}{images/Grass_GIS}
 %Please insert your institution logo here
-\addlogo[north east]{(-2,-2.5)}{4cm}{svg_images/logo_FEM_CRI.pdf}
-\addlogo[north east]{(-2,-5.5)}{4cm}{svg_images/NC_State_Seal.pdf}
-\addlogo[north east]{(-8,-2.5)}{4cm}{images/Logo_cvut.jpg}
-\addlogo[north east]{(-8,-6.5)}{4cm}{svg_images/IWMI_logo.pdf}
+\addlogo[north east]{(-2,-2.5)}{4cm}{images/logo_FEM_CRI}
+\addlogo[north east]{(-2,-5.5)}{4cm}{images/NC_State_Seal}
+\addlogo[north east]{(-8,-2.5)}{4cm}{images/Logo_cvut}
+\addlogo[north east]{(-8,-6.5)}{4cm}{images/IWMI_logo}
+\addlogo[north east]{(-2,-10.5)}{4cm}{images/logo_ec-jrc}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Abstract}{
-\small \noindent Geographical Information Systems (GIS) is known for its capacity to spatially enhance the capacity of man- agement of natural resources.
-While being often used as an analytical tool, it also represents a collaborative scientific platform to develop new algorithms.
-GRASS GIS \cite{neteler2012grass}, a free and open source GIS, is used by many scientists directly or through other projects such as R or QGIS to perform geoprocessing tasks.
-Thus, a large number of scientific geospatial computations depend on quality and correct functionality of GRASS GIS.
-Integrating scientific algorithms into GRASS GIS helps to preserve reproducibility of scientific results over time as the original author designed it \cite{rocchini2012let}.
-Moreover, subsequent improvements are tracked in the source code versioning system and are immediately available to the public (Petras, 2014).
-Thus, GRASS GIS acts as a repository of scientific peer-reviewed code and algorithm/knowledge hub for future generation of scientists.\vspace{5mm}\newline
-With the various types of actual ET models being developed in the last 20 years, it becomes necessary to inter-compare methods.
-Most of already published ETa models comparisons address few number of models, and small to medium areas (\cite{chemin2012distributed}; \cite{gao2008intercomparison}; \cite{garcia2007comparison}; \cite{suleiman2008intercomparison}; \cite{timmermans2007intercomparison}).
-With the large amount of remote sensing data covering the Earth, and the daily information available for the past ten years (i.e.
-Aqua/Terra-MODIS) for each pixel location, it becomes paramount to have a more complete comparison, in space and time.\vspace{5mm}\newline
-To address this new experimental requirement, a distributed computing framework was designed, and created \cite{chemin2012distributed}.
-The design architecture was built from original satellite datasets to various levels of processing until reaching the requirement of various ETa models input dataset.
-Each input product is computed once and reused in all ETa models requiring such input.
-This permits standardization of inputs as much as possible to zero-in variations of models to the models internals/specificities.
-All of the ET models are available in the new GRASS GIS version 7 as imagery modules and replicability is complete for future research.\vspace{5mm}\newline
-A set of modules for multiscale analysis of landscape structure was added in 1992 by \cite{baker1992r} who developed the r.le model similar to FRAGSTATS \cite{mcgarigal1995fragstats}, see manual.
-The modules were gradually improved to become r.li in 2006.
-Further development continued, with a significant speed up (Trac1, 2014) and new interactive user interface.\vspace{5mm}\newline
-The module v.surf.rst for spatial interpolation was developed approximately 12 years ago, since then it was improved several times (Trac2, 2014).
-It is an important part of GRASS GIS and is even taught at geospatial modeling courses, for example http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html.\vspace{5mm}\newline
-GRASS GIS entails several modules that constitute the result of active research on natural hazard.
-The r.sim.water simulation model (Mitas and Mitasova, 1998) for overland flow under rainfall excess conditions was integrated into the Emergency Routing Decision Planning system as a WPS \cite{raghavan2014deploying}.
-It was also modified by Petrasova et al.
-(2014) and is now part of a specialised software called Tangible Landscape (previously Tangible GIS), which also incorporated the r.damflood module.\vspace{5mm}\newline
-The wildfire simulation toolset, firstly developed by \cite{xu1994simulating}, implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS functions r.ros and r.spread, is object of active research.
-It has been exten- sively tested and recently adapted to European fuel types (\cite{rodriguez2013data} ; \cite{derigo2013architecture} ; Di Leo et al., 2013).
+\blocknode{Abstract}
+{
+\small \noindent Geographical Information Systems (GIS) is known for its capacity 
+to spatially enhance the capacity of man- agement of natural resources. 
+While being often used as an analytical tool, it also represents a collaborative 
+scientific platform to develop new algorithms. GRASS GIS \cite{neteler2012grass}, 
+a free and open source GIS, is used by many scientists directly or through other 
+projects such as R or QGIS to perform geoprocessing tasks. Thus, a large number 
+of scientific geospatial computations depend on quality and correct functionality 
+of GRASS GIS. Integrating scientific algorithms into GRASS GIS helps to preserve 
+reproducibility of scientific results over time as the original author designed 
+it \cite{rocchini2012let}. Moreover, subsequent improvements are tracked in the 
+source code versioning system and are immediately available to the public (Petras, 2014). 
+Thus, GRASS GIS acts as a repository of scientific peer-reviewed code and 
+algorithm/knowledge hub for future generation of scientists.\vspace{5mm}\newline
+
+With the various types of actual ET models being developed in the last 20 years, 
+it becomes necessary to inter-compare methods. Most of already published ETa models 
+comparisons address few number of models, and small to medium areas 
+(\cite{chemin2012distributed}; \cite{gao2008intercomparison}; \cite{garcia2007comparison}; 
+\cite{suleiman2008intercomparison}; \cite{timmermans2007intercomparison}). 
+With the large amount of remote sensing data covering the Earth, and the daily 
+information available for the past ten years (i.e. Aqua/Terra-MODIS) for each pixel 
+location, it becomes paramount to have a more complete comparison, 
+in space and time.\vspace{5mm}\newline
+
+To address this new experimental requirement, a distributed computing framework was 
+designed, and created \cite{chemin2012distributed}. The design architecture was built 
+from original satellite datasets to various levels of processing until reaching the 
+requirement of various ETa models input dataset. Each input product is computed once 
+and reused in all ETa models requiring such input. This permits standardization of 
+inputs as much as possible to zero-in variations of models to the models 
+internals/specificities. All of the ET models are available in the new GRASS GIS 
+version 7 as imagery modules and replicability is complete for future 
+research.\vspace{5mm}\newline
+
+A set of modules for multiscale analysis of landscape structure was added in 1992 
+by \cite{baker1992r} who developed the r.le model similar to 
+FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
+improved to become r.li in 2006. Further development continued, with a significant 
+speed up (Trac1, 2014) and new interactive user interface.\vspace{5mm}\newline
+The module v.surf.rst for spatial interpolation was developed approximately 12 years 
+ago, since then it was improved several times (Trac2, 2014). It is an important part 
+of GRASS GIS and is even taught at geospatial modeling courses, for example 
+http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html.\vspace{5mm}\newline
+
+GRASS GIS entails several modules that constitute the result of active research on 
+natural hazard. The r.sim.water simulation model (Mitas and Mitasova, 1998) for 
+overland flow under rainfall excess conditions was integrated into the Emergency 
+Routing Decision Planning system as a WPS \cite{raghavan2014deploying}. It was also 
+modified by Petrasova et al. (2014) and is now part of a specialised software 
+called Tangible Landscape (previously Tangible GIS), which also incorporated the 
+r.damflood module.\vspace{5mm}\newline
+
+The wildfire simulation toolset, firstly developed by \cite{xu1994simulating}, 
+implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS 
+functions r.ros and r.spread, is object of active research. It has been extensively 
+tested and recently adapted to European fuel types (\cite{rodriguez2013data} ; 
+\cite{derigo2013architecture} ; Di Leo et al., 2013).
 }
@@
 \begin{minipage}{0.15\textwidth}
-\includegraphics[width=0.7in]{./svg_images/public_domain_logo.pdf}
+\includegraphics[width=0.7in]{./images/public_domain_logo}
 \end{minipage}

### 2015-03-05 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
Some fixes in bibliography
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64804 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 While being often used as an analytical tool, it also represents a collaborative 
-scientific platform to develop new algorithms. GRASS GIS \cite{neteler2012grass}, 
-a free and open source GIS, is used by many scientists directly or through other 
-projects such as R or QGIS to perform geoprocessing tasks. Thus, a large number 
-of scientific geospatial computations depend on quality and correct functionality 
-of GRASS GIS. Integrating scientific algorithms into GRASS GIS helps to preserve 
-reproducibility of scientific results over time as the original author designed 
-it \cite{rocchini2012let}. Moreover, subsequent improvements are tracked in the 
-source code versioning system and are immediately available to the public (Petras, 2014). 
-Thus, GRASS GIS acts as a repository of scientific peer-reviewed code and 
-algorithm/knowledge hub for future generation of scientists.\vspace{5mm}\newline
+scientific platform to develop new algorithms. GRASS GIS (Neteler et al., 2012 
+\cite{neteler2012grass}), a free and open source GIS, is used by many scientists 
+directly or through other projects such as R or QGIS to perform geoprocessing tasks. 
+Thus, a large number of scientific geospatial computations depend on quality and 
+correct functionality of GRASS GIS. Integrating scientific algorithms into GRASS GIS 
+helps to preserve reproducibility of scientific results over time as the original author 
+designed it (Rocchini \& Neteler, 2012 \cite{rocchini2012let}). Moreover, subsequent 
+improvements are tracked in the source code versioning system and are immediately 
+available to the public (Petras, 2014 \cite{Petras2014}). Thus, GRASS GIS acts as a 
+repository of scientific peer-reviewed code and algorithm/knowledge hub for future 
+generation of scientists.\vspace{5mm}\newline
 
@@
 comparisons address few number of models, and small to medium areas 
-(\cite{chemin2012distributed}; \cite{gao2008intercomparison}; \cite{garcia2007comparison}; 
-\cite{suleiman2008intercomparison}; \cite{timmermans2007intercomparison}). 
+(Chemin, 2014 \cite{chemin2012distributed}; Gao and Long, 2008 \cite{gao2008intercomparison}; 
+Garcia et al., 2007 \cite{garcia2007comparison}; Suleiman et al., 2008
+\cite{suleiman2008intercomparison}; Timmermans et al., 2007 \cite{timmermans2007intercomparison}). 
 With the large amount of remote sensing data covering the Earth, and the daily 
@@
 To address this new experimental requirement, a distributed computing framework was 
-designed, and created \cite{chemin2012distributed}. The design architecture was built 
-from original satellite datasets to various levels of processing until reaching the 
-requirement of various ETa models input dataset. Each input product is computed once 
-and reused in all ETa models requiring such input. This permits standardization of 
+designed, and created (Chemin, 2012 \cite{chemin2012distributed}). 
+The design architecture was built from original satellite datasets to various levels 
+of processing until reaching the requirement of various ETa models input dataset. 
+Each input product is computed once and reused in all ETa models requiring such input. 
+This permits standardization of 
 inputs as much as possible to zero-in variations of models to the models 
@@
 A set of modules for multiscale analysis of landscape structure was added in 1992 
-by \cite{baker1992r} who developed the r.le model similar to 
+by Baker et al. \cite{baker1992r}, who developed the r.le model similar to 
 FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
@@
 GRASS GIS entails several modules that constitute the result of active research on 
-natural hazard. The r.sim.water simulation model (Mitas and Mitasova, 1998) for 
-overland flow under rainfall excess conditions was integrated into the Emergency 
-Routing Decision Planning system as a WPS \cite{raghavan2014deploying}. It was also 
-modified by Petrasova et al. (2014) and is now part of a specialised software 
-called Tangible Landscape (previously Tangible GIS), which also incorporated the 
-r.damflood module.\vspace{5mm}\newline
+natural hazard. The r.sim.water simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b}) 
+for overland flow under rainfall excess conditions was integrated into the Emergency 
+Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}). 
+It was also modified by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of a 
+specialised software called Tangible Landscape (previously Tangible GIS), which also 
+incorporated the r.damflood module.\vspace{5mm}\newline
 
-The wildfire simulation toolset, firstly developed by \cite{xu1994simulating}, 
+The wildfire simulation toolset, firstly developed by Xu, 1994 \cite{xu1994simulating}, 
 implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS 
 functions r.ros and r.spread, is object of active research. It has been extensively 
-tested and recently adapted to European fuel types (\cite{rodriguez2013data} ; 
-\cite{derigo2013architecture} ; Di Leo et al., 2013).
+tested and recently adapted to European fuel types (Rodriguez-Aseretto et al.,
+2013 \cite{rodriguez2013data} ; de Rigo et al., 2013 \cite{derigo2013architecture} ; 
+Di Leo et al., 2013 \cite{2013_DiLeo_etAl}).
 }

### 2015-03-05 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
Some fixes in bibliography
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64805 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 A set of modules for multiscale analysis of landscape structure was added in 1992 
-by Baker et al. \cite{baker1992r}, who developed the r.le model similar to 
+by Baker et al., 1992 \cite{baker1992r}, who developed the r.le model similar to 
 FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 

### 2015-03-05 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
Some typos fixes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64806 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2015-03-05 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
@@
 \title{\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip}
-\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$, Soeren Gebbert$^5$, 
-\\Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Magherita di Leo$^8$\\ \bigskip
+
+\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$, Soeren Gebbert$^5$, \\
+Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Margherita Di Leo$^8$\\ 
+\bigskip
 $^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, 
@@
 \small \noindent Geographical Information Systems (GIS) is known for its capacity 
-to spatially enhance the capacity of man- agement of natural resources. 
+to spatially enhance the capacity of management of natural resources. 
 While being often used as an analytical tool, it also represents a collaborative 
@@
 Each input product is computed once and reused in all ETa models requiring such input. 
-This permits standardization of 
-inputs as much as possible to zero-in variations of models to the models 
-internals/specificities. All of the ET models are available in the new GRASS GIS 
-version 7 as imagery modules and replicability is complete for future 
+This permits standardization of inputs as much as possible to zero-in variations of 
+models to the models internals/specificities. All of the ET models are available in the 
+new GRASS GIS version 7 as imagery modules and replicability is complete for future 
 research.\vspace{5mm}\newline
@@
 FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
-improved to become r.li in 2006. Further development continued, with a significant 
+improved to become \textit{r.li} in 2006. Further development continued, with a significant 
 speed up (Trac1, 2014) and new interactive user interface.\vspace{5mm}\newline
@@
 of GRASS GIS and is even taught at geospatial modeling courses, for example 
-http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html.\vspace{5mm}\newline
+\textit{http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html}.
+\vspace{5mm}\newline
 
 GRASS GIS entails several modules that constitute the result of active research on 
-natural hazard. The r.sim.water simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b}) 
+natural hazard. The \textit{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b}) 
 for overland flow under rainfall excess conditions was integrated into the Emergency 
@@
 It was also modified by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of a 
-specialised software called Tangible Landscape (previously Tangible GIS), which also 
-incorporated the r.damflood module.\vspace{5mm}\newline
+specialised software called \textit{Tangible Landscape} (previously \textit{Tangible GIS}), which also 
+incorporated the \textit{r.damflood} module.\vspace{5mm}\newline
 
@@
 implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS 
-functions r.ros and r.spread, is object of active research. It has been extensively 
+functions \textit{r.ros} and \textit{r.spread}, is object of active research. It has been extensively 
 tested and recently adapted to European fuel types (Rodriguez-Aseretto et al.,

### 2015-03-23 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
draft sections, add images for interp, water, fire and geomorphons
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64894 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 % x-coordinate by specifying explicitly the coordinate of the new block node as follows:
-\usepackage[czech]{babel}
+
 \usepackage[utf8]{inputenc}
 \usepackage{wrapfig}
-\usepackage{url}
+\usepackage[hidelinks]{hyperref}
 
@@
 
+\graphicspath{{images/}}
+
+% GRASS module
+\newcommand{\gmodule}[1]{\href{http://grass.osgeo.org/grass70/manuals/#1.html}{\emph{#1}}}
+\newcommand{\gamodule}[1]{\href{http://grass.osgeo.org/grass70/manuals/addons/#1.html}{\emph{#1}}}
+
 \begin{document}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Abstract}
+\blocknode{Introduction}
 {
-\small \noindent Geographical Information Systems (GIS) is known for its capacity 
+Geographical Information Systems (GIS) is known for its capacity 
 to spatially enhance the capacity of management of natural resources. 
@@
 repository of scientific peer-reviewed code and algorithm/knowledge hub for future 
-generation of scientists.\vspace{5mm}\newline
+generation of scientists.
+}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Landform detection: Geomorphons}{
+
+\gamodule{r.geomorphon}
+
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth]{geomorphon}
+Geomorphons for part of Yakima Training Center (area 5x3~km, USA)
+\end{minipage}
+~
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth]{geomorphon_tangible_high_tatras}
+Ridges and valleys detected on the sand physical model of High Tatras (Slovakia) using \gamodule{r.geomorphon} integrated in Tangible Landscape system
+\end{minipage}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\startsecondcolumn
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Evapotranspiration (ET)}{
 With the various types of actual ET models being developed in the last 20 years, 
@@
 location, it becomes paramount to have a more complete comparison, 
-in space and time.\vspace{5mm}\newline
+in space and time.
 
@@
 research.\vspace{5mm}\newline
+}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\startthirdcolumn
+
+\blocknode{}{
 A set of modules for multiscale analysis of landscape structure was added in 1992 
@@
 improved to become \textit{r.li} in 2006. Further development continued, with a significant 
-speed up (Trac1, 2014) and new interactive user interface.\vspace{5mm}\newline
-The module v.surf.rst for spatial interpolation was developed approximately 12 years 
-ago, since then it was improved several times (Trac2, 2014). It is an important part 
-of GRASS GIS and is even taught at geospatial modeling courses, for example 
-\textit{http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html}.
-\vspace{5mm}\newline
+speed up (Trac1, 2014) and new interactive user interface.
+}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Natural Hazards: Water, Floods and Erosion}{
 GRASS GIS entails several modules that constitute the result of active research on 
-natural hazard. The \textit{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b}) 
+natural hazard. The \gmodule{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b}) 
 for overland flow under rainfall excess conditions was integrated into the Emergency 
@@
 specialised software called \textit{Tangible Landscape} (previously \textit{Tangible GIS}), which also 
-incorporated the \textit{r.damflood} module.\vspace{5mm}\newline
+incorporated the \gamodule{r.damflood} module.
 
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth]{rsimwater_architects}
+Overland flow used for landscape architecture design in Tangible Landscape environment
+\end{minipage}
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth]{damflood_tangible}
+Coal ash pond breach in Tangible Landscape environment using \gamodule{r.damflood} module
+\end{minipage}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Natural Hazards: Wildfire Spread}{
 The wildfire simulation toolset, firstly developed by Xu, 1994 \cite{xu1994simulating}, 
@@
 tested and recently adapted to European fuel types (Rodriguez-Aseretto et al.,
-2013 \cite{rodriguez2013data} ; de Rigo et al., 2013 \cite{derigo2013architecture} ; 
+2013 \cite{rodriguez2013data}; de Rigo et al., 2013 \cite{derigo2013architecture} ; 
 Di Leo et al., 2013 \cite{2013_DiLeo_etAl}).
+
+\begin{minipage}{0.5\linewidth}
+\includegraphics{fire}
+Wildfire simulation in Tangible Landscape environment
+\end{minipage}
+
+\begin{minipage}{0.5\linewidth}
+%\includegraphics[width=\textwidth]{fire}
+% TODO: Something from Europe
+\end{minipage}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\startfourthcolumn
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Spatial interpolation}{
+The module v.surf.rst for spatial interpolation was developed approximately 12 years 
+ago, since then it was improved several times (Trac2, 2014). It is now an important part 
+of GRASS GIS and is even taught at geospatial modeling courses, for example 
+\url{http://courses.ncsu.edu/gis582/common/grass/interpolation_2.html}.
+
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth]{interpolation_precip_vsurfrst}
+Precipitation interpolated from meteorological stations in 3D space using \gmodule{v.vol.rst}
+\end{minipage}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Conclusions}{
+
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\getcurrentrow{box}
-%\coordinate (funkcionalita) at (box.south west);
-%\coordinate (funkcionalitaeast) at (box.east);
-%\coordinate (screenshot) at (box.north west);
-%
-%\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
 \blocknode{References}{
@@
 
-%\hrulefill
-%\vspace{-5pt}
+\subsubsection*{Acknowledgement}
+
+Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS}
+% http://www4.ncsu.edu/~jcfounta/Summer14Posters/horvath.pdf
+
+Eva Stopkova for physical model of High Tatras.
+
+\hrulefill
+\vspace{-5pt}
 
@@
 \begin{minipage}{0.15\textwidth}
-\includegraphics[width=0.7in]{./images/public_domain_logo}
+\href{http://creativecommons.org/licenses/by-sa/4.0/}{\includegraphics[width=0.7in]{ccbysa}}
 \end{minipage}
@@
 
-\startsecondcolumn
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{}{
-\bigskip
-
-}
-
-\startthirdcolumn
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{}{
-\smallskip
-
-}
-
-\blocknode{Conclusions}{
-\smallskip
-}
-
-\startfourthcolumn
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{}{
-\smallskip
-
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{}{
-
-}%End of Block
-
 \end{tikzpicture}

### 2015-03-23 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
add references for r.geomorphon, image for r.diversity and v.surf.rst
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64896 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-\gamodule{r.geomorphon}
+Jasiewicz and Stepinski \cite{jasiewicz2013geomorphons} developed a method and module \gamodule{r.geomorphon}
+which provide orientation-invariant and relief-invariant method to classify landforms
+in a scale-independent way.
+Ashtekar et al. \cite{ashtekar2014digital} used geomorphons to study soil properties in northwestern South America.
 
@@
 Ridges and valleys detected on the sand physical model of High Tatras (Slovakia) using \gamodule{r.geomorphon} integrated in Tangible Landscape system
+\end{minipage}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Spatial interpolation}{
+The module v.surf.rst for spatial interpolation was developed approximately 12 years 
+ago, since then it was improved several times (Trac2, 2014). It is now an important part 
+of GRASS GIS and is even taught at geospatial modeling courses, for example 
+\url{http://courses.ncsu.edu/gis582/common/grass/interpolation_2.html}.
+
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth]{interpolation_precip_vvolrst}
+Precipitation interpolated from meteorological stations in 3D space using \gmodule{v.vol.rst} in the area of North Carolina mountains (USA)
+\end{minipage}
+~
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth]{elevation_lidar}
+Digital elevation model interpolated from lidar point cloud using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
 \end{minipage}
@@
 
-\blocknode{}{
+\blocknode{Landscape structure}{
 A set of modules for multiscale analysis of landscape structure was added in 1992 
@@
 speed up (Trac1, 2014) and new interactive user interface.
+Rocchini et al. \cite{rocchini2013calculating} used \gmodule{r.li} modules to implement
+high level tool for calculating landscape diversity.
+
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{rdiversity}
+Landscape diversity according to shannon index in near Charlotte (North Carolina, USA).
+\end{minipage}
 }
@@
 \startfourthcolumn
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Spatial interpolation}{
-The module v.surf.rst for spatial interpolation was developed approximately 12 years 
-ago, since then it was improved several times (Trac2, 2014). It is now an important part 
-of GRASS GIS and is even taught at geospatial modeling courses, for example 
-\url{http://courses.ncsu.edu/gis582/common/grass/interpolation_2.html}.
-
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{interpolation_precip_vsurfrst}
-Precipitation interpolated from meteorological stations in 3D space using \gmodule{v.vol.rst}
-\end{minipage}
-}
 
@@
 \blocknode{Conclusions}{
-
+\begin{itemize}
+ \item Algorithms and models once included into GRASS GIS are still available.
+ \item GRASS GIS development team takes care of API related updates and operating system related changes.
+ \item Scientists are using highly specialized tools implemented by other people when having both scientific publication and source code at hand.
+ \item New research and tools is build upon the existing one.
+\end{itemize}
 }
@@
 \blocknode{References}{
-\smallskip
 \scriptsize
@@
 
-\subsubsection*{Acknowledgement}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Acknowledgement}{
 
@@
 Eva Stopkova for physical model of High Tatras.
+}
 
-\hrulefill
-\vspace{-5pt}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{More information}{
+
+% \hrulefill
+% \vspace{-5pt}
+
+\newcommand{\qrcodesize}{0.05\textwidth}
+
+% TODO: add proper QR codes
 
@@
 \begin{tabular}{c}
-\hspace{5mm}
-\begin{minipage}{0.2\textwidth}
-\includegraphics[width=0.5in]{./images/grass_qr.pdf}
+
+% \hspace{5mm}
+
+\begin{minipage}{\qrcodesize}
+\includegraphics[width=\textwidth]{./images/grass_qr.pdf}
 \end{minipage}
 
-\begin{minipage}{0.25\textwidth}
+\begin{minipage}{0.15\textwidth}
+\small {\url{grass.osgeo.org}}
+\end{minipage}
+
+\begin{minipage}{\qrcodesize}
+\includegraphics[width=\textwidth]{./images/grass_qr.pdf}
+\end{minipage}
+
+\begin{minipage}{0.2\textwidth}
 \small {\url{grasswiki.osgeo.org}}
@@
 
-\begin{minipage}{0.15\textwidth}
-\href{http://creativecommons.org/licenses/by-sa/4.0/}{\includegraphics[width=0.7in]{ccbysa}}
+\begin{minipage}{0.1\textwidth}
+\href{http://creativecommons.org/licenses/by-sa/4.0/}{\includegraphics[width=\textwidth]{ccbysa}}
 \end{minipage}
 
-\begin{minipage}{0.3\textwidth}
-\small {\url{grass.osgeo.org}}
-\end{minipage}
-
-\begin{minipage}{0.2\textwidth}
-\includegraphics[width=0.5in]{./images/grass_qr.pdf}
+\begin{minipage}{0.35\textwidth}
+\small This poster is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License.
 \end{minipage}

### 2015-03-24 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
migrate to official tikzposter class (some changes in layout required - less space, fixes author list)
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64900 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
-\documentclass[landscape,a0,final]{a0poster}
-\usepackage[dvipsnames,svgnames]{xcolor}
-\usepackage{tikzposter} % here most of the things are defined
-% change parameters only after this line You can also start a new column with an arbitrary 
-% x-coordinate by specifying explicitly the coordinate of the new block node as follows:
+% License: CC BY-SA
+% Authors: See authors below and see also acknowledgement for authors of some images or research
+
+\documentclass[25pt, margin=0mm, innermargin=15mm, blockverticalspace=15mm, colspace=15mm, subcolspace=8mm]{tikzposter}
+\geometry{paperwidth=197cm,paperheight=100cm}
+
+% to stretch boxes over whole paper with custor paper size
+\makeatletter
+\setlength{\TP@visibletextwidth}{\textwidth-2\TP@innermargin}
+\setlength{\TP@visibletextheight}{\textheight-2\TP@innermargin}
+\makeatother
 
@@
 
-%Used for better control on code display
+\definecolor{titleTextColor}{HTML}{009000}
+\definecolorpalette{grassColorPalette} {
+  \definecolor{colorOne}{HTML}{419041}
+}
+\usecolorstyle[colorPalette=grassColorPalette]{Britain}
 
-\usepackage[margin=\margin cm, paperwidth=197cm, paperheight=100cm]{geometry}
+\title{
+\Huge
+\textcolor{titleTextColor}{
+\textsf{\textbf{
+\fontsize{85}{60}\selectfont
+GRASS GIS: a peer-reviewed scientific platform and future research repository
+}}
+}
+}
 
-% \setbackgrounddarkcolor{ForestGreen!70!black}
-% \setbackgroundlightcolor{YellowGreen!90!}
+\newlength{\grasslogoheight}
+\setlength{\grasslogoheight}{0.08\textheight}
+\newlength{\instlogoheight}
+\setlength{\instlogoheight}{0.45\grasslogoheight}
 
-% \setfirstcolor{YellowGreen!80!}
-% \setsecondcolor{gray!80!}
-% \setthirdcolor{red!80!black}
+\titlegraphic{
+\begin{minipage}{0.3\linewidth}
+\includegraphics[height=\grasslogoheight]{grass}
+~
+\includegraphics[height=\grasslogoheight]{osgeo_project}
+\end{minipage}
+\hfill
+\begin{minipage}{0.16\linewidth}
+\setlength{\baselineskip}{120pt}
+\begin{flushright}
+\includegraphics[height=\instlogoheight]{iwmi}
+~
+\includegraphics[height=\instlogoheight]{ncstate}
+~
+\includegraphics[height=\instlogoheight]{ctu_prague}
+~
+\includegraphics[height=\instlogoheight]{fem_cri}
+~
+\includegraphics[height=\instlogoheight]{ec_jrc}
+\end{flushright}
+\end{minipage}
+\vspace{-\grasslogoheight}
+}
 
-\title{\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip}
+% \setlength{\blocktitleheight}{0.02\textheight}
 
-\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$, Soeren Gebbert$^5$, \\
-Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Margherita Di Leo$^8$\\ 
-\bigskip
-$^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, 
-$^5$ TICSA, Germany, $^6$ EURAC, Italy, $^7$ GNLST, Germany, $^8$ EC-JRC, Italy}
+% style for institute numbers
+\newcommand{\inst}[1]{\hspace{2pt}$^{\mbox{\normalsize#1}}$\hspace{-7pt}}
+\newcommand{\instlist}[1]{\hspace{1pt}$^{\mbox{\normalsize#1}}$\hspace{2pt}}
 
-\usetemplate{1}
-\setinstituteshift{1}
+\author{
+Yann Chemin\inst{2},
+V\'{a}clav Petr\'{a}\v{s}\inst{1},
+Anna Petr\'{a}\v{s}ov\'{a}\inst{1},
+Martin Landa\inst{4},
+S\"{o}ren Gebbert\inst{5},
+Pietro Zambelli\inst{3},
+Markus Neteler\inst{6}, and
+Peter L\"{o}we\inst{7}
+Margherita Di Leo\inst{8}
+}
+\institute{
+\instlist{1}NCSU, USA,
+\instlist{2}IWMI, Sri Lanka,
+\instlist{3}EURAC, Italy,
+\instlist{4}FCE CTU in Prague, Czech Republic,
+\instlist{5}TICSA, Germany,
+\instlist{6}CRI, FEM, Italy,
+\instlist{7}GNLST, Germany
+\instlist{8}EC-JRC, Italy
+}
 
-\setblocktitleheight{2}
-\setblockspacing{1}
+% \usetemplate{1}
+% \setinstituteshift{1}
 
-\graphicspath{{images/}}
+% \setblocktitleheight{2}
+% \setblockspacing{1}
+
+\graphicspath{{images/}{logos/}}
+
+\newcommand{\blocktitlewrap}[1]{\textsf{\textbf{\huge#1}}}
+% it is not possible (?) to change block title in the class, using wrapper
+% the command introduced using:
+%   sed -i 's/\\block{\([^}]*\)}/\\block{\\blocktitlewrap{\1}}/g' main.tex
 
@@
 \begin{document}
-\ClearShipoutPicture
-\AddToShipoutPicture{\BackgroundPicture}
-\noindent
-\tikzstyle{every picture}+=[remember picture]
-\begin{tikzpicture}
-\initializesizeandshifts
-\titleblock{90}{1}
-% \setblocktitleheight{1}
+\maketitle[width=0.92\textwidth]
+% \maketitle
+% \addlogo[north west]{(2,-1)}{9cm}{images/Grass_GIS}
+%Please insert your institution logo here
+% \addlogo[north east]{(-2,-2.5)}{4cm}{images/logo_FEM_CRI}
+% \addlogo[north east]{(-2,-5.5)}{4cm}{images/NC_State_Seal}
+% \addlogo[north east]{(-8,-2.5)}{4cm}{images/Logo_cvut}
+% \addlogo[north east]{(-8,-6.5)}{4cm}{images/IWMI_logo}
+% \addlogo[north east]{(-2,-10.5)}{4cm}{images/logo_ec-jrc}
 
-\addlogo[north west]{(2,-1)}{9cm}{images/Grass_GIS}
-%Please insert your institution logo here
-\addlogo[north east]{(-2,-2.5)}{4cm}{images/logo_FEM_CRI}
-\addlogo[north east]{(-2,-5.5)}{4cm}{images/NC_State_Seal}
-\addlogo[north east]{(-8,-2.5)}{4cm}{images/Logo_cvut}
-\addlogo[north east]{(-8,-6.5)}{4cm}{images/IWMI_logo}
-\addlogo[north east]{(-2,-10.5)}{4cm}{images/logo_ec-jrc}
+\begin{columns}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Introduction}
+\block{\blocktitlewrap{Introduction}}
 {
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Landform detection: Geomorphons}{
+\block{\blocktitlewrap{Landform detection: Geomorphons}}{
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Spatial interpolation}{
-The module v.surf.rst for spatial interpolation was developed approximately 12 years 
-ago, since then it was improved several times (Trac2, 2014). It is now an important part 
-of GRASS GIS and is even taught at geospatial modeling courses, for example 
-\url{http://courses.ncsu.edu/gis582/common/grass/interpolation_2.html}.
+\block{\blocktitlewrap{Natural Hazards: Wildfire Spread}}{
+The wildfire simulation toolset, firstly developed by Xu, 1994 \cite{xu1994simulating}, 
+implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS 
+functions \textit{r.ros} and \textit{r.spread}, is object of active research. It has been extensively 
+tested and recently adapted to European fuel types (Rodriguez-Aseretto et al.,
+2013 \cite{rodriguez2013data}; de Rigo et al., 2013 \cite{derigo2013architecture} ; 
+Di Leo et al., 2013 \cite{2013_DiLeo_etAl}).
 
 \begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{interpolation_precip_vvolrst}
-Precipitation interpolated from meteorological stations in 3D space using \gmodule{v.vol.rst} in the area of North Carolina mountains (USA)
+\includegraphics{fire}
+Wildfire simulation in Tangible Landscape environment
 \end{minipage}
-~
+
 \begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{elevation_lidar}
-Digital elevation model interpolated from lidar point cloud using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
+%\includegraphics[width=\textwidth]{fire}
+% TODO: Something from Europe
 \end{minipage}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\startsecondcolumn
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Evapotranspiration (ET)}{
+\block{\blocktitlewrap{Evapotranspiration (ET)}}{
 With the various types of actual ET models being developed in the last 20 years, 
@@
 new GRASS GIS version 7 as imagery modules and replicability is complete for future 
-research.\vspace{5mm}\newline
+research.
+
+% TODO: images width captions
 }
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\startthirdcolumn
-
-\blocknode{Landscape structure}{
-A set of modules for multiscale analysis of landscape structure was added in 1992 
-by Baker et al. \cite{baker1992r}, who developed the r.le model similar to 
-FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
-improved to become \textit{r.li} in 2006. Further development continued, with a significant 
-speed up (Trac1, 2014) and new interactive user interface.
-Rocchini et al. \cite{rocchini2013calculating} used \gmodule{r.li} modules to implement
-high level tool for calculating landscape diversity.
-
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{rdiversity}
-Landscape diversity according to shannon index in near Charlotte (North Carolina, USA).
-\end{minipage}
-}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Natural Hazards: Water, Floods and Erosion}{
+\block{\blocktitlewrap{Natural Hazards: Water, Floods and Erosion}}{
 GRASS GIS entails several modules that constitute the result of active research on 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Natural Hazards: Wildfire Spread}{
-The wildfire simulation toolset, firstly developed by Xu, 1994 \cite{xu1994simulating}, 
-implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS 
-functions \textit{r.ros} and \textit{r.spread}, is object of active research. It has been extensively 
-tested and recently adapted to European fuel types (Rodriguez-Aseretto et al.,
-2013 \cite{rodriguez2013data}; de Rigo et al., 2013 \cite{derigo2013architecture} ; 
-Di Leo et al., 2013 \cite{2013_DiLeo_etAl}).
+\block{\blocktitlewrap{Spatial interpolation}}{
+The module v.surf.rst for spatial interpolation was developed approximately 12 years 
+ago, since then it was improved several times (Trac2, 2014). It is now an important part 
+of GRASS GIS and is even taught at geospatial modeling courses, for example 
+\url{http://courses.ncsu.edu/gis582/common/grass/interpolation_2.html}.
+% TODO: move link to references
 
 \begin{minipage}{0.5\linewidth}
-\includegraphics{fire}
-Wildfire simulation in Tangible Landscape environment
+\includegraphics[width=\textwidth]{interpolation_precip_vvolrst}
+Precipitation interpolated from meteorological stations in 3D space using \gmodule{v.vol.rst} in the area of North Carolina mountains (USA)
 \end{minipage}
-
+~
 \begin{minipage}{0.5\linewidth}
-%\includegraphics[width=\textwidth]{fire}
-% TODO: Something from Europe
+\includegraphics[width=\textwidth]{elevation_lidar}
+Digital elevation model interpolated from lidar point cloud using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
 \end{minipage}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\startfourthcolumn
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
+\block{\blocktitlewrap{Landscape structure}}{
+A set of modules for multiscale analysis of landscape structure was added in 1992 
+by Baker et al. \cite{baker1992r}, who developed the r.le model similar to 
+FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
+improved to become \textit{r.li} in 2006. Further development continued, with a significant 
+speed up (Trac1, 2014) and new interactive user interface.
+Rocchini et al. \cite{rocchini2013calculating} used \gmodule{r.li} modules to implement
+high level tool for calculating landscape diversity.
+
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{rdiversity}
+Landscape diversity according to shannon index in near Charlotte (North Carolina, USA).
+\end{minipage}
+
+% TODO: some other example or something completely else?
+}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Conclusions}{
+\block{\blocktitlewrap{Conclusions}}{
+% TODO: review the points, it should be the highlight or something like that
+% TODO: style of bullets is strange
 \begin{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{References}{
+\block{\blocktitlewrap{References and Acknowledgements}}{
 \scriptsize
 
+\newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}
+
+\blocksectiontitle{References}
 \begingroup
@@
 
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Acknowledgement}{
-
+\blocksectiontitle{Acknowledgements}
 Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS}
@@
 Eva Stopkova for physical model of High Tatras.
+
+GRASS GIS project is a Open Source Geospatial Foundation (OSGeo) project and is using OSGeo infrastructure for websites and repositories.
+
+\textcolor{gray}{
+\hrulefill
 }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{More information}{
-
-% \hrulefill
 % \vspace{-5pt}
 
-\newcommand{\qrcodesize}{0.05\textwidth}
+\newcommand{\qrcodesize}{0.05\linewidth}
 
-% TODO: add proper QR codes
+% TODO: add proper QR codes and fix links
 
@@
 
-\begin{minipage}{0.15\textwidth}
+\begin{minipage}{0.15\linewidth}
 \small {\url{grass.osgeo.org}}
@@
 
-\begin{minipage}{0.2\textwidth}
+\begin{minipage}{0.2\linewidth}
 \small {\url{grasswiki.osgeo.org}}
@@
 
-\begin{minipage}{0.1\textwidth}
+\begin{minipage}{0.1\linewidth}
 \href{http://creativecommons.org/licenses/by-sa/4.0/}{\includegraphics[width=\textwidth]{ccbysa}}
@@
 
-\begin{minipage}{0.35\textwidth}
+\begin{minipage}{0.35\linewidth}
 \small This poster is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License.
@@
 
-\end{tikzpicture}
+\end{columns}
 

### 2015-03-24 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
EGU poster: Temporal framework stub
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64901 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 {
-Geographical Information Systems (GIS) is known for its capacity 
+Geographical Information Systems (GIS) are known for their capacity 
 to spatially enhance the capacity of management of natural resources. 
-While being often used as an analytical tool, it also represents a collaborative 
+While being often used as an analytical tool, they also represent a collaborative 
 scientific platform to develop new algorithms. GRASS GIS (Neteler et al., 2012 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Temporal framework (TGRASS)}}{
+
+Described some applications
+
+% TODO: images width captions
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-03-25 grassposter/2015_EGU_G7_Python/main.tex
add EURAC logo to posters
Including also original SVG for now.


git-svn-id: https://svn.osgeo.org/grass/grass-promo@64902 15284696-431f-4ddb-bdfa-cd5b030d7da7
write highlights, remove description, acknowledge LucaD
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64904 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2015-03-04 grassposter/2015_EGU_Python/main.tex
@@
 
-       % TODO: get other logos
        \includegraphics[width=\logowidth]{ncstate}
@@
        \logovspace
-
+       % TODO: TICSA logo (Soeren)
        \includegraphics[width=\logowidth]{ncstate}
@@
        \logohspace
-       \includegraphics[width=\logowidth]{ncstate}
+       \includegraphics[width=\logowidth]{eurac}
 
@@
        \logohspace
+       % TODO: GNLST logo (Peter)
        \includegraphics[width=\logowidth]{ncstate}
@@
 
-% TODO: the two blocks below are just taken from testing poster
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \renewcommand{\item}{\par\vspace{0.8ex}}
-\item GRASS GIS is a platform for geospatial computations.
-\item The framework supports code maintenance which results in long term preservation of algorithms.
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Description}}{
-% \textfontsize
-\Large
-\newcommand{\intropartitle}[1]{\parinlinetitle{#1}}
-% \setlength{\parskip}{1em}
-
-\intropartitle{Motivation}
-GRASS GIS \cite{Neteler2012}, a free and open source GIS, is used by many scientists directly or through other projects such as R or QGIS to perform geoprocessing tasks.
-Thus, a large number of scientific geospatial computations depend on quality and correct functionality of GRASS GIS.
-Automatic functionality testing is therefore necessary to ensure software reliability.
-
-\intropartitle{Unique features}
-We present a testing framework for GRASS GIS which addresses different needs of GRASS GIS and geospatial software in general.
-It tests GRASS tools (referred to as GRASS modules) and
-examines outputs including large raster and vector maps as well as temporal datasets.
-Furthermore, it enables to test all levels of GRASS GIS architecture including C and Python application programming interface and GRASS modules invoked as subprocesses.
-
-\intropartitle{Audience}
-Since GRASS GIS is used as a platform for development of geospatial algorithms and models,
-the testing framework allows not only to test GRASS GIS core functionality but also tools developed by scientists as a part of their research.
-
-\intropartitle{Scientific impact}
+\item GRASS GIS \cite{Neteler2012} is a platform for geospatial computations.
+\item GRASS GIS used directly using Python or GUI or through other software such as QGIS or R.
+\item GRASS GIS ecosystem supports code maintenance.
+\item The functionality is divided into set of modules (individual tools, functions, algorithms or models).
+\item Core libraries and algorithms implemented in C for high performance.
+\item The system together with the broad community ensures long term preservation of algorithms.
+% \end{itemize}
 }
@@
 \block{\blocktitlewrap{Temporal framework}}{
-
+\cite{Gebbert2014}
 }
@@
 \block{\blocktitlewrap{Testing the code}}{
-
+\cite{Petras2014}
 }
@@
 \end{minipage}
+
+\bigskip
+
+Luca Delucchi contributed significantly to development of Python interfaces for GRASS GIS
+by extensive testing in early stages of development, documenting the APIs
+and general contributions to the code itself.
 }

### 2015-03-25 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
add EURAC logo to posters
Including also original SVG for now.


git-svn-id: https://svn.osgeo.org/grass/grass-promo@64902 15284696-431f-4ddb-bdfa-cd5b030d7da7
Added one map for Biological fraction of 2014 ET in Cambodia
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64908 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \includegraphics[height=\instlogoheight]{ctu_prague}
+~
+\includegraphics[height=\instlogoheight]{eurac}
 ~
@@
 new GRASS GIS version 7 as imagery modules and replicability is complete for future 
-research.
+research.\newline
 
-% TODO: images width captions
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth]{TonleSapTa}
+Biological fraction of 2014 ET (cumul. mm/y), Tonle Sap, Cambodia.
+\end{minipage}
+
 }

### 2015-03-25 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
Added temporal GIS content
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64910 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \hfill
-\begin{minipage}{0.16\linewidth}
+\begin{minipage}{0.2\linewidth}
 \setlength{\baselineskip}{120pt}
@@
 \includegraphics[height=\instlogoheight]{ctu_prague}
+~
+\includegraphics[height=\instlogoheight]{ti}
 ~
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Temporal framework (TGRASS)}}{
+\block{\blocktitlewrap{GRASS as Temporal GIS}}{
+The time dimension was introduced in GRASS GIS version 7 for raster, 3D raster and
+vector map layers, transforming it into a full featured temporal GIS (Gebbert and Pebesma, 2014 \cite{Gebbert20141}).
+Time series of map layers are managed in space time datasets, a new data type in GRASS GIS.
+Based on the GRASS GIS Temporal Framework, more than 45 modules were implemented to manage, analyze, process
+and visualize space time datasets. The temporal enabled GRASS GIS is able to efficiently
+handle more than 100.000 map layers. It was used to analyze the
+European Climate Assessment \& Dataset ECA\&D (Haylock et al. \cite{Haylock2008_climate_series})
+for climate change indicators.
 
-Described some applications
-
-% TODO: images width captions
+\begin{minipage}{0.5\linewidth}
+\includegraphics[scale=0.5]{images/summer_mean_temp_slope.pdf}
+The linear regression slope computed with t.rast.series of the temperate climate zone in the European Union  
+for summer season from 1950 - 2011 (Gebbert and Pebesma, 2014 \cite{Gebbert20141}). Red color
+indicates rising temperature, blue indicates falling temperature. Units are degree Celsius per year.
+\end{minipage}
+~
+\begin{minipage}{0.5\linewidth}
+\includegraphics[scale=1.25]{images/Seasonal_temperature_trend_Europe_1950_2010.pdf}
+Seasonal mean temperature trend for the temperate climate zone of the European Union 
+(Gebbert and Pebesma, 2014 \cite{Gebbert20141}). The modules t.rast.aggregate, 
+t.rast.univar and the open source statistical software system R
+were used to create this plot.
+\end{minipage}
 }

### 2015-03-25 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
shuffling boxes, aesthetics
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64913 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Evapotranspiration (ET)}}{
-With the various types of actual ET models being developed in the last 20 years, 
-it becomes necessary to inter-compare methods. Most of already published ETa models 
-comparisons address few number of models, and small to medium areas 
-(Chemin, 2014 \cite{chemin2012distributed}; Gao and Long, 2008 \cite{gao2008intercomparison}; 
-Garcia et al., 2007 \cite{garcia2007comparison}; Suleiman et al., 2008
-\cite{suleiman2008intercomparison}; Timmermans et al., 2007 \cite{timmermans2007intercomparison}). 
-With the large amount of remote sensing data covering the Earth, and the daily 
-information available for the past ten years (i.e. Aqua/Terra-MODIS) for each pixel 
-location, it becomes paramount to have a more complete comparison, 
-in space and time.
-
-To address this new experimental requirement, a distributed computing framework was 
-designed, and created (Chemin, 2012 \cite{chemin2012distributed}). 
-The design architecture was built from original satellite datasets to various levels 
-of processing until reaching the requirement of various ETa models input dataset. 
-Each input product is computed once and reused in all ETa models requiring such input. 
-This permits standardization of inputs as much as possible to zero-in variations of 
-models to the models internals/specificities. All of the ET models are available in the 
-new GRASS GIS version 7 as imagery modules and replicability is complete for future 
-research.\newline
-
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{TonleSapTa}
-Biological fraction of 2014 ET (cumul. mm/y), Tonle Sap, Cambodia.
-\end{minipage}
-
-}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \block{\blocktitlewrap{Natural Hazards: Water, Floods and Erosion}}{
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{minipage}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Evapotranspiration (ET)}}{
+With the various types of actual ET models being developed in the last 20 years, 
+it becomes necessary to inter-compare methods. Most of already published ETa models 
+comparisons address few number of models, and small to medium areas 
+(Chemin, 2014 \cite{chemin2012distributed}; Gao and Long, 2008 \cite{gao2008intercomparison}; 
+Garcia et al., 2007 \cite{garcia2007comparison}; Suleiman et al., 2008
+\cite{suleiman2008intercomparison}; Timmermans et al., 2007 \cite{timmermans2007intercomparison}). 
+With the large amount of remote sensing data covering the Earth, and the daily 
+information available for the past ten years (i.e. Aqua/Terra-MODIS) for each pixel 
+location, it becomes paramount to have a more complete comparison, 
+in space and time.\newline
+
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=0.9\textwidth]{TonleSapTa}
+\vspace{1mm}
+Biological fraction of 2014 ET (cumul. mm/y), Tonle Sap, Cambodia.
+\end{minipage}
+\bigskip
+
+To address this new experimental requirement, a distributed computing framework was 
+designed, and created (Chemin, 2012 \cite{chemin2012distributed}). 
+The design architecture was built from original satellite datasets to various levels 
+of processing until reaching the requirement of various ETa models input dataset. 
+Each input product is computed once and reused in all ETa models requiring such input. 
+This permits standardization of inputs as much as possible to zero-in variations of 
+models to the models internals/specificities. All of the ET models are available in the 
+new GRASS GIS version 7 as imagery modules and replicability is complete for future 
+research.
 }

### 2015-03-25 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
Completed ET section
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64915 15284696-431f-4ddb-bdfa-cd5b030d7da7
unify style for module names
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64916 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \block{\blocktitlewrap{Natural Hazards: Wildfire Spread}}{
-The wildfire simulation toolset, firstly developed by Xu, 1994 \cite{xu1994simulating}, 
-implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS 
-functions \textit{r.ros} and \textit{r.spread}, is object of active research. It has been extensively 
+The wildfire simulation toolset, firstly developed by Xu, 1994~\cite{xu1994simulating}, 
+implementing Rothermel’s model~\cite{Rothermel1983how}, available through the GRASS 
+functions \gmodule{r.ros} and \gmodule{r.spread}, is object of active research. It has been extensively 
 tested and recently adapted to European fuel types (Rodriguez-Aseretto et al.,
-2013 \cite{rodriguez2013data}; de Rigo et al., 2013 \cite{derigo2013architecture} ; 
-Di Leo et al., 2013 \cite{2013_DiLeo_etAl}).
+2013~\cite{rodriguez2013data}; de Rigo et al., 2013~\cite{derigo2013architecture};
+Di Leo et al., 2013~\cite{2013_DiLeo_etAl}).
 
@@
 Seasonal mean temperature trend for the temperate climate zone of the European Union
-(Gebbert and Pebesma, 2014 \cite{Gebbert20141}). The modules t.rast.aggregate, 
-t.rast.univar and the open source statistical software system R
+(Gebbert and Pebesma, 2014 \cite{Gebbert20141}). The modules \gmodule{t.rast.aggregate},
+\gmodule{t.rast.univar} and the open source statistical software system R
 were used to create this plot.
@@
 location, it becomes paramount to have a more complete comparison, 
-in space and time.\newline
+in space and time.
+\newline
 
 \begin{minipage}{0.5\linewidth}
+\begin{center}
 \includegraphics[width=0.9\textwidth]{TonleSapTa}
-\vspace{1mm}
-Biological fraction of 2014 ET (cumul. mm/y), Tonle Sap, Cambodia.
+\end{center}
 \end{minipage}
-\bigskip
+~
+\begin{minipage}{0.5\linewidth}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{TonleSapTaGap}
+\end{center}
+\end{minipage}
+\vspace{2mm}
+\begin{center}
+Biological fraction of 2014 ET (cumul. mm/y) \& January average gap (mm/m), Tonle Sap, Cambodia.
+\end{center}
 
@@
 FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
-improved to become \textit{r.li} in 2006. Further development continued, with a significant 
+improved to become \gmodule{r.li} in 2006. Further development continued, with a significant 
 speed up (Trac1, 2014) and new interactive user interface.

### 2015-03-25 grassposter/2015_EGU_G7_Python/listings/tgrass_examples.tex
Added GRASS GIS Temporal Framework part
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64917 15284696-431f-4ddb-bdfa-cd5b030d7da7

% taken from grass-promo/grassposter, written by me I think

\documentclass{standalone}

\usepackage[active,tightpage]{preview}
\usepackage{listings}
\PreviewEnvironment{lstlisting}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\input{listings_settings}

\begin{document}

\begin{lstlisting}[language=Python,linewidth=34.2em]
# Import the GRASS GIS temporal framework
import grass.temporal as tgis
# Open an existing space time raster dataset (STRDS)
temp_strds = tgis.open_old_stds(name="temp_daily", 
                                type="strds")
# Shift all registered raster map layer 2 days in the future
temp_strds.shift("2 days")
# Open an exitsing time stamped raster map as map object
temp_19770324 = tgis.open_new_map_dataset(type='raster', 
                                name='temp_1977_Mar_24')
# Unregister the raster map from the STRDS
temp_strds.unregister_map(temp_19770324)
# Get a list of all registered raster map layers with
# a start time later 1990-05-22 from the STRDS
maps = temp_strds.get_registered_maps_as_objects(\
                     where="start_time > '1990-05-22'")
# Create a temporal buffer of 6h for each map in the list
for map in maps:
    map.temporal_buffer("6 hours", update=True)
# Compute new spatio-temporal extent and granularity 
temp_strds.update_from_registered_maps()
# Get the granuarity of the STRDS
gran = temp_strds.get_granularity()
\end{lstlisting}
\end{document}

### 2015-03-25 grassposter/2015_EGU_G7_Python/main.tex
Added Thuenen Institute Logo
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64911 15284696-431f-4ddb-bdfa-cd5b030d7da7
Added GRASS GIS Temporal Framework part
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64917 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
        % TODO: TICSA logo (Soeren)
-       \includegraphics[width=\logowidth]{ncstate}
+       \includegraphics[width=\logowidth]{ti}
        \logohspace
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{GRASS GIS Addons}}{
+The GRASS GIS Addons ensures long-term preservation of the code.
+Well maintained modules in Addons can be moved to GRASS GIS itself.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Alternatives to Python}}{
+GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
+and as subprocesses virtually any language as long as proper environment is set.
+
+The GRASS GIS library has a C API which is often used to create GRASS modules in C and C++.
+
+GRASS GIS modules can be used in R using \pkg{rgrass7} package.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Testing the code}}{
+\cite{Petras2014}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Temporal framework}}{
-\cite{Gebbert2014}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Testing the code}}{
-\cite{Petras2014}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{GRASS GIS Addons}}{
-The GRASS GIS Addons ensures long-term preservation of the code.
-Well maintained modules in Addons can be moved to GRASS GIS itself.
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Alternatives to Python}}{
-GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
-and as subprocesses virtually any language as long as proper environment is set.
-
-The GRASS GIS library has a C API which is often used to create GRASS modules in C and C++.
-
-GRASS GIS modules can be used in R using \pkg{rgrass7} package.
+\block{\blocktitlewrap{GRASS GIS Temporal Framework}}{
+The GRASS GIS Temporal Framework implements the temporal GIS functionality of GRASS GIS 
+and provides a Python API to implement spatio-temporal processing modules. 
+The framework introduces space time datasets that represent time series of raster, 
+3D raster or vector maps. Some API examples:
+\includegraphics[width=1\linewidth, clip, trim=0 0 0 0]{tgrass_examples}
 }

### 2015-03-26 grassposter/2015_EGU_WD_Ethiopia/poster.tex
Updated poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64923 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \blocknode{Abstract}{
-\small \noindent This research work is about finding the connection between farmers perspectives on changes of water conditions in their socio-agricultural environment and satellite remote sensing analysis.\newline
+\small \noindent This research work is about finding the connection between farmers perspectives on changes of water conditions in their socio-agricultural environment and satellite remote sensing analysis.\newline\linebreak
 Key informant surveys were conducted to investigate localised views on water scarcity as a counterpoint to the physical measurement of water availability.
@@
 	\begin{tabular}{c p{0.5\textwidth}}
-	 \raisebox{-0.9\totalheight}{\includegraphics[width=0.45\textwidth]{./images/fig1}}
+	 \raisebox{-0.9\totalheight}{\includegraphics[width=0.45\textwidth]{./images/ETH_UBN_Fogera}}
 	&
-	The transpiration data is created from energy balance modelling \citep{chemin2012distributed} modules (i.eb.*, i.evapo.*) within GRASS GIS version 7, by partitioning the net radiation (r.sun) into soil heat flux (i.eb.soilheatflux), sensible heat flux (i.eb.h\_*) and the residual being the energy needed to evaporate water (i.eb.evapfr, i.eb.eta).
+	The transpiration data is created from energy balance modelling \citep{chemin2012distributed} modules (i.eb.*, i.evapo.*) within GRASS GIS \cite{neteler2012grass} version 7, by partitioning the net radiation (r.sun) into soil heat flux (i.eb.soilheatflux), sensible heat flux (i.eb.h\_*) and the residual being the energy needed to evaporate water (i.eb.evapfr, i.eb.eta).
 This information is then fractionated into biotic (transpiration) and abiotic (evaporation) parts using vegetation fraction.\newline\linebreak
-The accumulated transpiration is subjected to temporal scrutiny ...\newline
+The accumulated transpiration is subjected to temporal scrutiny, the major transpiration peak every year is preceded by a temporary increment in transpiration.
+This temporary change may (or not) carry enough trasnpiration to crop Spring maize in Fogera, the topic of this research.\newline
 \end{tabular}\newline
@@
 \begin{center}
-	\begin{tabular}{cc}
- 	\includegraphics[width=0.45\textwidth]{./images/fig1}
- 	& 
- 	\includegraphics[width=0.45\textwidth]{./images/fig1}
-	\end{tabular}
+\includegraphics[width=\textwidth]{./images/Ta}
 \end{center}
-
-More info here...\newline
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Rainfall deficit in May perceived as water scarcity}{
+Farmers in upland Fogera associate the failure of the May rains with “drought”.
+For instance, a male farmer stated that, “When it is drought, it is the season of millet (teff).” A female farmer stressed this seasonal scarcity in water availability by insisting that “It is this drought that hinders crop production.” However, if the rain fails in May, it does not necessarily represent an inevitable drought year, in that rain can be available in the subsequent months.
+Nevertheless, rainfed maize and millet planting in May is a central concern as it provides food and fodder for season, buffering household food security and reducing stress on further crop-related decision-making.\newline\linebreak
+Rainfall variability has been one of the important factors impeding sustained implementation of intensification strategies, and particularly the use of fertilisers.
+Key informants indicated that rainfall variability has been discouraging the use of fertiliser due to risk of unsuccessful crop production which exacerbates farmers’ indebtedness besides losing production.i\newline\linebreak
+Vulnerability and capacity to respond to rainfall variability differs depending on individual natural, financial and social assets, as well as gender and socio-cultural variables.
+Farmers in Fogera have been attempting to respond to problems related to water availability based on adaptation, indigenous knowledge, practicing available options.
+Responses undertaken by individual farmers and communities include: adjusting planting times and cropping pattern; deploying traditional ecological knowledge of soil to mitigate risk associated with water availability, expanding traditional and motor-pump irrigation \citep{dessalegn2014is}; and sponsoring religious figures to ameliorate the violation of spiritual sanctions that are transgressed in contemporary agricultural production.\newline\linebreak
+}
+
+\startthirdcolumn
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \blocknode{Spring Maize and food security}{
@@
 
-}
-
-\startthirdcolumn
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{May rainfall deficit perceived water scarcity}{
-Farmers in upland Fogera associate the failure of the May rains with “drought”.
-For instance, a male farmer stated that, “When it is drought, it is the season of millet (teff).” A female farmer stressed this seasonal scarcity in water availability by insisting that “It is this drought that hinders crop production.” However, if the rain fails in May, it does not necessarily represent an inevitable drought year, in that rain can be available in the subsequent months.
-Nevertheless, rainfed maize and millet planting in May is a central concern as it provides food and fodder for season, buffering household food security and reducing stress on further crop-related decision-making.\newline\linebreak
-Rainfall variability has been one of the important factors impeding sustained implementation of intensification strategies, and particularly the use of fertilisers.
-Key informants indicated that rainfall variability has been discouraging the use of fertiliser due to risk of unsuccessful crop production which exacerbates farmers’ indebtedness besides losing production.i\newline\linebreak
-Vulnerability and capacity to respond to rainfall variability differs depending on individual natural, financial and social assets, as well as gender and socio-cultural variables.
-Farmers in Fogera have been attempting to respond to problems related to water availability based on adaptation, indigenous knowledge, practicing available options.
-Responses undertaken by individual farmers and communities include: adjusting planting times and cropping pattern; deploying traditional ecological knowledge of soil to mitigate risk associated with water availability, expanding traditional and motor-pump irrigation \citep{dessalegn2014is}; and sponsoring religious figures to ameliorate the violation of spiritual sanctions that are transgressed in contemporary agricultural production.\newline\linebreak
 }

### 2015-03-26 grassposter/2015_EGU_G7_Python/listings/tgrass_examples.tex
Fixed wrong raster object open method
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64924 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \begin{lstlisting}[language=Python,linewidth=34.2em]
-# Import the GRASS GIS temporal framework
+# Import and initialize the GRASS GIS temporal framework
 import grass.temporal as tgis
+tgis.init()
 # Open an existing space time raster dataset (STRDS)
@@
 # Open an exitsing time stamped raster map as map object
-temp_19770324 = tgis.open_new_map_dataset(type='raster', 
-                                name='temp_1977_Mar_24')
+temp_24Mar77 = tgis.RasterDataset('temp_1977_Mar_24@soeren')
 # Unregister the raster map from the STRDS
-temp_strds.unregister_map(temp_19770324)
+temp_strds.unregister_map(temp_24Mar77)
 # Get a list of all registered raster map layers with

### 2015-03-29 grassposter/2015_EGU_G7_Python/main.tex
2015_EGU_G7_Python poster: minor cleanup; parser text addition
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64927 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2015-03-25 grassposter/2015_EGU_G7_Python/main.tex
@@
 % License: CC0
-% The license is CC0 but you can acknowledge the authors if you want to. See their names bellow.
+% The license is CC0 but you can acknowledge the authors if you want to. See their names below.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{GRASS GIS Addons}}{
+The GRASS GIS Addons ensure long-term preservation of the code.
+Well maintained modules in Addons can be moved to GRASS GIS core.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Alternatives to Python}}{
+GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
+and as subprocesses virtually any language as long as proper environment is set.
+
+The GRASS GIS library povides a C API which is commonly used to create GRASS modules in C and C++.
+
+GRASS GIS modules can be used within R using the \pkg{rgrass7} package.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \block{\blocktitlewrap{More information}}{
@@
 
+The g.parser module provides full parser support for GRASS GIS scripts.
+It provides the creation of help page template, and command line option
+checking. Each command and scripts which uses the GRASS GIS parser can
+publish its parameter and flags description in XML. Through the included
+XML parser this description can be turned into a graphical user interface with
+standardized styling.
+
 \includegraphics[width=\linewidth, clip, trim=0 0 0 0]{grass_module}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Temporal framework}}{
-\cite{Gebbert2014}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Testing the code}}{
-\cite{Petras2014}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{GRASS GIS Addons}}{
-The GRASS GIS Addons ensures long-term preservation of the code.
-Well maintained modules in Addons can be moved to GRASS GIS itself.
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Alternatives to Python}}{
-GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
-and as subprocesses virtually any language as long as proper environment is set.
-
-The GRASS GIS library has a C API which is often used to create GRASS modules in C and C++.
-
-GRASS GIS modules can be used in R using \pkg{rgrass7} package.
+\block{\blocktitlewrap{GRASS GIS 7 Temporal Framework}}{
+The GRASS GIS Temporal Framework offers the temporal GIS functionality of GRASS GIS 
+and provides a Python API to implement spatio-temporal processing modules. 
+The framework introduces space-time datasets that represent time series of raster, 
+3D raster or vector maps. Some API examples:
+\includegraphics[width=1\linewidth, clip, trim=0 0 0 0]{tgrass_examples}
 }
@@
 \begin{minipage}{\listtextwidth}
-GRASS GIS is a OSGeo project. OSGeo provides infrastructure for websites and source code management.
+GRASS GIS is a OSGeo project. OSGeo provides infrastructure for project
+Web sites, mailing lists and source code management.
 \end{minipage}
@@
 \begin{minipage}{\listtextwidth}
-Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code.
+Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code 2014.
 \end{minipage}
@@
 
-Luca Delucchi contributed significantly to development of Python interfaces for GRASS GIS
-by extensive testing in early stages of development, documenting the APIs
+Luca Delucchi, Italy, contributed significantly to development of Python interfaces for GRASS GIS 7
+through extensive testing in early stages of development, documenting the APIs
 and general contributions to the code itself.
@@
   \emph{GRASS GIS: A multi-purpose open source GIS.}
-  Environmental Modelling \& Software, 31(0), 124-130.
+  Environmental Modelling \& Software, 31, 124--130.
 
@@
   Gebbert, S., Pebesma, E., 2014. A temporal GIS for field based environmental modeling. Environmental
-  Modelling \& Software 53, 1-12.
+  Modelling \& Software 53, 1--12.
 
@@
   Interface (API) for Geographic Resources Analysis Support System (GRASS) Geographic Information System
-  (GIS). ISPRS International Journal of Geo-Information 2, 201-219.
+  (GIS). ISPRS International Journal of Geo-Information 2, 201--219.
 

### 2015-03-29 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
2015_EGU_G7_PeerReview_SciPlatform poster: minor cleanup
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64929 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 % Authors: See authors below and see also acknowledgement for authors of some images or research
+
+% EGU: http://meetingorganizer.copernicus.org/EGU2015/posters/17174
+%      http://meetingorganizer.copernicus.org/EGU2015/EGU2015-8314-7.pdf
 
@@
 Pietro Zambelli\inst{3},
-Markus Neteler\inst{6}, and
-Peter L\"{o}we\inst{7}
+Markus Neteler\inst{6},
+Peter L\"{o}we\inst{7}, and
 Margherita Di Leo\inst{8}
@@
 \institute{
-\instlist{1}NCSU, USA,
-\instlist{2}IWMI, Sri Lanka,
-\instlist{3}EURAC, Italy,
-\instlist{4}FCE CTU in Prague, Czech Republic,
-\instlist{5}TICSA, Germany,
-\instlist{6}CRI, FEM, Italy,
-\instlist{7}GNLST, Germany
+\instlist{1}NCSU, USA;
+\instlist{2}IWMI, Sri Lanka;
+\instlist{3}EURAC, Italy;
+\instlist{4}FCE CTU in Prague, Czech Republic;
+\instlist{5}TICSA, Germany;
+\instlist{6}CRI, FEM, Italy;
+\instlist{7}GNLST, Germany;
 \instlist{8}EC-JRC, Italy
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{GRASS as Temporal GIS}}{
+\block{\blocktitlewrap{GRASS GIS as Temporal GIS}}{
 The time dimension was introduced in GRASS GIS version 7 for raster, 3D raster and
@@
 \blocksectiontitle{Acknowledgements}
-Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS}
+Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS};
 % http://www4.ncsu.edu/~jcfounta/Summer14Posters/horvath.pdf
@@
 
-GRASS GIS project is a Open Source Geospatial Foundation (OSGeo) project and is using OSGeo infrastructure for websites and repositories.
+GRASS GIS project is a Open Source Geospatial Foundation (OSGeo) project and is using OSGeo infrastructure for Web site and code repository.
 

### 2015-03-30 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
aligned graphs damflood, solved space for acknowledgements
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64930 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 specialised software called \textit{Tangible Landscape} (previously \textit{Tangible GIS}), which also 
-incorporated the \gamodule{r.damflood} module.
+incorporated the \gamodule{r.damflood} module.\newline\linebreak
 
@@
 
-\blocksectiontitle{References}
+%\blocksectiontitle{References}
 \begingroup
@@
 
-\blocksectiontitle{Acknowledgements}
+\hrulefill
+
+%\blocksectiontitle{Acknowledgements}
+\textbf{Acknowledgments}
+
 Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS};

### 2015-03-30 grassposter/2015_EGU_G7_Python/listings/pygrass_raster_examples.tex
Add ipython and pygrass examples
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64931 15284696-431f-4ddb-bdfa-cd5b030d7da7

% taken from grass-promo/grassposter, written by me I think

\documentclass{standalone}

\usepackage[active,tightpage]{preview}
\usepackage{listings}
\PreviewEnvironment{lstlisting}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\input{listings_settings}

\begin{document}

\begin{lstlisting}[language=Python,linewidth=44.2em]
import numpy as np
from grass.pygrass.raster import RasterRow
from grass.pygrass.raster.buffer import Buffer
from grass.pygrass.gis.region import Region

def raster2numpy(name, mapset):
    """Return a numpy array from a raster map"""
    with RasterRow(name, mapset, mode='r') as array:
        return np.array(array)

def numpy2raster(array, mtype, name):
    """Save a numpy array to a raster map"""
    reg = Region()
    if (reg.rows, reg.cols) != array.shape:
        msg = "Region and array shape are different: %r != %r"
        raise TypeError(msg % ((reg.rows, reg.cols), array.shape))
    with RasterRow(name, mode='w', mtype=mtype) as new:
        newrow = Buffer((array.shape[1],), mtype=mtype)
        for row in array:
            newrow[:] = row[:]   # cast array to raster type
            new.put_row(newrow)  # write row to raster map
\end{lstlisting}
\end{document}

### 2015-03-30 grassposter/2015_EGU_G7_Python/main.tex
Add ipython and pygrass examples
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64931 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}
-
+\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_sc_syntax}
 }
@@
 
+	IPython Notebook is a web-based application that provides a tool to: developing, documenting, and executing code, as well as communicating the results.
+	One great tool to process and visualize your data/maps, integrating formulas and explanatory text, interacting with remote server and clusters.
+
+	%\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{pygrass_ipython_cli}
+	\includegraphics[width=0.8\linewidth, clip, trim=0 0 0 0]{ipython_nb}
 }
@@
 \block{\blocktitlewrap{PyGRASS interface to C libraries}}{
+Some API examples to convert a raster map to a numpy array and then back to a raster.
+
+\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_raster_examples}
 

### 2015-03-30 grassposter/2015_EGU_WD_Ethiopia/poster.tex
Updated poster with new maps, beautified
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64932 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-\title{Water Dynamics in Fogera and the Upper Blue Nile\\Farmers perspectives and remote sensing\bigskip}
+\title{Water Dynamics in Fogera and the Upper Blue Nile\\Farmers perspectives and remote sensing\\}
 \author{Yann Chemin, Mengistu Dessalegn, Jayne Curnow\\
@@
 \blocknode{Abstract}{
-\small \noindent This research work is about finding the connection between farmers perspectives on changes of water conditions in their socio-agricultural environment and satellite remote sensing analysis.\newline\linebreak
+\noindent This research work is about finding the connection between farmers perspectives on changes of water conditions in their socio-agricultural environment and satellite remote sensing analysis.\newline\linebreak
 Key informant surveys were conducted to investigate localised views on water scarcity as a counterpoint to the physical measurement of water availability.
@@
 Such gap can be overcome, even by temporary supplemental irrigation practices, however, the economical and cultural set up is already developed in another way, as per seasonal renting of higher soil profile water retention capacity fields.
+\newline\linebreak
 }
@@
 \begin{center}
-	\begin{tabular}{c p{0.5\textwidth}}
-	 \raisebox{-0.9\totalheight}{\includegraphics[width=0.45\textwidth]{./images/ETH_UBN_Fogera}}
+	\begin{tabular}{p{0.5\textwidth} p{0.4\textwidth}}
+	 \raisebox{-0.95\totalheight}{\includegraphics[width=0.5\textwidth]{./images/ETH_UBN_Fogera}}
+	 \newline\linebreak
+	 Figure 1: Fogera woreda location near Lake Tana.\newline\linebreak
 	&
@@
 	The accumulated transpiration is subjected to temporal scrutiny, the major transpiration peak every year is preceded by a temporary increment in transpiration.
-This temporary change may (or not) carry enough trasnpiration to crop Spring maize in Fogera, the topic of this research.\newline
-\end{tabular}\newline
+This temporary change may (or not) carry enough transpiration to crop Spring maize in Fogera, the topic of this research.\newline
+	\end{tabular}
 \end{center}
@@
 \includegraphics[width=\textwidth]{./images/Ta}
+\newline
+Figure 2: 14 years of daily transpiration for Gumura basin in Fogera woreda.
+\newline
 \end{center}
 
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{Acknowledgements}{
-\smallskip
-\begin{tabular}{p{0.70\textwidth} c}
-	The authors would like to acknowledge the CGIAR Research Program on Water, Land and Ecosystems (WLE ; \url{wle.cgiar.org}) Innovation Fund.
-	&
-	\hspace{3mm}
-	\raisebox{-0.5\totalheight}{\includegraphics[width=0.27\textwidth]{./images/WLE}}
-\end{tabular}
 }
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blocknode{Acknowledgements}{
+\smallskip
+\begin{tabular}{p{0.70\textwidth} c}
+	The authors would like to acknowledge the CGIAR Research Program on Water, Land and Ecosystems (WLE ; \url{wle.cgiar.org}) Innovation Fund.
+	&
+	\hspace{3mm}
+	\raisebox{-0.5\totalheight}{\includegraphics[width=0.27\textwidth]{./images/WLE}}
+\end{tabular}
+}
+
 \startthirdcolumn
@@
 \blocknode{Spring Maize and food security}{
+We found that in one case (figure 3), farmers perspective on the Spring maize crop sensibility to variability of rainfall can be quantified in space and time by remote sensing cumulative transpiration.
+A crop transpiration gap of 1-2.5 mm/day for about 20 days is to be overcome, a full amount of 20 to 50 mm, depending on the type of year deficit.
+Such gap can be overcome, even by temporary supplemental irrigation practices.\newline\linebreak
+We argue that a better understanding of the dynamics of water variability and the implications on water management, agricultural production and livelihoods should consider small-holder farmers’ perceptions, concerns and responses.
+This is essential to devise well-targeted policies and interventions that can improve livelihoods, as well as optimising water management and agricultural production.
+
 \begin{center}
-	\begin{tabular}{c p{0.5\textwidth}}
- 	\raisebox{-0.9\totalheight}{\includegraphics[width=0.45\textwidth]{./images/fig1}}
-	&
-	We found that in one case (figure 1), farmers perspective on the Spring maize crop sensibility to variability of rainfall can be quantified in space and time by remote sensing cumulative transpiration.
-A crop transpiration gap of 1-2.5 mm/day for about 20 days is to be overcome, a full amount of 20 to 50 mm, depending on the type of year deficit.
-Such gap can be overcome, even by temporary supplemental irrigation practices.\newline
-We argue that a better understanding of the dynamics of water variability and the implications on water management, agricultural production and livelihoods should consider small-holder farmers’ perceptions, concerns and responses.
-This is essential to devise well-targeted policies and interventions that can improve livelihoods, as well as optimising water management and agricultural production.\newline\linebreak
-	\end{tabular}
+ \includegraphics[width=0.65\textwidth]{./images/fig1}\\
+ \vspace{5mm}
+ Figure 3: Transpiration deficiency, month of May, one year out four.
 \end{center}
+
 Cumulative transpiration on a yearly basis highlights different years, and heterogeneity periods (breaks) in the growing curve.
 Looking closely into the May-July period, one can identified the transpiration gap found most of the time for the early Maize crop much discussed by farmers.
-Out of 14 years, only 4 seem to have made the transpiration leap above the others (red ellipse in Figure 1).
-The leap can be quantified by an average of 20mm of rainfall over a period of 20 days, 1 mm of transpiration per day is missing at minimum (red ellipse) and 2.5mm/day at maximum (yellow ellipse) from mid-June to early July.\newline\linebreak
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{GRASS GIS script}{
-\smallskip
-{\footnotesize \fontfamily{pcr}\selectfont 
-\textbf{\#Select MODIS EVI archive\newline} 
-i.group \textcolor{blue}{group}=pca\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=*h28v07*EVI)\newline
-\textbf{\#Run the PCA on the EVI archive\newline}
-i.pca \textcolor{blue}{input}=pca\_group \textcolor{blue}{output\_prefix}=pca \textcolor{blue}{percent}=99 --o\newline
-\textbf{\#As an example, you can select the 1$^{st}$ to the 9$^{th}$ PCA members\newline}
-i.group \textcolor{blue}{group}=ta\_group \textcolor{blue}{input}=\$(g.mlist \textcolor{blue}{type}=rast \textcolor{blue}{pattern}=pca.[123456789] sep=,) \newline
-\textbf{\#and run an object-based classification analysis on them\newline}
-i.segment \textcolor{blue}{group}=ta\_group \textcolor{blue}{output}=seg\_ta \textcolor{blue}{threshold}=0.9 \textcolor{blue}{memory}=5000 \textcolor{blue}{iterations}=50 --o \& \newline}
+Out of 14 years, only 4 seem to have made the transpiration leap above the others (red ellipse in Figure 3).
+The leap can be quantified by an average of 20mm of rainfall over a period of 20 days, 1 mm of transpiration per day is missing at minimum (red ellipse) and 2.5mm/day at maximum (yellow ellipse) from mid-June to early July.
 
@@
 \blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
-\scriptsize
+\small
 \begingroup
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blocknode{TBC...}{
+\blocknode{Yearly Transpiration gap in the Upper Nile Basin}{
 \smallskip
-TBC...\newline\linebreak
 
-Object based classification (\textit{i.segment}) of the sum transpiration for each year has been done and merged, resulting areas were clumped (\textit{r.clump}) and averaged statistics of yearly transpiration extracted (\textit{r.stats.zonal}).\newline
 \begin{center}
-	\begin{tabular}{cc}
- 	\begin{tabular}{p{0.5\textwidth}}
- 	\includegraphics[width=0.45\textwidth]{./images/fig1}\\
- 	\vspace{5mm}
-blablablablablabla
+	\begin{tabular}{ll}
+ 	\begin{tabular}{c}
+ 	 \includegraphics[width=0.48\textwidth]{./images/Ta_Gap_2001}\\
+ 	 \includegraphics[width=0.48\textwidth]{./images/Ta_Gap_2006}
 	\end{tabular}
@@
  	\begin{tabular}{c}
- 	\includegraphics[width=0.45\textwidth]{./images/fig1}\\
- 	\includegraphics[width=0.45\textwidth]{./images/fig1}
+ 	\includegraphics[width=0.48\textwidth]{./images/Ta_Gap_2011}\\
+ 	\includegraphics[width=0.48\textwidth]{./images/Ta_Gap_2014}
 	\end{tabular}
 	\end{tabular}
+	Figure 4: Area Equalized Transpiration Gap in the Upper Nile Basin.\\
+	\vspace{5mm}
+ 	\begin{tabular}{| c | c |}
+	\hline
+	&\\
+	2001 & 2011\\
+	&\\
+	\hline
+	&\\
+	2006 & 2014\\
+	&\\
+	\hline
+	\end{tabular}
 \end{center}
+
 }

### 2015-03-30 grassposter/2015_EGU_WD_Ethiopia/poster.tex
Finalised poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64937 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \blocknode{Spring Maize and food security}{
-We found that in one case (figure 3), farmers perspective on the Spring maize crop sensibility to variability of rainfall can be quantified in space and time by remote sensing cumulative transpiration.
+\begin{center}
+	\begin{tabular}{ll}
+ 	\begin{tabular}{p{0.35\textwidth}}
+Looking into the cumulative transpiration yearly signals (Figure 3), there is non uniformity, thus variations in water availability to vegetation.
+Following farmers' interviews and looking more closely into the April-June period, we found that in one case (figure 4), farmers perspective on the Spring maize crop sensibility to variability of rainfall can be quantified in space and time by remote sensing cumulative transpiration.
 A crop transpiration gap of 1-2.5 mm/day for about 20 days is to be overcome, a full amount of 20 to 50 mm, depending on the type of year deficit.
@@
 We argue that a better understanding of the dynamics of water variability and the implications on water management, agricultural production and livelihoods should consider small-holder farmers’ perceptions, concerns and responses.
-This is essential to devise well-targeted policies and interventions that can improve livelihoods, as well as optimising water management and agricultural production.
-
-\begin{center}
- \includegraphics[width=0.65\textwidth]{./images/fig1}\\
- \vspace{5mm}
- Figure 3: Transpiration deficiency, month of May, one year out four.
-\end{center}
-
+This is essential to devise well-targeted policies and interventions that can improve livelihoods, as well as optimising water management and agricultural production.\newline\linebreak
 Cumulative transpiration on a yearly basis highlights different years, and heterogeneity periods (breaks) in the growing curve.
 Looking closely into the May-July period, one can identified the transpiration gap found most of the time for the early Maize crop much discussed by farmers.
-Out of 14 years, only 4 seem to have made the transpiration leap above the others (red ellipse in Figure 3).
+Out of 14 years, only 4 seem to have made the transpiration leap above the others (red ellipse in Figure 4).
 The leap can be quantified by an average of 20mm of rainfall over a period of 20 days, 1 mm of transpiration per day is missing at minimum (red ellipse) and 2.5mm/day at maximum (yellow ellipse) from mid-June to early July.
+	\end{tabular}
+ 	& 
+ 	\begin{tabular}{c}
+ 	\includegraphics[width=0.55\textwidth]{./images/fig1big}\\
+ 	\includegraphics[width=0.55\textwidth]{./images/fig1}\\
+	\end{tabular}
+	\end{tabular}
+	\vspace{5mm}
+\end{center}
+\begin{flushright}
+Figure 3\&4: Cumulative transpiration per year \& month of May.\\
+\end{flushright}
 
@@
 
-%\smallskip
-%\hrulefill
+\smallskip
+\hrulefill
 %\vspace{-5pt}
@@
 \smallskip
+The Upper Nile Basin has a dramatic range of altitude from 483m reaching to 4517m at most.
+While most of the high altitude areas and various water bodies (in blue in Figure 4) are not or very less vegetated, the transpiration gap is relatively uninteresting.
+On the other hand, very clearly (in red in Figure 4), valleys are under deficit of transpiration from their potential level, vegetation is under stress.
 
@@
 
+This averaged daily deficit for a full year does not do justice to seasonal variations, but encompasses the potential for analysis of much longer temporal periodicity, we are only starting to decifer the monthly and yearly structures.
+It is clear at this point that Fogera woreda and one of its basin Gumura are a more common case than thought initially in terms of yearly transpiration gap budget.\newline
+
 }
@@
 \smallskip
-Space science (i.e.
-remote sensing plant transpiration data and analysis) complements and augments farmer’s responses to rainfall variability.
-In such marginal landscapes access to this information can mean the difference between seasonal hunger and food security.
+Space science as in remote sensing plant transpiration data and analysis, enables to quantify the lack of water consumption to reach a minimum Spring maize harvest.
+This knowledge potentially complements and augments farmer’s resilience and responsiveness to rainfall variability.
+In such marginal landscapes access to this information, and development of a coping mechanism, can mean the difference between seasonal hunger and food security.\newline\linebreak
+
+Extending the exploration field of view to the Upper Nile Basin, we can see the Fogera woreda and its basin Gumura seem to have a fairly common yearly behaviour for watersheds.
+The lower section of the valleys seem to be consistently to have vegetation under water stress.
+Searching for monthly periodicity in the gap of transpiration is a subject of further studies.\newline
+
 }

### 2015-03-30 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
2015_EGU_G7_PeerReview_SciPlatform poster: bib cleanup; two TODOs added
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64941 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-% For blibliography styling
+% For bibliography styling
+%% TODO: all names should be abbreviated
 \usepackage{natbib}
@@
 \includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{rdiversity}
-Landscape diversity according to shannon index in near Charlotte (North Carolina, USA).
+Landscape diversity according to Shannon index in near Charlotte (North Carolina, USA).
 \end{minipage}
@@
 \begin{itemize}
- \item Algorithms and models once included into GRASS GIS are still available.
+ \item Algorithms and models once included into GRASS GIS remain available long term.
  \item GRASS GIS development team takes care of API related updates and operating system related changes.
+%% TODO: what does that mean?:
  \item Scientists are using highly specialized tools implemented by other people when having both scientific publication and source code at hand.

### 2015-03-30 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
2015_EGU_G7_PeerReview_SciPlatform poster: language fixes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64942 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \block{\blocktitlewrap{Natural Hazards: Wildfire Spread}}{
-The wildfire simulation toolset, firstly developed by Xu, 1994~\cite{xu1994simulating}, 
-implementing Rothermel’s model~\cite{Rothermel1983how}, available through the GRASS 
-functions \gmodule{r.ros} and \gmodule{r.spread}, is object of active research. It has been extensively 
+The wildfire simulation toolset, originally developed by Xu (1994~\cite{xu1994simulating}) 
+implements Rothermel’s model~\cite{Rothermel1983how}. It is available through the GRASS GIS 
+modules \gmodule{r.ros} and \gmodule{r.spread} and object of active research. It has been extensively 
 tested and recently adapted to European fuel types (Rodriguez-Aseretto et al.,
@@
 Based on the GRASS GIS Temporal Framework, more than 45 modules were implemented to manage, analyze, process
-and visualize space time datasets. The temporal enabled GRASS GIS is able to efficiently
-handle more than 100.000 map layers. It was used to analyze the
+and visualize space time datasets. The temporal enabled GRASS GIS is capable to efficiently
+handle more than 100,000 map layers. E.g., it was used to analyze the
 European Climate Assessment \& Dataset ECA\&D (Haylock et al. \cite{Haylock2008_climate_series})
@@
 \includegraphics[width=\textwidth]{elevation_lidar}
-Digital elevation model interpolated from lidar point cloud using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
+Digital elevation model interpolated from LiDAR point clouds using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
 \end{minipage}
@@
 With the large amount of remote sensing data covering the Earth, and the daily 
-information available for the past ten years (i.e. Aqua/Terra-MODIS) for each pixel 
+information available for more than twelve years (i.e. Aqua/Terra-MODIS) for each pixel 
 location, it becomes paramount to have a more complete comparison, 
@@
 To address this new experimental requirement, a distributed computing framework was 
-designed, and created (Chemin, 2012 \cite{chemin2012distributed}). 
-The design architecture was built from original satellite datasets to various levels 
+designed and created (Chemin, 2012 \cite{chemin2012distributed}). 
+The architecture design was built from original satellite datasets to various levels 
 of processing until reaching the requirement of various ETa models input dataset. 

### 2015-03-30 grassposter/2015_EGU_G7_Python/main.tex
finish basic script and pygrass boxes, merge R, A and I sections, reorganize boxes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64943 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{GRASS GIS Addons}}{
-The GRASS GIS Addons ensure long-term preservation of the code.
-Well maintained modules in Addons can be moved to GRASS GIS core.
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Alternatives to Python}}{
-GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
-and as subprocesses virtually any language as long as proper environment is set.
-
-The GRASS GIS library povides a C API which is commonly used to create GRASS modules in C and C++.
-
-GRASS GIS modules can be used within R using the \pkg{rgrass7} package.
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{More information}}{
-\newcommand{\qrcodewidth}{1\linewidth}
-\hspace{-0.02\linewidth}
-\begin{tabular}{lll}
-\begin{minipage}{0.1\linewidth}
-\includegraphics[height=\qrcodewidth]{grass_osgeo_org}
-\end{minipage}
-\begin{minipage}{0.27\linewidth}
-GRASS GIS website
-\end{minipage}
-&
-\begin{minipage}{0.1\linewidth}
-\includegraphics[height=\qrcodewidth]{python_doc}
-\end{minipage}
-\begin{minipage}{0.45\linewidth}
-GRASS GIS Python libraries documentation
-\end{minipage}
-\\
-% http://grass.osgeo.org/
-\url{grass.osgeo.org}
-&
-% http://grass.osgeo.org/grass71/manuals/libpython/
-\url{grass.osgeo.org/grass71/manuals/libpython}
-\end{tabular}
-
-% qrcode -t EPS -o grass-user.eps "http://lists.osgeo.org/listinfo/grass-user"
-% epstopdf grass-user.eps
-% rm grass-user.eps
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-\block{\blocktitlewrap{GRASS Scripting library interface to GRASS GIS modules}}{
-
-The same applies to \pkg{grass.pygrass} syntax:
-
-\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{script_doc_syntax}
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{PyGRASS interface to GRASS GIS modules}}{
-
-The same applies to \pkg{grass.pygrass} syntax:
-
-\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}
-\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_sc_syntax}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Using documentation for GRASS GIS modules}}{
-
-Documentation of GRASS GIS modules usually use Bash syntax for examples:
-
-\begin{alltt}
-r.neighbors input=elevation output=elevation\_smooth method=median -c
-\end{alltt}
-
-This can be easily rewritten to \pkg{grass.script} syntax:
-
-\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{script_doc_syntax}
-
-The same applies to \pkg{grass.script} syntax:
-
-\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{ctypes interface to C libraries}}{
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Using NumPy}}{
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Using IPython Notebook}}{
-
-	IPython Notebook is a web-based application that provides a tool to: developing, documenting, and executing code, as well as communicating the results.
-	One great tool to process and visualize your data/maps, integrating formulas and explanatory text, interacting with remote server and clusters.
-
-	%\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{pygrass_ipython_cli}
-	\includegraphics[width=0.8\linewidth, clip, trim=0 0 0 0]{ipython_nb}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \block{\blocktitlewrap{Automatic creation of GUI and CLI}}{
@@
 }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
+\block{\blocktitlewrap{GRASS Scripting library interface to GRASS GIS modules}}{
+
+The \pkg{grass.script} package offers simple and straightforward syntax to call GRASS GIS modules:
+
+\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{script_doc_syntax}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{PyGRASS interface to GRASS GIS modules}}{
+
+The \pkg{grass.pygrass} package provides a object-oriented way to work with GRASS GIS modules and their parameters:
+
+\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}
+
+Additionally, the \pkg{grass.pygrass} package offers simpler, Python oriented, way of accessing modules:
+
+\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_sc_syntax}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Using documentation for GRASS GIS modules}}{
+
+Documentation of GRASS GIS modules usually use Bash syntax for examples:
+
+\begin{alltt}
+r.neighbors input=elevation output=elevation\_smooth method=median -c
+\end{alltt}
+
+These can be easily rewritten to \pkg{grass.script} or \pkg{grass.pygrass} syntax shown above.
+
+% This can be easily rewritten to \pkg{grass.script} syntax:
+% 
+% \includegraphics[width=\linewidth, clip, trim=0 0 0 0]{script_doc_syntax}
+% 
+% The same applies to \pkg{grass.script} syntax:
+% 
+% \includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}
+% 
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Using IPython Notebook}}{
+
+	IPython Notebook is a web-based application that provides a tool to: developing, documenting, and executing code, as well as communicating the results.
+	One great tool to process and visualize your data/maps, integrating formulas and explanatory text, interacting with remote server and clusters.
+
+	\bigskip
+	%\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{pygrass_ipython_cli}
+	\centering
+	\includegraphics[width=0.95\linewidth, clip, trim=0 120 0 0]{ipython_nb}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{GRASS GIS Addons}}{
+The GRASS GIS Addons ensure long-term preservation of the code.
+Well maintained modules in Addons can be moved to GRASS GIS core.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{ctypes interface to C libraries}}{
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Using NumPy}}{
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Alternatives to Python}}{
+GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
+and as subprocesses virtually any language as long as proper environment is set.
+
+The GRASS GIS library povides a C API which is commonly used to create GRASS modules in C and C++.
+
+GRASS GIS modules can be used within R using the \pkg{rgrass7} package.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Acknowledgements}}{
+\block{\blocktitlewrap{References and Acknowledgements}}{
+
+\newcommand{\blocksectiontitle}[1]{\bigskip\textbf{\textcolor{gray}{\textsf{#1}}}}
+
+% disable the title
+\renewcommand{\section}[2]{}
+\begin{thebibliography}{9}
+
+\bibitem{Neteler2012}
+  Neteler, M., Bowman, M. H., Landa, M., Metz, M., 2012.
+  \emph{GRASS GIS: A multi-purpose open source GIS.}
+  Environmental Modelling \& Software, 31, 124--130.
+
+\bibitem{Gebbert2014}
+  Gebbert, S., Pebesma, E., 2014. A temporal GIS for field based environmental modeling. Environmental
+  Modelling \& Software 53, 1--12.
+
+\bibitem{Petras2014}
+  Petras, V., Gebbert, S., 2014. Testing framework for GRASS GIS: ensuring reproducibility of scientific
+  geospatial computing. Poster presented at: AGU Fall Meeting, December 15-19, 2014, San Francisco, USA.
+
+\bibitem{Zambelli2013}
+  Zambelli, P., Gebbert, S., Ciolli, M., 2013. Pygrass: An Object Oriented Python Application Programming
+  Interface (API) for Geographic Resources Analysis Support System (GRASS) Geographic Information System
+  (GIS). ISPRS International Journal of Geo-Information 2, 201--219.
+
+\end{thebibliography}
+
+\blocksectiontitle{Acknowledgements}
 
 \newcommand{\listhspace}{\hspace{0.005\linewidth}}
-\newcommand{\listlogowidth}{0.22\linewidth}
-\newcommand{\listtextwidth}{0.76\linewidth}
+\newcommand{\listlogowidth}{0.15\linewidth}
+\newcommand{\listtextwidth}{0.82\linewidth}
 
@@
 and general contributions to the code itself.
-}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{References}}{
+\blocksectiontitle{More information}
 
-% disable the title
-\renewcommand{\section}[2]{}
-\begin{thebibliography}{9}
+\newcommand{\qrcodewidth}{1\linewidth}
+\hspace{-0.02\linewidth}
+\begin{tabular}{lll}
+\begin{minipage}{0.1\linewidth}
+\includegraphics[height=\qrcodewidth]{grass_osgeo_org}
+\end{minipage}
+\begin{minipage}{0.27\linewidth}
+GRASS GIS website\newline
+% http://grass.osgeo.org/
+\url{grass.osgeo.org}
+\end{minipage}
+&
+\begin{minipage}{0.1\linewidth}
+\includegraphics[height=\qrcodewidth]{python_doc}
+\end{minipage}
+\begin{minipage}{0.45\linewidth}
+GRASS GIS Python libraries documentation\newline
+% http://grass.osgeo.org/grass71/manuals/libpython/
+\url{grass.osgeo.org/grass71/manuals}
+\end{minipage}
 
-\bibitem{Neteler2012}
-  Neteler, M., Bowman, M. H., Landa, M., Metz, M., 2012.
-  \emph{GRASS GIS: A multi-purpose open source GIS.}
-  Environmental Modelling \& Software, 31, 124--130.
+\end{tabular}
 
-\bibitem{Gebbert2014}
-  Gebbert, S., Pebesma, E., 2014. A temporal GIS for field based environmental modeling. Environmental
-  Modelling \& Software 53, 1--12.
+% qrcode -t EPS -o grass-user.eps "http://lists.osgeo.org/listinfo/grass-user"
+% epstopdf grass-user.eps
+% rm grass-user.eps
 
-\bibitem{Petras2014}
-  Petras, V., Gebbert, S., 2014. Testing framework for GRASS GIS: ensuring reproducibility of scientific
-  geospatial computing. Poster presented at: AGU Fall Meeting, December 15-19, 2014, San Francisco, USA.
-
-\bibitem{Zambelli2013}
-  Zambelli, P., Gebbert, S., Ciolli, M., 2013. Pygrass: An Object Oriented Python Application Programming
-  Interface (API) for Geographic Resources Analysis Support System (GRASS) Geographic Information System
-  (GIS). ISPRS International Journal of Geo-Information 2, 201--219.
-
-\end{thebibliography}
 }

### 2015-03-30 grassposter/2015_EGU_G7_Python/main.tex
reduce not filled boxes (NumPy and ctypes are in PyGRASS box)
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64944 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \block{\blocktitlewrap{PyGRASS interface to C libraries}}{
-Some API examples to convert a raster map to a numpy array and then back to a raster.
+Some API examples to convert a raster map to a NumPy array and then back to a raster.
 
@@
 
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Python script versus GRASS GIS module}}{
-and running code from IDE
+In addition to PyGRASS interface, advanced programmers can use \pkg{ctypes} interface
+to access C functions from GRASS GIS libraries directly.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{GRASS GIS Addons}}{
+\block{\blocktitlewrap{GRASS GIS modules, addons and Python scripts}}{
 The GRASS GIS Addons ensure long-term preservation of the code.
 Well maintained modules in Addons can be moved to GRASS GIS core.
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{ctypes interface to C libraries}}{
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Using NumPy}}{
-
+and running code from IDE
 }
@@
 \block{\blocktitlewrap{Alternatives to Python}}{
+GRASS GIS API is not limited only to Python.
 GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
-and as subprocesses virtually any language as long as proper environment is set.
-
-The GRASS GIS library povides a C API which is commonly used to create GRASS modules in C and C++.
-
-GRASS GIS modules can be used within R using the \pkg{rgrass7} package.
+and as subprocesses in virtually any language as long as the proper environment is set.
+The GRASS GIS library provides a C API which is commonly used to create GRASS GIS modules in C and C++ programming languages.
+Finally, GRASS GIS modules can be used within R statistical environment using the \pkg{rgrass7} package.
 }

### 2015-03-30 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
add original map before r.diversity
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64945 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
+\bigskip
+
 \begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{rdiversity}
-Landscape diversity according to Shannon index in near Charlotte (North Carolina, USA).
+\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{diversity_classes}
+\end{minipage}
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{diversity_shannon}
 \end{minipage}
 
-% TODO: some other example or something completely else?
+\medskip
+Landuse classes and derived landscape diversity according to Shannon index in near Charlotte (North Carolina, USA).
+% r.diversity input=development_2006 prefix=diversity alpha=0.5 size=65
+% r.li.shannon input="development_2006" config="conf_diversity_65.0" output="diversity_shannon_size_65.0"
 }
@@
 
-Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS};
+We acknowledge Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS} and
 % http://www4.ncsu.edu/~jcfounta/Summer14Posters/horvath.pdf
-
 Eva Stopkova for physical model of High Tatras.

### 2015-03-30 grassposter/2015_EGU_G7_Python/main.tex
two paragraphs about modules, addons and scripts
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64946 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \block{\blocktitlewrap{GRASS GIS modules, addons and Python scripts}}{
-The GRASS GIS Addons ensure long-term preservation of the code.
+A Python script can by turned into a GRASS GIS modules by adding a definition of the interface.
+Also, GRASS GIS modules expect to be executed in GRASS GIS session.
+Python scripts which are using GRASS GIS can be written in a way that GRASS GIS session is not required;
+the setup of a necessary environment is done in the script itself.
+% running code from IDE
+
+The GRASS GIS Addon repository ensures vendor-independent long-term preservation of the code
+and ensures an easy distribution of module to individual users.
 Well maintained modules in Addons can be moved to GRASS GIS core.
-and running code from IDE
 }

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
change order if institutions to match authors, change GNLST to TIB
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64950 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \author{
-Yann Chemin\inst{2},
-V\'{a}clav Petr\'{a}\v{s}\inst{1},
-Anna Petr\'{a}\v{s}ov\'{a}\inst{1},
-Martin Landa\inst{4},
-S\"{o}ren Gebbert\inst{5},
-Pietro Zambelli\inst{3},
+Yann Chemin\inst{1},
+V\'{a}clav Petr\'{a}\v{s}\inst{2},
+Anna Petr\'{a}\v{s}ov\'{a}\inst{2},
+Martin Landa\inst{3},
+S\"{o}ren Gebbert\inst{4},
+Pietro Zambelli\inst{5},
 Markus Neteler\inst{6},
@@
 \institute{
-\instlist{1}NCSU, USA;
-\instlist{2}IWMI, Sri Lanka;
-\instlist{3}EURAC, Italy;
-\instlist{4}FCE CTU in Prague, Czech Republic;
-\instlist{5}TICSA, Germany;
+\instlist{1}IWMI, Sri Lanka;
+\instlist{2}NCSU, USA;
+\instlist{3}FCE CTU in Prague, Czech Republic;
+\instlist{4}TICSA, Germany;
+\instlist{5}EURAC, Italy;
 \instlist{6}CRI, FEM, Italy;
-\instlist{7}GNLST, Germany;
+\instlist{7}TIB Hannover, Germany;
 \instlist{8}EC-JRC, Italy

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
introduction written by Peter Loewe (shorter version of it)
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64952 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
+\hypersetup
+{
+    pdfauthor={Y. Chemin, V. Petras, A. Petrasova, M. Landa, S. Gebbert, P. Zambelli, M. Neteler, P. Loewe, M. Di Leo},
+    pdfsubject={},
+    pdftitle={GRASS GIS: a peer-reviewed scientific platform and future research repository},
+    pdfkeywords={GIS, algorithms, methods, preservation, science, reproducibility}
+}
+
 % \usetemplate{1}
@@
 {
-Geographical Information Systems (GIS) are known for their capacity 
-to spatially enhance the capacity of management of natural resources. 
-While being often used as an analytical tool, they also represent a collaborative 
-scientific platform to develop new algorithms. GRASS GIS (Neteler et al., 2012 
-\cite{neteler2012grass}), a free and open source GIS, is used by many scientists 
-directly or through other projects such as R or QGIS to perform geoprocessing tasks. 
-Thus, a large number of scientific geospatial computations depend on quality and 
-correct functionality of GRASS GIS. Integrating scientific algorithms into GRASS GIS 
-helps to preserve reproducibility of scientific results over time as the original author 
-designed it (Rocchini \& Neteler, 2012 \cite{rocchini2012let}). Moreover, subsequent 
-improvements are tracked in the source code versioning system and are immediately 
-available to the public (Petras, 2014 \cite{Petras2014}). Thus, GRASS GIS acts as a 
-repository of scientific peer-reviewed code and algorithm/knowledge hub for future 
-generation of scientists.
+\setlength{\parskip}{0.3ex}
+
+Over the last decades, GIS has become a key driver in geospatial science, research and application.
+GIS software which is licensed under a free and open source software (FOSS) licence
+is more than just a mere tool for spatial analysis.
+
+GRASS GIS (Neteler et al., 2012 \cite{neteler2012grass}), a free and open source GIS,
+is used by many scientists directly or as a backend in other projects
+such as R or QGIS to perform geoprocessing tasks.
+
+Thanks to the user and developer community, submitted code is evaluated
+in different fields of application beyond
+the field of expertise of the original authors, and different scales of magnitude
+for the data to be processed.
+This exceeds the established review process for scientific writing in a given journal
+or a data publication in a defined field of science.
+
+Immediate access to software repository enables instant quality checking
+of the current software version both by continuous automated tests (Petras, 2014 \cite{Petras2014}),
+and code review by human experts.
+
+New scientific algorithms can be developed against the reviewed functionalities
+already provided by the GRASS GIS codebase.
+This avoids unnecessary overhead by re-implementation,
+ensures quality by use of trusted components and allows reuse and long term preservation
+within the project software repository:
+Integrating scientific algorithms into GRASS GIS helps to preserve reproducibility
+of scientific results over time as the original author designed it
+(Rocchini \& Neteler, 2012 \cite{rocchini2012let}).
 }
@@
 
+\bigskip
 \begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{geomorphon}
+\includegraphics[width=\textwidth, trim={0 0 0 125}, clip]{geomorphon}
 Geomorphons for part of Yakima Training Center (area 5x3~km, USA)

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
fix links and qrcodes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64953 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 ago, since then it was improved several times (Trac2, 2014). It is now an important part 
-of GRASS GIS and is even taught at geospatial modeling courses, for example 
-\url{http://courses.ncsu.edu/gis582/common/grass/interpolation_2.html}.
-% TODO: move link to references
+of GRASS GIS and is even taught at geospatial modeling courses, for example at North Carolina State University
+\cite{ncsugis582}.
 
@@
 \block{\blocktitlewrap{Conclusions}}{
+
+\renewcommand{\labelitemi}{\textcolor{gray}{$\bullet$}\hspace{0.5ex}}
+
 % TODO: review the points, it should be the highlight or something like that
-% TODO: style of bullets is strange
+
 \begin{itemize}
@@
 
-\newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}
+% \newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}
+\newcommand{\blocksectiontitle}[1]{\textbf{#1}}
 
@@
 
+\textcolor{gray}{
 \hrulefill
+}
 
-%\blocksectiontitle{Acknowledgements}
-\textbf{Acknowledgments}
+\blocksectiontitle{Acknowledgements}
 
@@
 
-% TODO: add proper QR codes and fix links
+% qrencode http://grass.osgeo.org -o qr_grass.eps -t EPS
+% epspdf -b qr_grass.eps qr_grass.pdf
 
@@
 \begin{minipage}{\qrcodesize}
-\includegraphics[width=\textwidth]{./images/grass_qr.pdf}
+\includegraphics[width=\textwidth]{./images/qr_grass.pdf}
 \end{minipage}
-
+~
 \begin{minipage}{0.15\linewidth}
-\small {\url{grass.osgeo.org}}
+\small {\href{http://grass.osgeo.org}{\nolinkurl{grass.osgeo.org}}}
 \end{minipage}
@@
 \begin{minipage}{\qrcodesize}
-\includegraphics[width=\textwidth]{./images/grass_qr.pdf}
+\includegraphics[width=\textwidth]{./images/qr_grasswiki.pdf}
 \end{minipage}
-
+~
 \begin{minipage}{0.2\linewidth}
-\small {\url{grasswiki.osgeo.org}}
+\small {\href{http://grasswiki.osgeo.org}{\nolinkurl{grasswiki.osgeo.org}}}
 \end{minipage}
@@
 \end{minipage}
-
+~
 \begin{minipage}{0.35\linewidth}

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
Updated Introduction with Peter's text
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64954 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \setlength{\parskip}{0.3ex}
+\normalsize
+Geographical Information Systems (GIS) are widely used for the management of both natural ressources and in more general terms all kind of information with a spatial dimension associated to it.
+Over the last decades, GIS has become a key driver in geospatial science, research and application.
 
-Over the last decades, GIS has become a key driver in geospatial science, research and application.
-GIS software which is licensed under a free and open source software (FOSS) licence
-is more than just a mere tool for spatial analysis.
+GIS software which is licensed under a free and open source software (FOSS) licence is more than just a mere tool for spatial analysis.
+FOSS GIS projects are maintained and continuously extended by international communities of volunteers, based on freely publicly available code base.
+Immediate access to this software repository enables instant quality checking of the current software version both by continuous automated tests, and code review by human experts.
+FOSS GIS project communities include members from many fields of Science and Industry, which leads to a many-faceted review process for incoming software submissions to the project code-base.
+Submitted code is evaluated in different software environments beyond the one originally used for development, in different fields of application beyond the field of expertise of the original authors, and different scales of magnitude for the data to be processed.
+This exceeds the established review process for scientific writing in a given journal or a data publication in a defined field of Science.
+FOSS GIS projects can serve as collaborative peer-reviewed environments to conduct verifiable science in a trusted and transparent environment.
 
-GRASS GIS (Neteler et al., 2012 \cite{neteler2012grass}), a free and open source GIS,
-is used by many scientists directly or as a backend in other projects
-such as R or QGIS to perform geoprocessing tasks.
+GRASS GIS (Neteler et al., 2012 \cite{neteler2012grass}), a free and open source GIS, is used by many scientists directly or as a backend in other projects such as R or QGIS to perform geoprocessing tasks.
+Thus, a large number of current scientific geospatial computations already rely on quality and correct functionality of the software, as a means to assure the replicability of the scientific results.
+In addition, GRASS GIS provides added-value for new and ongoing research as a stable and reliable platform: New scientific algorithms can be developed against the reviewed functionalities already provided by the GRASS GIS codebase.
+This avoids unnecessary overhead by re-implementation, ensures quality by use of trusted components and allows reuse and long term preservation within the project software repository:   Integrating scientific algorithms into GRASS GIS helps to preserve reproducibility of scientific results over time as the original author designed it (Rocchini & Neteler, 2012 \cite{rocchini2012let}).
 
-Thanks to the user and developer community, submitted code is evaluated
-in different fields of application beyond
-the field of expertise of the original authors, and different scales of magnitude
-for the data to be processed.
-This exceeds the established review process for scientific writing in a given journal
-or a data publication in a defined field of science.
+Moreover, subsequent improvements are tracked in the source code versioning system and are immediately available to the public (Petras, 2014 \cite{Petras2014}).
+Thus, GRASS GIS acts as a repository of scientific peer-reviewed code and algorithm/knowledge hub for future generation of scientists.
 
-Immediate access to software repository enables instant quality checking
-of the current software version both by continuous automated tests (Petras, 2014 \cite{Petras2014}),
-and code review by human experts.
-
-New scientific algorithms can be developed against the reviewed functionalities
-already provided by the GRASS GIS codebase.
-This avoids unnecessary overhead by re-implementation,
-ensures quality by use of trusted components and allows reuse and long term preservation
-within the project software repository:
-Integrating scientific algorithms into GRASS GIS helps to preserve reproducibility
-of scientific results over time as the original author designed it
-(Rocchini \& Neteler, 2012 \cite{rocchini2012let}).
 }

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
new version of water box (based on the latest version of the abstract); whitespace to align bottom
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64955 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
+\vspace*{1cm}
+
 \begin{minipage}{0.5\linewidth}
@@
 \end{minipage}
+
+\vspace*{1cm}
+
 }
@@
 \block{\blocktitlewrap{Natural Hazards: Water, Floods and Erosion}}{
-GRASS GIS entails several modules that constitute the result of active research on 
-natural hazard. The \gmodule{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b}) 
-for overland flow under rainfall excess conditions was integrated into the Emergency 
+
+GRASS GIS entails several modules that constitute the result of active research on natural hazard.
+The \gmodule{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b})
+for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
 Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}).
-It was also modified by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of a 
-specialised software called \textit{Tangible Landscape} (previously \textit{Tangible GIS}), which also 
-incorporated the \gamodule{r.damflood} module.\newline\linebreak
+The module \gmodule{r.sim.water} together with
+the module \gmodule{r.sim.sediment} for erosion-deposition modeling
+implements path sampling algorithm which is robust and easy to parallelize.
+The \gmodule{r.sim.water} module was also utilized by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of
+\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
+a dam break inundation simulation \cite{cannata2012two}.
+
+\bigskip
+
+\vspace*{1cm}
 
@@
 \end{minipage}
+~
 \begin{minipage}{0.5\linewidth}
@@
 \end{minipage}
+
+\vspace*{1.4cm}
 }
@@
 in space and time.
-\newline
+
+\bigskip
+
+\vspace*{1cm}
 
@@
 
+\bigskip
+
 To address this new experimental requirement, a distributed computing framework was 
@@
 research.
+
+\vspace*{0.6cm}
+
 }

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64957 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
@@
 \block{\blocktitlewrap{Spatial interpolation}}{
-The module v.surf.rst for spatial interpolation was developed approximately 12 years 
+The module \gmodule{v.surf.rst} for spatial interpolation was developed approximately 20 years
 ago, since then it was improved several times (Trac2, 2014). It is now an important part
@@
 \includegraphics[width=\textwidth]{interpolation_precip_vvolrst}
-Precipitation interpolated from meteorological stations in 3D space using \gmodule{v.vol.rst} in the area of North Carolina mountains (USA)
+Precipitation interpolated from meteorological stations in 3D space
+using \gmodule{v.vol.rst} in the area of North Carolina mountains (USA)
 \end{minipage}
@@
 \includegraphics[width=\textwidth]{elevation_lidar}
-Digital elevation model interpolated from LiDAR point clouds using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
+Digital elevation model interpolated from LiDAR point clouds
+using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
 \end{minipage}

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
add TIB logo to posters
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64959 15284696-431f-4ddb-bdfa-cd5b030d7da7
2015_EGU_G7_PeerReview_SciPlatform poster: highlights tuned; bibtex fix
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64960 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \newlength{\instlogoheight}
-\setlength{\instlogoheight}{0.45\grasslogoheight}
+\setlength{\instlogoheight}{0.35\grasslogoheight}
 
@@
 \includegraphics[height=\instlogoheight]{ec_jrc}
+~
+\includegraphics[height=\instlogoheight]{tib}
 \end{flushright}
@@
 \medskip
-Landuse classes and derived landscape diversity according to Shannon index in near Charlotte (North Carolina, USA).
+Landuse classes and derived landscape diversity according to Shannon index in near Charlotte (NC, USA)
 % r.diversity input=development_2006 prefix=diversity alpha=0.5 size=65
@@
 \begin{itemize}
- \item Algorithms and models once included into GRASS GIS remain available long term.
- \item GRASS GIS development team takes care of API related updates and operating system related changes.
-%% TODO: what does that mean?:
- \item Scientists are using highly specialized tools implemented by other people when having both scientific publication and source code at hand.
- \item New research and tools is build upon the existing one.
+ \item Algorithms and models, included into GRASS GIS remain long term available (already for 30 years).
+ \item The GRASS GIS development team takes care of API and operating system related changes. % in the provided contributions.
+ \item Scientists can use highly specialized tools implemented by others because of having both scientific publications and source code at hand.
+ \item The long term preservation of knowledge allows scientists to build new research and tools upon existing know-how.
 \end{itemize}

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
2015_EGU_G7_PeerReview_SciPlatform poster: fire Europe img added + caption (to be shortened) (provided by M Di Leo)
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64961 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \begin{minipage}{0.5\linewidth}
-%\includegraphics[width=\textwidth]{fire}
-% TODO: Something from Europe
+\includegraphics[width=\textwidth]{fire_valencia_040914}
+(Figure after Di Leo et al.
+2013).
+The event in the figure refers to a major wildfire occurred near Valencia on June 28th 2012 and was under control on July 4th.
+The case study is based on a Semantic Array Programming (SemAP) application of the Dynamic Data Driven Application Systems (DDDAS) concept.
+The case study is based on a new architecture for adaptive and robust modelling of wildfire behaviour.
+It focuses on the module for simulating wildfire dynamics under fire control scenarios.
+Uncertainty is assessed by ensembling an array of simulations which consider the uncertainty in meteorology, fuel, software modules.
+To illustrate, simplistic fire control scenarios are shown: low wetting (top); mid-low wetting (middle) and mid-high wetting (bottom). Interpolation
+driven uncertainty (IDU) is also assessed. Meteorological forecasts have been spatially disaggregated by either imposing local average invariance (LAI) (left) or not (usual non-LAI disaggregation).
 \end{minipage}

### 2015-03-31 grassposter/2015_EGU_G7_Python/main.tex
increase logo sizes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64951 15284696-431f-4ddb-bdfa-cd5b030d7da7
add TIB logo to posters
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64959 15284696-431f-4ddb-bdfa-cd5b030d7da7
finish testing box, improve highlights
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64962 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \instlist{6}Research and Innovation Centre, Fondazione Edmund Mach, San Michele all'Adige, Italy,
-\instlist{7}German National Library for Science and Technology, Hanover, Germany
+\instlist{7}TIB Hannover - German National Library of Science and Technology, Hanover, Germany
 }
@@
 
+\newlength{\logowidth}
+
 \makeatletter
@@
 
-       \newcommand{\logowidth}{0.17\textwidth}
+       \setlength{\logowidth}{0.17\textwidth}
        \newcommand{\logovspace}{\vspace{3ex}}
@@
 
-       \includegraphics[width=\logowidth]{ncstate}
+       \includegraphics[width=1.6\logowidth]{ncstate}
        \logohspace
@@
        \logovspace
-       % TODO: TICSA logo (Soeren)
-       \includegraphics[width=\logowidth]{ti}
+       \includegraphics[width=2\logowidth]{ti}
        \logohspace
-       \includegraphics[width=\logowidth]{ctu_prague}
+       \includegraphics[width=1.2\logowidth]{ctu_prague}
        \logohspace
-       \includegraphics[width=\logowidth]{eurac}
+       \includegraphics[width=2\logowidth]{eurac}
 
@@
 
-       \includegraphics[width=\logowidth]{fem_cri}
+       \includegraphics[width=1.5\logowidth]{fem_cri}
        \logohspace
-       % TODO: GNLST logo (Peter)
-       \includegraphics[width=\logowidth]{ncstate}
+       \includegraphics[width=3\logowidth]{tib}
     \end{minipage}%
@@
 \item GRASS GIS \cite{Neteler2012} is a platform for geospatial computations.
-\item GRASS GIS used directly using Python or GUI or through other software such as QGIS or R.
-\item GRASS GIS ecosystem supports code maintenance.
+% \item GRASS GIS used directly using Python or GUI or through other software.
 \item The functionality is divided into set of modules (individual tools, functions, algorithms or models).
 \item Core libraries and algorithms implemented in C for high performance.
-\item The system together with the broad community ensures long term preservation of algorithms.
+\item Python APIs for GRASS GIS are an interface for both the modules and the library.
+\item Standardization of inputs and interface serves as a tool for integration a sharing.
+\item Other Python tools such as NumPy or IPython can be used together with GRASS GIS.
+% \item The system together with the broad community ensures long term preservation of algorithms.
+% \item GRASS GIS ecosystem supports code maintenance.
 % \end{itemize}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth, clip, trim=0 120 0 0]{ipython_nb}
+	\includegraphics[width=0.95\linewidth, clip, trim=0 145 0 0]{ipython_nb}
 }
@@
 \block{\blocktitlewrap{Testing the code}}{
-\cite{Petras2014}
+% To facilitate the development of the module, GRASS GIS provides
+% a Python library for testing (Petras and Gebbert, 2014)
+% which helps researchers to ensure the robustness of the
+% algorithm, correctness of the results in edge cases
+% as well as the detection of changes in results due to new
+% development.
+
+To show that all promised functionality is available and algorithm works as expected
+every module should be supplied with a test.
+This also ensures that functionality
+can be simply tested any time in the future \cite{Petras2014}.
+
+\includegraphics[width=\linewidth, clip, trim=0 5 0 0]{gunittest}
+
+% Tests can be written to check the numerical results but also general functionality
+% such as if different parameters are accepted.
+Tests can use standardize datasets or use custom reference data.
+Basic tests can also just look at the statistical summary of a result.
 }

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
caption corrected
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64963 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
@@
 \begin{minipage}{0.5\linewidth}
-%\includegraphics[width=\textwidth]{fire}
-% TODO: Something from Europe
+\includegraphics[width=\textwidth]{fire_valencia_040914}
+The event in the figure refers to a major wildfire occurred near Valencia on June 28th 2012 and 
+under control on July 4th. The actual perimeters recorded by the JRC-EFFIS team are shown, in 
+comparison with the simulated burnt area obtained in GRASS.
 \end{minipage}

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
2015_EGU_G7_PeerReview_SciPlatform poster: better layout for fire fig + caption
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64964 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
@@
 
+\vspace*{-1cm}
+
 \begin{minipage}{0.5\linewidth}
-\includegraphics{fire}
+\includegraphics[width=\textwidth]{fire}
 Wildfire simulation in Tangible Landscape environment
 \end{minipage}
-
+~
 \begin{minipage}{0.5\linewidth}
-%\includegraphics[width=\textwidth]{fire}
-% TODO: Something from Europe
+\includegraphics[width=\textwidth]{fire_valencia_040914}
+Major wildfire event near Valencia (Spain) between June 28th and July 4th 2012.
+The actual perimeters recorded by JRC-EFFIS shown, in 
+comparison with burnt area simulated in GRASS GIS.
 \end{minipage}

### 2015-04-01 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
make space for fire box
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64965 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth, trim={0 0 0 125}, clip]{geomorphon}
+\includegraphics[width=\textwidth, trim={0 0 0 185}, clip]{geomorphon}
 Geomorphons for part of Yakima Training Center (area 5x3~km, USA)
@@
 \begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{geomorphon_tangible_high_tatras}
+\includegraphics[width=\textwidth, trim={0 30 0 90}, clip]{geomorphon_tangible_high_tatras}
 Ridges and valleys detected on the sand physical model of High Tatras (Slovakia) using \gamodule{r.geomorphon} integrated in Tangible Landscape system

### 2015-04-01 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
add references to Trac for r.li and v.surf.rst, make space for them
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64966 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \newcommand{\gamodule}[1]{\href{http://grass.osgeo.org/grass70/manuals/addons/#1.html}{\emph{#1}}}
+\newcommand{\gmodulenolink}[1]{\emph{#1}}
 
@@
 The module \gmodule{v.surf.rst} for spatial interpolation was developed approximately 20 years
-ago, since then it was improved several times (Trac2, 2014). It is now an important part
+ago, since then it was improved several times \cite{tracvsurfrst}. It is now an important part
 of GRASS GIS and is even taught at geospatial modeling courses, for example at North Carolina State University
@@
 A set of modules for multiscale analysis of landscape structure was added in 1992 
-by Baker et al. \cite{baker1992r}, who developed the r.le model similar to 
+by Baker et al. \cite{baker1992r}, who developed the \gmodulenolink{r.le} model similar to 
 FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
 improved to become \gmodule{r.li} in 2006. Further development continued, with a significant 
-speed up (Trac1, 2014) and new interactive user interface.
+speed up \cite{tracrli} and new interactive user interface.
 Rocchini et al. \cite{rocchini2013calculating} used \gmodule{r.li} modules to implement
@@
 \block{\blocktitlewrap{References and Acknowledgements}}{
+\vspace{-0.8cm}
+
 \scriptsize
@@
 
+\vspace{-0.2cm}
+
 \textcolor{gray}{
@@
 }
-% \vspace{-5pt}
+
+\vspace{-0.1cm}
 
@@
 
+\vspace{-0.8cm}
 }

### 2015-04-01 grassposter/2015_EGU_G7_Python/listings/pygrass_raster_examples.tex
rewrite Highlights, parser box, IPython box, revert temporal box to https://trac.osgeo.org/grass/changeset/64917 and other improvements
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64967 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
             new.put_row(newrow)  # write row to raster map
+# note that there is a specialized package which implements this functionality
 \end{lstlisting}

### 2015-04-01 grassposter/2015_EGU_G7_Python/main.tex
rewrite Highlights, parser box, IPython box, revert temporal box to https://trac.osgeo.org/grass/changeset/64917 and other improvements
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64967 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 % \begin{itemize}
-\renewcommand{\item}{\par\vspace{0.8ex}}
+\renewcommand{\item}{\par\vspace{0.9ex}}
 \item GRASS GIS \cite{Neteler2012} is a platform for geospatial computations.
 % \item GRASS GIS used directly using Python or GUI or through other software.
-\item The functionality is divided into set of modules (individual tools, functions, algorithms or models).
+\item The functionality is divided into a set of modules (individual tools, functions, algorithms or models).
 \item Core libraries and algorithms implemented in C for high performance.
-\item Python APIs for GRASS GIS are an interface for both the modules and the library.
-\item Standardization of inputs and interface serves as a tool for integration a sharing.
-\item Other Python tools such as NumPy or IPython can be used together with GRASS GIS.
+\item Both the modules and the libraries are accessible through the Python API.
+\item Specialized Python APIs support different use cases ranging from high level scripting to fine data editing.
+\item It is simple to build graphical user interface.
+\item NumPy or IPython can be used together with GRASS GIS Python APIs.
 % \item The system together with the broad community ensures long term preservation of algorithms.
@@
 
-The g.parser module provides full parser support for GRASS GIS scripts.
-It provides the creation of help page template, and command line option
-checking. Each command and scripts which uses the GRASS GIS parser can
-publish its parameter and flags description in XML. Through the included
-XML parser this description can be turned into a graphical user interface with
-standardized styling.
+The \gmodule{g.parser} module provides full interface definition support for Python scripts
+including creation of standardized part of a help page and command line checking.
+Each script which uses the GRASS GIS parser can
+publish definition of its parameters (options and flags) in XML.
+The GRASS GIS graphical user interface is able to use the XML
+to dynamically generate an interactive graphical dialog with unified styling.
+
+\bigskip
 
@@
 \includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{grass_module_gui}
+~
 \includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{grass_module_cli}
@@
 
-\block{\blocktitlewrap{GRASS Scripting library interface to GRASS GIS modules}}{
+\block{\blocktitlewrap{GRASS Scripting Library interface to GRASS GIS modules}}{
 
@@
 
-Documentation of GRASS GIS modules usually use Bash syntax for examples:
+Documentation of GRASS GIS modules usually use Bash syntax to provide an example of usage, e.g.:
 
@@
 
-These can be easily rewritten to \pkg{grass.script} or \pkg{grass.pygrass} syntax shown above.
+This syntax can be easily rewritten to the \pkg{grass.script} syntax or the \pkg{grass.pygrass} syntax shown above.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Using IPython Notebook}}{
+\block{\blocktitlewrap{IPython Notebook}}{
 
-	IPython Notebook is a web-based application that provides a tool to: developing, documenting, and executing code, as well as communicating the results.
-	One great tool to process and visualize your data/maps, integrating formulas and explanatory text, interacting with remote server and clusters.
+IPython Notebook is a web-based tool to develop, document, and execute code, as well as communicate the results.
+In combination with GRASS GIS, it is an excellent tool to process and visualize your geospatial data,
+integrate formulas, explanatory text and maps, and interact with remote servers and clusters.
 
@@
 \block{\blocktitlewrap{PyGRASS interface to C libraries}}{
-Some API examples to convert a raster map to a NumPy array and then back to a raster.
+Examples of using the API to convert a raster map to a NumPy array and back to raster:
 
-\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_raster_examples}
+\includegraphics[width=\linewidth, clip, trim=0 8 0 0]{pygrass_raster_examples}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Testing the code}}{
+\block{\blocktitlewrap{Testing the algorithms}}{
 % To facilitate the development of the module, GRASS GIS provides
@@
 
-\includegraphics[width=\linewidth, clip, trim=0 5 0 0]{gunittest}
+\includegraphics[width=\linewidth, clip, trim=0 8 0 0]{gunittest}
 
@@
 Tests can use standardize datasets or use custom reference data.
-Basic tests can also just look at the statistical summary of a result.
+It is very easy to write a sophisticated test just by checking a statistical summary of computation results.
 }
@@
 \block{\blocktitlewrap{GRASS GIS modules, addons and Python scripts}}{
-A Python script can by turned into a GRASS GIS modules by adding a definition of the interface.
-Also, GRASS GIS modules expect to be executed in GRASS GIS session.
+A Python script can by turned into a GRASS GIS module by adding a definition of the interface
+using GRASS GIS parser mechanism.
+Another difference is that GRASS GIS modules expect to be executed in GRASS GIS session.
 Python scripts which are using GRASS GIS can be written in a way that GRASS GIS session is not required;
-the setup of a necessary environment is done in the script itself.
+the setup of a necessary environment is done in the script itself in this case.
 % running code from IDE
 
-The GRASS GIS Addon repository ensures vendor-independent long-term preservation of the code
+The GRASS GIS Addon repository contains modules from wide range of contributors
+and ensures vendor-independent long-term preservation of the code
 and ensures an easy distribution of module to individual users.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{GRASS GIS 7 Temporal Framework}}{
-The GRASS GIS Temporal Framework offers the temporal GIS functionality of GRASS GIS 
+\block{\blocktitlewrap{GRASS GIS Temporal Framework}}{
+The GRASS GIS Temporal Framework implements the temporal GIS functionality
 and provides a Python API to implement spatio-temporal processing modules.
 The framework introduces space-time datasets that represent time series of raster,
-3D raster or vector maps. Some API examples:
+3D raster or vector maps.
+An API example:
 \includegraphics[width=1\linewidth, clip, trim=0 0 0 0]{tgrass_examples}
@@
 GRASS GIS is a OSGeo project. OSGeo provides infrastructure for project
-Web sites, mailing lists and source code management.
+websites, mailing lists and source code management.
 \end{minipage}
@@
 \begin{minipage}{\listtextwidth}
-Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code 2014.
+Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code 2012 and 2014.
 \end{minipage}

### 2015-04-01 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
modified references manually
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64968 15284696-431f-4ddb-bdfa-cd5b030d7da7
modified alignment of lower right box bottom
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64969 15284696-431f-4ddb-bdfa-cd5b030d7da7
Proof read by Tracy Durrant (Thank you)
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64972 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 the field of expertise of the original authors, and different scales of magnitude
-for the data to be processed.
+of data.
 This exceeds the established review process for scientific writing in a given journal
@@
 
-Immediate access to software repository enables instant quality checking
+Immediate access to the software repository enables instant quality checking
 of the current software version both by continuous automated tests (Petras, 2014 \cite{Petras2014}),
@@
 already provided by the GRASS GIS codebase.
-This avoids unnecessary overhead by re-implementation,
+This avoids unnecessary overheads, by re-implementation,
 ensures quality by use of trusted components and allows reuse and long term preservation
-within the project software repository:
+within the project software repository.
 Integrating scientific algorithms into GRASS GIS helps to preserve reproducibility
@@
 implements Rothermel’s model~\cite{Rothermel1983how}. It is available through the GRASS GIS 
-modules \gmodule{r.ros} and \gmodule{r.spread} and object of active research. It has been extensively 
+modules \gmodule{r.ros} and \gmodule{r.spread} and is object of active research. It has been extensively 
 tested and recently adapted to European fuel types (Rodriguez-Aseretto et al.,
@@
 Major wildfire event near Valencia (Spain) between June 28th and July 4th 2012.
-The actual perimeters recorded by JRC-EFFIS shown, in 
+The actual perimeters recorded by JRC-EFFIS are shown, in 
 comparison with burnt area simulated in GRASS GIS.
@@
 Based on the GRASS GIS Temporal Framework, more than 45 modules were implemented to manage, analyze, process
-and visualize space time datasets. The temporal enabled GRASS GIS is capable to efficiently
-handle more than 100,000 map layers. E.g., it was used to analyze the
+and visualize space time datasets. The temporal enabled GRASS GIS is capable of efficiently
+handling more than 100,000 map layers; e.g., it was used to analyze the
 European Climate Assessment \& Dataset ECA\&D (Haylock et al. \cite{Haylock2008_climate_series})
@@
 
-GRASS GIS entails several modules that constitute the result of active research on natural hazard.
+GRASS GIS entails several modules that constitute the result of active research on natural hazards.
 The \gmodule{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b})
@@
 the module \gmodule{r.sim.sediment} for erosion-deposition modeling
-implements path sampling algorithm which is robust and easy to parallelize.
+implements a path sampling algorithm which is robust and easy to parallelize.
 The \gmodule{r.sim.water} module was also utilized by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of
@@
 The module \gmodule{v.surf.rst} for spatial interpolation was developed approximately 20 years
-ago, since then it was improved several times \cite{tracvsurfrst}. It is now an important part
+ago, since then it has been improved several times (Trac2, 2014). It is now an important part
 of GRASS GIS and is even taught at geospatial modeling courses, for example at North Carolina State University
@@
 With the various types of actual ET models being developed in the last 20 years, 
-it becomes necessary to inter-compare methods. Most of already published ETa models 
-comparisons address few number of models, and small to medium areas 
+it becomes necessary to inter-compare methods. Most already published ETa model 
+comparisons address a low number of models, and small to medium areas 
 (Chemin, 2014 \cite{chemin2012distributed}; Gao and Long, 2008 \cite{gao2008intercomparison}; 
@@
 The architecture design was built from original satellite datasets to various levels 
-of processing until reaching the requirement of various ETa models input dataset. 
+of processing until reaching the input dataset requirements of various ETa models. 
 Each input product is computed once and reused in all ETa models requiring such input. 
 This permits standardization of inputs as much as possible to zero-in variations of 
-models to the models internals/specificities. All of the ET models are available in the 
+models to the models internals/specificities. % can this sentence be rephrased 
+All of the ET models are available in the 
 new GRASS GIS version 7 as imagery modules and replicability is complete for future 
@@
 improved to become \gmodule{r.li} in 2006. Further development continued, with a significant 
-speed up \cite{tracrli} and new interactive user interface.
+increase in speed \cite{tracrli} and a new interactive user interface.
 Rocchini et al. \cite{rocchini2013calculating} used \gmodule{r.li} modules to implement
@@
 \begin{itemize}
- \item Algorithms and models, included into GRASS GIS remain long term available (already for 30 years).
+ \item Algorithms and models, included in GRASS GIS remain available long term (already for 30 years).
  \item The GRASS GIS development team takes care of API and operating system related changes. % in the provided contributions.
- \item Scientists can use highly specialized tools implemented by others because of having both scientific publications and source code at hand.
+ \item Scientists can use highly specialized tools implemented by others as a result of having both scientific publications and source code at hand.
  \item The long term preservation of knowledge allows scientists to build new research and tools upon existing know-how.
@@
 \block{\blocktitlewrap{References and Acknowledgements}}{
-\vspace{-0.8cm}
+\vspace{0.2cm}
 
@@
 
-\vspace{-0.8cm}
+\vspace{0.4cm}
 }

### 2015-04-01 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
put back reference removed in https://trac.osgeo.org/grass/changeset/64972
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64973 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 The module \gmodule{v.surf.rst} for spatial interpolation was developed approximately 20 years
-ago, since then it has been improved several times (Trac2, 2014). It is now an important part
+ago, since then it has been improved several times \cite{tracvsurfrst}. It is now an important part
 of GRASS GIS and is even taught at geospatial modeling courses, for example at North Carolina State University

### 2015-04-06 grassposter/2015_EGU_WD_Ethiopia/poster.tex
remove czech babel which is not needed
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64939 15284696-431f-4ddb-bdfa-cd5b030d7da7
use standard block command for References
This changes its width from the custom size to the standard column width.


git-svn-id: https://svn.osgeo.org/grass/grass-promo@64940 15284696-431f-4ddb-bdfa-cd5b030d7da7
Fixed typos, English, readbility
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64995 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 % x-coordinate by specifying explicitly the coordinate of the new block node as follows:
-\usepackage[czech]{babel}
 \usepackage[utf8]{inputenc}
@@
 During the survey fieldwork the team also took photographs electronically stamped with GPS coordinates to compare and contrast the views of informants and the remote sensing information with high resolution images of the landscape.\newline\linebreak
-We found that farmers perspective on the Spring maize crop sensibility to variability of rainfall can be quantified in space and time by remote sensing cumulative transpiration.
+We found that farmers perspective on the Spring maize crop sensitivity to variability of rainfall can be quantified in space and time by remote sensing cumulative transpiration.
 A crop transpiration gap of 1-2.5 mm/day for about 20 days is to be overcome, a full amount of 20 to 50 mm, depending on the type of year deficit.
@@
 	&
-	The transpiration data is created from energy balance modelling \citep{chemin2012distributed} modules (i.eb.*, i.evapo.*) within GRASS GIS \cite{neteler2012grass} version 7, by partitioning the net radiation (r.sun) into soil heat flux (i.eb.soilheatflux), sensible heat flux (i.eb.h\_*) and the residual being the energy needed to evaporate water (i.eb.evapfr, i.eb.eta).
+	The transpiration data in the administrative unit of Fogera (woreda) is created from the energy balance modelling \citep{chemin2012distributed} modules (i.eb.*, i.evapo.*) within GRASS GIS \cite{neteler2012grass} version 7, by partitioning the net radiation (r.sun) into soil heat flux (i.eb.soilheatflux), sensible heat flux (i.eb.h\_*) and the residual being the energy needed to evaporate water (i.eb.evapfr, i.eb.eta).
 This information is then fractionated into biotic (transpiration) and abiotic (evaporation) parts using vegetation fraction.\newline\linebreak
@@
 The wet season crop calendar, i.e.
-planting and harvesting, starts in May and ends by December, depending on the type of crop (see Table 1).\newline\linebreak
+planting and harvesting, starts in May (Blue squares) and ends by December (Red squares), depending on the type of crop (see Table 1).
 \begin{center}
+Table 1: Crop calendar for Fogera woreda.\newline
 \includegraphics[width=0.6\textwidth]{./images/table1}
@@
 Farmers in upland Fogera associate the failure of the May rains with “drought”.
-For instance, a male farmer stated that, “When it is drought, it is the season of millet (teff).” A female farmer stressed this seasonal scarcity in water availability by insisting that “It is this drought that hinders crop production.” However, if the rain fails in May, it does not necessarily represent an inevitable drought year, in that rain can be available in the subsequent months.
+For instance, a male farmer stated that, “When it is drought, it is the season of millet \& teff.” A female farmer stressed this seasonal scarcity in water availability by insisting that “It is this drought that hinders crop production.” However, if the rain fails in May, it does not necessarily represent an inevitable drought year, in that rain can be available in the subsequent months.
 Nevertheless, rainfed maize and millet planting in May is a central concern as it provides food and fodder for season, buffering household food security and reducing stress on further crop-related decision-making.\newline\linebreak
 Rainfall variability has been one of the important factors impeding sustained implementation of intensification strategies, and particularly the use of fertilisers.
-Key informants indicated that rainfall variability has been discouraging the use of fertiliser due to risk of unsuccessful crop production which exacerbates farmers’ indebtedness besides losing production.i\newline\linebreak
+Key informants indicated that rainfall variability has been discouraging the use of fertiliser due to risk of unsuccessful crop production which exacerbates farmers’ indebtedness besides losing production.\newline\linebreak
 Vulnerability and capacity to respond to rainfall variability differs depending on individual natural, financial and social assets, as well as gender and socio-cultural variables.
-Farmers in Fogera have been attempting to respond to problems related to water availability based on adaptation, indigenous knowledge, practicing available options.
-Responses undertaken by individual farmers and communities include: adjusting planting times and cropping pattern; deploying traditional ecological knowledge of soil to mitigate risk associated with water availability, expanding traditional and motor-pump irrigation \citep{dessalegn2014is}; and sponsoring religious figures to ameliorate the violation of spiritual sanctions that are transgressed in contemporary agricultural production.\newline\linebreak
+Farmers in Fogera have been attempting to respond to problems related to water availability based on adaptation, indigenous knowledge, practicing available options.\newline\linebreak
+Responses undertaken by individual farmers and communities include: adjusting planting times and cropping pattern; deploying traditional ecological knowledge of soil to mitigate risk associated with water availability, expanding traditional and motor-pump irrigation \citep{dessalegn2014is}; and sponsoring religious figures to ameliorate the violation of spiritual sanctions that are transgressed in contemporary agricultural production.\newline
 }
@@
 Looking into the cumulative transpiration yearly signals (Figure 3), there is non uniformity, thus variations in water availability to vegetation.
-Following farmers' interviews and looking more closely into the April-June period, we found that in one case (figure 4), farmers perspective on the Spring maize crop sensibility to variability of rainfall can be quantified in space and time by remote sensing cumulative transpiration.
-A crop transpiration gap of 1-2.5 mm/day for about 20 days is to be overcome, a full amount of 20 to 50 mm, depending on the type of year deficit.
-Such gap can be overcome, even by temporary supplemental irrigation practices.\newline\linebreak
+Following farmers' interviews and looking more closely into the April-June period, we found that in one case (figure 4), farmers perspective on the Spring maize crop sensitivity to variability of rainfall can be quantified in space and time by remote sensing cumulative transpiration.
+We found that crops were not transpiring enough by an amount of 20 to 50 mm during a period of about 20 days, depending on the type of year.
+Averaged on a daily basis, this means a crop transpiration gap of 1-2.5 mm/day.
+Such gap is small and can be artifically provided by temporary supplemental irrigation practices for example.\newline\linebreak
 We argue that a better understanding of the dynamics of water variability and the implications on water management, agricultural production and livelihoods should consider small-holder farmers’ perceptions, concerns and responses.
@@
 
-\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
+\blocknode{References}{
 \small

### 2015-07-21 grassflyer/flyer1/en/grassflyer.tex
grass-promo flyer: update grass flyer
git-svn-id: https://svn.osgeo.org/grass/grass-promo@65735 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-GRASS (Geographic Resources Analysis Support System) is Free and Open Source Software for performing spatial analysis.
-It consists of more than 350 modules for processing vector (2D/3D), raster and voxel data.
-Many interfaces to other programs in related domains like geostatistics, databases, mapserver and even other GIS software exist.
-It is the largest Open Source GIS.
+GRASS GIS (Geographic Resources Analysis Support System) is Free and Open Source Software for performing spatial analysis.
+It consists of \textbf{more than 400 modules for processing vector (2D/3D), raster, voxel and temporal data (4D)}.
+Many interfaces to other programs in related domains like geostatistics, databases, map web services and even other GIS software exist.
+It is the oldest and largest Free and Open Source GIS.
 It can serve as a Desktop GIS and as the backbone of a complete GIS infrastructure.
@@
 
-GRASS is used in scientific applications, commercial settings and by public authorities all over the world.
-GRASS has shown strong potential for solving geospatial problems in numerous situations world-wide.
+GRASS GIS is used in scientific applications, commercial settings and by public authorities all over the world.
+GRASS GIS has shown strong potential for solving geospatial problems in numerous situations world-wide.
 
@@
 
-GRASS was originally developed in the early 1980's by the US Army Construction Engineering Research Laboratories (USA-CERL) and was published as public domain software.
-When the USA-CERL withdrew from GRASS development, an international developer team assumed responsibility for the task.
-Since 1999, GRASS has been published as free software under the terms of the GNU General Public Licence.
-\begin{myfig}[1.5ex]
-\includegraphics[width=0.7\textwidth]{visibility}
-\captionof{figure}{Viewshed analysis performed with GRASS}
+GRASS GIS was originally developed in the early 1980's by the US Army Construction Engineering Research Laboratories (USA-CERL) and was published as public domain software.
+When the USA-CERL withdrew from GRASS GIS development, an international developer team assumed responsibility for the task.
+Since 1999, GRASS GIS has been published as free software under the terms of the GNU General Public Licence.
+Several people during years contributed to improve the software, they helped to add new functionality, speedup existing modules, make \textbf{GRASS GIS easier, more useful and powerful to everybody}.
+\newline
+
+\begin{myfig}
+\includegraphics[width=0.8\textwidth]{isodist}
+\captionof{figure}{Default GUI configuration showing GRASS network analysis capabilites}
 \end{myfig}
 
-\section{Open Source Philosophy}
+\section{Free and Open Source Philosophy}
 
-The Open Source philosophy lets the user see the source code and structure of the program, which offers great transparency.
+The Free and Open Source philosophy lets the user see the source code and structure of the program, which offers great transparency.
 Users can extend the program for their own needs.
 Immediate source code peer review increases the quality.
-With the help of the extension manager, new modules can be created without GRASS package source code.
+With the help of the extension manager, new modules can be created without GRASS GIS package source code.
 
@@
 \begin{itemize}
-\item Modular
-\item Consists of more than 350 modules
+\item Modular commands
+\item Consists of more than 400 modules
 \end{itemize}
@@
 \item GRASS-SWIG interface
-\item Python for WebGIS applications
-\item Java Version: JGRASS
+\item Python API, scripting library and GUI
 \end{itemize}
@@
 \item Geostatistics (Interface to R)
+\item Temporal dataset
+\item WPS interface
 \end{itemize}
@@
 ASCII, ARC/GRID, E00, GIF, GMT, TIF, PNG, Vis5D, SURFER (.grd),\dots
-\begin{myfig}
-\includegraphics[width=0.7\textwidth]{isodist}
-\captionof{figure}{Default GUI configuration showing GRASS network analysis capabilites}
+\begin{myfig}[1.ex]
+\includegraphics[width=0.7\textwidth]{visibility}
+\captionof{figure}{Viewshed analysis performed with GRASS}
 \end{myfig}
@@
 
-CEOS (SAR, SRTM, LANDSAT7 etc.), ERDAS LAN / IMG, HDF, LANDSAT TM/MSS, NHAP aerial photos, SAR, SPOT, \dots
-\begin{myfig}[1.5ex]
-\includegraphics[width=0.7\textwidth]{ndvi}
-\captionof{figure}{Image processing options in GRASS}
+CEOS (SAR, SRTM, LANDSAT7 etc.), ERDAS LAN / IMG, HDF, LANDSAT TM/MSS, NHAP aerial photos, SAR, SPOT, MODIS \dots
+% \begin{myfig}[1.5ex]
+% \includegraphics[width=0.7\textwidth]{ndvi}
+% \captionof{figure}{Image processing options in GRASS}
+% \end{myfig}
+\begin{myfig}
+\includegraphics[width=0.7\textwidth]{mapswipe}
+\captionof{figure}{MapSwipe tool showing differences before and after Japan Tsunami 2011}
 \end{myfig}
@@
 \begin{itemize}
+\item SQLite
 \item PostgreSQL / PostGIS
 \item MySQL
-\item SQLite
 \item ODBC
@@
 \begin{itemize}
-\item Mapping modules
+\item Mapping modules (animation, cartographic \dots)
 \item NVIZ for visualization of 2.5D and 3D data (creation of animations \& flybys)
@@
 \item VTK, POVray
-\item WebGIS via Mapserver, Python, etc.
+\item Web Services
 \end{itemize}
@@
 \begin{itemize}
-\item Quantum GIS (Free geodata viewer and more)
+\item QGIS (Free geodata viewer and more)
 \item R-Language (Statistics)
 \item Gstat (Geostatistics)
-\item UMN Mapserver (Webmapping)
+\item UMN MapServer (Webmapping)
 \end{itemize}
@@
 \begin{itemize}
-%\begin{flushleft}
+% \begin{flushleft}
 \item{Project Website: \\\GRASSurl}
 \item{GRASS Wiki: \\\url{http://grass.osgeo.org/wiki}}
-\item{GRASS Promotion Team: \\\url{malte@perlomat.de}}
-\item{GRASS mailing lists: \\\url{http://grass.osgeo.org/community/support.php}}
-%\end{flushleft}
+% \item{GRASS Promotion Team: \\\url{malte@perlomat.de}}
+\item{GRASS mailing lists: \\\url{http://grass.osgeo.org/community}}
+% \end{flushleft}
 \end{itemize}
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{OSGeo_CMYK}\\
+\includegraphics[width=0.7\textwidth]{OSGeo_CMYK}\\
 \url{http://www.osgeo.org}

### 2017-02-17 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
promo: start How innovations thrive in GRASS GIS poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@70607 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2015-04-01 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
@@
 \fontsize{85}{60}\selectfont
-GRASS GIS: a peer-reviewed scientific platform and future research repository
+How innovations thrive in GRASS GIS
 }}
@@
     pdfsubject={},
-    pdftitle={GRASS GIS: a peer-reviewed scientific platform and future research repository},
+    pdftitle={How innovations thrive in GRASS GIS},
     pdfkeywords={GIS, algorithms, methods, preservation, science, reproducibility}
@@
 Each input product is computed once and reused in all ETa models requiring such input. 
-This permits standardization of inputs as much as possible to zero-in variations of 
-models to the models internals/specificities. % can this sentence be rephrased 
+This permits standardization of inputs as much as possible to reduce variations of 
+models to their own internals/specificities. % can this sentence be rephrased 
 All of the ET models are available in the 
@@
 \block{\blocktitlewrap{References and Acknowledgements}}{
-\vspace{0.2cm}
 
+\vspace{-0.2cm}
 \scriptsize
@@
 
-\vspace{0.4cm}
+\vspace{-0.08cm}
 }

### 2017-02-19 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
promo: GRASS GIS poster 2017: affiliation MN updated
git-svn-id: https://svn.osgeo.org/grass/grass-promo@70623 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \includegraphics[height=\instlogoheight]{eurac}
+%~
+%\includegraphics[height=\instlogoheight]{fem_cri} % history...
 ~
-\includegraphics[height=\instlogoheight]{fem_cri}
+\includegraphics[height=\instlogoheight]{mundialis_logo}
 ~
@@
 \instlist{5}EURAC, Italy;
-\instlist{6}CRI, FEM, Italy;
+\instlist{6}mundialis GmbH \& Co. KG, Germany;
 \instlist{7}TIB Hannover, Germany;
@@
 % GRASS module
-\newcommand{\gmodule}[1]{\href{http://grass.osgeo.org/grass70/manuals/#1.html}{\emph{#1}}}
-\newcommand{\gamodule}[1]{\href{http://grass.osgeo.org/grass70/manuals/addons/#1.html}{\emph{#1}}}
+\newcommand{\gmodule}[1]{\href{http://grass.osgeo.org/grass72/manuals/#1.html}{\emph{#1}}}
+\newcommand{\gamodule}[1]{\href{http://grass.osgeo.org/grass72/manuals/addons/#1.html}{\emph{#1}}}
 \newcommand{\gmodulenolink}[1]{\emph{#1}}

### 2017-02-20 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
add lidar, segmentation, topo, v.net, redo temporal, remove landforms, fire, interp, evapo
git-svn-id: https://svn.osgeo.org/grass/grass-promo@70638 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
-% EGU: http://meetingorganizer.copernicus.org/EGU2015/posters/17174
-%      http://meetingorganizer.copernicus.org/EGU2015/EGU2015-8314-7.pdf
-
 \documentclass[25pt, margin=0mm, innermargin=15mm, blockverticalspace=15mm, colspace=15mm, subcolspace=8mm]{tikzposter}
-\geometry{paperwidth=197cm,paperheight=100cm}
+\geometry{paperwidth=96in,paperheight=48in}
 
@@
 \includegraphics[height=\grasslogoheight]{grass}
-~
+\hspace{2em}
 \includegraphics[height=\grasslogoheight]{osgeo_project}
@@
 \hfill
-\begin{minipage}{0.2\linewidth}
+\begin{minipage}{0.15\linewidth}
 \setlength{\baselineskip}{120pt}
 \begin{flushright}
+\includegraphics[height=\instlogoheight]{ncstate}
+~
 \includegraphics[height=\instlogoheight]{iwmi}
-~
-\includegraphics[height=\instlogoheight]{ncstate}
 ~
@@
 \includegraphics[height=\instlogoheight]{eurac}
-%~
-%\includegraphics[height=\instlogoheight]{fem_cri} % history...
 ~
-\includegraphics[height=\instlogoheight]{mundialis_logo}
+\includegraphics[height=\instlogoheight]{mundialis}
+~
+\includegraphics[height=\instlogoheight]{fem_cri}
 ~
 \includegraphics[height=\instlogoheight]{ec_jrc}
-~
-\includegraphics[height=\instlogoheight]{tib}
 \end{flushright}
@@
 \author{
-Yann Chemin\inst{1},
-V\'{a}clav Petr\'{a}\v{s}\inst{2},
-Anna Petr\'{a}\v{s}ov\'{a}\inst{2},
+V\'{a}clav Petr\'{a}\v{s}\inst{1},
+Yann Chemin\inst{2},
 Martin Landa\inst{3},
+Thomas Leppelt\inst{4},
 S\"{o}ren Gebbert\inst{4},
@@
 Markus Neteler\inst{6},
-Peter L\"{o}we\inst{7}, and
+Luca Delucchi\inst{7}, and
 Margherita Di Leo\inst{8}
@@
 \institute{
-\instlist{1}IWMI, Sri Lanka;
-\instlist{2}NCSU, USA;
+\instlist{1}NCSU, USA;
+\instlist{2}IWMI, Sri Lanka;
 \instlist{3}FCE CTU in Prague, Czech Republic;
@@
 \instlist{6}mundialis GmbH \& Co. KG, Germany;
-\instlist{7}TIB Hannover, Germany;
+\instlist{7}CRI, FEM, Italy;
 \instlist{8}EC-JRC, Italy
@@
 {
-    pdfauthor={Y. Chemin, V. Petras, A. Petrasova, M. Landa, S. Gebbert, P. Zambelli, M. Neteler, P. Loewe, M. Di Leo},
+    pdfauthor={V. Petras, Y. Chemin, M. Landa, S. Gebbert, P. Zambelli, M. Neteler, M. Di Leo},
     pdfsubject={},
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Introduction}}
+\block{\blocktitlewrap{Highlights}}
 {
-\setlength{\parskip}{0.3ex}
+% \setlength{\parskip}{0.3ex}
 
-Over the last decades, GIS has become a key driver in geospatial science, research and application.
-GIS software which is licensed under a free and open source software (FOSS) licence
-is more than just a mere tool for spatial analysis.
+\renewcommand{\labelitemi}{\textcolor{gray}{$\bullet$}\hspace{0.5ex}}
 
-GRASS GIS (Neteler et al., 2012 \cite{neteler2012grass}), a free and open source GIS,
-is used by many scientists directly or as a backend in other projects
-such as R or QGIS to perform geoprocessing tasks.
+Poster topic highlights:
 
-Thanks to the user and developer community, submitted code is evaluated
-in different fields of application beyond
-the field of expertise of the original authors, and different scales of magnitude
-of data.
-This exceeds the established review process for scientific writing in a given journal
-or a data publication in a defined field of science.
+\begin{itemize}
+ \item Algorithms and models included in GRASS GIS remain available long term \citep{chemin2015grass}.
+ \item Analytical tools are not limited to one domain but spread across many fields.
+ \item New tools can be build based on functionality or code of the existing ones
+       regardless of the particular domain of problems they belong to.
+ \item Both the functionality and the code are evaluated
+       by the user and developer community in different fields of application beyond
+       the field of expertise of the original authors
+       and different scales of magnitude of data.
+% continuous automated tests (Petras, 2014 \cite{Petras2014}),
+\end{itemize}
 
-Immediate access to the software repository enables instant quality checking
-of the current software version both by continuous automated tests (Petras, 2014 \cite{Petras2014}),
-and code review by human experts.
+General GRASS GIS highlights:
 
-New scientific algorithms can be developed against the reviewed functionalities
-already provided by the GRASS GIS codebase.
-This avoids unnecessary overheads, by re-implementation,
-ensures quality by use of trusted components and allows reuse and long term preservation
-within the project software repository.
-Integrating scientific algorithms into GRASS GIS helps to preserve reproducibility
-of scientific results over time as the original author designed it
-(Rocchini \& Neteler, 2012 \cite{rocchini2012let}).
-}
+\begin{itemize}
+%  \item Community supports users and new developments through online
+%  \item long-term moving forward
+ \item The GRASS GIS development team takes care of interface and operating system related changes
+       in the code provided by scientists and contributors.
+ \item Cost estimated by Black Duck Open Hub is over \$30,000,000.
+ \item The free, libre and open source license used in GRASS GIS
+       not only allows users to reduce GIS software costs to minimum,
+       but also enables organizations to deploy cloud-based solutions without any license restrictions.
+ \item GRASS GIS is used both directly and as a backend in other projects
+       such as QGIS and R.
+\end{itemize}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Landform detection: Geomorphons}}{
-
-Jasiewicz and Stepinski \cite{jasiewicz2013geomorphons} developed a method and module \gamodule{r.geomorphon}
-which provide orientation-invariant and relief-invariant method to classify landforms
-in a scale-independent way.
-Ashtekar et al. \cite{ashtekar2014digital} used geomorphons to study soil properties in northwestern South America.
-
-\bigskip
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth, trim={0 0 0 185}, clip]{geomorphon}
-Geomorphons for part of Yakima Training Center (area 5x3~km, USA)
-\end{minipage}
-~
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth, trim={0 30 0 90}, clip]{geomorphon_tangible_high_tatras}
-Ridges and valleys detected on the sand physical model of High Tatras (Slovakia) using \gamodule{r.geomorphon} integrated in Tangible Landscape system
-\end{minipage}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Natural Hazards: Wildfire Spread}}{
-The wildfire simulation toolset, originally developed by Xu (1994~\cite{xu1994simulating}) 
-implements Rothermel’s model~\cite{Rothermel1983how}. It is available through the GRASS GIS 
-modules \gmodule{r.ros} and \gmodule{r.spread} and is object of active research. It has been extensively 
-tested and recently adapted to European fuel types (Rodriguez-Aseretto et al.,
-2013~\cite{rodriguez2013data}; de Rigo et al., 2013~\cite{derigo2013architecture};
-Di Leo et al., 2013~\cite{2013_DiLeo_etAl}).
-
-\vspace*{-1cm}
-
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{fire}
-Wildfire simulation in Tangible Landscape environment
-\end{minipage}
-~
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{fire_valencia_040914}
-Major wildfire event near Valencia (Spain) between June 28th and July 4th 2012.
-The actual perimeters recorded by JRC-EFFIS are shown, in 
-comparison with burnt area simulated in GRASS GIS.
-\end{minipage}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{GRASS GIS as Temporal GIS}}{
-The time dimension was introduced in GRASS GIS version 7 for raster, 3D raster and
-vector map layers, transforming it into a full featured temporal GIS (Gebbert and Pebesma, 2014 \cite{Gebbert20141}).
-Time series of map layers are managed in space time datasets, a new data type in GRASS GIS.
-Based on the GRASS GIS Temporal Framework, more than 45 modules were implemented to manage, analyze, process
-and visualize space time datasets. The temporal enabled GRASS GIS is capable of efficiently
-handling more than 100,000 map layers; e.g., it was used to analyze the
-European Climate Assessment \& Dataset ECA\&D (Haylock et al. \cite{Haylock2008_climate_series})
-for climate change indicators.
-
-\vspace*{1cm}
-
-\begin{minipage}{0.5\linewidth}
-\includegraphics[scale=0.5]{images/summer_mean_temp_slope.pdf}
-The linear regression slope computed with t.rast.series of the temperate climate zone in the European Union
-for summer season from 1950 - 2011 (Gebbert and Pebesma, 2014 \cite{Gebbert20141}). Red color
-indicates rising temperature, blue indicates falling temperature. Units are degree Celsius per year.
-\end{minipage}
-~
-\begin{minipage}{0.5\linewidth}
-\includegraphics[scale=1.25]{images/Seasonal_temperature_trend_Europe_1950_2010.pdf}
-Seasonal mean temperature trend for the temperate climate zone of the European Union
-(Gebbert and Pebesma, 2014 \cite{Gebbert20141}). The modules \gmodule{t.rast.aggregate},
-\gmodule{t.rast.univar} and the open source statistical software system R
-were used to create this plot.
-\end{minipage}
-
-\vspace*{1cm}
+% oholoh hours
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Natural Hazards: Water, Floods and Erosion}}{
+\block{\blocktitlewrap{Spatio-Temporal Data Analysis}}{
+The time dimension was introduced in GRASS GIS version 7 for vector maps, rasters, and 3D rasters
+which transformed GRASS GIS into a fully-featured temporal GIS \citep{Gebbert20141, gebbert2015grass}.
+Time series of map layers are managed in space time datasets, a new data type in GRASS GIS,
+and are still accessible also as individual map layers.
+Based on the GRASS GIS Temporal Framework Python application programming interface (API),
+more than 50 modules were implemented to manage, analyze, process
+and visualize space time datasets.
+More than 100,000 map layers can be now handled efficiently in GRASS GIS.
+Example usages of this functionality include
+analysis of the
+European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
+and temperate climate zone in the European Union identification \citep{Gebbert20141}.
 
-GRASS GIS entails several modules that constitute the result of active research on natural hazards.
-The \gmodule{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b})
-for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
-Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}).
-The module \gmodule{r.sim.water} together with
-the module \gmodule{r.sim.sediment} for erosion-deposition modeling
-implements a path sampling algorithm which is robust and easy to parallelize.
-The \gmodule{r.sim.water} module was also utilized by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of
-\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
-a dam break inundation simulation \cite{cannata2012two}.
-
-\bigskip
+The new temporal modules (staring with \gmodulenolink{t.})
+work beside well established \gmodule{r.series} module
+and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing}
+or \gamodule{r.seasons}.
+Latest addition includes raster and vector temporal algebra
+which can be used for tasks such as computing hydrothermal coefficient for a time series of climate data
+using the actual mathematical formula \citep{leppelt2015grass}.
 
@@
 
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{rsimwater_architects}
-Overland flow used for landscape architecture design in Tangible Landscape environment
-\end{minipage}
-~
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{damflood_tangible}
-Coal ash pond breach in Tangible Landscape environment using \gamodule{r.damflood} module
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=.7\linewidth]{images/temporal_precip_temp}
+\\
+Creating a synchronized animation of monthly total precipitation and mean temperature for NC, USA
 \end{minipage}
 
-\vspace*{1.4cm}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Spatial interpolation}}{
-The module \gmodule{v.surf.rst} for spatial interpolation was developed approximately 20 years
-ago, since then it has been improved several times \cite{tracvsurfrst}. It is now an important part
-of GRASS GIS and is even taught at geospatial modeling courses, for example at North Carolina State University
-\cite{ncsugis582}.
-
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{interpolation_precip_vvolrst}
-Precipitation interpolated from meteorological stations in 3D space
-using \gmodule{v.vol.rst} in the area of North Carolina mountains (USA)
-\end{minipage}
-~
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth]{elevation_lidar}
-Digital elevation model interpolated from LiDAR point clouds
-using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
-\end{minipage}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Evapotranspiration (ET)}}{
-With the various types of actual ET models being developed in the last 20 years, 
-it becomes necessary to inter-compare methods. Most already published ETa model 
-comparisons address a low number of models, and small to medium areas 
-(Chemin, 2014 \cite{chemin2012distributed}; Gao and Long, 2008 \cite{gao2008intercomparison}; 
-Garcia et al., 2007 \cite{garcia2007comparison}; Suleiman et al., 2008
-\cite{suleiman2008intercomparison}; Timmermans et al., 2007 \cite{timmermans2007intercomparison}). 
-With the large amount of remote sensing data covering the Earth, and the daily 
-information available for more than twelve years (i.e. Aqua/Terra-MODIS) for each pixel 
-location, it becomes paramount to have a more complete comparison, 
-in space and time.
-
-\bigskip
-
-\vspace*{1cm}
-
-\begin{minipage}{0.5\linewidth}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{TonleSapTa}
-\end{center}
-\end{minipage}
-~
-\begin{minipage}{0.5\linewidth}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{TonleSapTaGap}
-\end{center}
-\end{minipage}
-\vspace{2mm}
-\begin{center}
-Biological fraction of 2014 ET (cumul. mm/y) \& January average gap (mm/m), Tonle Sap, Cambodia.
-\end{center}
-
-\bigskip
-
-To address this new experimental requirement, a distributed computing framework was 
-designed and created (Chemin, 2012 \cite{chemin2012distributed}). 
-The architecture design was built from original satellite datasets to various levels 
-of processing until reaching the input dataset requirements of various ETa models. 
-Each input product is computed once and reused in all ETa models requiring such input. 
-This permits standardization of inputs as much as possible to reduce variations of 
-models to their own internals/specificities. % can this sentence be rephrased 
-All of the ET models are available in the 
-new GRASS GIS version 7 as imagery modules and replicability is complete for future 
-research.
-
-\vspace*{0.6cm}
+% \vspace*{1cm}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-\block{\blocktitlewrap{Landscape structure}}{
+\block{\blocktitlewrap{Landscape Structure}}{
 A set of modules for multiscale analysis of landscape structure was added in 1992
-by Baker et al. \cite{baker1992r}, who developed the \gmodulenolink{r.le} model similar to 
-FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
-improved to become \gmodule{r.li} in 2006. Further development continued, with a significant 
-increase in speed \cite{tracrli} and a new interactive user interface.
-Rocchini et al. \cite{rocchini2013calculating} used \gmodule{r.li} modules to implement
+by \cite{baker1992r}, who developed the \gmodulenolink{r.le} model similar to
+FRAGSTATS \citep{mcgarigal1995fragstats}.
+The modules were gradually improved to become \gmodule{r.li} in 2006.
+Further development continued, with a significant
+increase in speed \citep{tracrli} and a new interactive user interface.
+\cite{rocchini2013calculating} used \gmodule{r.li} modules to implement
 high level tool for calculating landscape diversity.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Water, Floods and Erosion}}{
+
+GRASS GIS entails several modules that constitute the result of active research on natural hazards.
+The \gmodule{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b})
+for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
+Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}).
+The module \gmodule{r.sim.water} together with
+the module \gmodule{r.sim.sediment} for erosion-deposition modeling
+implements a path sampling algorithm which is robust and easy to parallelize.
+The \gmodule{r.sim.water} module was also utilized by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of
+\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
+a dam break inundation simulation \cite{cannata2012two}.
+
+\bigskip
+
+\vspace*{1cm}
+
+\centering
+\begin{minipage}{0.65\linewidth}
+\centering
+\includegraphics[width=0.5\textwidth]{rsimwater_architects}
+\\
+Overland flow simulated by \gmodule{r.sim.water} used for landscape
+architecture design in Tangible Landscape environment
+(Historical master plan for Lake Raleigh, NC, USA)
+\end{minipage}
+~
+\begin{minipage}{0.5\linewidth}
+% TODO: damflood on Lake Raleigh
+% \includegraphics[width=\textwidth]{damflood_tangible}
+% Coal ash pond breach in Tangible Landscape environment using \gamodule{r.damflood} module
+\end{minipage}
+
+% \vspace*{1.4cm}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Lidar Data Processing}}{
+
+Filtering of ground and non-ground points was included into GRASS GIS
+early on in the lidar era in the \gmodule{v.lidar.edgedetection} group of modules.
+% TODO: ref
+% v.lidar.correction Corrects the v.lidar.growing output. It is the last of the three algorithms for LIDAR .
+% v.lidar.edgedetection Detects the object's edges from a LIDAR data set.
+% v.lidar.growing Building contour determination and Region Growing algorithm for determining the building inside
+The module \gmodule{v.surf.rst} for spatial interpolation was developed approximately 20 years
+ago, but since then it has been improved several times \cite{tracvsurfrst}
+including recent parallelization which will be included in GRASS GIS 7.4.
+Currently the module is used for both digital terrain model interpolation and interpolations in general.
+
+The module \gmodule{r.in.lidar} statistically analyzes massive point clouds.
+% TODO: base_raster, ref
+For advanced general point analysis GRASS GIS
+\gmodule{v.outlier} implemented originally specifically for lidar data
+and recently also \gmodule{v.cluster}
+implementing variety of clustering methods including
+DBSCAN (Density-Based Spatial Clustering of Applications with Noise)
+and OPTICS (Ordering Points to Identify the Clustering Structure).
+The \gmodule{v.outlier} module serves as a base for a user contributed module \gamodule{v.lidar.mcc}
+implementing MMC.
+% TODO: ref
+
+% v.delaunay v.voronoi New option to create Voronoi diagrams for areas.
+
+\centering
+\begin{minipage}{0.7\linewidth}
+\centering
+\includegraphics[width=0.5\textwidth]{elevation_lidar}
+\\
+Digital elevation model interpolated from LiDAR point clouds
+using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
+\end{minipage}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Conclusions}}{
+\block{\blocktitlewrap{Image Segmentations}}{
+\gamodule{r.smooth.seg} (formerly \gmodulenolink{r.seg})
+was created by Alfonso Vitti \citep{vitti2008free, vitti2012mumford}
+and implemented a piece-wise smooth approximation of the original image
+according to \cite{mumford1989optimal} and \cite{march1997variational}
+which can be used to reduce noise in the original image.
+This supplemented \gmodule{r.clump} available from 1980s
+which groups pixes with same categories (or integer values).
+The latest version of \gmodule{r.clump} coming in GRASS GIS 7.4
+supports multiple image bands (or any rasters maps) as input.
+Clumping of cells based on threshold value and clumping
+of double precision floating point input is supported as well in the new version.
 
-\renewcommand{\labelitemi}{\textcolor{gray}{$\bullet$}\hspace{0.5ex}}
+Eric Momsen implemented initial version of region-growing image segmentation in 2012
+and Markus Metz then extended and optimized the code resulting in
+the inclusion of the \gmodule{i.segment} module into GRASS GIS 7.0
+and final replacement of old multi-resolution classification module of the same name
+which was available in 1992 \citep{zhuang1992image}.
+Another module called \gamodule{i.segment.hierarchical} by Pietro Zambelli is based on \gmodule{i.segment}
+and performs parallelized hierarchical segmentation.
 
-% TODO: review the points, it should be the highlight or something like that
+In 2016 GRASS GIS implementation of SLIC Superpixels segmentation \citep{achanta2010epfl, achanta2012slic}
+was requested by the community
+and Rashad Kanavath and Markus Metz implemented \gmodule{i.superpixels.slic}
+which provides users both with SLIC and SLIC0 methods.
 
-\begin{itemize}
- \item Algorithms and models, included in GRASS GIS remain available long term (already for 30 years).
- \item The GRASS GIS development team takes care of API and operating system related changes. % in the provided contributions.
- \item Scientists can use highly specialized tools implemented by others as a result of having both scientific publications and source code at hand.
- \item The long term preservation of knowledge allows scientists to build new research and tools upon existing know-how.
-\end{itemize}
+\bigskip
+
+\vspace*{1cm}
+
+\begin{minipage}{0.5\linewidth}
+\begin{center}
+\includegraphics[width=\textwidth]{superpixels_slic_pseudo}
+\end{center}
+\end{minipage}
+~
+\begin{minipage}{0.5\linewidth}
+\begin{center}
+\includegraphics[width=\textwidth]{superpixels_slic_colored}
+\end{center}
+\end{minipage}
+\vspace{2mm}
+\begin{center}
+Superpixels (back outlines) on pseudo-color image of central Wake county, NC, USA (left)
+and same superpixels colored according to a mean NDVI value per pixel (right).
+\end{center}
+
+\vspace*{0.6cm}
+
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{References and Acknowledgements}}{
+\block{\blocktitlewrap{Topology, Cleaning, Overlays, Attributes}}{
+Besides basic vector analysis tools such as \gmodule{v.buffer}
+and \gmodule{v.overlay},
+% TODO: v.overlay: The processing speed has been substantially improved
+
+cleaning (also v.build error
+% + clustering + neighorhood + vector algebra
+
+v.feature.algebra (formerly v.mapcalc) replaced by Python for GRASS GIS C libraries (PyGRASS)
+
+Attribute processing and queries in GRASS GIS can take an advantage of latest developments
+in database management systems (DBMSs) as several DBMSs are supported most notably SQLite and PostgreSQL.
+
+Non-topological vector
+data are automatically converted to a topological representation upon import. Further more, various cleaning tools exist
+to remove non-trivial topological errors.
+
+The GRASS GIS 7 releases come with faster vector processing backend
+and more efficient internal vector format;
+both disk and memory requirements were reduced.
+The new spatial index performs queries faster (more than 10 times for large vectors compared to GRASS GIS 6).
+
+All topological cleaning tools have been optimized with regard to processing speed, robustness, and system
+requirements.
+
+Considering the wide spread usage of Esri Shapefile, a non-topological format for vector data exchange, it is particularly
+advantageous that GRASS GIS 7 offers advanced cleaning tools.
+
+postgis incl topo
+GRASS GIS 7 supports various data sources in read and write access. Beside native file-based raster and vector format
+GRASS allows to specify external data sources through GDAL/OGR library. GRASS GIS 7 also natively supports
+PostGIS database including its topological extension.
+
+In parallel to that native support the OGC Simple Features was added.
+
+\centering
+\begin{minipage}{0.9\linewidth}
+\begin{center}
+\includegraphics[width=.3\textwidth]{topo_original}
+~
+\includegraphics[width=.3\textwidth]{topo_errors}
+~
+\includegraphics[width=.3\textwidth]{topo_fixed}
+Original vector imported without cleaning (left),
+identified errors (middle),
+automatically topologically corrected vector (right)
+\end{center}
+\end{minipage}
+
+% v.in.ascii input= output=imported format=standard
+% v.build -e map=imported error=errors
+% v.clean -c input=imported output=clean error=cleaning_errors tool=snap,rmdangle,rmbridge,chbridge,bpol,prune threshold=5
+% d.vect map=cleaning_errors color=255:33:36 fill_color=none width=5 icon=basic/point size=30
+% d.vect map=imported color=56:16:108 fill_color=205:64:113 width=5
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Vector Network Analysis}}{
+All vector network analysis tools provide now fine control over node costs.
+
+\centering
+\begin{minipage}{0.5\linewidth}
+\begin{center}
+\includegraphics[width=\textwidth]{network}
+Shortest path between two points in the Wake County road network (NC, USA)
+\end{center}
+\end{minipage}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{References}}{
 
@@
 \renewcommand{\section}[2]{}%
-\bibliographystyle{plain}
+\bibliographystyle{apalike}
 \bibliography{poster}
 \endgroup
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Acknowledgements}}{
+
+\newcommand{\listhspace}{\hspace{0.005\linewidth}}
+\newcommand{\listlogowidth}{0.10\linewidth}
+\newcommand{\listtextwidth}{0.82\linewidth}
+
+\begin{minipage}{\listlogowidth}
+\includegraphics[width=\linewidth]{osgeo}
+\end{minipage}
+\listhspace
+\begin{minipage}{\listtextwidth}
+Open Source Geospatial Foundation (OSGeo)
+supports the collaborative development of open source geospatial software.
+GRASS GIS is a OSGeo project.
+OSGeo provides infrastructure for project
+websites, mailing lists and source code management.
+\end{minipage}
+
+\bigskip
+
+\begin{minipage}{\listlogowidth}
+\includegraphics[width=\linewidth]{google}
+\end{minipage}
+\listhspace
+\begin{minipage}{\listtextwidth}
+Initial development of \gmodule{i.segement} module as well as several other developments
+were done as a part of the Google Summer of Code project.
+Google provides financial support to students and organizations participating in the Google Summer of Code project.
+\end{minipage}
+
+\bigskip
+
+\vspace{0.2cm}
 
@@
 
-\blocksectiontitle{Acknowledgements}
-
-We acknowledge Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS} and
-% http://www4.ncsu.edu/~jcfounta/Summer14Posters/horvath.pdf
-Eva Stopkova for physical model of High Tatras.
-
-GRASS GIS project is a Open Source Geospatial Foundation (OSGeo) project and is using OSGeo infrastructure for Web site and code repository.
-
-\vspace{-0.2cm}
-
-\textcolor{gray}{
-\hrulefill
-}
-
-\vspace{-0.1cm}
+\vspace{0.1cm}
 
@@
 
-\begin{minipage}{\qrcodesize}
-\includegraphics[width=\textwidth]{./images/qr_grasswiki.pdf}
-\end{minipage}
-~
-\begin{minipage}{0.2\linewidth}
-\small {\href{http://grasswiki.osgeo.org}{\nolinkurl{grasswiki.osgeo.org}}}
-\end{minipage}
-
 \begin{minipage}{0.1\linewidth}

### 2017-02-20 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
text for topo and v.net blocks
git-svn-id: https://svn.osgeo.org/grass/grass-promo@70649 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 \documentclass[25pt, margin=0mm, innermargin=15mm, blockverticalspace=15mm, colspace=15mm, subcolspace=8mm]{tikzposter}
-\geometry{paperwidth=96in,paperheight=48in}
+\geometry{paperwidth=82in,paperheight=41in}
 
@@
  \item Cost estimated by Black Duck Open Hub is over \$30,000,000.
+ % https://www.openhub.net/p/grass_gis/estimated_cost
  \item The free, libre and open source license used in GRASS GIS
@@
 implements a path sampling algorithm which is robust and easy to parallelize.
+A unique least cost path algorithm which doesn't need any depression filling
+was implemented in \gmodule{r.watershed} module in 1989
+and it was updated for massive data sets in 2011.
+% TODO: refs
 The \gmodule{r.sim.water} module was also utilized by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of
@@
 \centering
-\begin{minipage}{0.7\linewidth}
+\begin{minipage}{0.48\linewidth}
 \centering
-\includegraphics[width=0.5\textwidth]{elevation_lidar}
-\\
+\includegraphics[width=0.7\textwidth]{elevation_lidar}
+\end{minipage}
+~
+\begin{minipage}{0.48\linewidth}
+\centering
+\includegraphics[width=\textwidth]{lidar_profile}
+\end{minipage}
+
+\bigskip
+
+\begin{minipage}{0.48\linewidth}
+\centering
 Digital elevation model interpolated from LiDAR point clouds
 using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
+\end{minipage}
+~
+\begin{minipage}{0.48\linewidth}
+\centering
+Profile (vertical slice) of a small portion of a point cloud showing tree structure as captured by the returns
 \end{minipage}
@@
 and \gmodule{v.overlay},
-% TODO: v.overlay: The processing speed has been substantially improved
+which has processing speed substantially improved in GRASS GIS 7.0,
+suite of functionality for topology checking and cleaning is available
+through \gmodule{v.build} and \gmodule{v.clean} modules.
+The vector cleaning tools are particularly advantageous considering the use of non-topological exchange formats.
+\gmodule{v.clean} module was introduced in 2002 and several different contributors
+extended its functionality with last large set of improvements included in GRASS GIS 7.0.
+For that release all topological cleaning tools have been optimized
+with regard to processing speed, robustness, and system requirements.
 
-cleaning (also v.build error
-% + clustering + neighorhood + vector algebra
-
-v.feature.algebra (formerly v.mapcalc) replaced by Python for GRASS GIS C libraries (PyGRASS)
+% + vector algebra
+An experimental module \gamodule{v.feature.algebra} (formerly \gmodulenolink{v.mapcalc}) from 2002
+% actually, the original by Radim Blazek (Jun 11, 2002) seems to be more similar to the current v.mapcalc
+% it was using Vect_overlay_str_to_operator Vect_overlay
+% it was replaced by code by Christoph Simon in Aug 7, 2002
+was replaced by Python for GRASS GIS C libraries (PyGRASS) in GRASS GIS 7.0.
+However, new \gamodule{v.mapcalc} module is available with richer syntax and functionality.
 
@@
 in database management systems (DBMSs) as several DBMSs are supported most notably SQLite and PostgreSQL.
-
-Non-topological vector
-data are automatically converted to a topological representation upon import. Further more, various cleaning tools exist
-to remove non-trivial topological errors.
+A PostGIS database can be connected including it geometry and topology.
+In parallel to that native support the OGC Simple Features is available.
 
@@
 The new spatial index performs queries faster (more than 10 times for large vectors compared to GRASS GIS 6).
-
-All topological cleaning tools have been optimized with regard to processing speed, robustness, and system
-requirements.
-
-Considering the wide spread usage of Esri Shapefile, a non-topological format for vector data exchange, it is particularly
-advantageous that GRASS GIS 7 offers advanced cleaning tools.
-
-postgis incl topo
-GRASS GIS 7 supports various data sources in read and write access. Beside native file-based raster and vector format
-GRASS allows to specify external data sources through GDAL/OGR library. GRASS GIS 7 also natively supports
-PostGIS database including its topological extension.
-
-In parallel to that native support the OGC Simple Features was added.
 
@@
 % v.in.ascii input= output=imported format=standard
-% v.build -e map=imported error=errors
+% v.build -e map=imported error=build_errors
 % v.clean -c input=imported output=clean error=cleaning_errors tool=snap,rmdangle,rmbridge,chbridge,bpol,prune threshold=5
+% d.vect map=build_errors color=255:33:36 fill_color=none width=5 icon=basic/point size=30
 % d.vect map=cleaning_errors color=255:33:36 fill_color=none width=5 icon=basic/point size=30
@@
 \block{\blocktitlewrap{Vector Network Analysis}}{
-All vector network analysis tools provide now fine control over node costs.
+In 2003 Radim Blazek introduced shortest path analysis (\gmodule{v.net.path}),
+traveling salesman (\gmodule{v.net.salesman}),
+and several other modules for vector network analysis (staring with \gmodule{v.net}).
+Over the years, the number of available algorithms increased to over 15 modules
+including for example, centrality measures and connected components added in 2009 by Daniel Bundala.
+In 2014 Stepan Turek implemented turns support into all relevant vector network modules.
+Also since GRASS GIS 7.0 all vector network analysis tools provide fine control over node costs.
+
+\bigskip
 

### 2017-02-21 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
rearrange, add background
git-svn-id: https://svn.osgeo.org/grass/grass-promo@70650 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 
+\definecolor{textcolor}{HTML}{000000}
+
 \definecolor{titleTextColor}{HTML}{009000}
@@
   \definecolor{colorOne}{HTML}{419041}
+  % \definecolor{colorTwo}{HTML}{cccccc}
+  \definecolor{colorTwo}{HTML}{dddddd}
+  \definecolor{colorThree}{HTML}{F1B52D}
+  % \definecolor{colorThree}{HTML}{EFA126}
 }
+
+\usetheme{Rays}
 \usecolorstyle[colorPalette=grassColorPalette]{Britain}
@@
 \renewcommand{\labelitemi}{\textcolor{gray}{$\bullet$}\hspace{0.5ex}}
+\newcommand{\blocksectiontitle}[1]{\bigskip\textbf{\textcolor{gray}{\textsf{#1}}}}
 
-Poster topic highlights:
+\blocksectiontitle{Poster topic highlights}
 
@@
 
-General GRASS GIS highlights:
+\blocksectiontitle{General GRASS GIS highlights}
 
@@
 
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Spatio-Temporal Data Analysis}}{
-The time dimension was introduced in GRASS GIS version 7 for vector maps, rasters, and 3D rasters
-which transformed GRASS GIS into a fully-featured temporal GIS \citep{Gebbert20141, gebbert2015grass}.
-Time series of map layers are managed in space time datasets, a new data type in GRASS GIS,
-and are still accessible also as individual map layers.
-Based on the GRASS GIS Temporal Framework Python application programming interface (API),
-more than 50 modules were implemented to manage, analyze, process
-and visualize space time datasets.
-More than 100,000 map layers can be now handled efficiently in GRASS GIS.
-Example usages of this functionality include
-analysis of the
-European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
-and temperate climate zone in the European Union identification \citep{Gebbert20141}.
-
-The new temporal modules (staring with \gmodulenolink{t.})
-work beside well established \gmodule{r.series} module
-and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing}
-or \gamodule{r.seasons}.
-Latest addition includes raster and vector temporal algebra
-which can be used for tasks such as computing hydrothermal coefficient for a time series of climate data
-using the actual mathematical formula \citep{leppelt2015grass}.
-
-\vspace*{1cm}
-
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=.7\linewidth]{images/temporal_precip_temp}
-\\
-Creating a synchronized animation of monthly total precipitation and mean temperature for NC, USA
-\end{minipage}
-
-% \vspace*{1cm}
-
-}
-
-\block{\blocktitlewrap{Landscape Structure}}{
-A set of modules for multiscale analysis of landscape structure was added in 1992
-by \cite{baker1992r}, who developed the \gmodulenolink{r.le} model similar to
-FRAGSTATS \citep{mcgarigal1995fragstats}.
-The modules were gradually improved to become \gmodule{r.li} in 2006.
-Further development continued, with a significant
-increase in speed \citep{tracrli} and a new interactive user interface.
-\cite{rocchini2013calculating} used \gmodule{r.li} modules to implement
-high level tool for calculating landscape diversity.
-
-\bigskip
-
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{diversity_classes}
-\end{minipage}
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{diversity_shannon}
-\end{minipage}
-
-\medskip
-Landuse classes and derived landscape diversity according to Shannon index in near Charlotte (NC, USA)
-% r.diversity input=development_2006 prefix=diversity alpha=0.5 size=65
-% r.li.shannon input="development_2006" config="conf_diversity_65.0" output="diversity_shannon_size_65.0"
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Water, Floods and Erosion}}{
-
-GRASS GIS entails several modules that constitute the result of active research on natural hazards.
-The \gmodule{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b})
-for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
-Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}).
-The module \gmodule{r.sim.water} together with
-the module \gmodule{r.sim.sediment} for erosion-deposition modeling
-implements a path sampling algorithm which is robust and easy to parallelize.
-A unique least cost path algorithm which doesn't need any depression filling
-was implemented in \gmodule{r.watershed} module in 1989
-and it was updated for massive data sets in 2011.
-% TODO: refs
-The \gmodule{r.sim.water} module was also utilized by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of
-\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
-a dam break inundation simulation \cite{cannata2012two}.
-
-\bigskip
-
-\vspace*{1cm}
-
-\centering
-\begin{minipage}{0.65\linewidth}
-\centering
-\includegraphics[width=0.5\textwidth]{rsimwater_architects}
-\\
-Overland flow simulated by \gmodule{r.sim.water} used for landscape
-architecture design in Tangible Landscape environment
-(Historical master plan for Lake Raleigh, NC, USA)
-\end{minipage}
-~
-\begin{minipage}{0.5\linewidth}
-% TODO: damflood on Lake Raleigh
-% \includegraphics[width=\textwidth]{damflood_tangible}
-% Coal ash pond breach in Tangible Landscape environment using \gamodule{r.damflood} module
-\end{minipage}
-
-% \vspace*{1.4cm}
 }
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Image Segmentations}}{
-\gamodule{r.smooth.seg} (formerly \gmodulenolink{r.seg})
-was created by Alfonso Vitti \citep{vitti2008free, vitti2012mumford}
-and implemented a piece-wise smooth approximation of the original image
-according to \cite{mumford1989optimal} and \cite{march1997variational}
-which can be used to reduce noise in the original image.
-This supplemented \gmodule{r.clump} available from 1980s
-which groups pixes with same categories (or integer values).
-The latest version of \gmodule{r.clump} coming in GRASS GIS 7.4
-supports multiple image bands (or any rasters maps) as input.
-Clumping of cells based on threshold value and clumping
-of double precision floating point input is supported as well in the new version.
-
-Eric Momsen implemented initial version of region-growing image segmentation in 2012
-and Markus Metz then extended and optimized the code resulting in
-the inclusion of the \gmodule{i.segment} module into GRASS GIS 7.0
-and final replacement of old multi-resolution classification module of the same name
-which was available in 1992 \citep{zhuang1992image}.
-Another module called \gamodule{i.segment.hierarchical} by Pietro Zambelli is based on \gmodule{i.segment}
-and performs parallelized hierarchical segmentation.
-
-In 2016 GRASS GIS implementation of SLIC Superpixels segmentation \citep{achanta2010epfl, achanta2012slic}
-was requested by the community
-and Rashad Kanavath and Markus Metz implemented \gmodule{i.superpixels.slic}
-which provides users both with SLIC and SLIC0 methods.
-
-\bigskip
-
-\vspace*{1cm}
-
-\begin{minipage}{0.5\linewidth}
-\begin{center}
-\includegraphics[width=\textwidth]{superpixels_slic_pseudo}
-\end{center}
-\end{minipage}
-~
-\begin{minipage}{0.5\linewidth}
-\begin{center}
-\includegraphics[width=\textwidth]{superpixels_slic_colored}
-\end{center}
-\end{minipage}
-\vspace{2mm}
-\begin{center}
-Superpixels (back outlines) on pseudo-color image of central Wake county, NC, USA (left)
-and same superpixels colored according to a mean NDVI value per pixel (right).
-\end{center}
-
-\vspace*{0.6cm}
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Topology, Cleaning, Overlays, Attributes}}{
-Besides basic vector analysis tools such as \gmodule{v.buffer}
-and \gmodule{v.overlay},
-which has processing speed substantially improved in GRASS GIS 7.0,
-suite of functionality for topology checking and cleaning is available
-through \gmodule{v.build} and \gmodule{v.clean} modules.
-The vector cleaning tools are particularly advantageous considering the use of non-topological exchange formats.
-\gmodule{v.clean} module was introduced in 2002 and several different contributors
-extended its functionality with last large set of improvements included in GRASS GIS 7.0.
-For that release all topological cleaning tools have been optimized
-with regard to processing speed, robustness, and system requirements.
-
-% + vector algebra
-An experimental module \gamodule{v.feature.algebra} (formerly \gmodulenolink{v.mapcalc}) from 2002
-% actually, the original by Radim Blazek (Jun 11, 2002) seems to be more similar to the current v.mapcalc
-% it was using Vect_overlay_str_to_operator Vect_overlay
-% it was replaced by code by Christoph Simon in Aug 7, 2002
-was replaced by Python for GRASS GIS C libraries (PyGRASS) in GRASS GIS 7.0.
-However, new \gamodule{v.mapcalc} module is available with richer syntax and functionality.
-
-Attribute processing and queries in GRASS GIS can take an advantage of latest developments
-in database management systems (DBMSs) as several DBMSs are supported most notably SQLite and PostgreSQL.
-A PostGIS database can be connected including it geometry and topology.
-In parallel to that native support the OGC Simple Features is available.
-
-The GRASS GIS 7 releases come with faster vector processing backend
-and more efficient internal vector format;
-both disk and memory requirements were reduced.
-The new spatial index performs queries faster (more than 10 times for large vectors compared to GRASS GIS 6).
-
-\centering
-\begin{minipage}{0.9\linewidth}
-\begin{center}
-\includegraphics[width=.3\textwidth]{topo_original}
-~
-\includegraphics[width=.3\textwidth]{topo_errors}
-~
-\includegraphics[width=.3\textwidth]{topo_fixed}
-Original vector imported without cleaning (left),
-identified errors (middle),
-automatically topologically corrected vector (right)
-\end{center}
-\end{minipage}
-
-% v.in.ascii input= output=imported format=standard
-% v.build -e map=imported error=build_errors
-% v.clean -c input=imported output=clean error=cleaning_errors tool=snap,rmdangle,rmbridge,chbridge,bpol,prune threshold=5
-% d.vect map=build_errors color=255:33:36 fill_color=none width=5 icon=basic/point size=30
-% d.vect map=cleaning_errors color=255:33:36 fill_color=none width=5 icon=basic/point size=30
-% d.vect map=imported color=56:16:108 fill_color=205:64:113 width=5
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Vector Network Analysis}}{
-In 2003 Radim Blazek introduced shortest path analysis (\gmodule{v.net.path}),
-traveling salesman (\gmodule{v.net.salesman}),
-and several other modules for vector network analysis (staring with \gmodule{v.net}).
-Over the years, the number of available algorithms increased to over 15 modules
-including for example, centrality measures and connected components added in 2009 by Daniel Bundala.
-In 2014 Stepan Turek implemented turns support into all relevant vector network modules.
-Also since GRASS GIS 7.0 all vector network analysis tools provide fine control over node costs.
-
-\bigskip
-
-\centering
-\begin{minipage}{0.5\linewidth}
-\begin{center}
-\includegraphics[width=\textwidth]{network}
-Shortest path between two points in the Wake County road network (NC, USA)
-\end{center}
-\end{minipage}
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{References}}{
-
-\vspace{-0.2cm}
-\scriptsize
-
-% \newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}
-\newcommand{\blocksectiontitle}[1]{\textbf{#1}}
-
-%\blocksectiontitle{References}
-\begingroup
-\renewcommand{\section}[2]{}%
-\bibliographystyle{apalike}
-\bibliography{poster}
-\endgroup
-
-}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\listtextwidth}{0.82\linewidth}
+
+\begin{minipage}{\listlogowidth}
+\centering
+\includegraphics[width=0.5\linewidth]{grass}
+\end{minipage}
+\listhspace
+\begin{minipage}{\listtextwidth}
+We acknowledge all members of the GRASS GIS community both users and developers.
+Specifically we
+\end{minipage}
+
+\bigskip
 
@@
 \end{minipage}
-
-\bigskip
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Water, Floods and Erosion}}{
+
+GRASS GIS entails several modules that constitute the result of active research on natural hazards.
+The \gmodule{r.sim.water} simulation model \citep{Mitas1998b}.
+for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
+Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}).
+The module \gmodule{r.sim.water} together with
+the module \gmodule{r.sim.sediment} for erosion-deposition modeling
+implements a path sampling algorithm which is robust and easy to parallelize.
+A unique least cost path algorithm which doesn't need any depression filling
+was implemented in \gmodule{r.watershed} module in 1989
+and it was updated for massive data sets in 2011.
+% TODO: refs
+The \gmodule{r.sim.water} module was also utilized by \cite{Petrasova2014} and is now part of
+\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
+a dam break inundation simulation \citep{cannata2012two}.
+
+\bigskip
+
+\vspace*{1cm}
+
+\centering
+
+\begin{minipage}{0.49\linewidth}
+\centering
+\includegraphics[width=0.7\textwidth]{rsimwater_architects}
+\end{minipage}
+~
+\begin{minipage}{0.49\linewidth}
+\includegraphics[width=\textwidth]{damflood_tangible}
+\end{minipage}
+
+\bigskip
+
+\begin{minipage}{0.49\linewidth}
+\centering
+Overland flow simulated by \gmodule{r.sim.water} used for landscape
+architecture design in Tangible Landscape environment
+(Historical master plan for Lake Raleigh, NC, USA)
+\end{minipage}
+~
+\begin{minipage}{0.49\linewidth}
+Dam breach on Lake Raleigh (NC, USA) in Tangible Landscape environment simulated using \gamodule{r.damflood} module
+\end{minipage}
+
+% \vspace*{1.4cm}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Image Segmentations}}{
+\gamodule{r.smooth.seg} (formerly \gmodulenolink{r.seg})
+was created by Alfonso Vitti \citep{vitti2008free, vitti2012mumford}
+and implemented a piece-wise smooth approximation of the original image
+according to \cite{mumford1989optimal} and \cite{march1997variational}
+which can be used to reduce noise in the original image.
+
+This supplemented \gmodule{r.clump} available from 1980s
+which groups pixes with same categories (or integer values).
+The latest version of \gmodule{r.clump} coming in GRASS GIS 7.4
+supports multiple image bands (or any rasters maps) as input.
+Clumping of cells based on threshold value and clumping
+of double precision floating point input is supported as well in the new version.
+
+Eric Momsen implemented initial version of region-growing image segmentation in 2012
+and Markus Metz then extended and optimized the code resulting in
+the inclusion of the \gmodule{i.segment} module into GRASS GIS 7.0
+and final replacement of old multi-resolution classification module of the same name
+which was available in 1992 \citep{zhuang1992image}.
+Another module called \gamodule{i.segment.hierarchical} by Pietro Zambelli is based on \gmodule{i.segment}
+and performs parallelized hierarchical segmentation.
+
+\vspace*{0.7cm}
+
+\begin{minipage}{0.5\linewidth}
+\begin{center}
+\includegraphics[width=\textwidth]{superpixels_slic_pseudo}
+\end{center}
+\end{minipage}
+~
+\begin{minipage}{0.5\linewidth}
+\begin{center}
+\includegraphics[width=\textwidth]{superpixels_slic_colored}
+\end{center}
+\end{minipage}
+\vspace{2mm}
+\begin{center}
+Superpixels (back outlines) on pseudo-color image of central Wake county, NC, USA (left)
+and same superpixels colored according to a mean NDVI value per pixel (right).
+\end{center}
+
+\vspace*{1cm}
+
+In 2016 GRASS GIS implementation of SLIC Superpixels segmentation \citep{achanta2010epfl, achanta2012slic}
+was requested by the community
+and Rashad Kanavath and Markus Metz implemented \gmodule{i.superpixels.slic}
+which provides users both with SLIC and SLIC0 methods.
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Topology, Cleaning, Overlays, Attributes}}{
+Besides basic vector analysis tools such as \gmodule{v.buffer}
+and \gmodule{v.overlay},
+which has processing speed substantially improved in GRASS GIS 7.0,
+suite of functionality for topology checking and cleaning is available
+through \gmodule{v.build} and \gmodule{v.clean} modules.
+The vector cleaning tools are particularly advantageous considering the use of non-topological exchange formats.
+\gmodule{v.clean} module was introduced in 2002 and several different contributors
+extended its functionality with last large set of improvements included in GRASS GIS 7.0.
+For that release all topological cleaning tools have been optimized
+with regard to processing speed, robustness, and system requirements.
+
+\vspace*{1cm}
+
+\begin{center}
+\begin{minipage}{0.9\linewidth}
+\begin{center}
+\includegraphics[width=.3\textwidth]{topo_original}
+~
+\includegraphics[width=.3\textwidth]{topo_errors}
+~
+\includegraphics[width=.3\textwidth]{topo_fixed}
+Original vector imported without cleaning (left),
+identified errors (middle),
+automatically topologically corrected vector (right)
+\end{center}
+\end{minipage}
+\end{center}
+
+% v.in.ascii input= output=imported format=standard
+% v.build -e map=imported error=build_errors
+% v.clean -c input=imported output=clean error=cleaning_errors tool=snap,rmdangle,rmbridge,chbridge,bpol,prune threshold=5
+% d.vect map=build_errors color=255:33:36 fill_color=none width=5 icon=basic/point size=30
+% d.vect map=cleaning_errors color=255:33:36 fill_color=none width=5 icon=basic/point size=30
+% d.vect map=imported color=56:16:108 fill_color=205:64:113 width=5
+
+\vspace*{1cm}
+
+An experimental module \gamodule{v.feature.algebra} (formerly \gmodulenolink{v.mapcalc}) from 2002
+% actually, the original by Radim Blazek (Jun 11, 2002) seems to be more similar to the current v.mapcalc
+% it was using Vect_overlay_str_to_operator Vect_overlay
+% it was replaced by code by Christoph Simon in Aug 7, 2002
+was replaced by Python for GRASS GIS C libraries (PyGRASS) in GRASS GIS 7.0.
+However, new \gamodule{v.mapcalc} module is available with richer syntax and functionality.
+
+Attribute processing and queries in GRASS GIS can take an advantage of latest developments
+in database management systems (DBMSs) as several DBMSs are supported most notably SQLite and PostgreSQL.
+A PostGIS database can be connected including it geometry and topology.
+In parallel to that native support the OGC Simple Features is available.
+
+The GRASS GIS 7 releases come with faster vector processing backend
+and more efficient internal vector format;
+both disk and memory requirements were reduced.
+The new spatial index performs queries faster (more than 10 times for large vectors compared to GRASS GIS 6).
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Spatio-Temporal Data Analysis}}{
+The time dimension was introduced in GRASS GIS version 7 for vector maps, rasters, and 3D rasters
+which transformed GRASS GIS into a fully-featured temporal GIS \citep{Gebbert20141, gebbert2015grass}.
+Time series of map layers are managed in space time datasets, a new data type in GRASS GIS,
+and are still accessible also as individual map layers.
+Based on the GRASS GIS Temporal Framework Python application programming interface (API),
+more than 50 modules were implemented to manage, analyze, process
+and visualize space time datasets.
+More than 100,000 map layers can be now handled efficiently in GRASS GIS.
+%
+Example usages of this functionality include
+analysis of the
+European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
+and temperate climate zone in the European Union identification \citep{Gebbert20141}.
+
+The new temporal modules (staring with \gmodulenolink{t.})
+work beside well established \gmodule{r.series} module
+and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing}
+or \gamodule{r.seasons}.
+Latest addition includes raster and vector temporal algebra
+which can be used for tasks such as computing hydrothermal coefficient for a time series of climate data
+using the actual mathematical formula \citep{leppelt2015grass}.
+
+\vspace*{1.5cm}
+
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=.7\linewidth]{images/temporal_precip_temp}
+\\
+Creating a synchronized animation of monthly total precipitation and mean temperature for NC, USA
+\end{minipage}
+
+\vspace*{1cm}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Vector Network Analysis}}{
+In 2003 Radim Blazek introduced shortest path analysis (\gmodule{v.net.path}),
+traveling salesman (\gmodule{v.net.salesman}),
+and several other modules for vector network analysis (staring with \gmodule{v.net}).
+Over the years, the number of available algorithms increased to over 15 modules
+including for example, centrality measures and connected components added in 2009 by Daniel Bundala.
+In 2014 Stepan Turek implemented turns support into all relevant vector network modules.
+Also since GRASS GIS 7.0 all vector network analysis tools provide fine control over node costs.
+% combination with r.cost/r.walk workflows \citep{Petrasova2014}
+
+\bigskip
+
+\centering
+\begin{minipage}{0.5\linewidth}
+\begin{center}
+\includegraphics[width=\textwidth]{network}
+Shortest path between two points in the Wake County road network (NC, USA)
+\end{center}
+\end{minipage}
+
+}
+
+\block{\blocktitlewrap{Landscape Structure}}{
+A set of modules for multiscale analysis of landscape structure was added in 1992
+by \cite{baker1992r}, who developed the \gmodulenolink{r.le} model similar to
+FRAGSTATS \citep{mcgarigal1995fragstats}.
+The modules were gradually improved to become \gmodule{r.li} in 2006.
+Further development continued, with a significant
+increase in speed \citep{tracrli} and a new interactive user interface.
+\cite{rocchini2013calculating} used \gmodule{r.li} modules to implement
+high level tool for calculating landscape diversity.
+
+\vspace*{0.5cm}
+
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{diversity_classes}
+\end{minipage}
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{diversity_shannon}
+\end{minipage}
+
+\vspace*{1ex}
+
+Landuse classes and derived landscape diversity according to Shannon index in near Charlotte (NC, USA)
+% r.diversity input=development_2006 prefix=diversity alpha=0.5 size=65
+% r.li.shannon input="development_2006" config="conf_diversity_65.0" output="diversity_shannon_size_65.0"
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{References}}{
+
+\vspace{-0.2cm}
+\scriptsize
+
+% \newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}
+\newcommand{\blocksectiontitle}[1]{\textbf{#1}}
+
+%\blocksectiontitle{References}
+\begingroup
+\renewcommand{\section}[2]{}%
+\bibliographystyle{apalike}
+\bibliography{poster}
+\endgroup
+
+}
+
 \end{columns}

### 2017-02-21 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
authors, typos
git-svn-id: https://svn.osgeo.org/grass/grass-promo@70651 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 ~
-\includegraphics[height=\instlogoheight]{iwmi}
-~
 \includegraphics[height=\instlogoheight]{ctu_prague}
 ~
-\includegraphics[height=\instlogoheight]{ti}
+\includegraphics[height=\instlogoheight]{dwd}
 ~
@@
 V\'{a}clav Petr\'{a}\v{s}\inst{1},
-Yann Chemin\inst{2},
-Martin Landa\inst{3},
-Thomas Leppelt\inst{4},
-S\"{o}ren Gebbert\inst{4},
-Pietro Zambelli\inst{5},
-Markus Neteler\inst{6},
-Luca Delucchi\inst{7}, and
-Margherita Di Leo\inst{8}
+Yann Chemin,
+Martin Landa\inst{2},
+Thomas Leppelt\inst{3},
+Pietro Zambelli\inst{4},
+Luca Delucchi\inst{5},
+Margherita Di Leo\inst{6}
+S\"{o}ren Gebbert,
+Markus Neteler\inst{7},
 }
@@
 \instlist{1}NCSU, USA;
-\instlist{2}IWMI, Sri Lanka;
-\instlist{3}FCE CTU in Prague, Czech Republic;
-\instlist{4}TICSA, Germany;
-\instlist{5}EURAC, Italy;
-\instlist{6}mundialis GmbH \& Co. KG, Germany;
-\instlist{7}CRI, FEM, Italy;
-\instlist{8}EC-JRC, Italy
+\instlist{2}FCE CTU in Prague, Czech Republic;
+\instlist{3}Deutscher Wetterdienst, Germany;
+\instlist{4}EURAC, Italy;
+\instlist{5}CRI, FEM, Italy;
+\instlist{6}EC-JRC, Italy
+\instlist{7}mundialis GmbH \& Co. KG, Germany;
 }
@@
  \item Analytical tools are not limited to one domain but spread across many fields.
- \item New tools can be build based on functionality or code of the existing ones
+ \item New tools can be built based on functionality or code of the existing ones
        regardless of the particular domain of problems they belong to.
  \item Both the functionality and the code are evaluated
-       by the user and developer community in different fields of application beyond
-       the field of expertise of the original authors
-       and different scales of magnitude of data.
+       by the community of users and developers in different fields and scales.
 % continuous automated tests (Petras, 2014 \cite{Petras2014}),
@@
 The module \gmodule{v.surf.rst} for spatial interpolation was developed approximately 20 years
-ago, but since then it has been improved several times \cite{tracvsurfrst}
+ago, but since then it has been improved several times \citep{tracvsurfrst}
 including recent parallelization which will be included in GRASS GIS 7.4.
@@
 The \gmodule{v.outlier} module serves as a base for a user contributed module \gamodule{v.lidar.mcc}
-implementing MMC.
+implementing Multiscale Curvature Classification (MCC).
 % TODO: ref
@@
 \centering
-Digital elevation model interpolated from LiDAR point clouds
+Digital elevation model interpolated from lidar point clouds
 using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
@@
 Profile (vertical slice) of a small portion of a point cloud showing tree structure as captured by the returns
+(\gamodule{v.profile.points})
 \end{minipage}
@@
 We acknowledge all members of the GRASS GIS community both users and developers.
-Specifically we
+We would like to thank Markus Metz, Anna Petrasova, Stepan Turek, and Radim Blazek.
 \end{minipage}
@@
 supports the collaborative development of open source geospatial software.
-GRASS GIS is a OSGeo project.
+GRASS GIS is a OSGeo project and
 OSGeo provides infrastructure for project
@@
 GRASS GIS entails several modules that constitute the result of active research on natural hazards.
-The \gmodule{r.sim.water} simulation model \citep{Mitas1998b}.
+The \gmodule{r.sim.water} simulation model \citep{Mitas1998b}
 for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
-Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}).
+Routing Decision Planning system as a WPS \citep{raghavan2014deploying}.
 The module \gmodule{r.sim.water} together with
@@
 \emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
-a dam break inundation simulation \citep{cannata2012two}.
+a dam break inundation simulation by \cite{cannata2012two}.
 
@@
 This supplemented \gmodule{r.clump} available from 1980s
-which groups pixes with same categories (or integer values).
+which groups pixels with the same categories (or integer values).
 The latest version of \gmodule{r.clump} coming in GRASS GIS 7.4
@@
 \begin{center}
-Superpixels (back outlines) on pseudo-color image of central Wake county, NC, USA (left)
-and same superpixels colored according to a mean NDVI value per pixel (right).
+Superpixels (black outlines) on pseudo-color image of central Wake county, NC, USA (left)
+and the same superpixels colored according to the mean NDVI value per pixel (right).
 \end{center}
@@
 and \gmodule{v.overlay},
-which has processing speed substantially improved in GRASS GIS 7.0,
 suite of functionality for topology checking and cleaning is available
@@
 The vector cleaning tools are particularly advantageous considering the use of non-topological exchange formats.
-\gmodule{v.clean} module was introduced in 2002 and several different contributors
+The \gmodule{v.clean} module was introduced in 2002 and several different contributors
 extended its functionality with last large set of improvements included in GRASS GIS 7.0.
@@
 with regard to processing speed, robustness, and system requirements.
+The processing speed of the \gmodule{v.clean} module was substantially improved as well.
 
@@
 \block{\blocktitlewrap{Spatio-Temporal Data Analysis}}{
-The time dimension was introduced in GRASS GIS version 7 for vector maps, rasters, and 3D rasters
+The time dimension was introduced in GRASS GIS 7.0 for vector maps, rasters, and 3D rasters
 which transformed GRASS GIS into a fully-featured temporal GIS \citep{Gebbert20141, gebbert2015grass}.
@@
 Over the years, the number of available algorithms increased to over 15 modules
-including for example, centrality measures and connected components added in 2009 by Daniel Bundala.
+including, for example, centrality measures and connected components added in 2009 by Daniel Bundala.
 In 2014 Stepan Turek implemented turns support into all relevant vector network modules.
@@
 
-Landuse classes and derived landscape diversity according to Shannon index in near Charlotte (NC, USA)
+Landuse classes and derived landscape diversity according to Shannon index near Charlotte, NC, USA
 % r.diversity input=development_2006 prefix=diversity alpha=0.5 size=65

### 2017-02-21 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
authors cosmentics
git-svn-id: https://svn.osgeo.org/grass/grass-promo@70652 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 Luca Delucchi\inst{5},
-Margherita Di Leo\inst{6}
+Margherita Di Leo\inst{6},
 S\"{o}ren Gebbert,
-Markus Neteler\inst{7},
+Markus Neteler\inst{7}
 }
@@
 \instlist{5}CRI, FEM, Italy;
-\instlist{6}EC-JRC, Italy
-\instlist{7}mundialis GmbH \& Co. KG, Germany;
+\instlist{6}EC-JRC, Italy;
+\instlist{7}mundialis GmbH \& Co. KG, Germany
 }

### 2017-02-21 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
author list and typos
git-svn-id: https://svn.osgeo.org/grass/grass-promo@70654 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2017-02-21 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
@@
 \newlength{\grasslogoheight}
-\setlength{\grasslogoheight}{0.08\textheight}
+\setlength{\grasslogoheight}{0.09\textheight}
 \newlength{\instlogoheight}
-\setlength{\instlogoheight}{0.35\grasslogoheight}
+\setlength{\instlogoheight}{0.33\grasslogoheight}
 
@@
 \hfill
-\begin{minipage}{0.15\linewidth}
+\begin{minipage}{0.20\linewidth}
 \setlength{\baselineskip}{120pt}
@@
 ~
-\includegraphics[height=\instlogoheight]{eurac}
-~
 \includegraphics[height=\instlogoheight]{mundialis}
@@
 ~
+\includegraphics[height=\instlogoheight]{iwmi}
+~
 \includegraphics[height=\instlogoheight]{ec_jrc}
+~
+\includegraphics[height=\instlogoheight]{eurac}
 \end{flushright}
@@
 V\'{a}clav Petr\'{a}\v{s}\inst{1},
-Yann Chemin,
-Martin Landa\inst{2},
-Thomas Leppelt\inst{3},
-Pietro Zambelli\inst{4},
-Luca Delucchi\inst{5},
-Margherita Di Leo\inst{6}
+Yann Chemin\inst{2},
+Martin Landa\inst{3},
+Thomas Leppelt\inst{4},
+Pietro Zambelli\inst{5},
+Luca Delucchi\inst{6},
+Margherita Di Leo\inst{7},
 S\"{o}ren Gebbert,
-Markus Neteler\inst{7},
+and
+Markus Neteler\inst{8}
 }
 \institute{
-\instlist{1}NCSU, USA;
-\instlist{2}FCE CTU in Prague, Czech Republic;
-\instlist{3}Deutscher Wetterdienst, Germany;
-\instlist{4}EURAC, Italy;
-\instlist{5}CRI, FEM, Italy;
-\instlist{6}EC-JRC, Italy
-\instlist{7}mundialis GmbH \& Co. KG, Germany;
+\large
+\instlist{1}North Carolina State University, USA (wenzeslaus@gmail.com, vpetras@ncsu.edu);
+\instlist{2}IWMI, Sri Lanka;
+\instlist{3}FCE CTU in Prague, Czech Republic;
+\instlist{4}DWD, Germany;\\
+\instlist{5}EURAC Research, Institute for Renewable Energy, Italy;
+\instlist{6}Fondazione Edmund Mach, Research and Innovation Centre, Italy;
+\instlist{7}European Commission, JRC, Italy;
+\instlist{8}mundialis GmbH \& Co. KG, Germany;
 }
@@
 \begin{minipage}{\listtextwidth}
-Initial development of \gmodule{i.segement} module as well as several other developments
+Initial development of \gmodule{i.segment} module as well as several other developments
 were done as a part of the Google Summer of Code project.
@@
 in database management systems (DBMSs) as several DBMSs are supported most notably SQLite and PostgreSQL.
-A PostGIS database can be connected including it geometry and topology.
+A PostGIS database can be connected including its geometry and topology.
 In parallel to that native support the OGC Simple Features is available.

### 2018-11-29 grassposter/2018_AGU_Geospatial_Research_Tool/poster.tex
poster: GRASS GIS: A General-purpose Geospatial Research Tool
git-svn-id: https://svn.osgeo.org/grass/grass-promo@73722 15284696-431f-4ddb-bdfa-cd5b030d7da7

--- 2017-02-21 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
@@
 % License: CC BY-SA
-% Authors: See authors below and see also acknowledgement for authors of some images or research
+% Authors: See the authors below and see also acknowledgement for authors of some images or research
 
-\documentclass[25pt, margin=0mm, innermargin=15mm, blockverticalspace=15mm, colspace=15mm, subcolspace=8mm]{tikzposter}
-\geometry{paperwidth=82in,paperheight=41in}
+\documentclass[25pt, margin=0mm, innermargin=25mm, blockverticalspace=25mm, colspace=25mm, subcolspace=8mm]{tikzposter}
+\geometry{paperwidth=63in,paperheight=42in}
 
@@
 \makeatother
+
+% Fira Sans, GRASS GIS branding sans serif font
+\usepackage{FiraSans}
+\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
+
+% EB Garamond, GRASS GIS branding serif font
+% note that EB Garamond does not have bold
+\usepackage[cmintegrals,cmbraces]{newtxmath}
+\usepackage{ebgaramond-maths}
+
+% might be needed for both font packages
+\usepackage[T1]{fontenc}
+
+% uncomment for all sans serif
+% \renewcommand{\familydefault}{\sfdefault}
 
@@
 
-\definecolor{titleTextColor}{HTML}{009000}
+\definecolor{titleTextColor}{HTML}{000000}
 \definecolorpalette{grassColorPalette} {
@@
 
-\usetheme{Rays}
+\usetheme{Default}
+\usetitlestyle{Empty}
 \usecolorstyle[colorPalette=grassColorPalette]{Britain}
+\colorlet{backgroundcolor}{white}
 
@@
 \textcolor{titleTextColor}{
-\textsf{\textbf{
-\fontsize{85}{60}\selectfont
-How innovations thrive in GRASS GIS
-}}
+\textsf{
+% \textbf{
+\fontsize{130}{100}\selectfont
+\textbf{GRASS}\,{\firalight GIS}: A General-purpose Geospatial Research Tool
+% }
+}
 }
@@
 \newlength{\grasslogoheight}
-\setlength{\grasslogoheight}{0.08\textheight}
+\setlength{\grasslogoheight}{0.09\textheight}
 \newlength{\instlogoheight}
-\setlength{\instlogoheight}{0.35\grasslogoheight}
-
-\titlegraphic{
-\begin{minipage}{0.3\linewidth}
-\includegraphics[height=\grasslogoheight]{grass}
-\hspace{2em}
-\includegraphics[height=\grasslogoheight]{osgeo_project}
-\end{minipage}
-\hfill
-\begin{minipage}{0.15\linewidth}
-\setlength{\baselineskip}{120pt}
-\begin{flushright}
-\includegraphics[height=\instlogoheight]{ncstate}
-~
-\includegraphics[height=\instlogoheight]{ctu_prague}
-~
-\includegraphics[height=\instlogoheight]{dwd}
-~
-\includegraphics[height=\instlogoheight]{eurac}
-~
-\includegraphics[height=\instlogoheight]{mundialis}
-~
-\includegraphics[height=\instlogoheight]{fem_cri}
-~
-\includegraphics[height=\instlogoheight]{ec_jrc}
-\end{flushright}
-\end{minipage}
-\vspace{-\grasslogoheight}
-}
+\setlength{\instlogoheight}{0.33\grasslogoheight}
 
@@
 \author{
-V\'{a}clav Petr\'{a}\v{s}\inst{1},
-Yann Chemin,
-Martin Landa\inst{2},
-Thomas Leppelt\inst{3},
-Pietro Zambelli\inst{4},
-Luca Delucchi\inst{5},
-Margherita Di Leo\inst{6},
-S\"{o}ren Gebbert,
-Markus Neteler\inst{7}
+Helena Mitasova\inst{1},
+Vaclav Petras\inst{1}\,*\hspace{-7pt},
+Anna Petrasova\inst{1},
+\&
+Markus Neteler\inst{2}
+\\
+% AGU allows to specify a scientific team, but it does not seem to fit
+% with our case 100%; simply using formatting which is in the AGU program
+% (but adding note)
+Scientific Team: GRASS GIS Development Team**
 }
 \institute{
-\instlist{1}NCSU, USA;
-\instlist{2}FCE CTU in Prague, Czech Republic;
-\instlist{3}Deutscher Wetterdienst, Germany;
-\instlist{4}EURAC, Italy;
-\instlist{5}CRI, FEM, Italy;
-\instlist{6}EC-JRC, Italy;
-\instlist{7}mundialis GmbH \& Co. KG, Germany
+\large
+\instlist{1}Center for Geospatial Analytics, North Carolina State University, USA;
+\instlist{2}mundialis GmbH \& Co. KG, Germany;
+*Corresponding author: wenzeslaus@gmail.com, vpetras@ncsu.edu;
+% using Black Duck Open Hub to ``guestimate'' that
+**Over 10 other members of the core team and numerous other contributors
+\\[1.7cm]
+\includegraphics[height=3cm]{ncstate}%
+\hspace{1cm}%
+\includegraphics[height=3cm]{cga}%
+\hspace{3cm}%
+\includegraphics[height=3.4cm]{mundialis}%
 }
@@
 {
-    pdfauthor={V. Petras, Y. Chemin, M. Landa, S. Gebbert, P. Zambelli, M. Neteler, M. Di Leo},
-    pdfsubject={},
-    pdftitle={How innovations thrive in GRASS GIS},
+    pdfauthor={H. Mitasova, V. Petras, A. Petrasova, M. Neteler},
+    pdfsubject={AGU Fall Meeting 2018 Poster},
+    pdftitle={GRASS GIS: A General-purpose Geospatial Research Tool},
     pdfkeywords={GIS, algorithms, methods, preservation, science, reproducibility}
@@
 
-\newcommand{\blocktitlewrap}[1]{\textsf{\textbf{\huge#1}}}
+\newcommand{\blocktitlewrap}[1]{\textnormal{\textsf{\textsc{\huge#1}}}}
 % it is not possible (?) to change block title in the class, using wrapper
@@
 %   sed -i 's/\\block{\([^}]*\)}/\\block{\\blocktitlewrap{\1}}/g' main.tex
+
+% bullet point style
+\renewcommand{\labelitemi}{\textcolor{gray}{$\bullet$}\hspace{0.5ex}}
 
@@
 \begin{document}
+
+\node[above left,opacity=0.99,inner sep=0pt,outer sep=4cm] at (bottomleft -| topright)%
+  {\includegraphics[width=0.3\paperwidth]{grass}};
+
 \maketitle[width=0.92\textwidth]
+
 % \maketitle
@@
 
+% Abstract
+%
+% GRASS GIS (grass.osgeo.org) is an open source software for geospatial analysis,
+% remote sensing, general geoprocessing and visualization. It is a
+% community-driven project with over 35 years of continuous software development
+% based on scientific expertise from many geospatial fields. It is characterized
+% by long-term releases, stable APIs, and emphasis on science. GRASS GIS
+% distribution strives to provide single integrated environment for 2D and 3D
+% raster analysis, image processing, vector data analysis, and spatio-temporal
+% data processing. It supports large raster files (billions of cells), vector
+% topology, coupling with databases, and 64 bit memory. New code based on recent
+% research is typically contributed to GRASS GIS Addons repository. Mature, widely
+% used code is then moved to the main code base to maximize integration and
+% availability. Whether it is addons or the main code base, code is usually
+% maintained by the community and preserved in long term even in cases when the
+% original author no longer supports the code. To support the needs of scientists,
+% the documentation includes not only links to the source code, its history, and
+% its authors, but also links to research papers that describe the algorithms
+% implemented in the modules.
+%
+% Code is not only maintained but also extended and improved. For example,
+% watershed and stream extraction using least cost path approach was implemented
+% in 1989 and extended for massive datasets in 2011. Similarly, vector topology
+% cleaning was introduced in 2002, updated over time and substantially improved in
+% 2016. Another example is a solar energy module available since 1993 and
+% parallelized in 2017. The current stable version of GRASS GIS 7.4 provides new
+% features for geosciences such as temporal framework with temporal algebra for
+% large time-series processing, fusion of elevation models from various sensors,
+% 3D flows, landform detection, image segmentation, simplified batch processing,
+% and integrated Python editor among others. GRASS GIS runs in various
+% environments including Linux, Mac, Windows, Docker, Raspberry Pi, and on HPC
+% clusters. The modules are written in Python, C, or C++. Besides command line
+% interface, GRASS GIS provides a graphical user interface, a Python API, and a C
+% API. Interfaces with other languages such as R and Ruby are supplied by
+% collaborating communities.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Highlights}}
-{
-% \setlength{\parskip}{0.3ex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Overview}}{
 
-\renewcommand{\labelitemi}{\textcolor{gray}{$\bullet$}\hspace{0.5ex}}
-\newcommand{\blocksectiontitle}[1]{\bigskip\textbf{\textcolor{gray}{\textsf{#1}}}}
-
-\blocksectiontitle{Poster topic highlights}
+\Large
 
 \begin{itemize}
- \item Algorithms and models included in GRASS GIS remain available long term \citep{chemin2015grass}.
- \item Analytical tools are not limited to one domain but spread across many fields.
- \item New tools can be built based on functionality or code of the existing ones
-       regardless of the particular domain of problems they belong to.
- \item Both the functionality and the code are evaluated
-       by the community of users and developers in different fields and scales.
-% continuous automated tests (Petras, 2014 \cite{Petras2014}),
+% Basic Topics
+ \item Community-driven project
+ \item 35 years of continuous software development
+ \item long-term releases, stable APIs, and emphasis on science
+ \item single integrated environment for 2D and 3D raster analysis, image processing, vector data analysis, and spatio-temporal data processing
 \end{itemize}
 
-\blocksectiontitle{General GRASS GIS highlights}
+}
 
-\begin{itemize}
-%  \item Community supports users and new developments through online
-%  \item long-term moving forward
- \item The GRASS GIS development team takes care of interface and operating system related changes
-       in the code provided by scientists and contributors.
- \item Cost estimated by Black Duck Open Hub is over \$30,000,000.
- % https://www.openhub.net/p/grass_gis/estimated_cost
- \item The free, libre and open source license used in GRASS GIS
-       not only allows users to reduce GIS software costs to minimum,
-       but also enables organizations to deploy cloud-based solutions without any license restrictions.
- \item GRASS GIS is used both directly and as a backend in other projects
-       such as QGIS and R.
-\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Functionality}}{
 
-% oholoh hours
+\Large
+
+GRASS GIS
+distribution strives to provide single integrated environment for 2D and 3D
+raster analysis, image processing, vector data analysis, and spatio-temporal
+data processing. It supports large raster files (billions of cells), vector
+topology, coupling with databases, and 64 bit memory.
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Code Life Cycle}}{
+
+\Large
+
+New code based on recent
+research is typically contributed to GRASS GIS Addons repository. Mature, widely
+used code is then moved to the main code base to maximize integration and
+availability. Whether it is addons or the main code base, code is usually
+maintained by the community and preserved in long term even in cases when the
+original author no longer supports the code. To support the needs of scientists,
+the documentation includes not only links to the source code, its history, and
+its authors, but also links to research papers that describe the algorithms
+implemented in the modules.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Lidar Data Processing}}{
+\block{\blocktitlewrap{Example: Spatio-Temporal Data Analysis}}{
+The time dimension was introduced in GRASS GIS 7.0 for vector maps, rasters, and 3D rasters
+which transformed GRASS GIS into a fully-featured temporal GIS \citep{Gebbert20141, gebbert2015grass}.
+Time series of map layers are managed in space time datasets, a new data type in GRASS GIS,
+and are still accessible also as individual map layers.
+Based on the GRASS GIS Temporal Framework Python application programming interface (API),
+more than 50 modules were implemented to manage, analyze, process
+and visualize space time datasets.
+More than 100,000 map layers can be now handled efficiently in GRASS GIS.
+%
+Example usages of this functionality include
+analysis of the
+European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
+and temperate climate zone in the European Union identification \citep{Gebbert20141}.
+
+The new temporal modules (staring with \gmodulenolink{t.})
+work beside well established \gmodule{r.series} module
+and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing}
+or \gamodule{r.seasons}.
+Latest addition includes raster and vector temporal algebra
+which can be used for tasks such as computing hydrothermal coefficient for a time series of climate data
+using the actual mathematical formula \citep{leppelt2015grass}.
+
+\vspace*{1.5cm}
+
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=.7\linewidth]{images/temporal_precip_temp}
+\\
+Creating a synchronized animation of monthly total precipitation and mean temperature for NC, USA
+\end{minipage}
+
+\vspace*{1cm}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Example: Water, Floods and Erosion}}{
+
+GRASS GIS entails several modules that constitute the result of active research on natural hazards.
+The \gmodule{r.sim.water} simulation model \citep{Mitas1998b}
+for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
+Routing Decision Planning system as a WPS \citep{raghavan2014deploying}.
+The module \gmodule{r.sim.water} together with
+the module \gmodule{r.sim.sediment} for erosion-deposition modeling
+implements a path sampling algorithm which is robust and easy to parallelize.
+A unique least cost path algorithm which doesn't need any depression filling
+was implemented in \gmodule{r.watershed} module in 1989
+and it was updated for massive data sets in 2011.
+% TODO: refs
+The \gmodule{r.sim.water} module was also utilized by \cite{Petrasova2014} and is now part of
+\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
+a dam break inundation simulation by \cite{cannata2012two}.
+
+\bigskip
+
+\vspace*{1cm}
+
+\centering
+
+\begin{minipage}{0.49\linewidth}
+\centering
+\includegraphics[width=0.7\textwidth]{rsimwater_architects}
+\end{minipage}
+~
+\begin{minipage}{0.49\linewidth}
+\includegraphics[width=\textwidth]{damflood_tangible}
+\end{minipage}
+
+\bigskip
+
+\begin{minipage}{0.49\linewidth}
+\centering
+Overland flow simulated by \gmodule{r.sim.water} used for landscape
+architecture design in Tangible Landscape environment
+(Historical master plan for Lake Raleigh, NC, USA)
+\end{minipage}
+~
+\begin{minipage}{0.49\linewidth}
+Dam breach on Lake Raleigh (NC, USA) in Tangible Landscape environment simulated using \gamodule{r.damflood} module
+\end{minipage}
+
+% \vspace*{1.4cm}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Example: Vector Network Analysis}}{
+In 2003 Radim Blazek introduced shortest path analysis (\gmodule{v.net.path}),
+traveling salesman (\gmodule{v.net.salesman}),
+and several other modules for vector network analysis (staring with \gmodule{v.net}).
+Over the years, the number of available algorithms increased to over 15 modules
+including, for example, centrality measures and connected components added in 2009 by Daniel Bundala.
+In 2014 Stepan Turek implemented turns support into all relevant vector network modules.
+Also since GRASS GIS 7.0 all vector network analysis tools provide fine control over node costs.
+% combination with r.cost/r.walk workflows \citep{Petrasova2014}
+
+\bigskip
+
+\centering
+\begin{minipage}{0.9\linewidth}
+\begin{center}
+\includegraphics[width=\textwidth]{network_trips}
+A series of trips to collect samples across North Carolina, USA
+for water quality measurements
+as part of the Polyfluorinated Alkyl Substance Testing (PFAST) project.
+Trips are distinguished by color and were computed using multiple
+iterations of traveling salesman (\gmodule{v.net.salesman}).
+\end{center}
+\end{minipage}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Example: Image Segmentations}}{
+\gamodule{r.smooth.seg} (formerly \gmodulenolink{r.seg})
+was created by Alfonso Vitti \citep{vitti2008free, vitti2012mumford}
+and implemented a piece-wise smooth approximation of the original image
+according to \cite{mumford1989optimal} and \cite{march1997variational}
+which can be used to reduce noise in the original image.
+
+This supplemented \gmodule{r.clump} available from 1980s
+which groups pixels with the same categories (or integer values).
+The latest version of \gmodule{r.clump} coming in GRASS GIS 7.4
+supports multiple image bands (or any rasters maps) as input.
+Clumping of cells based on threshold value and clumping
+of double precision floating point input is supported as well in the new version.
+
+Eric Momsen implemented initial version of region-growing image segmentation in 2012
+and Markus Metz then extended and optimized the code resulting in
+the inclusion of the \gmodule{i.segment} module into GRASS GIS 7.0
+and final replacement of old multi-resolution classification module of the same name
+which was available in 1992 \citep{zhuang1992image}.
+Another module called \gamodule{i.segment.hierarchical} by Pietro Zambelli is based on \gmodule{i.segment}
+and performs parallelized hierarchical segmentation.
+
+\vspace*{0.7cm}
+
+\begin{minipage}{0.5\linewidth}
+\begin{center}
+\includegraphics[width=\textwidth]{superpixels_slic_pseudo}
+\end{center}
+\end{minipage}
+~
+\begin{minipage}{0.5\linewidth}
+\begin{center}
+\includegraphics[width=\textwidth]{superpixels_slic_colored}
+\end{center}
+\end{minipage}
+\vspace{2mm}
+\begin{center}
+Superpixels (black outlines) on pseudo-color image of central Wake county, NC, USA (left)
+and the same superpixels colored according to the mean NDVI value per pixel (right).
+\end{center}
+
+\vspace*{1cm}
+
+In 2016 GRASS GIS implementation of SLIC Superpixels segmentation \citep{achanta2010epfl, achanta2012slic}
+was requested by the community
+and Rashad Kanavath and Markus Metz implemented \gmodule{i.superpixels.slic}
+which provides users both with SLIC and SLIC0 methods.
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{References}}{
+
+\vspace{-0.2cm}
+\scriptsize
+
+% \newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}
+\newcommand{\blocksectiontitle}[1]{\textbf{#1}}
+
+%\blocksectiontitle{References}
+\begingroup
+\renewcommand{\section}[2]{}%
+\bibliographystyle{apalike}
+\bibliography{poster}
+\endgroup
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Example: Lidar Data Processing}}{
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Acknowledgements}}{
-
-\newcommand{\listhspace}{\hspace{0.005\linewidth}}
-\newcommand{\listlogowidth}{0.10\linewidth}
-\newcommand{\listtextwidth}{0.82\linewidth}
-
-\begin{minipage}{\listlogowidth}
-\centering
-\includegraphics[width=0.5\linewidth]{grass}
-\end{minipage}
-\listhspace
-\begin{minipage}{\listtextwidth}
-We acknowledge all members of the GRASS GIS community both users and developers.
-We would like to thank Markus Metz, Anna Petrasova, Stepan Turek, and Radim Blazek.
-\end{minipage}
-
-\bigskip
-
-\begin{minipage}{\listlogowidth}
-\includegraphics[width=\linewidth]{osgeo}
-\end{minipage}
-\listhspace
-\begin{minipage}{\listtextwidth}
-Open Source Geospatial Foundation (OSGeo)
-supports the collaborative development of open source geospatial software.
-GRASS GIS is a OSGeo project and
-OSGeo provides infrastructure for project
-websites, mailing lists and source code management.
-\end{minipage}
-
-\bigskip
-
-\begin{minipage}{\listlogowidth}
-\includegraphics[width=\linewidth]{google}
-\end{minipage}
-\listhspace
-\begin{minipage}{\listtextwidth}
-Initial development of \gmodule{i.segement} module as well as several other developments
-were done as a part of the Google Summer of Code project.
-Google provides financial support to students and organizations participating in the Google Summer of Code project.
-\end{minipage}
-
-\vspace{0.2cm}
-
-\textcolor{gray}{
-\hrulefill
-}
-
-\vspace{0.1cm}
-
-\newcommand{\qrcodesize}{0.05\linewidth}
-
-% qrencode http://grass.osgeo.org -o qr_grass.eps -t EPS
-% epspdf -b qr_grass.eps qr_grass.pdf
-
-\begin{center}
-\begin{tabular}{c}
-
-% \hspace{5mm}
-
-\begin{minipage}{\qrcodesize}
-\includegraphics[width=\textwidth]{./images/qr_grass.pdf}
-\end{minipage}
-~
-\begin{minipage}{0.15\linewidth}
-\small {\href{http://grass.osgeo.org}{\nolinkurl{grass.osgeo.org}}}
-\end{minipage}
-
-\begin{minipage}{0.1\linewidth}
-\href{http://creativecommons.org/licenses/by-sa/4.0/}{\includegraphics[width=\textwidth]{ccbysa}}
-\end{minipage}
-~
-\begin{minipage}{0.35\linewidth}
-\small This poster is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License.
-\end{minipage}
-
-\end{tabular}
-\end{center}
-
-\vspace{-0.08cm}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Water, Floods and Erosion}}{
-
-GRASS GIS entails several modules that constitute the result of active research on natural hazards.
-The \gmodule{r.sim.water} simulation model \citep{Mitas1998b}
-for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
-Routing Decision Planning system as a WPS \citep{raghavan2014deploying}.
-The module \gmodule{r.sim.water} together with
-the module \gmodule{r.sim.sediment} for erosion-deposition modeling
-implements a path sampling algorithm which is robust and easy to parallelize.
-A unique least cost path algorithm which doesn't need any depression filling
-was implemented in \gmodule{r.watershed} module in 1989
-and it was updated for massive data sets in 2011.
-% TODO: refs
-The \gmodule{r.sim.water} module was also utilized by \cite{Petrasova2014} and is now part of
-\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
-a dam break inundation simulation by \cite{cannata2012two}.
-
-\bigskip
-
-\vspace*{1cm}
-
-\centering
-
-\begin{minipage}{0.49\linewidth}
-\centering
-\includegraphics[width=0.7\textwidth]{rsimwater_architects}
-\end{minipage}
-~
-\begin{minipage}{0.49\linewidth}
-\includegraphics[width=\textwidth]{damflood_tangible}
-\end{minipage}
-
-\bigskip
-
-\begin{minipage}{0.49\linewidth}
-\centering
-Overland flow simulated by \gmodule{r.sim.water} used for landscape
-architecture design in Tangible Landscape environment
-(Historical master plan for Lake Raleigh, NC, USA)
-\end{minipage}
-~
-\begin{minipage}{0.49\linewidth}
-Dam breach on Lake Raleigh (NC, USA) in Tangible Landscape environment simulated using \gamodule{r.damflood} module
-\end{minipage}
-
-% \vspace*{1.4cm}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Image Segmentations}}{
-\gamodule{r.smooth.seg} (formerly \gmodulenolink{r.seg})
-was created by Alfonso Vitti \citep{vitti2008free, vitti2012mumford}
-and implemented a piece-wise smooth approximation of the original image
-according to \cite{mumford1989optimal} and \cite{march1997variational}
-which can be used to reduce noise in the original image.
-
-This supplemented \gmodule{r.clump} available from 1980s
-which groups pixels with the same categories (or integer values).
-The latest version of \gmodule{r.clump} coming in GRASS GIS 7.4
-supports multiple image bands (or any rasters maps) as input.
-Clumping of cells based on threshold value and clumping
-of double precision floating point input is supported as well in the new version.
-
-Eric Momsen implemented initial version of region-growing image segmentation in 2012
-and Markus Metz then extended and optimized the code resulting in
-the inclusion of the \gmodule{i.segment} module into GRASS GIS 7.0
-and final replacement of old multi-resolution classification module of the same name
-which was available in 1992 \citep{zhuang1992image}.
-Another module called \gamodule{i.segment.hierarchical} by Pietro Zambelli is based on \gmodule{i.segment}
-and performs parallelized hierarchical segmentation.
-
-\vspace*{0.7cm}
-
-\begin{minipage}{0.5\linewidth}
-\begin{center}
-\includegraphics[width=\textwidth]{superpixels_slic_pseudo}
-\end{center}
-\end{minipage}
-~
-\begin{minipage}{0.5\linewidth}
-\begin{center}
-\includegraphics[width=\textwidth]{superpixels_slic_colored}
-\end{center}
-\end{minipage}
-\vspace{2mm}
-\begin{center}
-Superpixels (black outlines) on pseudo-color image of central Wake county, NC, USA (left)
-and the same superpixels colored according to the mean NDVI value per pixel (right).
-\end{center}
-
-\vspace*{1cm}
-
-In 2016 GRASS GIS implementation of SLIC Superpixels segmentation \citep{achanta2010epfl, achanta2012slic}
-was requested by the community
-and Rashad Kanavath and Markus Metz implemented \gmodule{i.superpixels.slic}
-which provides users both with SLIC and SLIC0 methods.
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Topology, Cleaning, Overlays, Attributes}}{
-Besides basic vector analysis tools such as \gmodule{v.buffer}
-and \gmodule{v.overlay},
-suite of functionality for topology checking and cleaning is available
-through \gmodule{v.build} and \gmodule{v.clean} modules.
-The vector cleaning tools are particularly advantageous considering the use of non-topological exchange formats.
-The \gmodule{v.clean} module was introduced in 2002 and several different contributors
-extended its functionality with last large set of improvements included in GRASS GIS 7.0.
-For that release all topological cleaning tools have been optimized
-with regard to processing speed, robustness, and system requirements.
-The processing speed of the \gmodule{v.clean} module was substantially improved as well.
-
-\vspace*{1cm}
-
-\begin{center}
-\begin{minipage}{0.9\linewidth}
-\begin{center}
-\includegraphics[width=.3\textwidth]{topo_original}
-~
-\includegraphics[width=.3\textwidth]{topo_errors}
-~
-\includegraphics[width=.3\textwidth]{topo_fixed}
-Original vector imported without cleaning (left),
-identified errors (middle),
-automatically topologically corrected vector (right)
-\end{center}
-\end{minipage}
-\end{center}
-
-% v.in.ascii input= output=imported format=standard
-% v.build -e map=imported error=build_errors
-% v.clean -c input=imported output=clean error=cleaning_errors tool=snap,rmdangle,rmbridge,chbridge,bpol,prune threshold=5
-% d.vect map=build_errors color=255:33:36 fill_color=none width=5 icon=basic/point size=30
-% d.vect map=cleaning_errors color=255:33:36 fill_color=none width=5 icon=basic/point size=30
-% d.vect map=imported color=56:16:108 fill_color=205:64:113 width=5
-
-\vspace*{1cm}
-
-An experimental module \gamodule{v.feature.algebra} (formerly \gmodulenolink{v.mapcalc}) from 2002
-% actually, the original by Radim Blazek (Jun 11, 2002) seems to be more similar to the current v.mapcalc
-% it was using Vect_overlay_str_to_operator Vect_overlay
-% it was replaced by code by Christoph Simon in Aug 7, 2002
-was replaced by Python for GRASS GIS C libraries (PyGRASS) in GRASS GIS 7.0.
-However, new \gamodule{v.mapcalc} module is available with richer syntax and functionality.
-
-Attribute processing and queries in GRASS GIS can take an advantage of latest developments
-in database management systems (DBMSs) as several DBMSs are supported most notably SQLite and PostgreSQL.
-A PostGIS database can be connected including it geometry and topology.
-In parallel to that native support the OGC Simple Features is available.
-
-The GRASS GIS 7 releases come with faster vector processing backend
-and more efficient internal vector format;
-both disk and memory requirements were reduced.
-The new spatial index performs queries faster (more than 10 times for large vectors compared to GRASS GIS 6).
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Spatio-Temporal Data Analysis}}{
-The time dimension was introduced in GRASS GIS 7.0 for vector maps, rasters, and 3D rasters
-which transformed GRASS GIS into a fully-featured temporal GIS \citep{Gebbert20141, gebbert2015grass}.
-Time series of map layers are managed in space time datasets, a new data type in GRASS GIS,
-and are still accessible also as individual map layers.
-Based on the GRASS GIS Temporal Framework Python application programming interface (API),
-more than 50 modules were implemented to manage, analyze, process
-and visualize space time datasets.
-More than 100,000 map layers can be now handled efficiently in GRASS GIS.
-%
-Example usages of this functionality include
-analysis of the
-European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
-and temperate climate zone in the European Union identification \citep{Gebbert20141}.
-
-The new temporal modules (staring with \gmodulenolink{t.})
-work beside well established \gmodule{r.series} module
-and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing}
-or \gamodule{r.seasons}.
-Latest addition includes raster and vector temporal algebra
-which can be used for tasks such as computing hydrothermal coefficient for a time series of climate data
-using the actual mathematical formula \citep{leppelt2015grass}.
-
-\vspace*{1.5cm}
-
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=.7\linewidth]{images/temporal_precip_temp}
-\\
-Creating a synchronized animation of monthly total precipitation and mean temperature for NC, USA
-\end{minipage}
-
-\vspace*{1cm}
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Vector Network Analysis}}{
-In 2003 Radim Blazek introduced shortest path analysis (\gmodule{v.net.path}),
-traveling salesman (\gmodule{v.net.salesman}),
-and several other modules for vector network analysis (staring with \gmodule{v.net}).
-Over the years, the number of available algorithms increased to over 15 modules
-including, for example, centrality measures and connected components added in 2009 by Daniel Bundala.
-In 2014 Stepan Turek implemented turns support into all relevant vector network modules.
-Also since GRASS GIS 7.0 all vector network analysis tools provide fine control over node costs.
-% combination with r.cost/r.walk workflows \citep{Petrasova2014}
-
-\bigskip
-
-\centering
-\begin{minipage}{0.5\linewidth}
-\begin{center}
-\includegraphics[width=\textwidth]{network}
-Shortest path between two points in the Wake County road network (NC, USA)
-\end{center}
-\end{minipage}
-
-}
-
-\block{\blocktitlewrap{Landscape Structure}}{
-A set of modules for multiscale analysis of landscape structure was added in 1992
-by \cite{baker1992r}, who developed the \gmodulenolink{r.le} model similar to
-FRAGSTATS \citep{mcgarigal1995fragstats}.
-The modules were gradually improved to become \gmodule{r.li} in 2006.
-Further development continued, with a significant
-increase in speed \citep{tracrli} and a new interactive user interface.
-\cite{rocchini2013calculating} used \gmodule{r.li} modules to implement
-high level tool for calculating landscape diversity.
-
-\vspace*{0.5cm}
-
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{diversity_classes}
-\end{minipage}
-\begin{minipage}{0.5\linewidth}
-\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{diversity_shannon}
-\end{minipage}
-
-\vspace*{1ex}
-
-Landuse classes and derived landscape diversity according to Shannon index near Charlotte, NC, USA
-% r.diversity input=development_2006 prefix=diversity alpha=0.5 size=65
-% r.li.shannon input="development_2006" config="conf_diversity_65.0" output="diversity_shannon_size_65.0"
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{References}}{
-
-\vspace{-0.2cm}
-\scriptsize
-
-% \newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}
-\newcommand{\blocksectiontitle}[1]{\textbf{#1}}
-
-%\blocksectiontitle{References}
-\begingroup
-\renewcommand{\section}[2]{}%
-\bibliographystyle{apalike}
-\bibliography{poster}
-\endgroup
-
-}
-
 \end{columns}
 
+\node[above left,opacity=0.5,inner sep=0pt,outer sep=4cm] at (bottomleft -| topright)%
+  {\includegraphics[width=0.3\paperwidth]{grass}};
+
 \end{document}

### 2018-11-29 grassposter/2018_AGU_Geospatial_Research_Tool/poster.tex
poster: shorten, increase font size, set svn props
git-svn-id: https://svn.osgeo.org/grass/grass-promo@73725 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 % using Black Duck Open Hub to ``guestimate'' that
-**Over 10 other members of the core team and numerous other contributors
+**Includes over 10 other members of the core team and numerous other contributors
 \\[1.7cm]
@@
 
+\newcommand{\CustomBlockFontSize}{\LARGE}
+
 % bullet point style
@@
 % GRASS module
-\newcommand{\gmodule}[1]{\href{http://grass.osgeo.org/grass72/manuals/#1.html}{\emph{#1}}}
-\newcommand{\gamodule}[1]{\href{http://grass.osgeo.org/grass72/manuals/addons/#1.html}{\emph{#1}}}
+\newcommand{\gmodule}[1]{\href{http://grass.osgeo.org/grass74/manuals/#1.html}{\emph{#1}}}
+\newcommand{\gamodule}[1]{\href{http://grass.osgeo.org/grass74/manuals/addons/#1.html}{\emph{#1}}}
 \newcommand{\gmodulenolink}[1]{\emph{#1}}
@@
 \node[above left,opacity=0.99,inner sep=0pt,outer sep=4cm] at (bottomleft -| topright)%
-  {\includegraphics[width=0.3\paperwidth]{grass}};
+  {\includegraphics[width=0.2\paperwidth]{grass}};
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Overview}}{
+\block{\blocktitlewrap{Overview and Functionality}}{
 
-\Large
+\LARGE
 
@@
  \item single integrated environment for 2D and 3D raster analysis, image processing, vector data analysis, and spatio-temporal data processing
+% GRASS GIS
+% distribution strives to provide single integrated environment for 2D and 3D
+% raster analysis, image processing, vector data analysis, and spatio-temporal
+% data processing. It supports large raster files (billions of cells), vector
+% topology, coupling with databases, and 64 bit memory.
+%  \item To support the needs of scientists, the documentation includes not only links to the source code, its history, and
+% its authors, but also links to research papers that describe the algorithms
+% implemented in the modules.
 \end{itemize}
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Functionality}}{
-
-\Large
-
-GRASS GIS
-distribution strives to provide single integrated environment for 2D and 3D
-raster analysis, image processing, vector data analysis, and spatio-temporal
-data processing. It supports large raster files (billions of cells), vector
-topology, coupling with databases, and 64 bit memory.
 
@@
 
-\Large
+\CustomBlockFontSize
 
-New code based on recent
-research is typically contributed to GRASS GIS Addons repository. Mature, widely
-used code is then moved to the main code base to maximize integration and
-availability. Whether it is addons or the main code base, code is usually
-maintained by the community and preserved in long term even in cases when the
-original author no longer supports the code. To support the needs of scientists,
-the documentation includes not only links to the source code, its history, and
-its authors, but also links to research papers that describe the algorithms
-implemented in the modules.
+\begin{itemize}
+ \item New code based on recent research is typically contributed to GRASS GIS Addons repository.
+ \item Mature, widely used code is then moved to the main code base to maximize integration and availability.
+ \item Both main code base and Addons maintained by the community.
+ \item Code preserved in long term even in cases when the original author no longer supports the code.
+\end{itemize}
 
@@
 \block{\blocktitlewrap{Example: Spatio-Temporal Data Analysis}}{
-The time dimension was introduced in GRASS GIS 7.0 for vector maps, rasters, and 3D rasters
-which transformed GRASS GIS into a fully-featured temporal GIS \citep{Gebbert20141, gebbert2015grass}.
-Time series of map layers are managed in space time datasets, a new data type in GRASS GIS,
-and are still accessible also as individual map layers.
-Based on the GRASS GIS Temporal Framework Python application programming interface (API),
-more than 50 modules were implemented to manage, analyze, process
-and visualize space time datasets.
-More than 100,000 map layers can be now handled efficiently in GRASS GIS.
-%
-Example usages of this functionality include
-analysis of the
-European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
-and temperate climate zone in the European Union identification \citep{Gebbert20141}.
 
-The new temporal modules (staring with \gmodulenolink{t.})
-work beside well established \gmodule{r.series} module
-and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing}
-or \gamodule{r.seasons}.
-Latest addition includes raster and vector temporal algebra
-which can be used for tasks such as computing hydrothermal coefficient for a time series of climate data
-using the actual mathematical formula \citep{leppelt2015grass}.
+\CustomBlockFontSize
+
+\begin{itemize}
+ \item The time dimension was introduced in version 7.0 \citep{Gebbert20141, gebbert2015grass}
+ \item Time series accessed as space time datasets and as individual vectors or rasters.
+ \item More than 50 modules available to manage, analyze, process, and visualize space time datasets.
+ \item More than 100,000 map layers can be now handled efficiently in GRASS GIS.
+ \item Used for analysis of the European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
+       and temperate climate zone identification \citep{Gebbert20141}.
+ \item New temporal modules (e.g. \gmodule{t.rast.aggregate}) work beside well established \gmodule{r.series} module
+       and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing} or \gamodule{r.seasons}.
+ \item Raster and vector temporal algebra can be used for tasks
+       such as computing hydrothermal coefficient for a time series of climate data using the actual mathematical formula
+       \citep{leppelt2015grass}.
+\end{itemize}
 
@@
 
-GRASS GIS entails several modules that constitute the result of active research on natural hazards.
-The \gmodule{r.sim.water} simulation model \citep{Mitas1998b}
+\CustomBlockFontSize
+
+\begin{itemize}
+ \item The \gmodule{r.sim.water} simulation model \citep{Mitas1998b}
 for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
 Routing Decision Planning system as a WPS \citep{raghavan2014deploying}.
-The module \gmodule{r.sim.water} together with
-the module \gmodule{r.sim.sediment} for erosion-deposition modeling
-implements a path sampling algorithm which is robust and easy to parallelize.
-A unique least cost path algorithm which doesn't need any depression filling
+% TODO: paralelized
+\item A unique least cost path algorithm which doesn't need any depression filling
 was implemented in \gmodule{r.watershed} module in 1989
@@
 % TODO: refs
-The \gmodule{r.sim.water} module was also utilized by \cite{Petrasova2014} and is now part of
+\item The \gmodule{r.sim.water} module was also utilized by \cite{Petrasova2014} and is now part of
 \emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
 a dam break inundation simulation by \cite{cannata2012two}.
+\end{itemize}
 
@@
 
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.485\linewidth}
 \centering
@@
 ~
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.485\linewidth}
 \includegraphics[width=\textwidth]{damflood_tangible}
@@
 \block{\blocktitlewrap{Example: Vector Network Analysis}}{
-In 2003 Radim Blazek introduced shortest path analysis (\gmodule{v.net.path}),
-traveling salesman (\gmodule{v.net.salesman}),
-and several other modules for vector network analysis (staring with \gmodule{v.net}).
-Over the years, the number of available algorithms increased to over 15 modules
-including, for example, centrality measures and connected components added in 2009 by Daniel Bundala.
-In 2014 Stepan Turek implemented turns support into all relevant vector network modules.
-Also since GRASS GIS 7.0 all vector network analysis tools provide fine control over node costs.
+
+\CustomBlockFontSize
+
+\begin{itemize}
+ \item Radim Blazek introduced several modules for vector network analysis in 2003
+       including shortest path analysis (\gmodule{v.net.path}) and traveling salesman (\gmodule{v.net.salesman}).
+ \item The number of available modules increased to almost 20.
+ \item Stepan Turek implemented turns support into all relevant vector network modules in 2014.
+%  \item Since version 7.0 fine control over node costs available.
 % combination with r.cost/r.walk workflows \citep{Petrasova2014}
+\end{itemize}
 
@@
 \block{\blocktitlewrap{Example: Image Segmentations}}{
-\gamodule{r.smooth.seg} (formerly \gmodulenolink{r.seg})
-was created by Alfonso Vitti \citep{vitti2008free, vitti2012mumford}
-and implemented a piece-wise smooth approximation of the original image
-according to \cite{mumford1989optimal} and \cite{march1997variational}
-which can be used to reduce noise in the original image.
 
-This supplemented \gmodule{r.clump} available from 1980s
-which groups pixels with the same categories (or integer values).
-The latest version of \gmodule{r.clump} coming in GRASS GIS 7.4
-supports multiple image bands (or any rasters maps) as input.
-Clumping of cells based on threshold value and clumping
-of double precision floating point input is supported as well in the new version.
+\CustomBlockFontSize
 
-Eric Momsen implemented initial version of region-growing image segmentation in 2012
-and Markus Metz then extended and optimized the code resulting in
-the inclusion of the \gmodule{i.segment} module into GRASS GIS 7.0
-and final replacement of old multi-resolution classification module of the same name
-which was available in 1992 \citep{zhuang1992image}.
-Another module called \gamodule{i.segment.hierarchical} by Pietro Zambelli is based on \gmodule{i.segment}
-and performs parallelized hierarchical segmentation.
+\begin{itemize}
+ \item \gamodule{r.smooth.seg} was created by Alfonso Vitti \citep{vitti2008free, vitti2012mumford} and implemented a piece-wise smooth approximation of the original image which can be used to reduce noise in the original image.
+% according to \cite{mumford1989optimal} and \cite{march1997variational}
+ \item \gmodule{r.clump} for grouping pixels with the same integer values available since 1980s.
+       The latest version of \gmodule{r.clump} supports multiple image bands and clumping of floating point values.
+ \item Eric Momsen implemented region-growing image segmentation in 2012.
+       Markus Metz then extended and optimized the code resulting in the inclusion of the \gmodule{i.segment} module into version 7.0.
+       This replaced a multi-resolution classification module of the same name from 1992 \citep{zhuang1992image}.
+ \item \gamodule{i.segment.hierarchical} by Pietro Zambelli is based on \gmodule{i.segment} and performs parallelized hierarchical segmentation.
+ \item Rashad Kanavath and Markus Metz implemented SLIC Superpixels segmentation \citep{achanta2010epfl, achanta2012slic} in 2016 as \gmodule{i.superpixels.slic}.
+\end{itemize}
 
@@
 \begin{center}
-Superpixels (black outlines) on pseudo-color image of central Wake county, NC, USA (left)
-and the same superpixels colored according to the mean NDVI value per pixel (right).
+Superpixels (black outlines) with pseudo-color and NDVI images, central Wake county, NC, USA
 \end{center}
 
-\vspace*{1cm}
-
-In 2016 GRASS GIS implementation of SLIC Superpixels segmentation \citep{achanta2010epfl, achanta2012slic}
-was requested by the community
-and Rashad Kanavath and Markus Metz implemented \gmodule{i.superpixels.slic}
-which provides users both with SLIC and SLIC0 methods.
+\vspace*{0cm}
 
@@
 \vspace{-0.2cm}
+
 \scriptsize
@@
 
-Filtering of ground and non-ground points was included into GRASS GIS
+\CustomBlockFontSize
+
+\begin{itemize}
+ \item Filtering of ground and non-ground points was included
 early on in the lidar era in the \gmodule{v.lidar.edgedetection} group of modules.
@@
 % v.lidar.growing Building contour determination and Region Growing algorithm for determining the building inside
-The module \gmodule{v.surf.rst} for spatial interpolation was developed approximately 20 years
+ \item The module \gmodule{v.surf.rst} for spatial interpolation was developed approximately 20 years
 ago, but since then it has been improved several times \citep{tracvsurfrst}
 including recent parallelization which will be included in GRASS GIS 7.4.
-Currently the module is used for both digital terrain model interpolation and interpolations in general.
-
-The module \gmodule{r.in.lidar} statistically analyzes massive point clouds.
+% TODO: ref for paralelized
+ \item The module \gmodule{r.in.lidar} statistically analyzes massive point clouds.
 % TODO: base_raster, ref
-For advanced general point analysis GRASS GIS
-\gmodule{v.outlier} implemented originally specifically for lidar data
-and recently also \gmodule{v.cluster}
-implementing variety of clustering methods including
-DBSCAN (Density-Based Spatial Clustering of Applications with Noise)
-and OPTICS (Ordering Points to Identify the Clustering Structure).
-The \gmodule{v.outlier} module serves as a base for a user contributed module \gamodule{v.lidar.mcc}
-implementing Multiscale Curvature Classification (MCC).
+ \item The \gmodule{v.outlier} module serves as a base for a module \gamodule{v.lidar.mcc} implementing Multiscale Curvature Classification.
 % TODO: ref
+\end{itemize}
 
@@
 \centering
-Digital elevation model interpolated from lidar point clouds
-using \gmodule{v.surf.rst}. Data are showing tillage in an agricultural field near Raleigh (North Carolina, USA)
+Digital elevation model interpolated from lidar data shows tillage in an field in Raleigh, NC, USA
 \end{minipage}
@@
 \centering
-Profile (vertical slice) of a small portion of a point cloud showing tree structure as captured by the returns
-(\gamodule{v.profile.points})
+Vertical slice of a point cloud created with \gamodule{v.profile.points} shows tree structure in lidar data
 \end{minipage}
@@
 
-\node[above left,opacity=0.5,inner sep=0pt,outer sep=4cm] at (bottomleft -| topright)%
-  {\includegraphics[width=0.3\paperwidth]{grass}};
-
 \end{document}

### 2018-11-30 grassposter/2018_AGU_Geospatial_Research_Tool/poster.tex
poster: take home message, further shorten, swap boxes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@73726 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 % \renewcommand{\familydefault}{\sfdefault}
+
+\usepackage{setspace}
 
@@
 
-\node[above left,opacity=0.99,inner sep=0pt,outer sep=4cm] at (bottomleft -| topright)%
+\node[above left,opacity=0.99,inner sep=0pt,outer sep=6cm] at (bottomleft -| topright)%
   {\includegraphics[width=0.2\paperwidth]{grass}};
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Overview and Functionality}}{
+\block{\blocktitlewrap{Why GRASS GIS as a Tool?}}{
 
-\LARGE
+\CustomBlockFontSize
+
+Multiple researchers for over three decades
+contributed code,
+published associated papers,
+implemented other's papers
+and improved and built on each others work.
+
+\includegraphics[width=\linewidth]{grass_team}
 
@@
  \item Community-driven project
- \item 35 years of continuous software development
- \item long-term releases, stable APIs, and emphasis on science
- \item single integrated environment for 2D and 3D raster analysis, image processing, vector data analysis, and spatio-temporal data processing
+ \item Long-term releases, stable APIs and emphasis on science
+ \item Single integrated environment for 2D and 3D raster analysis, image processing, vector data analysis and spatio-temporal data processing
 % GRASS GIS
 % distribution strives to provide single integrated environment for 2D and 3D
-% raster analysis, image processing, vector data analysis, and spatio-temporal
+% raster analysis, image processing, vector data analysis and spatio-temporal
 % data processing. It supports large raster files (billions of cells), vector
-% topology, coupling with databases, and 64 bit memory.
-%  \item To support the needs of scientists, the documentation includes not only links to the source code, its history, and
+% topology, coupling with databases and 64 bit memory.
+%  \item To support the needs of scientists, the documentation includes not only links to the source code, its history and
 % its authors, but also links to research papers that describe the algorithms
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Code Life Cycle}}{
+\block{\blocktitlewrap{Why GRASS GIS as a Platform?}}{
 
@@
 
+Contributed code is maintained and extended by community
+and prevails even in cases when the original author cannot support its users.
+
 \begin{itemize}
- \item New code based on recent research is typically contributed to GRASS GIS Addons repository.
- \item Mature, widely used code is then moved to the main code base to maximize integration and availability.
+ \item New code typically contributed to Addons repository.
+ \item Mature code is moved to the main code base.
  \item Both main code base and Addons maintained by the community.
- \item Code preserved in long term even in cases when the original author no longer supports the code.
 \end{itemize}
 
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Example: Spatio-Temporal Data Analysis}}{
-
-\CustomBlockFontSize
-
-\begin{itemize}
- \item The time dimension was introduced in version 7.0 \citep{Gebbert20141, gebbert2015grass}
- \item Time series accessed as space time datasets and as individual vectors or rasters.
- \item More than 50 modules available to manage, analyze, process, and visualize space time datasets.
- \item More than 100,000 map layers can be now handled efficiently in GRASS GIS.
- \item Used for analysis of the European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
-       and temperate climate zone identification \citep{Gebbert20141}.
- \item New temporal modules (e.g. \gmodule{t.rast.aggregate}) work beside well established \gmodule{r.series} module
-       and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing} or \gamodule{r.seasons}.
- \item Raster and vector temporal algebra can be used for tasks
-       such as computing hydrothermal coefficient for a time series of climate data using the actual mathematical formula
-       \citep{leppelt2015grass}.
-\end{itemize}
-
-\vspace*{1.5cm}
-
-\begin{minipage}{\linewidth}
-\centering
-\includegraphics[width=.7\linewidth]{images/temporal_precip_temp}
-\\
-Creating a synchronized animation of monthly total precipitation and mean temperature for NC, USA
-\end{minipage}
-
-\vspace*{1cm}
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\column{0.25}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Example: Water, Floods and Erosion}}{
-
-\CustomBlockFontSize
-
-\begin{itemize}
- \item The \gmodule{r.sim.water} simulation model \citep{Mitas1998b}
-for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
-Routing Decision Planning system as a WPS \citep{raghavan2014deploying}.
-% TODO: paralelized
-\item A unique least cost path algorithm which doesn't need any depression filling
-was implemented in \gmodule{r.watershed} module in 1989
-and it was updated for massive data sets in 2011.
-% TODO: refs
-\item The \gmodule{r.sim.water} module was also utilized by \cite{Petrasova2014} and is now part of
-\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
-a dam break inundation simulation by \cite{cannata2012two}.
-\end{itemize}
-
-\bigskip
-
-\vspace*{1cm}
-
-\centering
-
-\begin{minipage}{0.485\linewidth}
-\centering
-\includegraphics[width=0.7\textwidth]{rsimwater_architects}
-\end{minipage}
-~
-\begin{minipage}{0.485\linewidth}
-\includegraphics[width=\textwidth]{damflood_tangible}
-\end{minipage}
-
-\bigskip
-
-\begin{minipage}{0.485\linewidth}
-\centering
-Overland flow simulated by \gmodule{r.sim.water} used for landscape
-architecture design in Tangible Landscape environment
-(Historical master plan for Lake Raleigh, NC, USA)
-\end{minipage}
-~
-\begin{minipage}{0.49\linewidth}
-Dam breach on Lake Raleigh (NC, USA) in Tangible Landscape environment simulated using \gamodule{r.damflood} module
-\end{minipage}
-
-% \vspace*{1.4cm}
 }
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Example: Spatio-Temporal Data Analysis}}{
+
+\CustomBlockFontSize
+
+\begin{itemize}
+ \item The time dimension was introduced in version 7.0 \citep{Gebbert20141, gebbert2015grass}
+ \item Time series accessed as space time datasets and as individual vectors or rasters.
+ \item More than 50 modules available to manage, analyze, process and visualize space time datasets.
+ \item More than 100,000 map layers can be now handled efficiently in GRASS GIS.
+ \item Used for analysis of the European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
+       and temperate climate zone identification \citep{Gebbert20141}.
+ \item New temporal modules (e.g. \gmodule{t.rast.aggregate}) work beside well established \gmodule{r.series} module
+       and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing} or \gamodule{r.seasons}.
+ \item Raster and vector temporal algebra can be used for tasks
+       such as computing hydrothermal coefficient for a time series of climate data using the actual mathematical formula
+       \citep{leppelt2015grass}.
+\end{itemize}
+
+\vspace*{1.5cm}
+
+\begin{minipage}{\linewidth}
+\centering
+\includegraphics[width=.7\linewidth]{images/temporal_precip_temp}
+\\
+Creating a synchronized animation of monthly total precipitation and mean temperature for NC, USA
+\end{minipage}
+
+\vspace*{1cm}
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{References}}{
+
+\vspace{-0.2cm}
+
+\scriptsize
+\setstretch{0.5}
+
+% \newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}
+\newcommand{\blocksectiontitle}[1]{\textbf{#1}}
+
+%\blocksectiontitle{References}
+\begingroup
+\renewcommand{\section}[2]{}%
+\bibliographystyle{apalike}
+\bibliography{poster}
+\endgroup
+
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\column{0.25}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{itemize}
- \item \gamodule{r.smooth.seg} was created by Alfonso Vitti \citep{vitti2008free, vitti2012mumford} and implemented a piece-wise smooth approximation of the original image which can be used to reduce noise in the original image.
 % according to \cite{mumford1989optimal} and \cite{march1997variational}
- \item \gmodule{r.clump} for grouping pixels with the same integer values available since 1980s.
-       The latest version of \gmodule{r.clump} supports multiple image bands and clumping of floating point values.
- \item Eric Momsen implemented region-growing image segmentation in 2012.
-       Markus Metz then extended and optimized the code resulting in the inclusion of the \gmodule{i.segment} module into version 7.0.
-       This replaced a multi-resolution classification module of the same name from 1992 \citep{zhuang1992image}.
- \item \gamodule{i.segment.hierarchical} by Pietro Zambelli is based on \gmodule{i.segment} and performs parallelized hierarchical segmentation.
+ \item \gmodule{r.clump} for grouping pixels with the same integer values available since '80s.
+       Now \gmodule{r.clump} handles multiple image bands and floating point values.
+ \item \gamodule{r.smooth.seg} for noise reduction \citep{vitti2008free, vitti2012mumford}
+ \item Region-growing image segmentation originally from Eric Momsen (2012)
+       was improved by Markus Metz and included as \gmodule{i.segment} into version 7.0.
+%        This replaced a multi-resolution classification module of the same name from 1992 \citep{zhuang1992image}.
+ \item \gamodule{i.segment.hierarchical} by Pietro Zambelli based on \gmodule{i.segment} performs parallelized hierarchical segmentation.
  \item Rashad Kanavath and Markus Metz implemented SLIC Superpixels segmentation \citep{achanta2010epfl, achanta2012slic} in 2016 as \gmodule{i.superpixels.slic}.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{References}}{
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\block{\blocktitlewrap{Example: Water, Floods and Erosion}}{
 
-\vspace{-0.2cm}
+\CustomBlockFontSize
 
-\scriptsize
+\begin{itemize}
+ \item \gmodule{r.sim.water} module \citep{Mitas1998b}
+       for simulating overland flow integrated into the Emergency Routing Decision Planning \citep{raghavan2014deploying}.
+% TODO: paralelized
+ \item \gmodule{r.watershed} for least cost path water accumulation from 1989
+       and updated for massive data sets in 2011.
+% TODO: refs
+ \item \cite{Petrasova2014} utilized in \emph{Tangible Landscape}, a tangible GIS system,
+       \gmodule{r.damflood}, a dam break inundation simulation by \cite{cannata2012two}.
+\end{itemize}
 
-% \newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}
-\newcommand{\blocksectiontitle}[1]{\textbf{#1}}
+% \bigskip
 
-%\blocksectiontitle{References}
-\begingroup
-\renewcommand{\section}[2]{}%
-\bibliographystyle{apalike}
-\bibliography{poster}
-\endgroup
+% \vspace*{0.5cm}
 
+\centering
+
+\begin{minipage}{0.485\linewidth}
+\centering
+\includegraphics[width=0.7\textwidth]{rsimwater_architects}
+\end{minipage}
+~
+\begin{minipage}{0.485\linewidth}
+\includegraphics[width=\textwidth]{damflood_tangible}
+\end{minipage}
+\vspace{2mm}
+\begin{center}
+Overland flow simulated used for landscape
+architecture design in Tangible Landscape environment (left)
+and a dam breach on Lake Raleigh, NC, USA (right)
+\end{center}
+
+% \vspace*{1.4cm}
 }
@@
 \begin{itemize}
- \item Filtering of ground and non-ground points was included
-early on in the lidar era in the \gmodule{v.lidar.edgedetection} group of modules.
+ \item Filtering of ground points was included
+       in the \gmodule{v.lidar.edgedetection} group of modules.
 % TODO: ref
+% TODO: year
 % v.lidar.correction Corrects the v.lidar.growing output. It is the last of the three algorithms for LIDAR .
@@
 % v.lidar.growing Building contour determination and Region Growing algorithm for determining the building inside
- \item The module \gmodule{v.surf.rst} for spatial interpolation was developed approximately 20 years
-ago, but since then it has been improved several times \citep{tracvsurfrst}
-including recent parallelization which will be included in GRASS GIS 7.4.
+ \item \gmodule{v.outlier} module serves as a base for a module \gamodule{v.lidar.mcc} implementing Multiscale Curvature Classification.
+% TODO: ref
+ \item \gmodule{v.surf.rst} (spatial interpolation) for developed in '90s;
+       improved several times and parallelized for version 7.4.
+% \citep{tracvsurfrst}
+% TODO: different ref
 % TODO: ref for paralelized
- \item The module \gmodule{r.in.lidar} statistically analyzes massive point clouds.
+ \item Improved \gmodule{r.in.lidar} statistically analyzes large point clouds.
 % TODO: base_raster, ref
- \item The \gmodule{v.outlier} module serves as a base for a module \gamodule{v.lidar.mcc} implementing Multiscale Curvature Classification.
-% TODO: ref
+
 \end{itemize}
 
-% v.delaunay v.voronoi New option to create Voronoi diagrams for areas.
-
 \centering
-\begin{minipage}{0.48\linewidth}
+\begin{minipage}{0.4\linewidth}
 \centering
@@
 ~
-\begin{minipage}{0.48\linewidth}
+\begin{minipage}{0.55\linewidth}
 \centering
@@
 \end{minipage}
-
-\bigskip
-
-\begin{minipage}{0.48\linewidth}
-\centering
+\vspace{2mm}
+\begin{center}
 Digital elevation model interpolated from lidar data shows tillage in an field in Raleigh, NC, USA
-\end{minipage}
-~
-\begin{minipage}{0.48\linewidth}
-\centering
-Vertical slice of a point cloud created with \gamodule{v.profile.points} shows tree structure in lidar data
-\end{minipage}
+and a point cloud transect created with \gamodule{v.profile.points} shows tree structure
+\end{center}
 

### 2018-11-30 grassposter/2018_AGU_Geospatial_Research_Tool/poster.tex
poster: short points to fit the paper
git-svn-id: https://svn.osgeo.org/grass/grass-promo@73727 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
  \item Long-term releases, stable APIs and emphasis on science
- \item Single integrated environment for 2D and 3D raster analysis, image processing, vector data analysis and spatio-temporal data processing
+ \item Single environment for vector data analysis, 2D and 3D raster analysis, image processing and spatio-temporal data
 % GRASS GIS
@@
  \item Mature code is moved to the main code base.
- \item Both main code base and Addons maintained by the community.
+ \item Organization into modules makes contributions easy.
+ %  \item Both main code base and Addons maintained by the community.
 \end{itemize}
@@
 \begin{itemize}
- \item Radim Blazek introduced several modules for vector network analysis in 2003
-       including shortest path analysis (\gmodule{v.net.path}) and traveling salesman (\gmodule{v.net.salesman}).
- \item The number of available modules increased to almost 20.
- \item Stepan Turek implemented turns support into all relevant vector network modules in 2014.
+ \item Several modules for vector network analysis by Radim Blazek available since 2003 (e.g. \gmodule{v.net.salesman}).
+ \item The number of modules increased to almost 20.
+ \item Turn support added by Stepan Turek in 2014.
 %  \item Since version 7.0 fine control over node costs available.
@@
 \includegraphics[width=\textwidth]{network_trips}
-A series of trips to collect samples across North Carolina, USA
-for water quality measurements
-as part of the Polyfluorinated Alkyl Substance Testing (PFAST) project.
-Trips are distinguished by color and were computed using multiple
-iterations of traveling salesman (\gmodule{v.net.salesman}).
+Trips to collect samples across North Carolina, USA
+as part of a water pollution testing project (PFAST).
+% Polyfluorinated Alkyl Substance Testing
+% Trips are distinguished by color and were computed using multiple
+% iterations of traveling salesman (\gmodule{v.net.salesman}).
 \end{center}
@@
 
-\vspace*{1.5cm}
+\vspace*{.5ex}
 
@@
 \centering
-\includegraphics[width=.7\linewidth]{images/temporal_precip_temp}
+\includegraphics[width=\linewidth]{images/temporal_precip_temp}
 \\
@@
 
-\vspace*{1cm}
+% \vspace*{1cm}
 
@@
 \begin{itemize}
- \item \gmodule{r.sim.water} module \citep{Mitas1998b}
-       for simulating overland flow integrated into the Emergency Routing Decision Planning \citep{raghavan2014deploying}.
+ \item \gmodule{r.sim.water} \citep{Mitas1998b}
+       overland flow simulation used for emergency routing \citep{raghavan2014deploying}.
 % TODO: paralelized
- \item \gmodule{r.watershed} for least cost path water accumulation from 1989
-       and updated for massive data sets in 2011.
+ \item Least cost flow \gmodule{r.watershed} from '89
+       updated for massive data in '11.
 % TODO: refs
- \item \cite{Petrasova2014} utilized in \emph{Tangible Landscape}, a tangible GIS system,
-       \gmodule{r.damflood}, a dam break inundation simulation by \cite{cannata2012two}.
+ \item \cite{Petrasova2014} used in \emph{Tangible Landscape}
+       dam break inundation \gmodule{r.damflood} \cite{cannata2012two}.
 \end{itemize}
@@
 
-\begin{minipage}{0.485\linewidth}
+\begin{minipage}{0.47\linewidth}
 \centering
@@
 ~
-\begin{minipage}{0.485\linewidth}
+\begin{minipage}{0.5\linewidth}
 \includegraphics[width=\textwidth]{damflood_tangible}
 \end{minipage}
-\vspace{2mm}
+\vspace{0.1ex}
 \begin{center}
-Overland flow simulated used for landscape
-architecture design in Tangible Landscape environment (left)
+Flow used for landscape
+architecture design (left)
 and a dam breach on Lake Raleigh, NC, USA (right)

### 2018-11-30 grassposter/2018_AGU_Geospatial_Research_Tool/poster.tex
poster: sans font, put back oxford comma, typos
git-svn-id: https://svn.osgeo.org/grass/grass-promo@73728 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@
 % uncomment for all sans serif
-% \renewcommand{\familydefault}{\sfdefault}
+\renewcommand{\familydefault}{\sfdefault}
 
@@
 \&
-Markus Neteler\inst{2}
+Markus Neteler\hspace{0.05em}\inst{2}
 \\
@@
 % using Black Duck Open Hub to ``guestimate'' that
-**Includes over 10 other members of the core team and numerous other contributors
+**Includes over 10 other members of the core team and numerous other contributors.
 \\[1.7cm]
@@
 
-\newcommand{\CustomBlockFontSize}{\LARGE}
+\newcommand{\CustomBlockFontSize}{\Large}
 
@@
 contributed code,
-published associated papers,
-implemented other's papers
+wrote associated papers,
+implemented already published methods,
 and improved and built on each others work.
@@
  \item Community-driven project
- \item Long-term releases, stable APIs and emphasis on science
- \item Single environment for vector data analysis, 2D and 3D raster analysis, image processing and spatio-temporal data
+ \item Long-term releases, stable APIs, and emphasis on science
+ \item Single environment for vector data analysis, 2D and 3D raster analysis, image processing, and spatio-temporal data
 % GRASS GIS
@@
 Contributed code is maintained and extended by community
-and prevails even in cases when the original author cannot support its users.
+and prevails even in cases when the original author cannot maintain the code anymore.
 
@@
  \item Mature code is moved to the main code base.
- \item Organization into modules makes contributions easy.
+ \item Structuring code into modules makes contributing easy.
  %  \item Both main code base and Addons maintained by the community.
@@
 \includegraphics[width=\textwidth]{network_trips}
-Trips to collect samples across North Carolina, USA
+Trips to collect samples across North Carolina, USA,
 as part of a water pollution testing project (PFAST).
@@
 \begin{itemize}
- \item The time dimension was introduced in version 7.0 \citep{Gebbert20141, gebbert2015grass}
+ \item The time dimension was introduced in version 7.0 \citep{Gebbert20141, gebbert2015grass}.
  \item Time series accessed as space time datasets and as individual vectors or rasters.
- \item More than 50 modules available to manage, analyze, process and visualize space time datasets.
+ \item More than 50 modules available to manage, analyze, process, and visualize space time datasets.
  \item More than 100,000 map layers can be now handled efficiently in GRASS GIS.
@@
        and temperate climate zone identification \citep{Gebbert20141}.
- \item New temporal modules (e.g. \gmodule{t.rast.aggregate}) work beside well established \gmodule{r.series} module
+ \item New temporal modules (e.g. \gmodule{t.rast.aggregate}) work alongside well established \gmodule{r.series} module
        and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing} or \gamodule{r.seasons}.
  \item Raster and vector temporal algebra can be used for tasks
-       such as computing hydrothermal coefficient for a time series of climate data using the actual mathematical formula
+       such as computing hydrothermal coefficient for a time series of climate data using a mathematical formula
        \citep{leppelt2015grass}.
@@
 
-\scriptsize
-\setstretch{0.5}
-
 % \newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}
@@
 \bibliographystyle{apalike}
+\setstretch{0.5}
+\scriptsize
 \bibliography{poster}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\block{\blocktitlewrap{Example: Water, Floods and Erosion}}{
+\block{\blocktitlewrap{Example: Water, Floods, and Erosion}}{
 
@@
 \begin{itemize}
- \item Filtering of ground points was included
+ \item Filtering of ground and non-ground points was included
        in the \gmodule{v.lidar.edgedetection} group of modules.
@@
 % v.lidar.growing Building contour determination and Region Growing algorithm for determining the building inside
- \item \gmodule{v.outlier} module serves as a base for a module \gamodule{v.lidar.mcc} implementing Multiscale Curvature Classification.
+ \item \gmodule{v.outlier} module serves as a base for \gamodule{v.lidar.mcc} implementing Multiscale Curvature Classification.
 % TODO: ref
- \item \gmodule{v.surf.rst} (spatial interpolation) for developed in '90s;
+ \item \gmodule{v.surf.rst} for spatial interpolation developed in '90s;
        improved several times and parallelized for version 7.4.
@@
 \begin{center}
-Digital elevation model interpolated from lidar data shows tillage in an field in Raleigh, NC, USA
-and a point cloud transect created with \gamodule{v.profile.points} shows tree structure
+DEM interpolated from lidar data shows tillage of a field in Raleigh, NC, USA (left)
+and a point cloud transect created with \gamodule{v.profile.points} shows tree structure (right)
 \end{center}
